### 2019-07-23 article4_tommylars.rnw
initial commit

%https://www.gnu.org/software/emacs/manual/html_node/emacs/Fill-Commands.html
%https://academic.oup.com/journals/pages/authors/latex_files
%latexmk -pdf -pvc -auxdir=/Users/larshovdanmolden/Documents/Output/  article2_mancap.tex

\documentclass[review,fleqn]{elsarticle}
\usepackage[textsize=tiny,colorinlistoftodos]{todonotes}
\usepackage{subfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{filecontents}
\input{preamble.tex}
%%\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\setlength{\mathindent}{0pt} %% NB MAYBEREMOVE BEFORE SUBMISSION

%%%% TURN OFF PAGE NUMBER FOR INCLUSION IN THESIS
%\pagenumbering{gobble}
%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Evolution of (dynamic) capabilities and its performance implications: An empirical test and extension}
%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

%% Group authors per affiliation:
%\author{Lars Hovdan Molden \fnref{myfootnote}}
%\address{Kongensgt 42, 7713 Steinkjer}
%\fntext[myfootnote]{Nord University Business School}

%% or include affiliations in footnotes:
%\author[mymainaddress,mysecondaryaddress]{Elsevier Inc}
%\ead[url]{www.elsevier.com}

%\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
%\cortext[mycorrespondingauthor]{Corresponding author}
%\ead{support@elsevier.com}

%\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
%\address[mysecondaryaddress]{360 Park Avenue South, New York}

\begin{abstract}
  Despite considerable interest from the research community the theory of dynamic
  capabilities is still very much evolving. Several recent literature reviews demonstrate
  the need for better understanding of the antecedents and outcome of dynamic
  capabilities. Building on a much cited theoretical framework developed by
  \cite{zollo2002} and longitudinal dataset of Norwegian technology firms, we explore
  the role of learning as an antecedent to dynamic capabilities, and relates this to the
  outcome of dynamic capabilities themselves.

\end{abstract}

\begin{keyword}
\texttt{Dynamic Capabilities, Deliberate Learning, Dynamics }
\end{keyword}

\end{frontmatter}

%\linenumbers

\doublespacing

\section{Introduction}
There is ongoing interest in (dynamic) capabilities and how they influence firm
performance \citep{Fainshmidt2016a,Teece2014}. Indeed, \emph{dynamic capabilities} (DC),
and its front runner, the resource-based view \citep{Barney2001,Helfat2007}, is now
considered one of the major theories in strategic management
\citep{Schilke2018}. Arguably, the key reason is that this theory clearly articulates how
firms can alter their operating routines through dynamic capabilities. Thus, a key
ingredient in this theory is that DCs can alter firms operating routines, with subsequent
performance implications.

An issue that has received far less attention, however, is whether dynamics capabilities
themselves undergo an evolution \citep{Schilke2018}. Moreover, if DCs undergo an
evolution, is the evolution inert and past-dependent, or more deliberate and represent
purposeful change in firms DCs over time? Unpacking this is crucial to the development of
DC theory as it goes into the very nature of the issue as to whether and to what extent
DCs can purposefully alter firms operating routines, and the performance implications
stemming from such change \citep{Helfat2007}. It is therefore surprising that the
literature has dealt with it sparingly. What is the exception to this is \cite{Zollo2002a}
highly influential model over DC evolution where they postulate that (dynamic)
capabilities evolve with regard to firms’ \emph{deliberate learning} (DL). However, Zollo
\& Winter`s insightful theorizing has received scant empirical testing. Moreover, their
model can be developed further, by incorporating insights from subsequent research and
theorizing since this model was published. One salient issue in this regard is that Zollo
\& Winter did not consider how DCs can influence firms’ DL. Moreover, their model does not
consider how firm performance may be influenced by the evolution of (dynamic)\todo{should
  we really go with the parantheses around dynamic throuhgt the whole paper - it feels
  like we are not certain about the concept} capabilities (through DL). Such feedback
loops may significantly alter how we understand the relationship between deliberate
learning and evolution of (dynamic) capabilities in extant DC theory, including the
performance implications of such evolution. Reflecting this gap in our understanding, we
ask the following research question:

\emph{What is the role of deliberate learning in the evolution of (dynamic) capabilities and the
performance implications for such evolution?}

To answer this research question, we not only empirically test ZW’s a highly influential
model of the evolution of (dynamic) capabilities, but also extend it by incorporating (a)
feedback loops between DCs and deliberate learning and (b) incorporating firm performance
into the model.

\section{Theory}\label{sec:theory}
Firm capabilities can roughly be divided into two categories. First, ordinary capabilities
(OR) “are directed toward maintaining and leveraging the status quo in terms of the scale
and scope of activities, businesses, product lines, customer segments”
\citep[p. 393]{Schilke2018}. In other words these capabilities are the ones who “permit a
firm to ‘make a living’ in the short term” \citep[p. 991]{Winter2003}. On the other hand,
dynamic capabilities (DC) are “those that operate to extend, modify or create ordinary
capabilities” (ibid). DC theory is emerging as an important paradigm in strategic
management research, but also facing some considerable challenges with respect to its
antecedents and outcomes \citep{Eriksson2014,Schilke2018}, as well as its evolution
and development trajectory \citep{Romme2010,Zollo2002a}. Extant
literature has dealt with antecedents in many forms such as ### (ref) etc. Similarly,
outcomes have been the focal point of several contributions focusing on ### (ref)
etc. However, despite DC building on an evolutionary view of resource development, less
attention has been dealt to the evolution of DC over time than one could expect. Partly
this could be due to lacking data (ref), unclear conceptual definitions (ref) or sheer
complexity of studying evolution (ref). One remarkable exception is Zollo \& Winter (2002)
who propose a clear evolutionary argument and hypothesis on DC evolution. Still, little
empirical work has attempted to test their propositions.

\textcolor{red}{DL definition – makes sure all definitions are in order}

By combining insights from 20 years of DC research on external factors such as antecedents
and outcomes with the internal process shaping DC over time, we can shed light on the
workings of DC and extend the knowledge of its implications. Using Zollo \& Winter as our
point of departure we will be able to study the internal process of DC evolution, and by
adding new dimensions related to antecedents and outcomes we will gain insight into
important implications of the concept.

\subsection{Deliberate learning as antecedent and evolution driver}
When Zollo \& Winter (2002) put deliberate learning at the center of their model for DC
evolution they tap into a core tenant of DC theory more developed in later
contributions. Learning theory in organizations distinguishes between autonomous learning
processes \citep{Arthur2005} (e.g. learning by doing \citep{Zollo2002a,Arrow1962} based on
repetitive actions by employees in firms and organizations, and deliberate learning where
learning takes the form of a planned and deliberate process \citep{Arthur2005}. This
deliberation and intent as a driver behind the learning process, corresponds well with the
idea of purposefulness behind strategic intent as evident in the definition of dynamic
capabilities \citep{Helfat2007}: “the ability to {\bf purposefully} build, extend and
modify ordinary capabilities” (our emphasis added). (ref). When organizations invest in
systems to facilitate learning, they invest in capabilities for changing routines in line
with strategic direction of the organization itself. Hence, investments in deliberate
learning corresponds with investments in dynamic capabilities and both concepts contribute
to the development of operational routines.

\emph{H1: Deliberate learning has a direct positive effect on organizations development of
  operating routines.}

They depart conceptually, however, when we look at the functioning of each. The main
function of DL is to accumulate knowledge and experience about the operation of the
organization and its environment (ref). Through this process DL generates insights into
what should be changed and not in order to achieve improved organizational
performance. Contrary, DC deals with how change in operational routines should be done
through putting experience from DL to work (ref). Thus, for DC to be well functioning in
its quest to change OR, a DL process needs to be in place. Without a proper DL the
learning will be less purposeful and hence less attune to the strategic intent of the
firm. Change may still appear, but as organizational change rather than strategic (helfat
distinction between strategix and organizational change). In other words, without DL firms
can achieve technical fitness (ref), but only through DL shaping DC can firms achieve
evolutionary fitness (ref). Consequently, DL is an important antecedent to DC.

\emph{H2: Deliberate learning leads to stronger dynamic capabilities and has a positive
  influence on the level of dynamic capabilities within the firm.}

\emph{H3: Deliberate learning has an indirect effect on operational routines through
  dynamic capabilities.}

Besides impacting the level of DC as an antecedent, DL also contributes to the evolution
of DC over time. Conventional insights suggest that DC cannot be aquired in factor markets
and thus has to be developed internally \citep{Coen2011,Schilke2014a}\todo{(Helfat,
  Finkelstein, Mitchell, Peteraf, Singh,\& Teece, 2007; Katkalo, Pitelis, \& Teece, 2010;
  Maritan \& Peteraf, 2011; Teece, 2014). in Schilke 2014} . This has performance
implications related to the VRIO principle \citep{Barney1991} (as discussed later in this
article), as well as consequences for the evolution of DC. Considering DC as itself a
hierarchy of capabilities \citep{Collis1994,Winter2003} opens up for a distinction between
first-order and second-order DC. On the one hand, systematic learning generates insights
into how routines and lower level capabilities should change (i.e. impacting first-order
DC) \citep{Mahoney1995,Schilke2014a}. On the other, the same learning process is very much
involved in developing and shaping these capabilities over time (Kianto and Ritala 2010;
Schilke2014). Consequently, in addition to being an antecedent to DC, DL also would work
as a second-order DC influencing the evolution of DC over time (the ability of
“learning-to-learn” (Collis, 1994)).

\emph{H4: Deliberate learning has a direct positive effect on changes in dynamic
  capabilities over time}

Dynamic capabilities enables firms to adapt better to changing environments
\citep{Teece1997} and hence creating strategic change in terms of purposefully changing
operational routines \citep{Helfat2007}. Thus, firms with well-functioning DC would be
able to utilize more instances of change and thus more opportunities for learning
(ref). Consequently, high DC leads to more opportunities for both ad-hoc and deliberate
learning to take place and disclose the demand for investments in methods for systematic
experiential learning. As deliberate learning emphasizes a purposefulness of learning by
focusing “on the effect of planned processes for acquiring, codifying, and transferring
existing knowledge within and between organizations” \citep[p. 1160]{Arthur2005}, many
opportunities generated from enhanced DC should lead to more investments in learning
systems. This notion is also supported by previous work emphasizing that doing more of the
same over time leads experience accumulation and hence improved outcomes
\citep{Zollo2004a}. Similarly, by being active in changing its resource base firms
accumulate experience and the importance of deliberate approaches to leading will become
more apparent. A related point is that when the number of opportunities for learning
increases due to higher DC, the incentives for the firm to invest in DL increases due to
potential intensified agency problems \citep{Arthur2005}. The more potential for
knowledge accumulation through learning, the higher potential for misaligned incentives
between workers keeping information back in fear of not being sufficiently compensated,
and management. Hence, the incentive for the firm to invest in DL to better align these
incentives, increases (ibid). In sum these arguments shape an interesting hypothesis on
the feedback loop between DL and DC and how DL could be an outcome as well as an
antecedent of DC \cite{Schilke2018}.(HERE WE ALSO HAVE A DIRECT QUOTE).

\emph{H5: Dynamic capabilities enhances demand for systematic learning so investments in
  deliberate learning abilities will increase over time.}

\subsection{Direct and indirect outcomes of dynamic capabilities}
The objective of strategic change is to enhance a firm’s competitive advantage
(ref). Doing so over time makes for the evolutionary fitness of the firm \citep{Helfat2007}. When firms
are developing capabilities for strategic change through creating, extending and modifying
the resource base this means making decisions to develop operational routines. Such
routines can in turn stem from an inherent learning process evolutionary distinct to the
firm. OR can thus lead to competitive advantage because of their evolutionary character
\citep{Nelson1982,Winter2003}. To the extent OR stems from idiosyncratic
evolutionary process of individual firms rather than being the result of investments in
factor markets, they can satisfy the VRIO condition and thus be a source of competitive
advantage. In such instances, DC works through OR in creating CA. This indirect impact on
CA is very much at the core of the DC literature (ref). Firms with high DC will be able to
better change operating routines to facilitate strategic change in response to changing
conditions facing the firm. DC then creates VRIO OR and hence CA. When this happens, firms
improves their OR and the OR itself satisfies the VRIO condition.

\emph{H6a: Operating routines mediates the effect of dynamic capabilities in generating
competitive advantage.}

On the other hand, resources and capabilities can to a certain extent be captured in
factor markets through investment decisions (ref) or through alliances (ref) or M\&A
activates (ref). By acquiring resources through investments, the operating routines of the
firms may not be directly affected. When these acquisitions happen as a response to
systematic resource orchestration (ref), i.e. reshaping the resource mix to obtain
coordinated resource deployments \citep{Kor2005,Pan2006}, they would indeed have
potential performance implications for the firm. Moreover, when this process of resource
acquisition process of DC develops a way to acquire and mix resource for the purpose of
adapting to change, the resources themselves would not necessarily satisfy the VRIO
condition. The way in which this happens may be much harder to imitate due to the
complexities such routines exhibit. Although resources themselves exhibit clear
equifinality in their impact on competitive advantage, the complex routines of the
orchestration (i.e. dynamic capabilities) would likely satisfy the VRIO condition. In
other words, there are several ways in which resources can be orchestrated to generate CA,
whereas improved OR will always mean improved competitiveness et ceteris paribus. In such
instances DC itself can lead to CA directly.

\emph{H6b: Dynamic capabilities has a direct effect on competitive advantage through the process
of resource orchestration and acquisition of resources in factor markets.}

In other words, we would expect DC to have both a direct and an indirect impact on
CA. Although both the direct and the indirect path stems from DC creating, extending and
modifying the resource base (OR or factor market resources), the difference in the path’s
stems from to what extent the mediating construct can itself satisfy the VRIO
condition. OR can, due to their evolutionary nature, in turn shaped by DC, achieve CA
\citep{Collis1994,Winter2003}. Factor market resources and market acquired capabilities and
best practices can not \citep{Eisenhardt2000,Peteraf2013}.

\begin{figure}

\begin{minipage}[t]{.5\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{./figure/fig1.png}
  \captionsetup{width=0.9\linewidth}
  \captionof{figure}{Conceptual relationship based on Zollo and Winter. Extensions in grey}
  \label{fig:fig1}
\end{minipage}%
\begin{minipage}[t]{.5\textwidth}
  \centering
  \captionsetup{width=0.98\linewidth}
  \includegraphics[width=0.98\linewidth]{./figure/fig2.png}
  \captionof{figure}{Dynamic capabilities direct and indirect paths to competitive advantage determined by the VRIO condition}
  \label{fig:fig2}
\end{minipage}
\end{figure}

Figure \ref{fig:fig1} sums up the hypothesis proposed in this section of our paper. The
white boxes and black arrows represent the parts of the model that was originally proposed
by \cite{Zollo2002a} whereas the grey parts are extensions based on more recent
contributions to the field of dynamic capabilities. Figure \ref{fig:fig2} illustrates the
two proposed paths through which DC affect competitive advantage. The main take away from
this is that dynamic capabilities can affect CA through changing operational routines that
by themselves can satisfy the VRIO condition by means of their evolutionary nature. Thus,
we hypothesize that operating routines mediates the relationship between DC and CA – the
indirect path. Conversely, the same DC enable the firm to identify resources and
capabilities in factor markets that are less idiosyncratic and often takes the shape of
best practices that are definitely imitable and thus bot VRIO. In such instances, the VRIO
condition is satisfied by the DC itself through its complex process of orchestrating and
mixing resources – the direct path.

\section{Data and methods}
An empirical test of the Zollo \& Winter model necessitates a certain time span of
observations in order to enable the study of dynamics over time. The lack of such
longitudinal studies to investigate dynamics has also been a permanent limitation for
moving the DC literature forward empirically and theoretically \cite{Schilke2018}. To
remedy this gap in the literature and to investigate the empirical characteristics of the
Zollo \& Winter model we sampled a subset of Norwegian technology firms ($N=241$) over two
time periods.

We collected survey data from R\&D active firms in Norway at two points in time ($T_1=2005$
and $T_2=2014$). The population was all businesses registered to a scheme for tax deduction
of R\&D costs (called SkatteFUNN). As all enterprises which are eligible for taxation could
register their R\&D activities to receive a tax refund, the registered enterprises include
close to all enterprises which are involved in such activities at the time of our study.

All firms that registered R\&D activities during May to December 2005 were approached
totaling in all 1721 firms. A web-based questionnaire was developed containing the
measures of the key constructs of this paper. A link to the questionnaire was e-mailed to
the firms within a month after they registered R\&D activities. The initial mailing was
followed by two e-mail reminders. Of the firms approached, 1199 (70 \%) returned filled-in
questionnaires. The 1199 companies that filled out the questionnaire were contacted again
9 years later. The majority of firms were contacted in spring/summer 2014. All received a
web-based questionnaire containing the same measures of DC, CA, OR and so on. 283 of the
firms returned filled-in questionnaire.

All the firms in the sample was identifiable by means of the official firm
identifier. This enabled us to attach financial data from the annual accounts of the firms
despite none of the firms in the sample being publicly traded companies. We obtained the
financial accounts from the National Firm Registry (BRREG) for all years between 2007 and
2014 (prior to 2007 was not accessible through our database).

To control for survivor and non-response among our firms over time due to exogenous
factors such as exit, bankruptcy and so on, we estimate a model Heckman correction (Hair,
2010). Applied to the context of this paper, Heckman regression is a method that in the
first step analyses the probability that a firm at $T_1$ will answer the survey at $T_2$
depending on observables at $T_1$. This is modeled as a probit regression. Based on the
probit regression in $T_1$, the inverse Mills ratio (sometimes called lambda) is added to the
analysis in the second step where the goal is to analyze the relationship between our
focal constructs (using regular OLS regression). The inverse Mills ratio is a control
factor which controls for unobserved heterogeneity. More concretely, the inverse Mills
ratio will control for unobserved factors that are related to both firms’ probability of
answering the survey at $T_2$ (ref).

\subsection{Variable construction}

The focal constructs of this paper are deliberate learning, dynamic capabilities,
operational routines and competitive advantage. These are all operationalized using the
survey data described above. Table 1 below describes the items used to operationalize the
focal constructs and their internal validity in forming an additive index (Cronbach´s
alpha). The results show that our key constructs can be represented by the items in the
survey.

There are no established measurement models of dynamic capabilities
\citep{McKelvie2009,Schilke2018}. Therefore this study builds on a mixture of qualitative
case study methodology, literature review and statistical techniques to develop and refine
measures of DCs. First, exploratory qualitative interviews, using a semistructured
interview guide, were conducted with management representatives from 10 R\&D/innovative
firms. The aim of the interviews was to get an overview of each firm's innovation and
development processes, in particular the processes related to its dynamic capabilities and
the management of its resources. Themes raised in the interviews were about network,
co-operation with external R\&D-institutions, learning in the firm, adaptation and changes
in the firm. We interviewed SMEs and larger firms, and the industries varied from
high-tech and ICT to publishing.  Based on the interviews and an extensive literature
review, statements identified as descriptions of dynamic capabilities and resources were
developed and included in a questionnaire.

Second, the informants from the 10 firms were subsequently asked to take part in a pretest
of the questionnaire, including the preliminary items developed to measure dynamic
capabilities and resources, by responding to the questionnaire and giving comments on the
individual questions. This was followed up by a telephone call to the interviewees where
they were asked to report their views on the various questions/items.

Third, the face validity of the items was further examined by pre-testing the measurements
among experts. Researchers with knowledge of business strategy within firms were asked to
evaluate the questionnaire. Based on the results from the pilot study, the items were
adjusted and refined.

Although we recognize at the outset that the concept of dynamic capabilities and their
underlying resource components are very challenging to research in a systematic and
econometric fashion \citep{McKelvie2009}, we follow the argument in the
literature that more empirical work is necessary to test and refine the dynamic
capabilities concept and how it is related to the evolutionary economic theory
\citep{Arend2009,McKelvie2009} \todo{Rosenblom, 2000; Verona and Ravasi, 2003;}.  It
is in this spirit that the research reported in this paper has been undertaken.

Items measuring DC and OCs were developed as statements for which the respondents were
asked to indicate to what extent each statement fitted a description of their business. We
adopted one-sided seven point Likert scale where: 1 = strongly disagree and 7 = strongly
agree. We built on prior studies where items measuring OCs have been measured relative to
competitors \citep{McKelvie2009}.

\text{red}{CONTINUE WITH THE OTHER KEY CONSTRUCTS – INPUT FROM TOMMY}

\subsection{Control variables}

We add a set of control variables expected to explain parts of the variation in our focal
constructs. From the survey we add firm size, firm age, the level of dynamism facing the
firm. Size is the reported number of employees in the firm at $T_2$, and age is the number of
years since establishment. Dynamism is captured by asking a number of questions about the
competitive environment facing the firm. A full list of items and their internal validity
(0.75) is available in appendix ##.

To partly remedy the problem of common method bias, we add controls of financial data from
the firm´s profit and loss statements, and balance sheet. Specifically, we add the natural
logarithm of the assets and debt of the firm to capture the leverage (debt risk) of the
firm, as well as the capital intensity.

One core critique of the dynamic capabilities literature is that it simply is a response
to the firm being a good firm \citep{Arend2009}. This tautology makes it hard to
distinguish the direction of the effects the performance implications of dynamic
capabilities. Simply put both firm performance and dynamic capabilities can be due to some
unobserved factor of the firm simply being a “good firm”. In such cases we would simply
regress one on the other and get positive results without the exact mechanism being
pointed out. To partly control for this we add a proxy for the quality of the firm as a
control variable. In this paper we use the profit margin of the firm as this type of
control. It is not perfect as profit margins can be due to many factors outside our model,
but it serves to control for parts of the possible cofounding factors of firm quality.

\subsection{Estimation and empirical model}

To test our hypotheses, we run a sequential linear regression with heteroskedastic robust
standard errors and Heckmann two-step correction to control for attrition and survival
bias (ref). We test the mediation hypotheses within this framework using a causal
mediation \citep{Baron1986,MacKinnon2008} with quasi-Bayesian confidence intervals
over a million simulations \citep{Imai2010}. The sequential regression
model is presented chronologically in accordance with figure \ref{fig:fig1}. This entails that the
dependent variable in one model will be the independent in the next to study the evolution
of the proposed model sufficiently. The following models are estimated:

\par\noindent
\begin{align}
  OR_{2,i} &= \beta_0 + \beta_1 OR_{1,i} + \beta_2 DL_{i} + \mathbf{\Gamma C_i} + \epsilon_i\\
  OR_{2,i} &= \beta_0 + \beta_1 OR_{1,i} + \beta_2 DL_{i} + \beta_3 DC_{1,i} + \beta_4
               \Delta DC + \mathbf{\Gamma C_i} + \epsilon_i\\
  DC_{2,i} &= \gamma_0 + \gamma_1 DL_{1} + \gamma_2 DC_{1,i} + \mathbf{\Gamma C_i} + \upsilon_i\\
  CA_{2,i} &= \lambda_0 + \lambda_1 CA_{1,i} +
             \lambda_2 DC_{1,i} + \lambda_3 \Delta DC_i +\mathbf{\Gamma C_i}+ \mu_i \\
  CA_{2,i} &= \lambda_0 + \lambda_1 CA_{1,i} + \lambda_2 OR_{1,i} + \lambda_3 \Delta OR_i
             \lambda_4 DC_{1,i} + \lambda_5 \Delta DC_i +\mathbf{\Gamma C_i}+ \mu_i \\
  DL_{i} &= \xi_0 + \xi_1 DC_{1,i} +\mathbf{\Gamma C_i}+ \nu_i
\end{align}

Here $ \mathbf{\Gamma C_i}$ represents a vector of control variables including size, age,
dynamism, financial assets and profit margin. $\Delta DC_i$ is the change in $DC$ from
$T_1$ to $T_2$. Similarly $\Delta OR_i$ represents the change in $OR$.

In addition we estimate mediating models and test formally for mediation using the Baron
\& Kenny method \citep{Baron1986,MacKinnon2008}. We estimate two mediating model to test
if OR mediates the effect of DC on CA, and if DC mediates the effect of DL on OR,
respectively. The mediation equations for OR and DC respectively are state below:

\begin{align}
 \Delta DC_i &= \alpha_0 + \alpha_1 OR_{1,i} + \alpha_2 DL_{i} + \mathbf{\Gamma C_i} + u_i \\
 \Delta OR_i &= \omega_0 + \omega_1 CA_{1,i} + \omega_2 \Delta DC_{i} + \omega_3 CA_{1,i} + \mathbf{\Gamma C_i} + v_i
\end{align}

Finally, we run a Heckman selection model with selecting in to the sample at time $T_2$ is
determined by the following model:

\begin{align}
  P(R=1) &= \eta_0 + \eta_1 L_i + \eta_2 DC_{1,i} + \mathbf{\Gamma C_i} + m_i
\end{align}

$R$ is an indicator variable equal to 1 if the firm has responded at $T_2$ and 0 if
not. $L_i$ is an indicator set to 1 if the person answering the survey is the managing
director or CEO. This acts as an instrument for considering the probability of the firm
selection into the sample, but without having any theorized relationship with the main
outcome variables $DC$, $OR$, and $CA$. It is reasonable to assume that if the CEO was
involved in answering the survey at $T_1$, would increase the probability of the firm
answering at $T_2$ as well.

\section{Results}
The focal variables of our study is presented with pairwise correlation, mean and standard
deviation in table \ref{tab:desc}.It is worth noting that the mean value of OR and DC is
declining over time suggesting that the average firm experience a negative development in
core resources. The ability of the firms in our sample to generate CA is somewhat
unchanged over the sample period. We also observe a certain correlation in the development
in DC over time suggesting that prior period DC is a strong predictor of future
DC. Furthermore, we see a strong correlation between DL and DC which indicates that these
two constructs are indeed related.

\begin{table}[t]
\begin{singlespace}
  \caption{\small Descriptive statistics and correlations for variables in this paper}
  \label{tab:desc}

<<resultscorr, results="asis",echo=FALSE >>=

print(xtable(art2cor ,size="\\small",caption="Correlation matrix \\label{tab:cor}", align = c("l", rep("p{0.3in}",9)),table.placement="h", size = "\\small", tabular.environment="longtable"), size="scriptsize", label='tab:cor', caption.placement="top", floating=FALSE,latex.environments=NULL)

@
\vspace{1ex}

     \raggedright {\scriptsize Notes: Pairwise correlations between variables in the study
    excluding controls}
\end{singlespace}
\end{table}

\begin{table*}[t]
  \centering

\caption{Regression -How are MDC influencing evolution of lower level capabilities }

<<result1, results="asis", echo=FALSE >>=
stargazer(mainres,
          add.lines =list(c("Adjusted $R^2$",r1,r2,r3,r4,r5,r6)),
          single.row=FALSE, column.sep.width = "1pt", omit.stat=c("LL","ser","f","aic","rsq","adj.rsq"),
          no.space=FALSE,
          dep.var.labels=c("OR_{T_2}", "DC_{T_2}","CA_{T_2}","DL"),
        #  column.labels=c("HECKMAN","OLS","HECKMAN","OLS","HECKMAN","OLS"),
          model.names=FALSE,
          object.names=FALSE,

          ### order=c(1,3,2),

           ## covariate.labels= c("$OR_{T_1}$",
           ##                "$\\Delta OR$",
           ##                "$CA_{T_1}$"
           ##                "$DL$",
           ##                "$DC_{T_1}$",
           ##                "$\\Delta DC$",
           ##                "Firm size",
           ##                "Firm age",
           ##                "Environmental Dynamism",
           ##                "Firm profit margin",
           ##                "Firm assets"
           ##          ),

          title= "Regression results for model C", font.size="scriptsize",float=FALSE
          )

@
\label{tab:reg}
\end{table*}

\begin{figure}[t]

\begin{minipage}[t]{.5\textwidth}

  \resizebox{7cm}{!}{\input{./figure/medanalysis1.tex}}
  \captionof{figure}{Mediation analysis 1}
  \label{fig:fig3}
\end{minipage}%
\begin{minipage}[t]{.5\textwidth}
 \resizebox{7cm}{!}{\input{./figure/medanalysis2.tex}}
  \captionof{figure}{Mediation analysis 2}
  \label{fig:fig4}
\end{minipage}
\end{figure}

Table \ref{tab:reg} shows a summary of the regression models proposed in the previous
chapter. Models 1,2 and 3 are designed to test DL as \emph{antecedent} for $OR$ and
$DC$. Consider model 1 we observe that $DL$ is influencing the level of $OR$ within the
firm ($\beta_2 =$ \Sexpr{mod1_dl}) supporting H1. However, the effect disappears when we
add $DC$ in model 2 suggesting a mediating effect. In other words we see that firms with
initial high $DC$($\beta_3=$ \Sexpr{mod2_dc0}) and increasing $DC$ over time ($\beta_4=$
\Sexpr{mod2_ddc}) also have better $OR$. To control for the mediating effect suggested by
the change in coefficients for $DL$ between models 1 and 2, we performed a causal
mediation analysis as reported in figure \ref{fig:fig3}. This analysis confirms the
indications from models 1 and 2 showing that the direct effect from $DL$ on $OR$ is
insignificant and small (ADE = \Sexpr{medmod1_ade}). Meanwhile, the indirect effect
running through changes in $DC$ over time, is significant yielding a positive and
significant indirect effect of \Sexpr{medmod1_acme}. The proportion of the effect that is
mediated amounts to \Sexpr{medmod1_shmed}. In sum these results suggest that H1 is
unsupported, and that the bulk of the effect is indirect running through $DC$, in line with
the expectations in H3. Similarly, we see from model 3 that $DC$ is indeed influenced by $DL$
above and beyond its own evolutionary trajectory. This is in line with our expectations
and lend support to H4.

To evaluate H5 proposing a feedback effect from $DC$ to $DL$, we turn to model 6 in table
\ref{tab:reg}. Controlled for the usual firm level controls we find a positive effect
($\xi_1=$ \Sexpr{mod6_dc0}) from $DC_{T_1}$ on $DL$ measured at $T_1$. This supports H5
suggesting that firms with more $DC$ is more likely to generate opportunities where it
becomes more prevalent that learning will need to take place. One interesting finding is
also that this effect environmental dynamism decreases firms level of $DL$. This is indeed
puzzling and we will look in to this in a post-hoc analysis.\todo{When adding interactions
  we see that high environmental dynamism in conjunction with DC is positive for DL
  meaning that DC will indeed work to make firms more aware of the benefits of DL when
  environments are changing} It is also worth noting that models 1,2 and 3 have positive
and significant $\rho$ from the Heckman selection model indicating that selection is
leading to biased estimates. By running a Heckman correction we avoid this potential
problem.

Models 4 and 5 in table \ref{tab:reg} deals with the \emph{outcome} of DC. H6a and H6b
both considers effects of $DC$ on the competitive advantage of the firm $CA$. $CA$ is
influenced by the level of $DC$ of the firm indicating that dynamic capabilities are a
source of competitive advantage in line with our expectations. Furthermore, considering
model 5 we see that $OR$ also has a significant positive effect on $CA$ indicating that
operating routines can also be a source of advantage for the firm. Moreover, the
coefficient of $\Delta DC$ decline from \Sexpr{mod4_ddc} to \Sexpr{mod5_ddc} when we add
$OR$. This suggests that some mediation is at work, i.e. that changes in $DC$ leads to
changes in changes in $OR$ leading to $CA$. This indirect path is in line with the
expectations from our hypotheses and as described in figure \ref{fig:fig2}. When formally
testing this mediation running a causal mediation analysis (see figure \ref{fig:fig4}), we
find added support that both a \emph{direct-} and an \emph{indirect} path exist to explain
the relationship between $DC$ and $CA$ (ADE = \Sexpr{medmod5_ade}, ACME =
\Sexpr{medmod5_acme}) and a total mediated share of \Sexpr{medmod5_shmed}.

Table \ref{tab:hyptab} depict a summary of the hypotheses and indicate if they are
supported or not in our analysis. We will now turn to the discussion.

\begin{table}
     \footnotesize
  \centering
\input{./figure/hyptab.tex}}
\end{table}

\section{Discussion}

The objective of this article is to study the antecedents and outcomes of dynamic
capabilities, particularly the role of deliberate learning in shaping dynamic capabilities
over time. Learning is arguably an important determinant of firm success (ref arrow and
more), and the deliberate investment in learning to learning (i.e. deliberate learning)
has a long standing position as a theoretical antecedent of dynamic capabilities
\citep{Zollo2002a,Eriksson2014,Schilke2018}. Furthermore, the role of deliberate learning
in creating better operational routines is well established (ref), but it`s role in
generating competietive advantage for the firm, is less understood. Alas, the main
mechanism, the VRIO principle \citep{Barney1991a} is well known and still deemed highly
relevant relevant in understanding the source of competitive advantage of the firm
\citep{Priem2001}. Despite the prevalent and considerable citation of the
\cite{Zollo2002a} model, neither an empirical analysis of the model propositions, nor it`s
connection to outcomes such as competitive advantage has, to our knowledge, been
undertaken.

Our proposed extension of \cite{Zollo2002a} as depicted in figure \ref{fig:fig1}, taps
into the debate on the most important \emph{antecedents} and \emph{outcomes} of dynamic
capabilities \cite{Eriksson2014,Schilke2018}. Our results indicate that deliberate
learning is indeed an important antecedent of dynamic capabilities. Firms with stronger
capabilities for deliberate learning will develop higher levels of dynamic
capabilities. Thus the deliberate decision to invest in systems for learning will lead to
the evolution of better capacities to "purposefully create, extend, or modify its resource
base" \citep[p. ###]{Helfat2007}. Indeed, this also follows from Zollo \& Winter`s
definition where "a dynamic capability is a learned and stable pattern of collective
activity through which the organization systematically generates and modifies its
operating routines in pursuit of improved effectiveness" \citep[p
###]{Zollo2002a}.

The next step of figure \ref{fig:fig1} is to establish the link between deliberate
learning and the operational routines of the firm. These operating routines are what
\cite{Winter2003} calls "how we can earn a living now" (p. 992) or the technical fitness
of the firm \citep{Helfat2007}. Such operational routines are the product of learning
processes over time and should indeed be linked to deliberate learning of the firm as
proposed by \cite{Zollo2002a}. However, we find that this direct effect between deliberate
learning and operational capabilities disappear when we introduce dynamic capabilities into
the model. This suggest that dynamic capabilities are evolving as a response to deliberate
learning and, in turn, shaping operational capabilities in line with expectations of Zollo
\& Winter. In other words, we find support for an indirect link between deliberate
learning and operational routines, but no direct path.

This finding may come from the fact that learning works differently at different levels of
the capabilities hierarchy \citep{Collis1994}. Considering operational capabilities as
zero-order capabilities \citep{Winter2003,Schilke2014a} defined as more "geared towards
the operational functioning of the firm" \citep[p. 340]{Zollo2002a}, learning may be more
ad-hoc and less routinized as experiences are accumulated "on the fly" or through
"learning by doing" (ref) rather than deliberate and systematic. Indeed, learning by doing
is established as a robust result in the empirical literature on it`s link to operational
excellence (ref). When learning becomes deliberate and systematic through investments in
learning to learn capabilities, this would not automatically strengthen the short term
evolution of operational capabilities directly \citep{Arthur2005}. \todo{Need some more
  references here}. These findings would also lend support to the notion of higher-order
dynamic capabilities (capabilities to change dynamic capabilities)
\citep{Collis1994,Winter2003,Schilke2014a} and that deliberate learning could be
classified as such. In contrast, ad-hoc learning based on repetitive actions by employees
does not satisfy the requirements for a dynamic capability as the actions are less
strategic and purposeful.

An interesting finding is also that deliberate learning itself could be seen as a function
of dynamic capabilities. We argue that this stems from firms with high levels and
evolution of dynamic capabilities will take more advantage of adapting to change and hence
creating more opportunities for learning. This leads the firm to realize the need for
more deliberate approach to systematic learning. Particularly, this would lead to more
investments in systems for learning and, in turn, improvements in dynamic and operational
capabilities. For obvious reasons this is a tough causal claim to make and we have little
support for a causal argument. The insight will thus need considerably better data and
empirical analysis going forward. However, it has some support in the literature where
learning can be seen as an outcome as well as an antecedent to dynamic capabilities
\citep{Schilke2018}. \todo{maybe add someting about the interaction with dynamism}

Moving from antecedents to outcomes we extended the \cite{Zollo2002a} model by adding
competitive advantage to the model. We find that both operational capabilities and dynamic
capabilities can lead to competitive advantage. The most obvious path from the mere
definition of dynamic capabilities, runs through the evolution of operational
capabilities. Dynamic capabilities shape operational capabilities and changes them to
adapt, hence safeguarding that they are adapted. This is beyond the ad-hoc learning and
adaptation taking place as repetitive actions by employees. TO BE CONTINUED

\subsection{Limitations}

Our operational construst of $DC$ captures dynamic capabilities in
a broad, non-functional, sense (e.g. as a broad-purpose capability rather than one for
a particular purpose) \citep{Schilke2018}, and will hence capture a mind-set of the
organization rather than a narrow set of learned capabilites. This makes our conclusions
more general, albeit maybe less precise in predicting what investments in deliberate
learning would nmean for important capacities such as new product development and
innovation. 
 BLABLABLABLA

\section{Bibliography}

\singlespacing
\bibliography{Dissertation_clean}

\section{Appendix}

\end{document}

### 2019-07-23 estimation/article4_analysis.r

@@ -1,0 +1,266 @@
+
+
+setwd("/Users/larshovdanmolden/Documents/git/article3")
+source("./estimation/packages.r")
+source("./estimation/article_functions.r")
+
+require("MASS")
+library(sampleSelection)
+library(mediation)
+library(polycor)
+
+## This loads the data workspace where skattefunn_data.r is already loaded
+load("./data/art3base.RData")
+
+## Overall system settings
+options(digits=8)
+Sys.setlocale("LC_ALL", 'en_US.UTF-8')
+
+## Importing and cleaningemail address and the project number
+regdataraw = read.spss("./data/regdata_tommy.sav", to.data.frame=TRUE, labels=F)
+regdatazw <- regdataraw[,c("epost","prosjektnummer")] #could add ny_epost too
+regdatazw$epost <- str_trim(as.character(regdatazw$epost))
+names(regdatazw) <- c("email","pnr")
+
+## Importing Skattefunn data
+regdatasf <- sfmain[,c("Prosjektnummmer","Organisasjonsnummer")]
+names(regdatasf) <- c("pnr","orgnr") #orgnr is a unique identifier for each firm / same for pnr at project level
+datazw = read.csv("./data/skattefunn_10_clean.csv", sep=";",dec=",", header=T, na.strings="-1")
+
+md <- datazw[c("Resp","dc_t0","dc_t1")]
+md$Resp <- str_trim(as.character(md$Resp))
+colnames(md) <- c("email","dc0","dc1")
+
+## NB / regdf comes from skattefunn_data.r contains all projects, not only endreport
+matchvec <- match(md$email,regdf$email)
+regdata <- cbind(md,regdf[matchvec,])
+datazw <- cbind(datazw,regdata)
+
+## Splitting datazw in first wave and second wave
+zw0 <- data.frame(orgnr=datazw$orgnr);zw0$yr <- 2004
+zw1 <- data.frame(orgnr=datazw$orgnr);zw1$yr <- 2014
+
+zw0[,3:117] <- datazw[,2:116]
+zw1[,3:70] <- datazw[,117:184];zw1 <- zw1[1:263,]
+
[…]

### 2019-07-23 estimation/packages.r

@@ -1,0 +1,45 @@
+
+
+
+list.of.packages = c("kableExtra",
+                     "foreign",
+                     "stringr",
+                     "Hmisc",
+                     "reshape2",
+                     "dplyr",
+                     "broom",
+                     "tableHTML",
+                     "condformat",
+                     "factoextra",
+                     "stargazer",
+                     "xtable",
+                     "pixiedust",
+                     "RColorBrewer",
+                     "glmnet",
+                     "mice",
+                     "basicTrendline",
+                     "oaxaca",
+                     "GeneralOaxaca",
+                     "plm",
+                     "BaylorEdPsych",
+                     "jtools",
+                     "lfe",
+                     "openxlsx",
+                     "lavaan"
+                     )
+
+
+
+
+new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
+if(length(new.packages) > 0) {install.packages(new.packages)}
+
+lapply(list.of.packages, require, character.only=T)
+
+
+
+
+
+
+
+

### 2019-07-23 article4_analysis.r
removed a file

@@ -1,266 +1,0 @@
-
-
-setwd("/Users/larshovdanmolden/Documents/git/article3")
-source("./estimation/packages.r")
-source("./estimation/article_functions.r")
-
-require("MASS")
-library(sampleSelection)
-library(mediation)
-library(polycor)
-
-## This loads the data workspace where skattefunn_data.r is already loaded
-load("./data/art3base.RData")
-
-## Overall system settings
-options(digits=8)
-Sys.setlocale("LC_ALL", 'en_US.UTF-8')
-
-## Importing and cleaningemail address and the project number
-regdataraw = read.spss("./data/regdata_tommy.sav", to.data.frame=TRUE, labels=F)
-regdatazw <- regdataraw[,c("epost","prosjektnummer")] #could add ny_epost too
-regdatazw$epost <- str_trim(as.character(regdatazw$epost))
-names(regdatazw) <- c("email","pnr")
-
-## Importing Skattefunn data
-regdatasf <- sfmain[,c("Prosjektnummmer","Organisasjonsnummer")]
-names(regdatasf) <- c("pnr","orgnr") #orgnr is a unique identifier for each firm / same for pnr at project level
-datazw = read.csv("./data/skattefunn_10_clean.csv", sep=";",dec=",", header=T, na.strings="-1")
-
-md <- datazw[c("Resp","dc_t0","dc_t1")]
-md$Resp <- str_trim(as.character(md$Resp))
-colnames(md) <- c("email","dc0","dc1")
-
-## NB / regdf comes from skattefunn_data.r contains all projects, not only endreport
-matchvec <- match(md$email,regdf$email)
-regdata <- cbind(md,regdf[matchvec,])
-datazw <- cbind(datazw,regdata)
-
-## Splitting datazw in first wave and second wave
-zw0 <- data.frame(orgnr=datazw$orgnr);zw0$yr <- 2004
-zw1 <- data.frame(orgnr=datazw$orgnr);zw1$yr <- 2014
-
-zw0[,3:117] <- datazw[,2:116]
-zw1[,3:70] <- datazw[,117:184];zw1 <- zw1[1:263,]
-
[…]

### 2019-07-23 figure/medanalysis1.tex
added folder for figure and dummy figure

\begin{tikzpicture}

   \tikzstyle{mynode}=[draw, ultra thin, draw=black, fill=white, minimum size=17mm,inner sep=0pt, align=center]

    \node[mynode] (m){$\Delta DC$};
    \node[mynode,below left=of m](a) {$DL$};
    \node[mynode,below right=of m](b) {$OR_{t_2}$};
    \draw[-latex] (a.north) -- node[text width=1.3cm,font=\footnotesize, align=left, fill=white] {$\beta=0.46$ \\ $p<0.001$} (m.west);
    \draw[-latex] (m.east) -- node[text width=1.3cm,font=\footnotesize,align=right, fill=white] {$\beta=0.48$ \\ $p<0.001$} (b.north);
    \draw[-latex] (a.east) --
            node[below=10mm,font=\footnotesize,align=left] {Average Direct Effect, $ADE=0.05$,
              \\ Average Causal Mediated Effect, $ACME=0.22^{***}$ \\
            Proportion of effect mediated: 82\%}
                 (b.west);
\end{tikzpicture}

### 2019-09-03 article4_analysis.r
Commit before writing paper 4 up

@@ -1,0 +1,357 @@
+
+
+setwd("/Users/larshovdanmolden/Documents/git/article3")
+source("./estimation/packages.r")
+source("./estimation/article_functions.r")
+
+require("MASS")
+library(sampleSelection)
+library(mediation)
+library(polycor)
+
+## This loads the data workspace where skattefunn_data.r is already loaded
+load("./data/art3base.RData")
+
+## Overall system settings
+options(digits=8)
+Sys.setlocale("LC_ALL", 'en_US.UTF-8')
+
+## Importing and cleaningemail address and the project number
+regdataraw = read.spss("./data/regdata_tommy.sav", to.data.frame=TRUE, labels=F)
+regdatazw <- regdataraw[,c("epost","prosjektnummer")] #could add ny_epost too
+regdatazw$epost <- str_trim(as.character(regdatazw$epost))
+names(regdatazw) <- c("email","pnr")
+
+## Importing Skattefunn data
+regdatasf <- sfmain[,c("Prosjektnummmer","Organisasjonsnummer")]
+names(regdatasf) <- c("pnr","orgnr") #orgnr is a unique identifier for each firm / same for pnr at project level
+datazw = read.csv("./data/skattefunn_10_clean.csv", sep=";",dec=",", header=T, na.strings="-1")
+
+md <- datazw[c("Resp","dc_t0","dc_t1")]
+md$Resp <- str_trim(as.character(md$Resp))
+colnames(md) <- c("email","dc0","dc1")
+
+## NB / regdf comes from skattefunn_data.r contains all projects, not only endreport
+matchvec <- match(md$email,regdf$email)
+regdata <- cbind(md,regdf[matchvec,])
+datazw <- cbind(datazw,regdata)
+
+## Splitting datazw in first wave and second wave
+zw0 <- data.frame(orgnr=datazw$orgnr);zw0$yr <- 2004
[…]

### 2019-09-05 article4_tommylars.rnw
Some focus on the mechanism and mediation

@@
 \section{Introduction}
+
+Dynamic capabilities are proposed to confer a competitive advantage by adding unique value to the firm through systematic change, which enhances operational efficiency and enables increased alignment with the environment (Di Stefano et al., 2014; Peteraf et al., 2013)
+
+Not all organizations possess them (Collis, 1996); their path dependencies, intangibility, complexity, and organizational specificity make them hard to imitate (Gibson & Birkinshaw, 2004; Helfat & Winter, 2011); and few other means allow organizations to purposefully change on a continuous basis (Day & Wensley, 1988; Helfat et al., 2007).
+
+Consistent with the theoretical positions of Eisenhardt and Martin (2000), Helfat and Peteraf (2003), Zahra et al.
+(2006), and Zott (2003), among others, these researchers have argued that dynamic capabilities’ immediate purpose is to change the resource base, and that this change in the resource base, in turn, explains performance variations.
+According to this argument, resource changes serve as mediators through which dynamic capabilities affect performance.
+We
+
+One of the major unresolved issues in dynamic capabilities theory is to what extent and
+how competitive advantage is the ultimate outcome of dynamic capabilities. This very idea
+has
+
+This paper asks two questions: to what extent does a direct lnk between DC and CA exist,
+and what determines variations in the role of mediation between them?
+
+The idea that Dc impacts CA is uncontroversial (not). Little is known about how this
+happens. The theory holds that this happens through xreating extending and modifying the
+resource base. YEt, the change in firm capabilities can themselves lead to CA due to their
+evlutionary nature.
+
+Variations in the share of mediation stems from variation sin the environment. When envdyn
+is high firms need to act faster and hence tends to choose strategies including resource
+orchestration buying in factor markets cause it tkes more time to develop OR.
+
+In less dynamism the role of OR increases and leads to a significant proportion of CA
+stemming throhg the mediating effect of OR
+
 There is ongoing interest in (dynamic) capabilities and how they influence firm
@@
 performance implications.
-
-An issue that has received far less attention, however, is whether dynamics capabilities
-themselves undergo an evolution \citep{Schilke2018}. Moreover, if DCs undergo an
-evolution, is the evolution inert and past-dependent, or more deliberate and represent
-purposeful change in firms DCs over time? Unpacking this is crucial to the development of
-DC theory as it goes into the very nature of the issue as to whether and to what extent
-DCs can purposefully alter firms operating routines, and the performance implications
-stemming from such change \citep{Helfat2007}. It is therefore surprising that the
-literature has dealt with it sparingly. What is the exception to this is \cite{Zollo2002a}
-highly influential model over DC evolution where they postulate that (dynamic)
-capabilities evolve with regard to firms’ \emph{deliberate learning} (DL). However, Zollo
-\& Winter`s insightful theorizing has received scant empirical testing. Moreover, their
-model can be developed further, by incorporating insights from subsequent research and
-theorizing since this model was published. One salient issue in this regard is that Zollo
-\& Winter did not consider how DCs can influence firms’ DL. Moreover, their model does not
-consider how firm performance may be influenced by the evolution of (dynamic)\todo{should
-  we really go with the parantheses around dynamic throuhgt the whole paper - it feels
-  like we are not certain about the concept} capabilities (through DL). Such feedback
-loops may significantly alter how we understand the relationship between deliberate
-learning and evolution of (dynamic) capabilities in extant DC theory, including the
-performance implications of such evolution. Reflecting this gap in our understanding, we
-ask the following research question:
-
-\emph{What is the role of deliberate learning in the evolution of (dynamic) capabilities and the
-performance implications for such evolution?}
-
-To answer this research question, we not only empirically test ZW’s a highly influential
-model of the evolution of (dynamic) capabilities, but also extend it by incorporating (a)
-feedback loops between DCs and deliberate learning and (b) incorporating firm performance
-into the model.
 
@@
 antecedents and outcomes \citep{Eriksson2014,Schilke2018}, as well as its evolution
-and development trajectory \citep{Romme2010,Zollo2002a}. Extant
-literature has dealt with antecedents in many forms such as ### (ref) etc. Similarly,
-outcomes have been the focal point of several contributions focusing on ### (ref)
-etc. However, despite DC building on an evolutionary view of resource development, less
-attention has been dealt to the evolution of DC over time than one could expect. Partly
-this could be due to lacking data (ref), unclear conceptual definitions (ref) or sheer
-complexity of studying evolution (ref). One remarkable exception is Zollo \& Winter (2002)
-who propose a clear evolutionary argument and hypothesis on DC evolution. Still, little
-empirical work has attempted to test their propositions.
-
-\textcolor{red}{DL definition – makes sure all definitions are in order}
-
-By combining insights from 20 years of DC research on external factors such as antecedents
-and outcomes with the internal process shaping DC over time, we can shed light on the
-workings of DC and extend the knowledge of its implications. Using Zollo \& Winter as our
-point of departure we will be able to study the internal process of DC evolution, and by
-adding new dimensions related to antecedents and outcomes we will gain insight into
-important implications of the concept.
-
-\subsection{Deliberate learning as antecedent and evolution driver}
-When Zollo \& Winter (2002) put deliberate learning at the center of their model for DC
-evolution they tap into a core tenant of DC theory more developed in later
-contributions. Learning theory in organizations distinguishes between autonomous learning
-processes \citep{Arthur2005} (e.g. learning by doing \citep{Zollo2002a,Arrow1962} based on
-repetitive actions by employees in firms and organizations, and deliberate learning where
-learning takes the form of a planned and deliberate process \citep{Arthur2005}. This
-deliberation and intent as a driver behind the learning process, corresponds well with the
-idea of purposefulness behind strategic intent as evident in the definition of dynamic
-capabilities \citep{Helfat2007}: “the ability to {\bf purposefully} build, extend and
-modify ordinary capabilities” (our emphasis added). (ref). When organizations invest in
-systems to facilitate learning, they invest in capabilities for changing routines in line
-with strategic direction of the organization itself. Hence, investments in deliberate
-learning corresponds with investments in dynamic capabilities and both concepts contribute
-to the development of operational routines.
-
-\emph{H1: Deliberate learning has a direct positive effect on organizations development of
-  operating routines.}
-
-They depart conceptually, however, when we look at the functioning of each. The main
-function of DL is to accumulate knowledge and experience about the operation of the
-organization and its environment (ref). Through this process DL generates insights into
-what should be changed and not in order to achieve improved organizational
-performance. Contrary, DC deals with how change in operational routines should be done
-through putting experience from DL to work (ref). Thus, for DC to be well functioning in
-its quest to change OR, a DL process needs to be in place. Without a proper DL the
-learning will be less purposeful and hence less attune to the strategic intent of the
-firm. Change may still appear, but as organizational change rather than strategic (helfat
-distinction between strategix and organizational change). In other words, without DL firms
-can achieve technical fitness (ref), but only through DL shaping DC can firms achieve
-evolutionary fitness (ref). Consequently, DL is an important antecedent to DC.
-
-\emph{H2: Deliberate learning leads to stronger dynamic capabilities and has a positive
-  influence on the level of dynamic capabilities within the firm.}
-
-\emph{H3: Deliberate learning has an indirect effect on operational routines through
-  dynamic capabilities.}
-
-Besides impacting the level of DC as an antecedent, DL also contributes to the evolution
-of DC over time. Conventional insights suggest that DC cannot be aquired in factor markets
-and thus has to be developed internally \citep{Coen2011,Schilke2014a}\todo{(Helfat,
-  Finkelstein, Mitchell, Peteraf, Singh,\& Teece, 2007; Katkalo, Pitelis, \& Teece, 2010;
-  Maritan \& Peteraf, 2011; Teece, 2014). in Schilke 2014} . This has performance
-implications related to the VRIO principle \citep{Barney1991} (as discussed later in this
-article), as well as consequences for the evolution of DC. Considering DC as itself a
-hierarchy of capabilities \citep{Collis1994,Winter2003} opens up for a distinction between
-first-order and second-order DC. On the one hand, systematic learning generates insights
-into how routines and lower level capabilities should change (i.e. impacting first-order
-DC) \citep{Mahoney1995,Schilke2014a}. On the other, the same learning process is very much
-involved in developing and shaping these capabilities over time (Kianto and Ritala 2010;
-Schilke2014). Consequently, in addition to being an antecedent to DC, DL also would work
-as a second-order DC influencing the evolution of DC over time (the ability of
-“learning-to-learn” (Collis, 1994)).
-
-\emph{H4: Deliberate learning has a direct positive effect on changes in dynamic
-  capabilities over time}
-
-Dynamic capabilities enables firms to adapt better to changing environments
-\citep{Teece1997} and hence creating strategic change in terms of purposefully changing
-operational routines \citep{Helfat2007}. Thus, firms with well-functioning DC would be
-able to utilize more instances of change and thus more opportunities for learning
-(ref). Consequently, high DC leads to more opportunities for both ad-hoc and deliberate
-learning to take place and disclose the demand for investments in methods for systematic
-experiential learning. As deliberate learning emphasizes a purposefulness of learning by
-focusing “on the effect of planned processes for acquiring, codifying, and transferring
-existing knowledge within and between organizations” \citep[p. 1160]{Arthur2005}, many
-opportunities generated from enhanced DC should lead to more investments in learning
-systems. This notion is also supported by previous work emphasizing that doing more of the
-same over time leads experience accumulation and hence improved outcomes
-\citep{Zollo2004a}. Similarly, by being active in changing its resource base firms
-accumulate experience and the importance of deliberate approaches to leading will become
-more apparent. A related point is that when the number of opportunities for learning
-increases due to higher DC, the incentives for the firm to invest in DL increases due to
-potential intensified agency problems \citep{Arthur2005}. The more potential for
-knowledge accumulation through learning, the higher potential for misaligned incentives
-between workers keeping information back in fear of not being sufficiently compensated,
-and management. Hence, the incentive for the firm to invest in DL to better align these
-incentives, increases (ibid). In sum these arguments shape an interesting hypothesis on
-the feedback loop between DL and DC and how DL could be an outcome as well as an
-antecedent of DC \cite{Schilke2018}.(HERE WE ALSO HAVE A DIRECT QUOTE).
-
-\emph{H5: Dynamic capabilities enhances demand for systematic learning so investments in
-  deliberate learning abilities will increase over time.}
+and development trajectory \citep{Romme2010,Zollo2002a}.
 

### 2019-09-05 article4_analysis.r

@@ -93,12 +93,13 @@ zw$or1 <-  rowMeans(zw[,c("Q5.1_t1", "Q5.2_t1", "Q5.3_t1", "Q5.4_t1", "Q5.5_t1",
 zw$dl1 <-  rowMeans(zw[,c("Q8.1_t1", "Q8.2_t1", "Q8.3_t1" , "Q8.4_t1" , "Q8.5_t1", "Q8.6_t1")], na.rm=TRUE)
 zw$dyn <-  rowMeans(zw[,c("Q27", "Q27a", "Q27b", "Q27c", "Q27e", "Q27g")], na.rm=TRUE)
 
+
 Zw$ddc <- as.double(zw$dc1-zw$dc0)
 zw$dor <-  zw$or1-zw$or0
 zw$size <- zw$Q1_t1
 zw$age <- zw$Q2_t1
-zw$dynhigh <- ifelse(zw$dyn > 6, 1,0)
-zw$dynstable <- ifelse(zw$dyn < 6, 1,0)
+zw$dynhigh <- ifelse(zw$dyn > 4, 1,0)
+zw$dynstable <- ifelse(zw$dyn < 4, 1,0)
 
 zw$normdyn <-  scale(zw$dyn)
 ## Adjusting data set by removing NA for pm
@@ -162,11 +163,39 @@ summary(med.out1) ## ADE is insignificant telling us that DL has no direct effec
 
 mod3 <- lm(dc1 ~ dc0 + dl + size + age + dyn + pm + lassets, data=zw);summary(mod3)
 mod4 <- lm(ca1 ~ ca0 +  dc0 + ddc + size + age + dyn + pm + lassets, data=zw);summary(mod4)
-mod5 <- lm(ca1 ~ ca0 +  dc0 + ddc + or0 + dor + size + age + dyn + pm + lassets, data=zw);summary(mod5)
-mod5m <- lm(dor ~ ca0 + ddc + or0 + dl + dc0 + size + age + dyn + pm + lassets, data=zw);summary(mod5m)
+mod5 <- lm(ca1 ~ ca0 +  dc0 + dc1 + or0 + dor + size + age + dyn + pm + lassets, data=zw);summary(mod5)
+mod5m <- lm(dor ~ ca0 + dc1 + or0 + dl + dc0 + size + age + dyn + pm + lassets, data=zw);summary(mod5m)
 
-med.out5 <- mediate(mod5m,mod5, treat="ddc",mediator="dor",robustSE=TRUE, sims=1000)
[…]

### 2019-09-09 article4_notes.tex
added theory and hypotheses take 1

The other path, the market path, is characerized by smaller routines and practices that
themselves are not satisfying the VRIO condition (preciclsy as argued by EM). However, in
factor markets  
simple routines and complex processes can lead to comp

Market path: simple rules guiding actions in markets for aquistion of assets. Not
themselves VRIO, but taken together with the assets they aquire more idiosyncratic to the
firm. These simple rules are routines and they corresponds to rapid changes and the rear
wheel. mor profound in dynamic environments
Eisenhardt and Sull (2001) credited its prowess in this arena to the simple rules that Cisco has developed to guide its acquisition process. Cisco

Evolutionary path: More complex rules and process working to change the operational
routines of the firm. These are themselves idiosyncratic and VRIO (vrio stems from the DC
level and hence generates path dependent routines at theOR level. Corresponds to more
gradual change. the front crank / more gradual environments. More complex processes need
to work thorugh a mediation (OR). More simple rules works more directly (unobserved)

\cite{DiStefano2014} propose a metaphore to think of these paths to competetive
advantage through the idea of the "organizational drivetrain".

The interplay prposed by DiStefano

We find that DC as routines to shape routines is most prevelant under moderate dynamism,
whereas DC as routines to capture resources in factor markets are more prevelant under
dynamic environments.

Under certain conditions the DC operates through changing underlying routines. OTher times
they work through factor markets such as EM and the Cisco case.

Routinization indicates the extent to which organizational pro- cesses are stable and repetitive (Nelson &Winter, 1982) and constitutes an important revelatory access to the nature of dynamic capabilities (Barney & Felin, 2013). The sub-stream around Teece et al.’s (1997) seminal work largely argues that dynamic capabilities rely on highly rou- tinized processes, whereas the sub-stream around Eisenhardt and Martin's (2000) conceptualization argues for reduced routinization (Peteraf et al., 2013; Schreyögg & Kliesch-Eberl, 2007)

Start with two contradictory definitions:
Kale and Singh (2007, p. 982) ex- plained that “dynamic capability refers to the capac- ity of an organization to purposefully create, extend, or modify its resources or skills.”

Zollo and Winter (2002, p. 340) explained that “a dynamic capability is a learned and stable pattern of collective activity through which organizations systematically generate and modify operating rou- tines for improved effectiveness.”

One contentious issue surrounding the DC theory is the extent to which differing
views on the nature of dynamic capabilities \citep{Peteraf2013}. One strand of
contributions sees DC as routines that are simple in nature and more as best practices to
consider (EM). Thus, dynamic capabilities are more like behavioral patterns and
less idiosyncratic to the firm and will consequently not be able to satisfy the VRIO
condition for competitive advantage to emerge. These routines are

On the other hand, a stream of contributions see dynamic capabilities as evolutionary and
more complex routines (Ref) or processes (ref) set to change underlying capabilities in
the face of changing conditions (TPS).

CA RESULT OF DYNAIMC BUNDLE
to the socially complex and hard-to- imitate dynamic bundle of resources and capabili- ties (Peteraf et al., 2013) whose

Market path: simple rules guiding actions in markets for aquistion of assets. Not
themselves VRIO, but taken together with the assets they aquire more idiosyncratic to the
firm. These simple rules are routines and they corresponds to rapid changes and the rear
wheel. mor profound in dynamic environments
Eisenhardt and Sull (2001) credited its prowess in this arena to the simple rules that Cisco has developed to guide its acquisition process. Cisco

Evolutionary path: More complex rules and process working to change the operational
routines of the firm. These are themselves idiosyncratic and VRIO (vrio stems from the DC
level and hence generates path dependent routines at theOR level. Corresponds to more
gradual change. the front crank / more gradual environments. More complex processes need
to work thorugh a mediation (OR). More simple rules works more directly (unobserved)

On the notion of observability we can observe changes in underlying routines (OR) whereas
it is harder to observe routines generating opportunities in the market (dircet route)

Eisenhardt and Sull (2001) credited its prowess in this arena to the simple rules that
Cisco has developed to guide its acquisition process. Cisco

As an answer to the call for more nuanced theorizing on the differing role of dynamic
capabilities in shaping competitive advantage, and their contingencies
\citep{Peteraf2013}, \cite{DiStefano2014} propose theoretical model distinguishing between
rapid and routinized changes on the one hand, and slower, less routinized changes on the
other. Using the "organizational drive train" metaphor

The nature of DC: 
The fundamental difference between these two conceptions is related to the degree of observabil- ity. Action that is latent cannot be observed until called into use, while constituent elements have a more concrete and observable form (Helfat, Finkel- stein, Mitchell, Peteraf, Singh, & Winter, 2007). This has implications for the empirical identifica- tion of dynamic capabilities and suggests some of the challenges involved

DC as enabling device (latent) and as process (observable THROUGH changes in OR).

%Latent action / process vs routine - can be both??
 %% Interestingly, the distinction be- tween dynamic capabilities as an ability versus dy- namic capabilities as a process dates back to the two seminal manuscripts, with TPS advocating the former position and EM supporting the latter.

DRIVE TRAIN EXPLAINED

%% Given the extent and import of these differences
%% in the seminal views, how then can we bring them together fruitfully? Our answer is that we can do so by broadening our perspective to see the two views as each focused on a different part of a larger, interconnected, and more fully dynamic system.

We claoim, contrary to Di Stefano, that the two mechanisms in the drive train yields
differing results. The simple rules tend to only yield CA when they can operate in factor
markets to capture unique compistiosn of resources - ie.e their CA stems from their
ability to systematiclally find resrources in factor markets needed to adapt to
change. these resoures nor the routines themselves are sufficiently VRIO, but taken
together they form a powerful lever for change (increaseing or decreasing power from the
crankset).

OTHER METAPHOR: HYBRID CAR
Running electric motor in the gradual environment building speed continuosly (changing
rountines and hence moving more like a process.

ROLE OF DYN:
Last, our conception of an organizational drive-
train also suggests a resolution to the debate over whether dynamic capabilities in high-velocity en- vironments can go beyond managing change to also provide a sustainable competitive advantage. In this respect, we note that even if specific simple rules are unstable and ephemeral, the system as a whole is not. Moreover, the interconnectedness, reliance on tacit knowledge, and complexity of a system involving a variety of moving parts suggest that the real source of sustainable competitive ad- vantage for an enterprise is the difficulty of imitat- ing and substituting for the entire dynamic bundle (Peterafthat the system represents.

Previous work has highlighted the role of higher-order capabilities in a way that is
consistent with the idea of a dynamic bundle \citep{Schilke2014a}. This concept of higher-r
The view of the organiza- tional drivetrain is also consistent with works that tend to conceive dynamic capabilities as higher- order capabilities because it helps with envisioning different types of linkages between higher-order capabilities and organizational routines (see Kahl, 2014 and Schilke, 2014).

### 2019-09-09 article4_tommylars.rnw
added theory and hypotheses take 1

@@
 \begin{abstract}
-  Despite considerable interest from the research community the theory of dynamic
-  capabilities is still very much evolving. Several recent literature reviews demonstrate
-  the need for better understanding of the antecedents and outcome of dynamic
-  capabilities. Building on a much cited theoretical framework developed by
-  \cite{zollo2002} and longitudinal dataset of Norwegian technology firms, we explore
-  the role of learning as an antecedent to dynamic capabilities, and relates this to the
-  outcome of dynamic capabilities themselves.
+ We find that DC as routines to shape routines is most prevelant under moderate dynamism,
+whereas DC as routines to capture resources in factor markets are more prevelant under
+dynamic environments.
 
@@
 \section{Introduction}
+In a recent "state of the art" literature review on dynamic capabilities
+\cite{Schilke2018} state that much of the attention and interest surrounding the theory is
+that it offer a route to competitive advantage which they argue is "the virtual Holy Grail
+of strategic management" (p. 393). And indeed a considerable body of the extant literature
+concerns itself with exactly this path to competitive advantage (refs from
+shcilke). Still, a discourse regarding the contingencies of the dynamic
+capabilities-competitive advantage (DC-CA) nexus (?) has panned out in the literature,
+most notably coined "the elephant in the room" \citep{Peteraf2013}: Under which conditions
+will dynamic capabilities lead to competitive advantage?
 
-Dynamic capabilities are proposed to confer a competitive advantage by adding unique value to the firm through systematic change, which enhances operational efficiency and enables increased alignment with the environment (Di Stefano et al., 2014; Peteraf et al., 2013)
+\cite{Peteraf2013} argue that the seminal papers in the dynamic capabilities theory
+tradition (\cite{Teece1997} and \cite{Eisenhardt2000}) differ considerably in their view
+of to what extent the DC-CA nexus exist and under what conditions it is functional. A key
+tenant of this discourse is related to the level of routinization and the ability to
+satisfy the VRIO condition \citep{Barney1991a} of the resource-based view
+\citep{Peteraf2013}.
 
-Not all organizations possess them (Collis, 1996); their path dependencies, intangibility, complexity, and organizational specificity make them hard to imitate (Gibson & Birkinshaw, 2004; Helfat & Winter, 2011); and few other means allow organizations to purposefully change on a continuous basis (Day & Wensley, 1988; Helfat et al., 2007).
+In this paper we aim to contribute to dissecting the elephant by asking how does the DC-CA
+nexus differ between firms and what determines these differences?
 
-Consistent with the theoretical positions of Eisenhardt and Martin (2000), Helfat and Peteraf (2003), Zahra et al.
+We do this by exploring two paths from dynamic capabilities to competitive advantage: the
+\emph{evolutionary path} and the \emph{market path}. The former is thoroughly described
+and explored in the literature (refs) and stems from the core idea of the dynamic
+capabilities theorizing. In this path dynamic capabilities work to change the operating
+routines of the firm and hence contributing to it's competitive advantage. We argue that
+this path is more suited for less dynamic environments because of its path dependent
+functioning.
+
+The \emph{market path} works not through shaping operational capabilities and routines,
+but by enabling the firm to act in factor markets for new capabilities and
+resources. Hence, it is less path dependent and can be more rapidly
+deployed. Consequently, it is more prevalent in dynamic environments.
+
+This paper contributes to the extant literature on the link between dynamic capabilities
+and competitive advantage in three ways. First, provides an empirical test to the
+drive-train model of \cite{DiStefano2014} on how dynamic capabilities can operate both
+quickly and with high frequency more directly on the strategic direction of the firm by
+acting in factor markets for important resources, and also more slowly through the
+evolutionary path of changing operational capabilities. Second, by conceptually clarifying
+the different paths to competitive advantage by linking it closely to the role of
+capability evolution and the VRIO condition. Finally, we.........
+
+CLARIFIES THE ROLE OF THE ENVIRONMENT AND MEDIATIONS HAPPENING
+
+%% How does dynamic capabilities lead to competitive advantage? 
+%% Dynamic capabilities are proposed to confer a competitive advantage by adding unique value to the firm through systematic change, which enhances operational efficiency and enables increased alignment with the environment (Di Stefano et al., 2014; Peteraf et al., 2013)
+
+%% Not all organizations possess them (Collis, 1996); their path dependencies, intangibility, complexity, and organizational specificity make them hard to imitate (Gibson & Birkinshaw, 2004; Helfat & Winter, 2011); and few other means allow organizations to purposefully change on a continuous basis (Day & Wensley, 1988; Helfat et al., 2007).
+
+%% Consistent with the theoretical positions of Eisenhardt and Martin (2000), Helfat and Peteraf (2003), Zahra et al.
 (2006), and Zott (2003), among others, these researchers have argued that dynamic capabilities’ immediate purpose is to change the resource base, and that this change in the resource base, in turn, explains performance variations.
@@
 
-One of the major unresolved issues in dynamic capabilities theory is to what extent and
-how competitive advantage is the ultimate outcome of dynamic capabilities. This very idea
-has
+%% One of the major unresolved issues in dynamic capabilities theory is to what extent and
+%% how competitive advantage is the ultimate outcome of dynamic capabilities. This very idea
+%% has
 
-This paper asks two questions: to what extent does a direct lnk between DC and CA exist,
-and what determines variations in the role of mediation between them?
+%% This paper asks two questions: to what extent does a direct lnk between DC and CA exist,
+%% and what determines variations in the role of mediation between them?
 
-The idea that Dc impacts CA is uncontroversial (not). Little is known about how this
-happens. The theory holds that this happens through xreating extending and modifying the
-resource base. YEt, the change in firm capabilities can themselves lead to CA due to their
-evlutionary nature.
+%% The idea that Dc impacts CA is uncontroversial (not). Little is known about how this
+%% happens. The theory holds that this happens through xreating extending and modifying the
+%% resource base. YEt, the change in firm capabilities can themselves lead to CA due to their
+%% evlutionary nature.
 
-Variations in the share of mediation stems from variation sin the environment. When envdyn
-is high firms need to act faster and hence tends to choose strategies including resource
-orchestration buying in factor markets cause it tkes more time to develop OR.
+%% Variations in the share of mediation stems from variation sin the environment. When envdyn
+%% is high firms need to act faster and hence tends to choose strategies including resource
+%% orchestration buying in factor markets cause it tkes more time to develop OR.
 
-In less dynamism the role of OR increases and leads to a significant proportion of CA
-stemming throhg the mediating effect of OR
+%% In less dynamism the role of OR increases and leads to a significant proportion of CA
+%% stemming throhg the mediating effect of OR
 
-There is ongoing interest in (dynamic) capabilities and how they influence firm
-performance \citep{Fainshmidt2016a,Teece2014}. Indeed, \emph{dynamic capabilities} (DC),
-and its front runner, the resource-based view \citep{Barney2001,Helfat2007}, is now
-considered one of the major theories in strategic management
-\citep{Schilke2018}. Arguably, the key reason is that this theory clearly articulates how
-firms can alter their operating routines through dynamic capabilities. Thus, a key
-ingredient in this theory is that DCs can alter firms operating routines, with subsequent
-performance implications.
+%% There is ongoing interest in (dynamic) capabilities and how they influence firm
+%% performance \citep{Fainshmidt2016a,Teece2014}. Indeed, \emph{dynamic capabilities} (DC),
+%% and its front runner, the resource-based view \citep{Barney2001,Helfat2007}, is now
+%% considered one of the major theories in strategic management
+%% \citep{Schilke2018}. Arguably, the key reason is that this theory clearly articulates how
+%% firms can alter their operating routines through dynamic capabilities. Thus, a key
+%% ingredient in this theory is that DCs can alter firms operating routines, with subsequent
+%% performance implications.
 
-\section{Theory}\label{sec:theory}
-Firm capabilities can roughly be divided into two categories. First, ordinary capabilities
-(OR) “are directed toward maintaining and leveraging the status quo in terms of the scale
-and scope of activities, businesses, product lines, customer segments”
-\citep[p. 393]{Schilke2018}. In other words these capabilities are the ones who “permit a
-firm to ‘make a living’ in the short term” \citep[p. 991]{Winter2003}. On the other hand,
-dynamic capabilities (DC) are “those that operate to extend, modify or create ordinary
-capabilities” (ibid). DC theory is emerging as an important paradigm in strategic
-management research, but also facing some considerable challenges with respect to its
-antecedents and outcomes \citep{Eriksson2014,Schilke2018}, as well as its evolution
-and development trajectory \citep{Romme2010,Zollo2002a}.
+We demonstrate that two paths indeed do exist and that their relative importance varies
+with the degree of environmental dynamism facing the firm.
 
-\subsection{Direct and indirect outcomes of dynamic capabilities}
+\section{Hypotheses}\label{sec:hyp}
+
+%% We can use the drive train to determine hwo DC works differently under different levels of
+%% dynamism. It is not that DC does not work under stable conditions as EM claims. Is only
+%% that the effect runs stringer through the evolutionary path. Whereas the market path is
+%% stringer under higher dynamism
+
+One contentious issue surrounding the DC theory is the extent to which differing views on
+the nature of dynamic capabilities \citep{Peteraf2013} as well as their outcome. One
+strand of contributions sees DC as routines that are simple in nature and more as best
+practices to consider (EM). Thus, dynamic capabilities are more like behavioral patterns
+and less idiosyncratic to the firm and will consequently not be able to satisfy the VRIO
+condition for competitive advantage to emerge. Dynamic capabilities as such routines are
+short lived, unstable and “substitutable” (EM: 1110) thus violating a key VRIN condition,
+and they are more “more homogeneous (..) than is usually assumed” (EM: 1116). However, the
+simplicity of simple rules also makes them faster do deploy and put in motion, albeit
+potentially unstable. To the extent dynamic capabilities manifest themselves as simple
+rules they cannot alone create competitive advantage, but could very well generate
+strategic change by facilitating acquisition of resources in factor markets. One example
+is the role of post-acquisition routines where routines to identify and deal with
+acquisition partners are a source of generating strategic change (Eisenhardt and Sull
+2001, ref). Another example is (see refs from Schilke 2018). The functioning of this
+expression of dynamic capabilities are more latent and hence mainly observable ex
+post. Hence we can see this as direct route to competitive advantage as this expression of
+dynamic capabilities work directly in the factor market in capturing resources
+needed for strategic change. We coin this direct connection as the \emph{market path}.
+
+On the other hand, a stream of contributions see dynamic capabilities as evolutionary and
+more complex routines (ref) or processes (ref) set to change underlying capabilities in
+the face of changing conditions (TPS). This notion stems from evolutionary economics
+\citep{Winter2003,Nelson1982} and the behavioral theory of the firm \citep{Cyert1963}
+holding that path dependency and complex processes for changing underlying operating
+routines are a source of competitive advantage for the firm. Along this indirect path
+change is gradual and running through changes in underlying routines. We coin this the
+\emph{evolutionary path}.
+
+These paths from dynamic capabilities to competitive advantage are different expressions
+of dynamic capabilities with different mediums of intermediation. The \emph{market path}
+works in the market and his hence not typically altering lower order capabilities and
+resources in the firm directly, but rather acquiring new ones. The source of competitive
+advantage along this path stems from the interaction with the other, \emph{evolutionary
+  path} in a dynamic bundle \citep{Peteraf2013}. Such interactions create a bundle of
+capabilities and routines that are socially complex and hard to imitate
+\citep[p. 320]{DiStefano2014}. Moreover, the interactions between the two paths of dynamic
+capabilities is separable with respect to what intermediation exist. Consequently,
+separate paths exist albeit a part of a dynamic bundle.
+
+\cite{DiStefano2014} propose an integrated framework where simple routines and more
+complex processes could contribute simultanously to the firms outcome, specifically its
+competitive advantage. In this framework, coined the "organizational drivetrain" the
+authors envision the movement of an organization as set in motion by a drivetrain system
+not unlike that of a bicycle.
+
+Building on the notion of an organizational drivetrain we argue that dynamic capabilities
+can indeed impact the organizational movement or change through two distinct but
+interconnected mechanisms (i.e. the crank set and the rear shifter). The two mechanisms
+consitutting the drivetrain is consistent with our notion of \emph{evolutionary path} and the \emph{market path}. The
+evolutionary path is instigated by more complex processes setting in motiong a chance in
+the lower order (operational) routines \cite{Collis1994,Winter2003}. In the drivetrain
+metaphor this path corresponds to change stemming from the front crank set of thich there
+are fewer gears, but with larger impact. This path is slower
+and yields a more idiosyncratic set of organizational routines which is very much in line
+with the idea put forth in the seminal founding papers \citep{Teece1997,Winter2003}.
+
+Seeing the bike rider and her efforts to handle the levers of control (i.e. the gear
+shifter) as the dynamic capability, and consider it not only as a management effort, but
+that of the organization as a whole. The process of changing front gears are more profound
+(i.e. evolutionary) and costly, and it is for larger and slower strategic
+changes. Operating with simple routines in factor markets, however, is quicker and the
+rider does this on a more frequent basis with less effort.
+
+H1: Dynamic capabilities works to create competitive advantage through two distinctly
+different paths.
+
+\subsection{The two paths of dynamic capabilities}
 The objective of strategic change is to enhance a firm’s competitive advantage
-(ref). Doing so over time makes for the evolutionary fitness of the firm \citep{Helfat2007}. When firms
-are developing capabilities for strategic change through creating, extending and modifying
-the resource base this means making decisions to develop operational routines. Such
-routines can in turn stem from an inherent learning process evolutionary distinct to the
-firm. OR can thus lead to competitive advantage because of their evolutionary character
-\citep{Nelson1982,Winter2003}. To the extent OR stems from idiosyncratic
-evolutionary process of individual firms rather than being the result of investments in
-factor markets, they can satisfy the VRIO condition and thus be a source of competitive
-advantage. In such instances, DC works through OR in creating CA. This indirect impact on
-CA is very much at the core of the DC literature (ref). Firms with high DC will be able to
-better change operating routines to facilitate strategic change in response to changing
-conditions facing the firm. DC then creates VRIO OR and hence CA. When this happens, firms
-improves their OR and the OR itself satisfies the VRIO condition.
+(ref). Doing so over time makes for the evolutionary fitness of the firm
+\citep{Helfat2007}. When firms are developing capabilities for strategic change through
+creating, extending and modifying the resource base this means making decisions to develop
+operational routines. Such routines can in turn stem from an inherent learning process
+evolutionary distinct to the firm. Operating routines can thus lead to competitive
+advantage because of their evolutionary character \citep{Nelson1982,Winter2003}. To the
+extent operating routines stems from idiosyncratic evolutionary process of individual
+firms rather than being the result of investments in factor markets, they can satisfy the
+VRIO condition and thus be a source of competitive advantage. In such instances, dynamic
+capabilities work through operating routines in creating competitive advantage. This
+indirect impact on competitive advantage is very much at the core of the DC literature
+(ref). Firms with high dynamic capabilities will be able to better change operating
+routines to facilitate strategic change in response to changing conditions facing the
+firm. Dynamic capabilities then creates VRIO operating routines and hence competitive
+advantage. When this happens, firms changes their operating routines in a evolutionary
+making operating routines themselves OR itself satisfies the VRIO condition.
 
-\emph{H6a: Operating routines mediates the effect of dynamic capabilities in generating
-competitive advantage.}
+\emph{H2: Dynamic capabilities has an indirect effect on competitive advantage through
+  changing the operating routines of the firm.}
 
@@
 systematic resource orchestration (ref), i.e. reshaping the resource mix to obtain
-coordinated resource deployments \citep{Kor2005,Pan2006}, they would indeed have
-potential performance implications for the firm. Moreover, when this process of resource
-acquisition process of DC develops a way to acquire and mix resource for the purpose of
-adapting to change, the resources themselves would not necessarily satisfy the VRIO
-condition. The way in which this happens may be much harder to imitate due to the
-complexities such routines exhibit. Although resources themselves exhibit clear
-equifinality in their impact on competitive advantage, the complex routines of the
-orchestration (i.e. dynamic capabilities) would likely satisfy the VRIO condition. In
-other words, there are several ways in which resources can be orchestrated to generate CA,
+coordinated resource deployments \citep{Kor2005,Pan2006}, they would indeed have potential
+performance implications for the firm. Moreover, when this process of resource acquisition
+process of DC develops a way to acquire and mix resource for the purpose of adapting to
+change, the resources themselves would not necessarily satisfy the VRIO condition. The way
+in which this happens may be much harder to imitate due to the complexities such routines
+exhibit. Although resources themselves exhibit clear equifinality in their impact on
+competitive advantage, combined with the simple routines of the orchestration
+(i.e. dynamic capabilities), the sum would likely satisfy the VRIO condition. This is
+especially true if routines are deployed rapidly in changing market conditions. In other
+words, there are several ways in which resources can be orchestrated to generate CA,
 whereas improved OR will always mean improved competitiveness et ceteris paribus. In such
@@
 
-\emph{H6b: Dynamic capabilities has a direct effect on competitive advantage through the process
-of resource orchestration and acquisition of resources in factor markets.}
+\emph{H3: Dynamic capabilities has a direct effect on competitive advantage through the
+  process of resource orchestration and acquisition of resources in factor markets.}
 
-In other words, we would expect DC to have both a direct and an indirect impact on
-CA. Although both the direct and the indirect path stems from DC creating, extending and
-modifying the resource base (OR or factor market resources), the difference in the path’s
-stems from to what extent the mediating construct can itself satisfy the VRIO
-condition. OR can, due to their evolutionary nature, in turn shaped by DC, achieve CA
-\citep{Collis1994,Winter2003}. Factor market resources and market acquired capabilities and
-best practices can not \citep{Eisenhardt2000,Peteraf2013}.
+In other words, we would expect DC to have both a direct and an indirect impact on CA. The
+indirect impact stems from the \emph{evolutionary path} of complex processes, whereas the
+direct impact stems from the \emph{market path}.  Although both the direct and the
+indirect path stems from DC creating, extending and modifying the resource base (OR or
+factor market resources), the difference in the path’s stems from to what extent the
+mediating construct alone can by itself satisfy the VRIO condition. Operating routines
+can, due to their evolutionary nature, in turn shaped by DC, achieve CA
+\citep{Collis1994,Winter2003}. Factor market resources and market acquired capabilities
+and best practices can not \citep{Eisenhardt2000,Peteraf2013}, but in conjuncture with the
+routines of acting in factor markets as well as the speed of deployment, the sum of
+dynamic capabilities and factor market action would lead to competitive advantage.
+
+However, the interlinkages between simple routines (the market path) and the coplex
+processes (the evolutionary path) would vary with the environment.
+
+\subsection{Interplay under environmental dynamism}
+
+\cite{DiStefano2014} note that "even if specific simple rules are unstable and ephemeral,
+the system as a whole is not" and that the "real source of sustainable competitive ad- vantage for an enterprise is the difficulty of imitating and substituting for the entire dynamic bundle that the system represents" (p.sss).
+
+But the interlinkages between the parts of the system (the evolutionary- and the market
+path), are likely to vary with the environmental dynamism. Under moderatly dynamism
+dynamic capabilities takes the form of best pracitces (e.g. aquisition targeting) and is
+less important than under more dynamic environments. However, albeit best practices, the
+way they are implemented in the factor markets are still idiosyncratic. And taken into
+conjunction with the routinzed process of changing underlying routines, VRIO will very
+likely emerge under more stable conditions. It is not that the market/direct expression
+of dynamic capabilities are not present in stable environments, rather it is less pronounced and the indirect
+mediated effect (evolutionary path) is more important. In other words, it is not neither
+nor, but degrees of importance.
+
+Moreover, in high velocity environments the role of the evolutionary path tends to
+weaken as such path-dependent changes occur slower compared to the market path. From the
+market path with its simple routines we can argue that creation of "new knowledge” to
+“allow for emergent adaptation” (EM, p. 1116) is the consequence. Consequently, the market
+path is stronger and more prevalent under higher levels of environmental dynamism.
+
+\emph{H4: Dynamic capabilities works relatively stronger through the market path in highly
+dynamic environments.}
 
 \begin{figure}
-
-\begin{minipage}[t]{.5\textwidth}
   \centering
-  \includegraphics[width=0.9\linewidth]{./figure/fig1.png}
-  \captionsetup{width=0.9\linewidth}
-  \captionof{figure}{Conceptual relationship based on Zollo and Winter. Extensions in grey}
-  \label{fig:fig1}
-\end{minipage}%
-\begin{minipage}[t]{.5\textwidth}
-  \centering
-  \captionsetup{width=0.98\linewidth}
-  \includegraphics[width=0.98\linewidth]{./figure/fig2.png}
+  \captionsetup{width=0.5\linewidth}
+  \includegraphics[width=0.5\linewidth]{./figure/fig2.png}
   \captionof{figure}{Dynamic capabilities direct and indirect paths to competitive advantage determined by the VRIO condition}
   \label{fig:fig2}
-\end{minipage}
 \end{figure}
 
-Figure \ref{fig:fig1} sums up the hypothesis proposed in this section of our paper. The
-white boxes and black arrows represent the parts of the model that was originally proposed
-by \cite{Zollo2002a} whereas the grey parts are extensions based on more recent
-contributions to the field of dynamic capabilities. Figure \ref{fig:fig2} illustrates the
-two proposed paths through which DC affect competitive advantage. The main take away from
-this is that dynamic capabilities can affect CA through changing operational routines that
-by themselves can satisfy the VRIO condition by means of their evolutionary nature. Thus,
-we hypothesize that operating routines mediates the relationship between DC and CA – the
-indirect path. Conversely, the same DC enable the firm to identify resources and
-capabilities in factor markets that are less idiosyncratic and often takes the shape of
-best practices that are definitely imitable and thus bot VRIO. In such instances, the VRIO
-condition is satisfied by the DC itself through its complex process of orchestrating and
-mixing resources – the direct path.
+Figure \ref{fig:fig2} illustrates the two proposed paths through which DC affect
+competitive advantage. The main take away from this is that dynamic capabilities can
+affect CA through changing operational routines that by themselves can satisfy the VRIO
+condition by means of their evolutionary nature. Thus, we hypothesize that operating
+routines mediates the relationship between dynamic capabilities and competitive advantage
+the evolutionary path. Conversely, the same dynamic capabilities enable the firm to
+identify resources and capabilities in factor markets that are less idiosyncratic and
+often takes the shape of best practices that are definitely imitable and thus bot VRIO. In
+such instances, the VRIO condition is satisfied by the DC itself through its complex
+process of orchestrating and mixing resources – the market path.
 
 \section{Data and methods}
-An empirical test of the Zollo \& Winter model necessitates a certain time span of
-observations in order to enable the study of dynamics over time. The lack of such
-longitudinal studies to investigate dynamics has also been a permanent limitation for
-moving the DC literature forward empirically and theoretically \cite{Schilke2018}. To
-remedy this gap in the literature and to investigate the empirical characteristics of the
-Zollo \& Winter model we sampled a subset of Norwegian technology firms ($N=241$) over two
-time periods.
+
+To test the relationships between dynamic capabilities and competitive advantage we need a
+proper metric of both. We also benefit vastly from studying the same firms over time.  The
+lack of h longitudinal studies to investigate dynamics over time and control for path
+dependency of organizational routines has been noted as permanent limitation for moving
+the DC literature forward empirically and theoretically \cite{Schilke2018}. To remedy this
+gap in the literature and to investigate the empirical characteristics of the Zollo \&
+Winter model we sampled a subset of Norwegian technology firms ($N=241$) over two time
+periods.
 

### 2019-09-09 article4_analysis.r

@@ -182,13 +182,13 @@ zwlow <- subset(zw,zw$dynhigh==0)
 nrow(zwhigh)
 nrow(zwlow)
 
-mod5 <- lm(ca1 ~ ca0 +  dc0 + dc1 + or0 + dor + size + age  + dyn+ pm + lassets, data=zwhigh);summary(mod5)
-mod5m <- lm(dor ~ ca0 + dc1 + or0 + dl + dc0 + size + age + dyn+pm + lassets, data=zwhigh);summary(mod5m)
+mod5 <- lm(ca1 ~ ca0 +  dc0 + dc1 + or0 + dor + size + age  + pm + lassets, data=zwhigh);summary(mod5)
+mod5m <- lm(dor ~ ca0 + dc1 + or0 + dc0 + size + age + dyn + pm + lassets, data=zwhigh);summary(mod5m)
 
 med.out5hi <- mediate(mod5m,mod5, treat="dc1",mediator="dor",robustSE=TRUE, sims=1000)
 
-mod5 <- lm(ca1 ~ ca0 +  dc0 + dc1 + or0 + dor + size + age  + dyn+ pm + lassets, data=zwlow);summary(mod5)
-mod5m <- lm(dor ~ ca0 + dc1 + or0 + dl + dc0 + size + age  + pm + dyn + lassets, data=zwlow);summary(mod5m)
+mod5 <- lm(ca1 ~ ca0 +  dc0 + dc1 + or0 + dor + size + age  + pm + lassets, data=zwlow);summary(mod5)
+mod5m <- lm(dor ~ ca0 + dc1 + or0  + dc0 + size + age  + pm + lassets, data=zwlow);summary(mod5m)
 
 med.out5lw <- mediate(mod5m,mod5, treat="dc1",mediator="dor",robustSE=TRUE, sims=1000)
 summary(med.out5lw)
@@ -270,6 +270,12 @@ medmod5_shmed <- round(med.out5$n.avg,3) ## proportion of effect mediated
 
 
 
+
+### TESTING DC CONSTRUCT
+
+mod1 <- lm(ca1~ ca0 + pm + lassets + dc1 + or1 , data=zw);summary(mod1)
+mod1 <- lm(ca1~ + pm , data=zw);summary(mod1)
+
 ## Expoting to mplus
 mplusexport <- zw[,c("Q19","Q19a","Q19b","Q19c","Q19d","Q20d",
                      "Q19e","Q20b","Q25","Q20",
[…]

### 2019-09-21 article4_tommylars.tex
before cleanup and writeup

--- 2019-09-09 article4_tommylars.rnw
@@
 
-\documentclass[review,fleqn]{elsarticle}
+\documentclass[review,fleqn]{elsarticle}\usepackage[]{graphicx}\usepackage[]{color}
+% maxwidth is the original width if it is less than linewidth
+% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 \usepackage[textsize=tiny,colorinlistoftodos]{todonotes}
@@
 %%%%%%%
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 
-\title{Evolution of (dynamic) capabilities and its performance implications: An empirical test and extension}
+\title{Dynamic capabilities and competitive advantage}
 %\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
@@
 dependency of organizational routines has been noted as permanent limitation for moving
-the DC literature forward empirically and theoretically \cite{Schilke2018}. To remedy this
-gap in the literature and to investigate the empirical characteristics of the Zollo \&
-Winter model we sampled a subset of Norwegian technology firms ($N=241$) over two time
-periods.
+the DC literature forward empirically and theoretically \cite{Schilke2018}.
 
-We collected survey data from R\&D active firms in Norway at two points in time ($T_1=2005$
-and $T_2=2014$). The population was all businesses registered to a scheme for tax deduction
-of R\&D costs (called SkatteFUNN). As all enterprises which are eligible for taxation could
-register their R\&D activities to receive a tax refund, the registered enterprises include
-close to all enterprises which are involved in such activities at the time of our study.
+We collected survey data from R\&D active firms in Norway at two points in time
+($T_1=2005$ and $T_2=2014$). The population was all businesses registered to a scheme for
+tax deduction of R\&D costs (called SkatteFUNN). As all enterprises which are eligible for
+taxation could register their R\&D activities to receive a tax refund, the registered
+enterprises include close to all enterprises which are involved in such activities at the
+time of our study.
 
@@
 9 years later. The majority of firms were contacted in spring/summer 2014. All received a
-web-based questionnaire containing the same measures of DC, CA, OR and so on. 283 of the
-firms returned filled-in questionnaire.
+web-based questionnaire containing the same measures of the focal constructs of this
+paper. 283 of the firms returned filled-in questionnaire.
 
@@
 
-To control for survivor and non-response among our firms over time due to exogenous
-factors such as exit, bankruptcy and so on, we estimate a model Heckman correction (Hair,
-2010). Applied to the context of this paper, Heckman regression is a method that in the
-first step analyses the probability that a firm at $T_1$ will answer the survey at $T_2$
-depending on observables at $T_1$. This is modeled as a probit regression. Based on the
-probit regression in $T_1$, the inverse Mills ratio (sometimes called lambda) is added to the
-analysis in the second step where the goal is to analyze the relationship between our
-focal constructs (using regular OLS regression). The inverse Mills ratio is a control
-factor which controls for unobserved heterogeneity. More concretely, the inverse Mills
-ratio will control for unobserved factors that are related to both firms’ probability of
-answering the survey at $T_2$ (ref).
-
 \subsection{Variable construction}
 
-The focal constructs of this paper are deliberate learning, dynamic capabilities,
-operational routines and competitive advantage. These are all operationalized using the
-survey data described above. Table 1 below describes the items used to operationalize the
-focal constructs and their internal validity in forming an additive index (Cronbach´s
-alpha). The results show that our key constructs can be represented by the items in the
-survey.
+The focal constructs of this paper are dynamic capabilities, operational routines and
+competitive advantage. These are all operationalized using the survey data described
+above. Table 1 below describes the items used to operationalize the focal constructs and
+their internal validity in forming an additive index (Cronbach´s alpha). The results show
+that our key constructs can be represented by the items in the survey.
 
@@
 
-\text{red}{CONTINUE WITH THE OTHER KEY CONSTRUCTS – INPUT FROM TOMMY}
-
 \subsection{Control variables}
@@
 To test our hypotheses, we run a sequential linear regression with heteroskedastic robust
-standard errors and Heckmann two-step correction to control for attrition and survival
-bias (ref). We test the mediation hypotheses within this framework using a causal
-mediation \citep{Baron1986,MacKinnon2008} with quasi-Bayesian confidence intervals
-over a million simulations \citep{Imai2010}. The sequential regression
-model is presented chronologically in accordance with figure \ref{fig:fig1}. This entails that the
-dependent variable in one model will be the independent in the next to study the evolution
-of the proposed model sufficiently. The following models are estimated:
-
-\par\noindent
-\begin{align}
-  OR_{2,i} &= \beta_0 + \beta_1 OR_{1,i} + \beta_2 DL_{i} + \mathbf{\Gamma C_i} + \epsilon_i\\
-  OR_{2,i} &= \beta_0 + \beta_1 OR_{1,i} + \beta_2 DL_{i} + \beta_3 DC_{1,i} + \beta_4
-               \Delta DC + \mathbf{\Gamma C_i} + \epsilon_i\\
-  DC_{2,i} &= \gamma_0 + \gamma_1 DL_{1} + \gamma_2 DC_{1,i} + \mathbf{\Gamma C_i} + \upsilon_i\\
-  CA_{2,i} &= \lambda_0 + \lambda_1 CA_{1,i} +
-             \lambda_2 DC_{1,i} + \lambda_3 \Delta DC_i +\mathbf{\Gamma C_i}+ \mu_i \\
-  CA_{2,i} &= \lambda_0 + \lambda_1 CA_{1,i} + \lambda_2 OR_{1,i} + \lambda_3 \Delta OR_i
-             \lambda_4 DC_{1,i} + \lambda_5 \Delta DC_i +\mathbf{\Gamma C_i}+ \mu_i \\
-  DL_{i} &= \xi_0 + \xi_1 DC_{1,i} +\mathbf{\Gamma C_i}+ \nu_i
-\end{align}
-
-Here $ \mathbf{\Gamma C_i}$ represents a vector of control variables including size, age,
-dynamism, financial assets and profit margin. $\Delta DC_i$ is the change in $DC$ from
-$T_1$ to $T_2$. Similarly $\Delta OR_i$ represents the change in $OR$.
+standard errors. We test the mediation hypotheses within this framework using a causal
+mediation \citep{Baron1986,MacKinnon2008} with quasi-Bayesian confidence intervals and
+over a million simulations \citep{Imai2010}.
 
@@
 if OR mediates the effect of DC on CA, and if DC mediates the effect of DL on OR,
-respectively. The mediation equations for OR and DC respectively are state below:
-
-\begin{align}
- \Delta DC_i &= \alpha_0 + \alpha_1 OR_{1,i} + \alpha_2 DL_{i} + \mathbf{\Gamma C_i} + u_i \\
- \Delta OR_i &= \omega_0 + \omega_1 CA_{1,i} + \omega_2 \Delta DC_{i} + \omega_3 CA_{1,i} + \mathbf{\Gamma C_i} + v_i
-\end{align}
-
-Finally, we run a Heckman selection model with selecting in to the sample at time $T_2$ is
-determined by the following model:
-
-\begin{align}
-  P(R=1) &= \eta_0 + \eta_1 L_i + \eta_2 DC_{1,i} + \mathbf{\Gamma C_i} + m_i
-\end{align}
-
-$R$ is an indicator variable equal to 1 if the firm has responded at $T_2$ and 0 if
-not. $L_i$ is an indicator set to 1 if the person answering the survey is the managing
-director or CEO. This acts as an instrument for considering the probability of the firm
-selection into the sample, but without having any theorized relationship with the main
-outcome variables $DC$, $OR$, and $CA$. It is reasonable to assume that if the CEO was
-involved in answering the survey at $T_1$, would increase the probability of the firm
-answering at $T_2$ as well.
+respectively.
 
@@
 
-\begin{table}[t]
-\begin{singlespace}
-  \caption{\small Descriptive statistics and correlations for variables in this paper}
-  \label{tab:desc}
-
-<<resultscorr, results="asis",echo=FALSE >>=
-
-print(xtable(art2cor ,size="\\small",caption="Correlation matrix \\label{tab:cor}", align = c("l", rep("p{0.3in}",9)),table.placement="h", size = "\\small", tabular.environment="longtable"), size="scriptsize", label='tab:cor', caption.placement="top", floating=FALSE,latex.environments=NULL)
-
-@
-\vspace{1ex}
-
-     \raggedright {\scriptsize Notes: Pairwise correlations between variables in the study
-    excluding controls}
-\end{singlespace}
-\end{table}
-
-\begin{table*}[t]
-  \centering
-
-\caption{Regression -How are MDC influencing evolution of lower level capabilities }
-
-<<result1, results="asis", echo=FALSE >>=
-stargazer(mainres,
-          add.lines =list(c("Adjusted $R^2$",r1,r2,r3,r4,r5,r6)),
-          single.row=FALSE, column.sep.width = "1pt", omit.stat=c("LL","ser","f","aic","rsq","adj.rsq"),
-          no.space=FALSE,
-          dep.var.labels=c("OR_{T_2}", "DC_{T_2}","CA_{T_2}","DL"),
-        #  column.labels=c("HECKMAN","OLS","HECKMAN","OLS","HECKMAN","OLS"),
-          model.names=FALSE,
-          object.names=FALSE,
-
-          ### order=c(1,3,2),
-
-           ## covariate.labels= c("$OR_{T_1}$",
-           ##                "$\\Delta OR$",
-           ##                "$CA_{T_1}$"
-           ##                "$DL$",
-           ##                "$DC_{T_1}$",
-           ##                "$\\Delta DC$",
-           ##                "Firm size",
-           ##                "Firm age",
-           ##                "Environmental Dynamism",
-           ##                "Firm profit margin",
-           ##                "Firm assets"
-           ##          ),
-
-          title= "Regression results for model C", font.size="scriptsize",float=FALSE
-          )
-
-@
-\label{tab:reg}
-\end{table*}
-
-\begin{figure}[t]
-
-\begin{minipage}[t]{.5\textwidth}
-
-  \resizebox{7cm}{!}{\input{./figure/medanalysis1.tex}}
-  \captionof{figure}{Mediation analysis 1}
-  \label{fig:fig3}
-\end{minipage}%
-\begin{minipage}[t]{.5\textwidth}
- \resizebox{7cm}{!}{\input{./figure/medanalysis2.tex}}
-  \captionof{figure}{Mediation analysis 2}
-  \label{fig:fig4}
-\end{minipage}
-\end{figure}
-
 Table \ref{tab:reg} shows a summary of the regression models proposed in the previous
@@
 $DC$. Consider model 1 we observe that $DL$ is influencing the level of $OR$ within the
-firm ($\beta_2 =$ \Sexpr{mod1_dl}) supporting H1. However, the effect disappears when we
+firm ($\beta_2 =$ 0.325) supporting H1. However, the effect disappears when we
 add $DC$ in model 2 suggesting a mediating effect. In other words we see that firms with
-initial high $DC$($\beta_3=$ \Sexpr{mod2_dc0}) and increasing $DC$ over time ($\beta_4=$
-\Sexpr{mod2_ddc}) also have better $OR$. To control for the mediating effect suggested by
+initial high $DC$($\beta_3=$ -0.007) and increasing $DC$ over time ($\beta_4=$
+0.497) also have better $OR$. To control for the mediating effect suggested by
 the change in coefficients for $DL$ between models 1 and 2, we performed a causal
@@
 indications from models 1 and 2 showing that the direct effect from $DL$ on $OR$ is
-insignificant and small (ADE = \Sexpr{medmod1_ade}). Meanwhile, the indirect effect
+insignificant and small (ADE = 0.05). Meanwhile, the indirect effect
 running through changes in $DC$ over time, is significant yielding a positive and
-significant indirect effect of \Sexpr{medmod1_acme}. The proportion of the effect that is
-mediated amounts to \Sexpr{medmod1_shmed}. In sum these results suggest that H1 is
+significant indirect effect of 0.222. The proportion of the effect that is
+mediated amounts to 0.818. In sum these results suggest that H1 is
 unsupported, and that the bulk of the effect is indirect running through $DC$, in line with
@@
 \ref{tab:reg}. Controlled for the usual firm level controls we find a positive effect
-($\xi_1=$ \Sexpr{mod6_dc0}) from $DC_{T_1}$ on $DL$ measured at $T_1$. This supports H5
+($\xi_1=$ 0.913) from $DC_{T_1}$ on $DL$ measured at $T_1$. This supports H5
 suggesting that firms with more $DC$ is more likely to generate opportunities where it
@@
 operating routines can also be a source of advantage for the firm. Moreover, the
-coefficient of $\Delta DC$ decline from \Sexpr{mod4_ddc} to \Sexpr{mod5_ddc} when we add
+coefficient of $\Delta DC$ decline from 0.589 to 0.425 when we add
 $OR$. This suggests that some mediation is at work, i.e. that changes in $DC$ leads to
@@
 find added support that both a \emph{direct-} and an \emph{indirect} path exist to explain
-the relationship between $DC$ and $CA$ (ADE = \Sexpr{medmod5_ade}, ACME =
-\Sexpr{medmod5_acme}) and a total mediated share of \Sexpr{medmod5_shmed}.
+the relationship between $DC$ and $CA$ (ADE = 0.371, ACME =
+0.198) and a total mediated share of 0.347.
 
@@
 
-\begin{table}
-     \footnotesize
-  \centering
-\input{./figure/hyptab.tex}}
-\end{table}
-
 \section{Discussion}
-
-The objective of this article is to study the antecedents and outcomes of dynamic
-capabilities, particularly the role of deliberate learning in shaping dynamic capabilities
-over time. Learning is arguably an important determinant of firm success (ref arrow and
-more), and the deliberate investment in learning to learning (i.e. deliberate learning)
-has a long standing position as a theoretical antecedent of dynamic capabilities
-\citep{Zollo2002a,Eriksson2014,Schilke2018}. Furthermore, the role of deliberate learning
-in creating better operational routines is well established (ref), but it`s role in
-generating competietive advantage for the firm, is less understood. Alas, the main
-mechanism, the VRIO principle \citep{Barney1991a} is well known and still deemed highly
-relevant relevant in understanding the source of competitive advantage of the firm
-\citep{Priem2001}. Despite the prevalent and considerable citation of the
-\cite{Zollo2002a} model, neither an empirical analysis of the model propositions, nor it`s
-connection to outcomes such as competitive advantage has, to our knowledge, been
-undertaken.
-
-Our proposed extension of \cite{Zollo2002a} as depicted in figure \ref{fig:fig1}, taps
-into the debate on the most important \emph{antecedents} and \emph{outcomes} of dynamic
-capabilities \cite{Eriksson2014,Schilke2018}. Our results indicate that deliberate
-learning is indeed an important antecedent of dynamic capabilities. Firms with stronger
-capabilities for deliberate learning will develop higher levels of dynamic
-capabilities. Thus the deliberate decision to invest in systems for learning will lead to
-the evolution of better capacities to "purposefully create, extend, or modify its resource
-base" \citep[p. ###]{Helfat2007}. Indeed, this also follows from Zollo \& Winter`s
-definition where "a dynamic capability is a learned and stable pattern of collective
-activity through which the organization systematically generates and modifies its
-operating routines in pursuit of improved effectiveness" \citep[p
-###]{Zollo2002a}.
-
-The next step of figure \ref{fig:fig1} is to establish the link between deliberate
-learning and the operational routines of the firm. These operating routines are what
-\cite{Winter2003} calls "how we can earn a living now" (p. 992) or the technical fitness
-of the firm \citep{Helfat2007}. Such operational routines are the product of learning
-processes over time and should indeed be linked to deliberate learning of the firm as
-proposed by \cite{Zollo2002a}. However, we find that this direct effect between deliberate
-learning and operational capabilities disappear when we introduce dynamic capabilities into
-the model. This suggest that dynamic capabilities are evolving as a response to deliberate
-learning and, in turn, shaping operational capabilities in line with expectations of Zollo
-\& Winter. In other words, we find support for an indirect link between deliberate
-learning and operational routines, but no direct path.
-
-This finding may come from the fact that learning works differently at different levels of
-the capabilities hierarchy \citep{Collis1994}. Considering operational capabilities as
-zero-order capabilities \citep{Winter2003,Schilke2014a} defined as more "geared towards
-the operational functioning of the firm" \citep[p. 340]{Zollo2002a}, learning may be more
-ad-hoc and less routinized as experiences are accumulated "on the fly" or through
-"learning by doing" (ref) rather than deliberate and systematic. Indeed, learning by doing
-is established as a robust result in the empirical literature on it`s link to operational
-excellence (ref). When learning becomes deliberate and systematic through investments in
-learning to learn capabilities, this would not automatically strengthen the short term
-evolution of operational capabilities directly \citep{Arthur2005}. \todo{Need some more
-  references here}. These findings would also lend support to the notion of higher-order
-dynamic capabilities (capabilities to change dynamic capabilities)
-\citep{Collis1994,Winter2003,Schilke2014a} and that deliberate learning could be
-classified as such. In contrast, ad-hoc learning based on repetitive actions by employees
-does not satisfy the requirements for a dynamic capability as the actions are less
-strategic and purposeful.
-
-An interesting finding is also that deliberate learning itself could be seen as a function
-of dynamic capabilities. We argue that this stems from firms with high levels and
-evolution of dynamic capabilities will take more advantage of adapting to change and hence
-creating more opportunities for learning. This leads the firm to realize the need for
-more deliberate approach to systematic learning. Particularly, this would lead to more
-investments in systems for learning and, in turn, improvements in dynamic and operational
-capabilities. For obvious reasons this is a tough causal claim to make and we have little
-support for a causal argument. The insight will thus need considerably better data and
-empirical analysis going forward. However, it has some support in the literature where
-learning can be seen as an outcome as well as an antecedent to dynamic capabilities
-\citep{Schilke2018}. \todo{maybe add someting about the interaction with dynamism}
 
@@
 
-Our operational construst of $DC$ captures dynamic capabilities in
-a broad, non-functional, sense (e.g. as a broad-purpose capability rather than one for
-a particular purpose) \citep{Schilke2018}, and will hence capture a mind-set of the
-organization rather than a narrow set of learned capabilites. This makes our conclusions
-more general, albeit maybe less precise in predicting what investments in deliberate
-learning would nmean for important capacities such as new product development and
-innovation. 
- BLABLABLABLA
-
 \section{Bibliography}

### 2019-09-21 article4_analysis.r

@@ -7,7 +7,7 @@ source("./estimation/article_functions.r")
 require("MASS")
 library(sampleSelection)
 library(mediation)
-library(polycor)
+#library(polycor)
 
 ## This loads the data workspace where skattefunn_data.r is already loaded
 load("./data/art3base.RData")
@@ -63,16 +63,7 @@ zw$lassets <- log(zw$assets)
 
 
 
-
-
-
-
-
-
-
-
-
-
+### Creating variable for determining constant in respondent
 
 
 ## Creating variables
@@ -92,9 +83,9 @@ zw$or0 <-  rowMeans(zw[,c("Q21c", "Q21d", "Q21e", "Q22", "Q22a", "Q22b", "Q22c",
 zw$or1 <-  rowMeans(zw[,c("Q5.1_t1", "Q5.2_t1", "Q5.3_t1", "Q5.4_t1", "Q5.5_t1", "Q5.6_t1", "Q5.7_t1")], na.rm=TRUE)
 zw$dl1 <-  rowMeans(zw[,c("Q8.1_t1", "Q8.2_t1", "Q8.3_t1" , "Q8.4_t1" , "Q8.5_t1", "Q8.6_t1")], na.rm=TRUE)
 zw$dyn <-  rowMeans(zw[,c("Q27", "Q27a", "Q27b", "Q27c", "Q27e", "Q27g")], na.rm=TRUE)
+zw$ma <-  rowMeans(zw[,c("Q24","Q24a", "Q24b", "Q23b","Q23c")], na.rm=TRUE)
 
-
-Zw$ddc <- as.double(zw$dc1-zw$dc0)
+zw$ddc <- as.double(zw$dc1-zw$dc0)
 zw$dor <-  zw$or1-zw$or0
 zw$size <- zw$Q1_t1
 zw$age <- zw$Q2_t1
@@ -154,273 +145,84 @@ names(art2cor) <- c("Mean","SD",paste(seq(1:7),sep=","))
 art2cor
 
 
-## Regressions
-mod1 <- lm(or1 ~ or0 + dl +  size + age + dyn + pm + lassets, data=zw);summary(mod1)
-mod2 <- lm(or1 ~ or0 + dl + dc0 + ddc + size + age + dyn + pm + lassets, data=zw);summary(mod2)
-mod1m <- lm(ddc ~ or0 + dl + size + age + dyn + pm + lassets, data=zw);summary(mod1m)
[…]

### 2019-09-21 article4_analysis_bck.r

@@ -1,0 +1,1183 @@
+
+
+setwd("/Users/larshovdanmolden/Documents/git/article3")
+source("./estimation/packages.r")
+source("./estimation/article_functions.r")
+
+require("MASS")
+library(sampleSelection)
+library(mediation)
+library(polycor)
+install.packages("missForest")
+library(missForest)
+
+## This loads the data workspace where skattefunn_data.r is already loaded
+load("./data/art3base.RData")
+
+## Overall system settings
+options(digits=8)
+Sys.setlocale("LC_ALL", 'en_US.UTF-8')
+
+## Importing and cleaningemail address and the project number
+regdataraw = read.spss("./data/regdata_tommy.sav", to.data.frame=TRUE, labels=F)
+regdatazw <- regdataraw[,c("epost","prosjektnummer")] #could add ny_epost too
+regdatazw$epost <- str_trim(as.character(regdatazw$epost))
+names(regdatazw) <- c("email","pnr")
+
+## Importing Skattefunn data
+regdatasf <- sfmain[,c("Prosjektnummmer","Organisasjonsnummer")]
+names(regdatasf) <- c("pnr","orgnr") #orgnr is a unique identifier for each firm / same for pnr at project level
+datazw = read.csv("./data/skattefunn_10_clean.csv", sep=";",dec=",", header=T, na.strings="-1")
+
+md <- datazw[c("Resp","dc_t0","dc_t1")]
+md$Resp <- str_trim(as.character(md$Resp))
+colnames(md) <- c("email","dc0","dc1")
+
+## NB / regdf comes from skattefunn_data.r contains all projects, not only endreport
+matchvec <- match(md$email,regdf$email)
+regdata <- cbind(md,regdf[matchvec,])
+datazw <- cbind(datazw,regdata)
+
+## Splitting datazw in first wave and second wave
+zw0 <- data.frame(orgnr=datazw$orgnr);zw0$yr <- 2004
[…]

### 2019-09-21 article4_analysis.r
organizing factor loading table / not done

@@ -7,7 +7,9 @@ source("./estimation/article_functions.r")
 require("MASS")
 library(sampleSelection)
 library(mediation)
-#library(polycor)
+library(reshape)
+install.packages("reshape")
+                                        #library(polycor)
 
 ## This loads the data workspace where skattefunn_data.r is already loaded
 load("./data/art3base.RData")
@@ -66,163 +68,277 @@ zw$lassets <- log(zw$assets)
 ### Creating variable for determining constant in respondent
 
 
-## Creating variables
-sense0 <- rowMeans(zw[,c("Q19", "Q19a", "Q19b", "Q19c", "Q19d", "Q20d")], na.rm=TRUE)
-seize0 <- as.double(rowMeans(zw[,c( "Q19e", "Q20b", "Q19c", "Q25", "Q20")], na.rm=TRUE))
-tran0 <- as.double(rowMeans(zw[,c("Q20c", "Q25a", "Q25b", "Q25c")], na.rm=TRUE))
-zw$dc0 <- rowMeans(cbind(sense0,seize0,tran0),na.rm=TRUE)
+## ## Creating variables
+## sense0 <- rowMeans(zw[,c("Q19", "Q19a", "Q19b", "Q19c", "Q19d", "Q20d")], na.rm=TRUE)
+## seize0 <- as.double(rowMeans(zw[,c( "Q19e", "Q20b", "Q19c", "Q25", "Q20")], na.rm=TRUE))
+## tran0 <- as.double(rowMeans(zw[,c("Q20c", "Q25a", "Q25b", "Q25c")], na.rm=TRUE))
+## zw$dc0 <- rowMeans(cbind(sense0,seize0,tran0),na.rm=TRUE)
 
-sense1 <- as.double(rowMeans(zw[,c("Q6.1_t1","Q6.2_t1","Q6.3_t1","Q6.4_t1","Q6.5_t1","Q7.3_t1")], na.rm=TRUE))
-seize1 <-as.double(rowMeans(zw[,c("Q6.6_t1","Q7.1_t1","Q6.4_t1","Q7.5_t1","Q6.7_t1")], na.rm=TRUE))
-tran1 <- as.double(rowMeans(zw[,c("Q7.2_t1","Q7.6_t1","Q7.7_t1","Q7.8_t1")], na.rm=TRUE))
[…]

### 2019-09-21 article4_analysis_bck.r

@@ -1002,8 +1002,8 @@ items <- c(#"Q19a","Q19c", "Q20b", "Q20c", #DC01
            #"Q19b","Q19d","Q20d", "Q20e", #DC02
            "Q6.2_t1","Q6.4_t1", "Q7.1_t1","Q7.2_t1","Q6.5_t1", #DC1
            "Q6.3_t1","Q7.3_t1","Q7.4_t1", #DC1
-           "Q28","Q28a","Q28c", #CA0
-           "Q16.1_t1","Q16.2_t1","Q16.4_t1")#CA1
+           "Q28a","Q28b","Q28c", #CA0
+           "Q16.2_t1","Q16.3_t1","Q16.4_t1")#CA1
            #"Q21c","Q21d","Q21e", #OC0
            #"Q5.4_t1","Q5.6_t1","Q5.7_t1", #OC1
            #"Q8.7_t1", "Q8.8_t1", "Q8.9_t1")
@@ -1048,7 +1048,7 @@ semPLS::gof(ecsi)
 items <- c(#"Q19a","Q19c", "Q20b", "Q20c", #DC01
            #"Q19b","Q19d","Q20d", "Q20e", #DC02
            "Q6.2_t1","Q6.4_t1", "Q7.1_t1","Q7.2_t1","Q6.5_t1", #DC1
-           "Q6.3_t1","Q7.3_t1","Q7.4_t1", #DC1
+           "Q6.1_t1","Q6.3_t1","Q7.4_t1", #DC1
            "Q28","Q28a","Q28c", #CA0
            "Q16.1_t1","Q16.2_t1","Q16.4_t1", #CA1
            #"Q21c","Q21d","Q21e", #OC0
@@ -1082,7 +1082,7 @@ ecsi
 pathDiagram(ecsi, file = "ecsiStructure", full = FALSE, edge.labels = "both", output.type = "graphics", digits = 2,graphics.fmt="pdf")
 
 
-ecsiBoot <- bootsempls(ecsi, nboot = 200, start = "ones", verbose = FALSE)
+ecsiBoot <- bootsempls(ecsi, nboot = 500, start = "ones", verbose = FALSE)
 ecsiBoot
 
 semPLS::rSquared(ecsi)
@@ -1142,7 +1142,7 @@ semPLS::gof(ecsi)
 items <- c(#"Q19a","Q19c", "Q20b", "Q20c", #DC01
[…]

### 2019-09-22 article4_analysis.r
started to add table huxtable

@@ -8,7 +8,8 @@ require("MASS")
 library(sampleSelection)
 library(mediation)
 library(reshape)
-install.packages("reshape")
+library(huxtable)
+install.packages("huxtable")
                                         #library(polycor)
 
 ## This loads the data workspace where skattefunn_data.r is already loaded
@@ -218,13 +219,13 @@ pma1imp
 ## Running median imputations
 dc01 <-  imputezw(zwadj[,c("Q6.2_t1","Q6.4_t1", "Q6.5_t1","Q7.1_t1","Q7.2_t1")] )
 dc02 <-  imputezw(zwadj[,c("Q6.1_t1","Q6.3_t1","Q7.4_t1")] )
-ca0 <-  imputezw(zwadj[,c("Q28","Q28b","Q28c")] )
+ca0 <-  imputezw(zwadj[,c("Q28","Q28a","Q28c")] )
 ca1 <-   imputezw(zwadj[,c("Q16.1_t1","Q16.2_t1","Q16.4_t1")] )
 or1 <-   imputezw(zwadj[,c("Q5.4_t1","Q5.6_t1","Q5.7_t1")])
-ma1 <-  imputezw(zwadj[,c( "Q8.7_t1", "Q8.8_t1", "Q8.9_t1")])
-complist <- list(dc11=dc11,dc12=dc12,ca0=ca0,ca1=ca1,or0=or0,ma1=ma1)
+ma01 <-  imputezw(zwadj[,c( "Q8.7_t1", "Q8.8_t1", "Q8.9_t1")])
+complist <- list(dc01=dc01,dc02=dc02,ca0=ca0,ca1=ca1,or1=or1,ma1=ma01)
 vcontrols <- zwadj[,c("size","age","dyn","pm","lassets")]
-zwadj <- cbind(dc11,dc12,ca0,ca1,or0,or1,ma1,vcontrols)
+zwadj <- cbind(dc01,dc02,ca0,ca1,or0,or1,ma01,vcontrols)
 
 
 names(complist[[1]])
@@ -242,12 +243,12 @@ latents <- c(rep("DC01",5),
              rep("CA0",3),
              rep("CA1",3),
              rep("OR1",3),
-             rep("MA01",3))
+             rep("MA1",3))
 
 
 mm <- cbind(latents,items); colnames(mm) <- c("source","target")
-iv <- c("MA01","CA0","DC01","DC01","DC02","DC02","OR1","DC01","DC02")
[…]

### 2019-09-26 article4_tommylars.rnw
Before write up

@@
 \usepackage{subfig}
-\usepackage{caption}
 \usepackage{subcaption}
-\usepackage{filecontents}
+
 \input{preamble.tex}
@@
 \section{Introduction}
+
+\Sexpr{resest[1,2]}
 In a recent "state of the art" literature review on dynamic capabilities
@@
 
-\text{red}{CONTINUE WITH THE OTHER KEY CONSTRUCTS – INPUT FROM TOMMY}
+<<result1, results="asis", echo=FALSE >>=
+
+ht
+
+@
 
@@
 competitive environment facing the firm. A full list of items and their internal validity
-(0.75) is available in appendix ##.
+(0.75) is available in appendix 1111.
 
@@
 
-\begin{table}[t]
-\begin{singlespace}
-  \caption{\small Descriptive statistics and correlations for variables in this paper}
-  \label{tab:desc}
-
-<<resultscorr, results="asis",echo=FALSE >>=
-
-print(xtable(art2cor ,size="\\small",caption="Correlation matrix \\label{tab:cor}", align = c("l", rep("p{0.3in}",9)),table.placement="h", size = "\\small", tabular.environment="longtable"), size="scriptsize", label='tab:cor', caption.placement="top", floating=FALSE,latex.environments=NULL)
-
-@
-\vspace{1ex}
-
-     \raggedright {\scriptsize Notes: Pairwise correlations between variables in the study
-    excluding controls}
-\end{singlespace}
-\end{table}
-
-\begin{table*}[t]
-  \centering
-
-\caption{Regression -How are MDC influencing evolution of lower level capabilities }
-
-<<result1, results="asis", echo=FALSE >>=
-stargazer(mainres,
-          add.lines =list(c("Adjusted $R^2$",r1,r2,r3,r4,r5,r6)),
-          single.row=FALSE, column.sep.width = "1pt", omit.stat=c("LL","ser","f","aic","rsq","adj.rsq"),
-          no.space=FALSE,
-          dep.var.labels=c("OR_{T_2}", "DC_{T_2}","CA_{T_2}","DL"),
-        #  column.labels=c("HECKMAN","OLS","HECKMAN","OLS","HECKMAN","OLS"),
-          model.names=FALSE,
-          object.names=FALSE,
-
-          ### order=c(1,3,2),
-
-           ## covariate.labels= c("$OR_{T_1}$",
-           ##                "$\\Delta OR$",
-           ##                "$CA_{T_1}$"
-           ##                "$DL$",
-           ##                "$DC_{T_1}$",
-           ##                "$\\Delta DC$",
-           ##                "Firm size",
-           ##                "Firm age",
-           ##                "Environmental Dynamism",
-           ##                "Firm profit margin",
-           ##                "Firm assets"
-           ##          ),
-
-          title= "Regression results for model C", font.size="scriptsize",float=FALSE
-          )
-
-@
-\label{tab:reg}
-\end{table*}
-
-\begin{figure}[t]
-
-\begin{minipage}[t]{.5\textwidth}
-
-  \resizebox{7cm}{!}{\input{./figure/medanalysis1.tex}}
-  \captionof{figure}{Mediation analysis 1}
-  \label{fig:fig3}
-\end{minipage}%
-\begin{minipage}[t]{.5\textwidth}
- \resizebox{7cm}{!}{\input{./figure/medanalysis2.tex}}
-  \captionof{figure}{Mediation analysis 2}
-  \label{fig:fig4}
+\begin{figure}[ht] \label{ fig7} 
+  \begin{minipage}[b]{0.5\linewidth}
+    \includegraphics[width=.99\linewidth]{full.pdf} 
+    \caption{Full model} 
+  \end{minipage} 
+  \begin{minipage}[b]{0.5\linewidth}
+    \includegraphics[width=.99\linewidth]{ma.pdf} 
+    \caption{Routine mediation} 
+  \end{minipage} 
+  \begin{minipage}[b]{0.5\linewidth}
+    \includegraphics[width=.99\linewidth]{or.pdf} 
+    \caption{Process mediation} 
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.5\linewidth}
+    \includegraphics[width=.99\linewidth]{dir.pdf} 
+    \caption{Direct model} 
   \end{minipage} 
 \end{figure}
+
+\begin{figure}
+     \centering
+  \caption{Structural model of full estimation - PLS-SEM}
+  \input{./figure/fullmod.tex}
+\end{figure}
+
+\begin{table}
+\begin{center}
+\script size
+\begin{tabular}{lcccc}
+
+\hline \\[-2pt]
+ & \multicolumn{4}{c}{{\bf Models:}} \\  \cline{2-5} \\[-3pt] 
+ & \emph{Direct} & \emph{Process} & \emph{Routines} & \emph{Full}\\
+ & (1) & (2) & (3) & (4)\\
+\hline
+ &  &  &  & \\
+\(CA_{t-1} \rightarrow CA\) & \Sexpr{plmest[1,2]} & \Sexpr{plmest[1,3]} & \Sexpr{plmest[1,4]} & \Sexpr{plmest[1,5]}\\
+ & (\Sexpr{plmt[1,2]}) & (\Sexpr{plmt[1,3]}) & (\Sexpr{plmt[1,4]}) & (\Sexpr{plmt[1,5]})\\[3pt]
+ &  &  &  & \\
+\(DC_P \rightarrow CA\) & \Sexpr{plmest[2,2]} & \Sexpr{plmest[2,3]} & \Sexpr{plmest[2,4]} & \Sexpr{plmest[2,5]}\\
+ & (\Sexpr{plmt[2,2]}) & (\Sexpr{plmt[2,3]}) & (\Sexpr{plmt[2,4]}) & (\Sexpr{plmt[2,5]})\\[4pt]
+\(DC_X \rightarrow CA\) & \Sexpr{plmest[3,2]} & \Sexpr{plmest[3,3]} & \Sexpr{plmest[3,4]} & \Sexpr{plmest[3,5]}\\
+ & (\Sexpr{plmt[3,2]}) & (\Sexpr{plmt[3,3]}) & (\Sexpr{plmt[3,4]}) & (\Sexpr{plmt[3,5]})\\[4pt]
+ &  &  &  & \\
+\(DC_P \rightarrow P\) &  & \Sexpr{plmest[4,3]} &  & \Sexpr{plmest[4,5]}\\
+ &  & (\Sexpr{plmt[4,3]}) &  & (\Sexpr{plmt[4,5]})\\[4pt]
+\(DC_P \rightarrow R\) &  &  & \Sexpr{plmest[5,4]} & \Sexpr{plmest[5,5]}\\
+ &  &  & (\Sexpr{plmt[5,4]}) & (\Sexpr{plmt[5,5]})\\[4pt]
+\(DC_X \rightarrow P\) &  & \Sexpr{plmest[6,3]} &  & \Sexpr{plmest[6,5]}\\
+ &  & (\Sexpr{plmt[6,3]}) &  & (\Sexpr{plmt[6,5]})\\[4pt]
+\(DC_X \rightarrow R\) &  &  & \Sexpr{plmest[7,4]} & \Sexpr{plmest[7,5]}\\
+ &  &  & (\Sexpr{plmt[7,4]}) & (\Sexpr{plmt[7,5]})\\[4pt]
+ &  &  &  & \\
+\(P \rightarrow CA\) &  & \Sexpr{plmest[8,3]} &  & \Sexpr{plmest[8,5]}\\
+ &  & (\Sexpr{plmt[8,3]}) &  & (\Sexpr{plmt[8,5]})\\[4pt]
+\(R \rightarrow CA\) &  &  & \Sexpr{plmest[9,4]} & \Sexpr{plmest[9,5]}\\
+ &  &  & (\Sexpr{plmt[9,4]}) & (\Sexpr{plmt[9,5]})\\[4pt]
+ &  &  &  & \\
+\hline \\[-3pt] 
+Goodness of fit & \Sexpr{gofdir} & \Sexpr{gofor} & \Sexpr{gofma} & \Sexpr{goffull}\\
+Number of observations & \Sexpr{N} & \Sexpr{N} & \Sexpr{N} & \Sexpr{N}\\
+  Firm level controls & YES & YES & YES & YES\\[3pt]
+\hline
+ &  &  &  & \\
+\end{tabular}
+\end{center}
+ \label{tab:reg}
+\end{table}
 
@@
 $DC$. Consider model 1 we observe that $DL$ is influencing the level of $OR$ within the
-firm ($\beta_2 =$ \Sexpr{mod1_dl}) supporting H1. However, the effect disappears when we
+firm ($\beta_2 =$r) supporting H1. However, the effect disappears when we
 add $DC$ in model 2 suggesting a mediating effect. In other words we see that firms with
-initial high $DC$($\beta_3=$ \Sexpr{mod2_dc0}) and increasing $DC$ over time ($\beta_4=$
-\Sexpr{mod2_ddc}) also have better $OR$. To control for the mediating effect suggested by
+initial high $DC$($\beta_3=$ \ {mod2_dc0}) and increasing $DC$ over time ($\beta_4=$
+\ {mod2_ddc}) also have better $OR$. To control for the mediating effect suggested by
 the change in coefficients for $DL$ between models 1 and 2, we performed a causal
@@
 indications from models 1 and 2 showing that the direct effect from $DL$ on $OR$ is
-insignificant and small (ADE = \Sexpr{medmod1_ade}). Meanwhile, the indirect effect
+insignificant and small (ADE = \ {medmod1_ade}). Meanwhile, the indirect effect
 running through changes in $DC$ over time, is significant yielding a positive and
-significant indirect effect of \Sexpr{medmod1_acme}. The proportion of the effect that is
-mediated amounts to \Sexpr{medmod1_shmed}. In sum these results suggest that H1 is
+significant indirect effect of \ {medmod1_acme}. The proportion of the effect that is
+mediated amounts to \ {medmod1_shmed}. In sum these results suggest that H1 is
 unsupported, and that the bulk of the effect is indirect running through $DC$, in line with
@@
 \ref{tab:reg}. Controlled for the usual firm level controls we find a positive effect
-($\xi_1=$ \Sexpr{mod6_dc0}) from $DC_{T_1}$ on $DL$ measured at $T_1$. This supports H5
+($\xi_1=$ \ {mod6_dc0}) from $DC_{T_1}$ on $DL$ measured at $T_1$. This supports H5
 suggesting that firms with more $DC$ is more likely to generate opportunities where it
@@
 operating routines can also be a source of advantage for the firm. Moreover, the
-coefficient of $\Delta DC$ decline from \Sexpr{mod4_ddc} to \Sexpr{mod5_ddc} when we add
+coefficient of $\Delta DC$ decline from  {mod4_ddc} to  {mod5_ddc} when we add
 $OR$. This suggests that some mediation is at work, i.e. that changes in $DC$ leads to
@@
 find added support that both a \emph{direct-} and an \emph{indirect} path exist to explain
-the relationship between $DC$ and $CA$ (ADE = \Sexpr{medmod5_ade}, ACME =
-\Sexpr{medmod5_acme}) and a total mediated share of \Sexpr{medmod5_shmed}.
+the relationship between $DC$ and $CA$ (ADE = \ {medmod5_ade}, ACME =
+\ {medmod5_acme}) and a total mediated share of \ {medmod5_shmed}.
 

### 2019-09-26 article4_tommylars.tex
Before write up

@@
 
-\title{Dynamic capabilities and competitive advantage}
+\title{Dynamic capabilities and competitive advantag}
 %\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
@@
 \section{Introduction}
+
+0.343
 In a recent "state of the art" literature review on dynamic capabilities
@@
 
+  \providecommand{\huxb}[2]{\arrayrulecolor[RGB]{#1}\global\arrayrulewidth=#2pt}
+  \providecommand{\huxvb}[2]{\color[RGB]{#1}\vrule width #2pt}
+  \providecommand{\huxtpad}[1]{\rule{0pt}{\baselineskip+#1}}
+  \providecommand{\huxbpad}[1]{\rule[-#1]{0pt}{#1}}
+
+\begin{table}[h]
+\centering
+\begin{threeparttable}
+\begin{tabularx}{0.9\textwidth}{p{0.18\textwidth} p{0.18\textwidth} p{0.18\textwidth} p{0.18\textwidth} p{0.18\textwidth}}
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \textbf{Factor}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft \textbf{Items}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft \textbf{Loading}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft \textbf{Alpha}\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft \textbf{CI}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.7}}->{\huxb{0, 0, 0}{0.7}}->{\huxb{0, 0, 0}{0.7}}->{\huxb{0, 0, 0}{0.7}}->{\huxb{0, 0, 0}{0.7}}-}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright $CA$\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft CA^1\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.86\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.83\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.90\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft CA^2\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.88\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft CA^3\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.85\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}-}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright $CA_t$\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft CA_{t-1}^1\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.88\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.79\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.88\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft CA_{t-1}^2\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.80\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft CA_{t-1}^3\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.84\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}-}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright $DC_P$\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_P^1\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.71\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.82\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.88\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_P^2\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.83\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_P^3\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.70\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_P^4\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.77\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_P^5\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.82\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}-}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright $DC_X$\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_X^1\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.83\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.74\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.84\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_X^2\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.72\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_X^3\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.85\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}-}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright $P$\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft P^1\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.71\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.70\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.84\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft P^2\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.82\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft P^3\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.85\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}-}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright $R$\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft R^1\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.91\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.94\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.96\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft R^2\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.94\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft R^3\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.96\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
+\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{>{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}-}
+\arrayrulecolor{black}
+\end{tabularx}\end{threeparttable}
+
+\end{table}
+
 \subsection{Control variables}
@@
 
+\begin{figure}[ht] \label{ fig7} 
+  \begin{minipage}[b]{0.5\linewidth}
+    \includegraphics[width=.99\linewidth]{full.pdf} 
+    \caption{Full model} 
+  \end{minipage} 
+  \begin{minipage}[b]{0.5\linewidth}
+    \includegraphics[width=.99\linewidth]{ma.pdf} 
+    \caption{Routine mediation} 
+  \end{minipage} 
+  \begin{minipage}[b]{0.5\linewidth}
+    \includegraphics[width=.99\linewidth]{or.pdf} 
+    \caption{Process mediation} 
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.5\linewidth}
+    \includegraphics[width=.99\linewidth]{dir.pdf} 
+    \caption{Direct model} 
+  \end{minipage} 
+\end{figure}
+
+\begin{figure}
+     \centering
+  \caption{Structural model of full estimation - PLS-SEM}
+  \input{./figure/fullmod.tex}
+\end{figure}
+
+\begin{table}
+\begin{center}
+\script size
+\begin{tabular}{lcccc}
+
+\hline \\[-2pt]
+ & \multicolumn{4}{c}{{\bf Models:}} \\  \cline{2-5} \\[-3pt] 
+ & \emph{Direct} & \emph{Process} & \emph{Routines} & \emph{Full}\\
+ & (1) & (2) & (3) & (4)\\
+\hline
+ &  &  &  & \\
+\(CA_{t-1} \rightarrow CA\) & 0.364 & 0.361 & 0.351 & 0.343\\
+ & (7.19) & (6.49) & (6.33) & (6.27)\\[3pt]
+ &  &  &  & \\
+\(DC_P \rightarrow CA\) & 0.378 & 0.342 & 0.314 & 0.299\\
+ & (5.23) & (4.48) & (4.08) & (3.82)\\[4pt]
+\(DC_X \rightarrow CA\) & -0.005 & -0.045 & 0.002 & -0.066\\
+ & (-0.07) & (-0.59) & (0.04) & (-0.98)\\[4pt]
+ &  &  &  & \\
+\(DC_P \rightarrow P\) &  & 0.146 &  & 0.129\\
+ &  & (1.93) &  & (1.7)\\[4pt]
+\(DC_P \rightarrow R\) &  &  & 0.502 & 0.496\\
+ &  &  & (6.23) & (6.13)\\[4pt]
+\(DC_X \rightarrow P\) &  & 0.3 &  & 0.343\\
+ &  & (3.63) &  & (4.79)\\[4pt]
+\(DC_X \rightarrow R\) &  &  & -0.099 & -0.091\\
+ &  &  & (-1.28) & (-1.14)\\[4pt]
+ &  &  &  & \\
+\(P \rightarrow CA\) &  & 0.182 &  & 0.185\\
+ &  & (2.53) &  & (3.14)\\[4pt]
+\(R \rightarrow CA\) &  &  & 0.137 & 0.123\\
+ &  &  & (2.3) & (2.15)\\[4pt]
+ &  &  &  & \\
+\hline \\[-3pt] 
+Goodness of fit & 0.45 & 0.4 & 0.43 & 0.41\\
+Number of observations & 260 & 260 & 260 & 260\\
+  Firm level controls & YES & YES & YES & YES\\[3pt]
+\hline
+ &  &  &  & \\
+\end{tabular}
+\end{center}
+ \label{tab:reg}
+\end{table}
+
 Table \ref{tab:reg} shows a summary of the regression models proposed in the previous
@@
 $DC$. Consider model 1 we observe that $DL$ is influencing the level of $OR$ within the
-firm ($\beta_2 =$ 0.325) supporting H1. However, the effect disappears when we
+firm ($\beta_2 =$r) supporting H1. However, the effect disappears when we
 add $DC$ in model 2 suggesting a mediating effect. In other words we see that firms with
-initial high $DC$($\beta_3=$ -0.007) and increasing $DC$ over time ($\beta_4=$
-0.497) also have better $OR$. To control for the mediating effect suggested by
+initial high $DC$($\beta_3=$ \ {mod2_dc0}) and increasing $DC$ over time ($\beta_4=$
+\ {mod2_ddc}) also have better $OR$. To control for the mediating effect suggested by
 the change in coefficients for $DL$ between models 1 and 2, we performed a causal
@@
 indications from models 1 and 2 showing that the direct effect from $DL$ on $OR$ is
-insignificant and small (ADE = 0.05). Meanwhile, the indirect effect
+insignificant and small (ADE = \ {medmod1_ade}). Meanwhile, the indirect effect
 running through changes in $DC$ over time, is significant yielding a positive and
-significant indirect effect of 0.222. The proportion of the effect that is
-mediated amounts to 0.818. In sum these results suggest that H1 is
+significant indirect effect of \ {medmod1_acme}. The proportion of the effect that is
+mediated amounts to \ {medmod1_shmed}. In sum these results suggest that H1 is
 unsupported, and that the bulk of the effect is indirect running through $DC$, in line with
@@
 \ref{tab:reg}. Controlled for the usual firm level controls we find a positive effect
-($\xi_1=$ 0.913) from $DC_{T_1}$ on $DL$ measured at $T_1$. This supports H5
+($\xi_1=$ \ {mod6_dc0}) from $DC_{T_1}$ on $DL$ measured at $T_1$. This supports H5
 suggesting that firms with more $DC$ is more likely to generate opportunities where it
@@
 operating routines can also be a source of advantage for the firm. Moreover, the
-coefficient of $\Delta DC$ decline from 0.589 to 0.425 when we add
+coefficient of $\Delta DC$ decline from  {mod4_ddc} to  {mod5_ddc} when we add
 $OR$. This suggests that some mediation is at work, i.e. that changes in $DC$ leads to
@@
 find added support that both a \emph{direct-} and an \emph{indirect} path exist to explain
-the relationship between $DC$ and $CA$ (ADE = 0.371, ACME =
-0.198) and a total mediated share of 0.347.
+the relationship between $DC$ and $CA$ (ADE = \ {medmod5_ade}, ACME =
+\ {medmod5_acme}) and a total mediated share of \ {medmod5_shmed}.
 

### 2019-09-26 figure/fullmod.rnw
Before write up

\begin{tikzpicture}

   \tikzstyle{mynode}=[circle,draw, ultra thin, draw=black, fill=white, minimum size=17mm,inner sep=0pt, align=center]

   \node[mynode] (dc1){$DC_P$};
   \node[mynode,below of=dc1, yshift=-2cm] (dc2){$DC_X$};
   \node[mynode,right of=dc1, xshift=3cm] (or){$P$};
   \node[mynode,right of=dc2, xshift=3cm] (ma){$R$};
   \node[mynode,right of=ma, xshift=3cm, yshift=1.5cm] (ca){$CA$};

   \draw[-latex] (dc1.east) -- node[text width=0.5cm,font=\footnotesize, above=2pt,align=left,
   fill=white] {\Sexpr{figOut[4,5]}} (or.west);

   \draw[-latex] (dc2.east) -- node[text width=0.5cm,font=\footnotesize, above=2pt, align=left,
   fill=white] {\Sexpr{figOut[7,5]}} (ma.west);

   \draw[-latex] (dc1.south east) -- node[text width=0.5cm,font=\footnotesize,  above=2pt,
   align=left, fill=white,sloped, near end] {\Sexpr{figOut[5,5]}} (ma.north west);

   \draw[-latex] (dc2.north east) -- node[text width=0.5cm,font=\footnotesize, above=2pt,align=left,
   fill=white,sloped, near end]{\Sexpr{figOut[6,5]}} (or.south west);

    \draw[-latex] (or.east) -- node[text width=0.5cm,font=\footnotesize, align=left,above=2pt,
   fill=white,sloped]{\Sexpr{figOut[8,5]}} (ca.north west);

   \draw[-latex] (ma.east) -- node[text width=0.5cm,font=\footnotesize, below=2pt,
   fill=white,sloped]{\Sexpr{figOut[9,5]}} (ca.south west);

   \draw[-latex] (dc1.north)[bend left] to node[text width=0.5cm,font=\footnotesize, above=2pt,align=center,
   fill=white]{\Sexpr{figOut[2,5]}}(ca.north);

   \draw[-latex] (dc2.south)[bend right] to node[text width=0.5cm,font=\footnotesize,below=2pt, align=left,
   fill=white]{\Sexpr{figOut[3,5]}} (ca.south);

\end{tikzpicture}

### 2019-09-26 figure/fullmod.tex
Before write up

\begin{tikzpicture}
   \centering
   \tikzstyle{mynode}=[circle,draw, ultra thin, draw=black, fill=white, minimum size=17mm,inner sep=0pt, align=center]

   \node[mynode] (dc1){$DC_P$};
   \node[mynode,below of=dc1, yshift=-2cm] (dc2){$DC_X$};
   \node[mynode,right of=dc1, xshift=3cm] (or){$P$};
   \node[mynode,right of=dc2, xshift=3cm] (ma){$R$};
   \node[mynode,right of=ma, xshift=3cm, yshift=1.5cm] (ca){$CA$};

   \draw[-latex] (dc1.east) -- node[text width=0.5cm,font=\footnotesize, above=2pt,align=left,
   fill=white] {$0.129^{*}$} (or.west);

   \draw[-latex] (dc2.east) -- node[text width=0.5cm,font=\footnotesize, above=2pt, align=left,
   fill=white] {$-0.091^{}$} (ma.west);

   \draw[-latex] (dc1.south east) -- node[text width=0.5cm,font=\footnotesize,  above=2pt,
   align=left, fill=white,sloped, near end] {$0.496^{***}$} (ma.north west);

   \draw[-latex] (dc2.north east) -- node[text width=0.5cm,font=\footnotesize, above=2pt,align=left,
   fill=white,sloped, near end]{$0.343^{***}$} (or.south west);

    \draw[-latex] (or.east) -- node[text width=0.5cm,font=\footnotesize, align=left,above=2pt,
   fill=white,sloped]{$0.185^{***}$} (ca.north west);

   \draw[-latex] (ma.east) -- node[text width=0.5cm,font=\footnotesize, below=2pt,
   fill=white,sloped]{$0.123^{**}$} (ca.south west);

   \draw[-latex] (dc1.north)[bend left] to node[text width=0.5cm,font=\footnotesize, above=2pt,align=center,
   fill=white]{$0.299^{***}$}(ca.north);

   \draw[-latex] (dc2.south)[bend right] to node[text width=0.5cm,font=\footnotesize,below=2pt, align=left,
   fill=white]{$-0.066^{}$} (ca.south);

\end{tikzpicture}

### 2019-09-26 article4_analysis.r

@@ -9,7 +9,8 @@ library(sampleSelection)
 library(mediation)
 library(reshape)
 library(huxtable)
-install.packages("huxtable")
+library(semPLS)
+###install.packages("huxtable")
                                         #library(polycor)
 
 ## This loads the data workspace where skattefunn_data.r is already loaded
@@ -64,88 +65,8 @@ zw <- merge(zw,assets,by=("orgnr"), all.x=TRUE)
 zw <- merge(zw,debt,by=("orgnr"), all.x=TRUE)
 zw$lassets <- log(zw$assets)
 
-
-
-### Creating variable for determining constant in respondent
-
-
-## ## Creating variables
-## sense0 <- rowMeans(zw[,c("Q19", "Q19a", "Q19b", "Q19c", "Q19d", "Q20d")], na.rm=TRUE)
-## seize0 <- as.double(rowMeans(zw[,c( "Q19e", "Q20b", "Q19c", "Q25", "Q20")], na.rm=TRUE))
-## tran0 <- as.double(rowMeans(zw[,c("Q20c", "Q25a", "Q25b", "Q25c")], na.rm=TRUE))
-## zw$dc0 <- rowMeans(cbind(sense0,seize0,tran0),na.rm=TRUE)
-
-## sense1 <- as.double(rowMeans(zw[,c("Q6.1_t1","Q6.2_t1","Q6.3_t1","Q6.4_t1","Q6.5_t1","Q7.3_t1")], na.rm=TRUE))
-## seize1 <-as.double(rowMeans(zw[,c("Q6.6_t1","Q7.1_t1","Q6.4_t1","Q7.5_t1","Q6.7_t1")], na.rm=TRUE))
-## tran1 <- as.double(rowMeans(zw[,c("Q7.2_t1","Q7.6_t1","Q7.7_t1","Q7.8_t1")], na.rm=TRUE))
-## zw$dc1 <- rowMeans(cbind(sense1,seize1,tran1),na.rm=TRUE)
-
-## zw$ca0 <-  rowMeans(zw[,c("Q28","Q28a", "Q28b", "Q28c")], na.rm=TRUE)
-## zw$ca1 <-  rowMeans(zw[,c("Q16.1_t1","Q16.2_t1", "Q16.3_t1", "Q16.4_t1")], na.rm=TRUE)
[…]

### 2019-09-26 article4_analysis_bck.r

@@ -1092,7 +1092,7 @@ semPLS::gof(ecsi)
 
 
 
-## PARTIAL MODEL OR 2DC
+## Partial MODEL OR 2DC
 items <- c(#"Q19a","Q19c", "Q20b", "Q20c", #DC0
                                         #"Q19b","Q19d","Q20d", "Q20e", #DC02
            "Q6.2_t1","Q6.4_t1", "Q7.1_t1","Q7.2_t1","Q6.5_t1", #DC1

### 2019-09-30 article4_tommylars.rnw
still struggling with framing

@@
 
-\Sexpr{resest[1,2]}
+DC is often critizesd for being tautological and less focus has been placed on instances
+when dynamism can lead to poorer competitive outcomes. 
+Structural inertia, commitment \cite{schreyogg2007}. Under what conditions are changing
+capabilities counterproducttive
+
+The relationship between dynamic capabilities and competitive advantage has been one of
+great contention in the extant literature \citep{Peteraf2013,Ambrosini2009}. From this
+debate a richer understanding of how different dynamic capabilities (or functional forms
+of them) work differently to change different types of firm resources
+\citep{Helfat2015a,Teece2007,Ambrosini2009a} with implications for competitive advantage
+\citep{Peteraf2013} has emerged. Increasingly the relationship between (1) dynamic
+capabilities, (2) firm resources and routines, and competitive advantage is seen as a
+complex system with interactions between different types of each 1 and 2. Many conceptual
+contributions have excellently discussed varieties or functional forms of either dynamic
+capabilities \citep{Ambrosini2009a,Helfat2015ad,DiStefano2014} or underlying resources or
+routines \citep{Winter2003,Eisenhardt2000}. However, very few, is any, papers attempts to
+integrate varieties at multiple levels simultaneously. The bulk of contributions focus
+only on heterogeneity at the dynamic capabilities level, or at
+
+work dDC offers a theory of how firms achieve
+competitive advantage over time. Yet the DC theory suffers from contradictory claims about
+competitive advantage as its outcome. On the one hand a stream of contributions argue that
+DC will lead to competitive advantage because it operates by changing operational
+capabilities in face of change and hence create strategic change (ref helfat). In this
+view these changes result in complex and path dependent processes that will be
+idiosyncratic to the firm and hard to imitate. Consequently, they can lead to competitive
+advantage.
+
+A contrary stream of literature argues that changes of operational capabilities over time
+takes the form of routines and converges towards best practice (ref EM). Such best
+practices are simpler and more observable routines that are both imitable and easy to
+copy. Such firm resources are then not idiosyncratic and can consequently not be the
+source of competitive advantage.
+
+The way DC work differnelty throug changing two sets of operational capabilities = complex
+and path dependent processes based capabilities, and simple rules/based routines.
+
+These contradictory positions have been thoroughly discussed in earlier work (see
+\cite{Peteraf2013} for a review). On the one hand DC takes the form of simple rules
+shaping underlying routines. On the other hand they take the form of complex processes.
+
+Regarding the action and the object ofthe action, simple rules are more likely to be
+involved in developing something new in response to new opportunities, while complex
+rou- tines are more concerned with changing existing resources and capabilities.
+
 In a recent "state of the art" literature review on dynamic capabilities

### 2019-09-30 article4_tommylars.tex
still struggling with framing

@@
 
-\title{Dynamic capabilities and competitive advantag}
+\title{Dynamic capabilities and competitive advantage}
 %\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
@@
 
-0.343
+The relationship between dynamic capabilities and competitive advantage has been one of
+great contention in the extant literature \citep{Peteraf2013,Ambrosini2009}. From this
+debate a richer understanding of how different dynamic capabilities (or functional forms
+of them) work differently to change different types of firm resources
+\citep{Helfat2015a,Teece2007,Ambrosini2009a} with implications for competitive advantage
+\citep{Peteraf2013}.  has emerged.  work dDC offers a theory of how firms achieve
+competitive advantage over time. Yet the DC theory suffers from contradictory claims about
+competitive advantage as its outcome. On the one hand a stream of contributions argue that
+DC will lead to competitive advantage because it operates by changing operational
+capabilities in face of change and hence create strategic change (ref helfat). In this
+view these changes result in complex and path dependent processes that will be
+idiosyncratic to the firm and hard to imitate. Consequently, they can lead to competitive
+advantage.
+
+A contrary stream of literature argues that changes of operational capabilities over time
+takes the form of routines and converges towards best practice (ref EM). Such best
+practices are simpler and more observable routines that are both imitable and easy to
+copy. Such firm resources are then not idiosyncratic and can consequently not be the
+source of competitive advantage.
+
+The way DC work differnelty throug changing two sets of operational capabilities = complex
+and path dependent processes based capabilities, and simple rules/based routines.
+
+These contradictory positions have been thoroughly discussed in earlier work (see
+\cite{Peteraf2013} for a review). On the one hand DC takes the form of simple rules
+shaping underlying routines. On the other hand they take the form of complex processes.
+
+Regarding the action and the object ofthe action, simple rules are more likely to be
+involved in developing something new in response to new opportunities, while complex
+rou- tines are more concerned with changing existing resources and capabilities.
+
 In a recent "state of the art" literature review on dynamic capabilities

### 2019-10-07 article4_tommylars.rnw
still trying to nail it - looking at different levels ov VRIO

@@
 
+Extant literature on DC struggles with a fundamental conception and prediction of the
+theory, namely if and when DC can lead to competitive advantage. This friction has been
+dubbed the "elephant in the room" (peteraf) and been tracked back to the seminal papers of
+Teece and Eisenhardt, as well as their their different theoretical antecedents of
+evolutionary economics (ref) and behavioral theory (ref) respectively (ref Arndt
+x2). Recently, distefaneo et al propopsed a theoretical integration of these varying
+conceptions of DC theory. They suggest that latent and constitutent elements of DC
+represent different constructs but are integrated in that they work differently in shaping
+strategic change.
+
 DC is often critizesd for being tautological and less focus has been placed on instances
@@
 capabilities \citep{Ambrosini2009a,Helfat2015ad,DiStefano2014} or underlying resources or
-routines \citep{Winter2003,Eisenhardt2000}. However, very few, is any, papers attempts to
-integrate varieties at multiple levels simultaneously. The bulk of contributions focus
+routines \citep{Winter2003,Eisenhardt2000}. However, very few, if any, papers attempt to
+integrate varieties at multiple levels simultaneously. By asking if dynamic capabilities
+can lead to competitive advantage and how this occurs, one is far better off asking "when"
+competitive advangate is an outcome of dynamic capabiliteis and its workings.
+
+The definition of dynamic capabilities, albeit contestst, seems to be converging on
+varieties of "the ability of firms to create, modicy and extend its resource base" (ref)
+\citep{Schilke2018}. Meanwhile both dynamic capabilities as the "governing entity" and
+resources as "the governed entity" takes different forms in the literature (ref). Dynamic
+capabilities themsleves can roughly be divided into sets of simple rules governing
+undelying resources, or more complex routines developed for the same purpose
+\citep{Peteraf2013}. In other words, dynamic capabilities themselves can and cannot satisfy
+the VRIO condition. This contention is throughly covered in the literature (refs) and
+recent contribiutions have argued for interplays between simple and complex types of
+dynamic capabilities foring a more complex and initmatble dynamic system
+\citep{DiStefano2014}. Moreover, granted different forms of dynamic capabilities exist
+their impact on the "governed entity", the underlying firm resources, should also be
+varying.
+
+To explore this we emply two radically differnet forms of dynamic capabilities / one
+geared towards transforming exitsgint resources in order to exploit them to gain
+competitive advantage (refs). The other form is geraed towards seizing new opportunities in order
+to explore new business opportunitieis (refs). We argue that competitive advantage can
+stem from each of these, but that the mechanism varies. Dynamic capabilities geared
+towards transforming for exploitation ($DC_P$) is by and of itself the result of a more
+complex set of routines configured in a way that is hard to imitate because of its path
+dependent and evolutionary nature. This legacy from evolutinoary economics is stressed as
+an important factor for creating VRIO resources (Ref peteraf). The stream of contributions
+maintaining dynamic capabilities working through the object of "changing existing
+capabilities" \citep{Teece1997,Zollo2002a,Winter2003,Zahra2006,Kale2002} also maintain
+that
+
+We argue that latent and constituted dynamic capabilites behave differently and work
+differnetly trhough differents modes (action or wahtever the term in DiStefano er).
+
+{\bf LAtent = complex process routines Teece
+Constitutent = simpler, ad hoc - Eisenhardt}
+
+We explore two different modes (natures) of dynamic capabilities and how they work
+differently (action) to create competitive advantage. Or is it the object of action as
+either resources or opportunities?
+
+By introducing different measures of different types of DC (latent and constiuted) as well
+as two different types of action (change existing or create new) we explore the workings
+of the drive train model proposed by DiStefano suggesting a fuller and more dynamic view
+on how latent and consittued DC works differently.
+
+The working of latent:
+Departing from the definintion of dynamic capabilities found in Teece (ref) and subsequent
+contributions in this tradition
+
+The working of cinstuted
+
+We identify two ditintctly different noptions of dynamic capabilities both following well
+known definitions byut weith different nature (ref distefano). We show that only the
+latent dc can directly and indirectly create CA,whereas the constituent element nature of
+DC only works through changing lower level routines.
+
+Different parts of the drive train works on different types of underlying routines
+
+Looks at competing hypotheses between Eisenhardt and teexe with respect to routinization. Finds that routininzation happens at DC level less than operational level?
+We argue that this depends on the purpose *action of the Dc and the composition of the
+focal operational capability.
+
+Reviewing the literature reveals that researchers have tended to identify dynamic capabilities post hoc, inferring their existence from successful organizational out- comes such as profitability and growth, as prior definitions would suggest (Table
+
+On the other hand we have dynamic capabilites geared toward sensing and seizing new
+opportunities as part of an effort of exploration. Such dynamic capabilities are described
+in the literature as themselves a set of more simple routines orchestrated in a manner
+such that x`
+
+Routinization at certain level, but depends on them being outward or inward looking.
+
+How can DC lead to competitive advangate. departing from the original definition this
+happens through the modification or aquisition of firm resources. But the resopurces
+themselves can and cannot be a source of competitive advantage
+
+At a minimum, in order for something to qualify as a capability, it must work in a reliable manner’ (Helfat and Peteraf, 2003: 999). Capabilities
+
+The bulk of contributions focus
 only on heterogeneity at the dynamic capabilities level, or at
+
+W
 

### 2019-10-07 article4_tommylars.tex
still trying to nail it - looking at different levels ov VRIO

@@
 
+DC is often critizesd for being tautological and less focus has been placed on instances
+when dynamism can lead to poorer competitive outcomes. 
+Structural inertia, commitment \cite{schreyogg2007}. Under what conditions are changing
+capabilities counterproducttive
+
 The relationship between dynamic capabilities and competitive advantage has been one of
@@
 \citep{Helfat2015a,Teece2007,Ambrosini2009a} with implications for competitive advantage
-\citep{Peteraf2013}.  has emerged.  work dDC offers a theory of how firms achieve
+\citep{Peteraf2013} has emerged. Increasingly the relationship between (1) dynamic
+capabilities, (2) firm resources and routines, and competitive advantage is seen as a
+complex system with interactions between different types of each 1 and 2. Many conceptual
+contributions have excellently discussed varieties or functional forms of either dynamic
+capabilities \citep{Ambrosini2009a,Helfat2015ad,DiStefano2014} or underlying resources or
+routines \citep{Winter2003,Eisenhardt2000}. However, very few, if any, papers attempt to
+integrate varieties at multiple levels simultaneously. By asking if dynamic capabilities
+can lead to competitive advantage and how this occurs, one is far better off asking "when"
+competitive advangate is an outcome of dynamic capabiliteis and its workings.
+
+The definition of dynamic capabilities, albeit contestst, seems to be converging on
+varieties of "the ability of firms to create, modicy and extend its resource base" (ref)
+\citep{Schilke2018}. Meanwhile both dynamic capabilities as the "governing entity" and
+resources as "the governed entity" takes different forms in the literature (ref). Dynamic
+capabilities themsleves can roughly be divided into sets of simple rules governing
+undelying resources, or more complex routines developed for the same purpose
+\citep{Peteraf2013}. In other words, dynamic capabilities themselves can and cannot satisfy
+the VRIO condition. This contention is throughly covered in the literature (refs) and
+recent contribiutions have argued for interplays between simple and complex types of
+dynamic capabilities foring a more complex and initmatble dynamic system
+\citep{DiStefano2014}. Moreover, granted different forms of dynamic capabilities exist
+their impact on the "governed entity", the underlying firm resources, should also be
+varying.
+
+To explore this we emply two radically differnet forms of dynamic capabilities / one
+geared towards transforming exitsgint resources in order to exploit them to gain
+competitive advantage (refs). The other form is geraed towards seizing new opportunities in order
+to explore new business opportunitieis (refs). We argue that competitive advantage can
+stem from each of these, but that the mechanism varies. Dynamic capabilities geared
+towards transforming for exploitation ($DC_P$) is by and of itself the result of a more
+complex set of routines configured in a way that is hard to imitate because of its path
+dependent and evolutionary nature. This legacy from evolutinoary economics is stressed as
+an important factor for creating VRIO resources (Ref peteraf). The stream of contributions
+maintaining dynamic capabilities working through the object of "changing existing
+capabilities" \citep{Teece1997,Zollo2002a,Winter2003,Zahra2006,Kale2002} also maintain
+that
+
+We argue that latent and constituted dynamic capabilites behave differently and work
+differnetly trhough differents modes (action or wahtever the term in DiStefano er).
+
+Looks at competing hypotheses between Eisenhardt and teexe with respect to routinization. Finds that routininzation happens at DC level less than operational level?
+We argue that this depends on the purpose *action of the Dc and the composition of the
+focal operational capability.
+
+Reviewing the literature reveals that researchers have tended to identify dynamic capabilities post hoc, inferring their existence from successful organizational out- comes such as profitability and growth, as prior definitions would suggest (Table
+
+On the other hand we have dynamic capabilites geared toward sensing and seizing new
+opportunities as part of an effort of exploration. Such dynamic capabilities are described
+in the literature as themselves a set of more simple routines orchestrated in a manner
+such that x
+
+Routinization at certain level, but depends on them being outward or inward looking.
+
+How can DC lead to competitive advangate. departing from the original definition this
+happens through the modification or aquisition of firm resources. But the resopurces
+themselves can and cannot be a source of competitive advantage
+
+At a minimum, in order for something to qualify as a capability, it must work in a reliable manner’ (Helfat and Peteraf, 2003: 999). Capabilities
+
+The bulk of contributions focus
+only on heterogeneity at the dynamic capabilities level, or at
+
+W
+
+work dDC offers a theory of how firms achieve
 competitive advantage over time. Yet the DC theory suffers from contradictory claims about
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright $CA_t$\huxbpad{6pt}} &
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright $CA_{t-1}$\huxbpad{6pt}} &
 \multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft CA_{t-1}^1\huxbpad{6pt}} &
@@
  &  &  &  & \\
-\(CA_{t-1} \rightarrow CA\) & 0.364 & 0.361 & 0.351 & 0.343\\
- & (7.19) & (6.49) & (6.33) & (6.27)\\[3pt]
+\(CA_{t-1} \rightarrow CA\) & NA & NA & NA & 0.343\\
+ & (NA) & (NA) & (NA) & (6.52)\\[3pt]
  &  &  &  & \\
-\(DC_P \rightarrow CA\) & 0.378 & 0.342 & 0.314 & 0.299\\
- & (5.23) & (4.48) & (4.08) & (3.82)\\[4pt]
-\(DC_X \rightarrow CA\) & -0.005 & -0.045 & 0.002 & -0.066\\
- & (-0.07) & (-0.59) & (0.04) & (-0.98)\\[4pt]
+\(DC_P \rightarrow CA\) & 0.378 & 0.342 & 0.342 & 0.299\\
+ & (5.3) & (4.78) & (4.69) & (3.77)\\[4pt]
+\(DC_X \rightarrow CA\) & -0.005 & -0.045 & -0.045 & -0.066\\
+ & (-0.08) & (-0.59) & (-0.6) & (-0.89)\\[4pt]
  &  &  &  & \\
-\(DC_P \rightarrow P\) &  & 0.146 &  & 0.129\\
- &  & (1.93) &  & (1.7)\\[4pt]
-\(DC_P \rightarrow R\) &  &  & 0.502 & 0.496\\
- &  &  & (6.23) & (6.13)\\[4pt]
-\(DC_X \rightarrow P\) &  & 0.3 &  & 0.343\\
- &  & (3.63) &  & (4.79)\\[4pt]
-\(DC_X \rightarrow R\) &  &  & -0.099 & -0.091\\
- &  &  & (-1.28) & (-1.14)\\[4pt]
+\(DC_P \rightarrow P\) &  & NA &  & 0.496\\
+ &  & (NA) &  & (6.07)\\[4pt]
+\(DC_P \rightarrow R\) &  &  & 0.146 & 0.129\\
+ &  &  & (1.97) & (1.63)\\[4pt]
+\(DC_X \rightarrow P\) &  & NA &  & -0.091\\
+ &  & (NA) &  & (-1.26)\\[4pt]
+\(DC_X \rightarrow R\) &  &  & 0.3 & 0.343\\
+ &  &  & (3.62) & (4.62)\\[4pt]
  &  &  &  & \\
-\(P \rightarrow CA\) &  & 0.182 &  & 0.185\\
- &  & (2.53) &  & (3.14)\\[4pt]
-\(R \rightarrow CA\) &  &  & 0.137 & 0.123\\
- &  &  & (2.3) & (2.15)\\[4pt]
+\(P \rightarrow CA\) &  & NA &  & 0.123\\
+ &  & (NA) &  & (2.02)\\[4pt]
+\(R \rightarrow CA\) &  &  & 0.182 & 0.185\\
+ &  &  & (2.72) & (2.77)\\[4pt]
  &  &  &  & \\
 \hline \\[-3pt] 
-Goodness of fit & 0.45 & 0.4 & 0.43 & 0.41\\
+Goodness of fit & 0.45 & 0.4 & 0.42 & 0.41\\
 Number of observations & 260 & 260 & 260 & 260\\

### 2019-10-07 article4_analysis.r

@@ -145,21 +145,21 @@ ca1 <-   imputezw(zwadj[,c("Q16.1_t1","Q16.2_t1","Q16.4_t1")] )
 or1 <-   imputezw(zwadj[,c("Q5.4_t1","Q5.6_t1","Q5.7_t1")])
 ma01 <-  imputezw(zwadj[,c( "Q8.7_t1", "Q8.8_t1", "Q8.9_t1")])
 complist <- list(DC_P=dc01,DC_X=dc02,CA_t=ca0,CA=ca1,P=or1,R=ma01)
-vcontrols <- zwadj[,c("size","age","dyn","pm","lassets")]
+vcontrols <- zwadj[,c("size","age","dyn","pm","lassets","Q17.5_t1")]
 zwadj <- cbind(dc01,dc02,ca0,ca1,or1,ma01,vcontrols)
 
 
 names(complist[[1]])
 
 ##Factor extraction full model based on insight from Polychoric PCA
-items <- c("Q6.2_t1","Q6.4_t1", "Q7.1_t1","Q7.2_t1","Q6.5_t1", #DC1
+items <- c("Q6.2_t1","Q6.4_t1", "Q7.2_t1", #DC1 "Q7.1_t1""Q6.5_t1",
            "Q6.1_t1","Q7.3_t1","Q7.4_t1", #DC2
            "Q28","Q28a","Q28c", #CA0
            "Q16.1_t1","Q16.2_t1","Q16.4_t1", #CA1
            "Q5.4_t1","Q5.6_t1","Q5.7_t1", #OR1
            "Q8.7_t1", "Q8.8_t1", "Q8.9_t1") #MA
 
-latents <- c(rep("DC_P",5),
+latents <- c(rep("DC_P",3),
              rep("DC_X",3),
              rep("CA_t",3),
              rep("CA",3),
@@ -266,9 +266,9 @@ ht
 
 ## Evaluating PLS model https://cran.r-project.org/web/packages/semPLS/vignettes/semPLS-intro.pdf
 ## PARTIAL MODEL MA 2DC
-ritems <- c(#"Q19a","Q19c", "Q20b", "Q20c", #DC01
+items <- c(#"Q19a","Q19c", "Q20b", "Q20c", #DC01
            #"Q19b","Q19d","Q20d", "Q20e", #DC02
[…]

### 2019-10-07 article4_analysis_bck.r

@@ -651,7 +651,8 @@ head(vsense0)
 
 vsense0
 foo
-nrow(foo)
+nrow(foo)xk
+
 
 vcontrols <- zwadj[,c("size","age","dynhigh","pm","lassets")]
 

### 2019-10-11 article4_tommylars.rnw
Possible results ready

@@
 
+%% Extant literature on dynamic capabilities is battling with a fundamental conception and
+%% prediction of the theory, namely if, when and how dynamic capabilities can lead to competitive
+%% advantage.
+
+Seminal contributions to the field of dynamic capabilities have argued for both direct
+\cite{Kor2005,Eriksson2014,Schilke2014a} and indirect (ref) effects of dynamic
+capabilities on competitive advantage, although increasingly the bulk of the literature
+focuses on the latter \citep{Schilke2018}. This indirect link is typically understood as
+dynamic capabilities modifying, extending or creating firm resources (helfat) (or
+lower-level operational capabilities (Winter, collis)) and thus generating competetive
+advantage (Eriksson and others). Furthermore, empirical evidence keep suggesting that both direct (ref)
+and indirect (ref) links exist. This warrant the question of \emph{when} direct and
+indirect links between dynamic capabilities and competitive advantage is most pronounced.
+
+Moreover, firm resources or capabiltiies themselves are far from a homogenous set and
+varies among other things with respect to their uniqueness, inimatbility and value
+(barney). Important contributions have thus argued for a deeper insighi into these
+intermediaries and their mechanism calling for a "deeper insight into the variety of mechanisms that
+underlie the performance effects of capabilities.” (Schilke, 2014a: 199). 
+as well as \emph{what} different intermediaries exis .
+
+%% Extant literature on dynamic capabilities is battling with a fundamental conception and
+%% prediction of the theory, namely if, when and how dynamic capabilities can lead to competitive
+%% advantage. 
+all items
+
+       Path   LOW     t  HIGH     t
+1 DC -> CA1 0.303 3.517 0.087 0.710
+2   DC -> P 0.445 6.070 0.435 3.972
+3  P -> CA1 0.273 3.174 0.308 3.164
+> R
+       Path   LOW     t  HIGH     t
+1 DC -> CA1 0.438 6.161 0.134 0.988
+2   DC -> R 0.400 5.661 0.549 8.033
+3  R -> CA1 0.015 0.186 0.195 1.555
+>
+
+fewer items
+
+      Path   LOW     t   HIGH      t
+1 DC -> CA1 0.173 1.771 -0.017 -0.172
+2   DC -> P 0.437 5.183  0.432  4.875
+3  P -> CA1 0.329 3.646  0.353  3.731
+> R
+       Path   LOW     t  HIGH     t
+1 DC -> CA1 0.292 2.891 0.049 0.438
+2   DC -> R 0.142 1.287 0.370 4.267
+3  R -> CA1 0.109 1.471 0.244 2.344
+
+more items
+
+       Path   LOW     t  HIGH     t
+1 DC -> CA1 0.314 4.107 0.139 1.236
+2   DC -> P 0.386 5.481 0.391 3.797
+3  P -> CA1 0.291 3.596 0.292 3.011
+> R
+       Path   LOW     t  HIGH     t
+1 DC -> CA1 0.439 6.095 0.163 1.122
+2   DC -> R 0.428 5.547 0.579 7.972
+3  R -> CA1 0.019 0.208 0.177 1.466
+
+Seminal contributions to the field of dynamic capabilities have argued for both direct
+\cite{Kor2005,Eriksson2014,Schilke2014a} and indirect (ref) effects of dynamic
+capabilities on competitive advantage, although increasingly the bulk of the literature
+focuses on the latter \citep{Schilke2018}. This indirect link is typically understood as
+dynamic capabilities modifying, extending or creating firm resources (helfat) (or
+lower-level operational capabilities (Winter, collis)) and thus generating competetive
+advantage (Eriksson and others). Furthermore, empirical evidence keep suggesting that both direct (ref)
+and indirect (ref) links exist. This warrant the question of \emph{when} and under which conditions direct and
+indirect links between dynamic capabilities and competitive advantage is most pronounced.
+
+Moreover, firm resources or capabiltiies themselves are far from a homogenous set and
+varies among other things with respect to their uniqueness, inimatbility and value
+(barney). Important contributions have thus argued for a deeper insighi into these
+intermediaries and their mechanism calling for a "deeper insight into the variety of mechanisms that
+underlie the performance effects of capabilities.” (Schilke, 2014a: 199). In other words,
+adding to the question of when direct and indirect links are most pronounced, we would
+also need to understand \emph{what} different forms of intermediatons work under these
+aforementioned conidtions.
+
+Still, important empirical contributions argue for a direct link although the emerginig
+consensus of the literature argues for an indirect link. This warrants the research question:
+"Under what conditions are dynamic capabilities working directly and indirectly on firm
+competetive advangate".
+
+We argue that the reason for these differing findings stems from a two distinctly
+different factor; the /emph{environmental dynamism} facing the firm, and the /emph{nature
+  of the mediating resource being employed}.
+
+TWO observetions>
+- Direct effect mediated away (disappears) in high velocity environments - Could be due to
+conception of DC as simple rules and best practices. Do they change nature? Or is it that
+they go from latent to constitutent and thus their impact becomes clearer
+
+- The mean of mediation matter in low environments.
+
+What happens? VRIO?
+Routines are never VRIO
+Processes are VRIO
+VRIO concept*idea is based on normal levels of change. In dyn changes happens faster and
+the modes of routines are more important because you need more rapid change and routinesa
+re simpler models. By being changed by DC they can generate CVRIO simply because of their
+rapid deployment. Processes on the other hand are equally important and do not get less
+VRIO facing environmental dynamism. Why? Cause they are path dependent and unique to the
+firm, however should expect them to be less important if speed of change is of
+importance.
+
+.
+
+ and a certain consensus leans toward defining
+the concept through the idea of a mediating effect through ordinary capabilities (winter,
+helfat
+
+“Moreover, we need deeper insight into the variety of mechanisms that
+underlie the performance effects of capabilities.” (Schilke, 2014a: 199)
+
+This,
+we argue, is due to the way DC behave differently under high-velocity industries compared
+to normal times, and goes back to the original contention between the seminal papers on EM
+and TPS and their different understanding of the concept.
+
+We argue that DC comes about working differently under different circumstances. As we cant
+exactly measure and observe DC (teece) we can only observe its effects when called
+upon. They are more likely to be called upon in high velocity environments when change is
+most needed. Consecnuently Eisenhardts notion of constitutent DC becomes more pronounced
+and visible under high velocity environments where DC turns to action working as
+intended. In such conditions DC will indeed work to change underlying routines and
+capabilities to enhance competetitieve advantage. However, what we usually observe in more
+stable industries nd contexts, is DC as latent and hence more correlated with competetive
+advantage cause it is related to the potential. Actual change of routines and capabilites
+are less needed so the mediation is less pronounced and we will observe a more direct
+effect cause other factors are playing into the CA explanation such as more
+generalmanagement, resources and so on. As many of these factors normally working in
+stable environments are left out in empirical models, the general idea of DC as a proxy
+for a good firm and management becomes more prevalant and we see a direct effect as a
+consequence. Proxy for a good firm is added and shows that being a good firm is more
+important in slow enviromnetn cause much of the ability to govern ana manage abusiness is
+captured in this variable in this conducion. DC is also more prevelant cause it captures a
+similar side as a latent potential to generate CA and act more as aproxy for a good
+firm. However, in high markets the impact of DC increases as it starts to work as a
+distinct force of change changing underslying routines and capabilites. Here we also see
+that the importance of other factors of a good firm diminishes because the usual metrics
+are not important - path dependency matters less and the ability to change resources
+matters increasingly and thus only ghrouhg mediation is CA achieved.
+
+However, a difference in the type of underlying resource matter. And this also goes back
+to the difference between simple rules of action and more complex routines. VRIO is
+achieved through either direct effects from DC who is VRIO because of the path dependency
+more pronounced in normal environments. 
+evidence has pointed to a dirc
+
+Noone has looked at how dc operates differently through different OC and how these
+interact with the dynamism in the environment. Conventional wisdom holds that routines are
+not able to ca[ture VRIO whereas processes can.
+
 Extant literature on DC struggles with a fundamental conception and prediction of the
@@
 
+Constitutent DC based on simpler rules will not create CA directly. 
 DC is often critizesd for being tautological and less focus has been placed on instances
@@
 %% stringer under higher dynamism
+This friction has been
+dubbed the "elephant in the room" (peteraf) and been tracked back to the seminal papers of
+Teece and Eisenhardt, as well as their their different theoretical antecedents of
+evolutionary economics (ref) and behavioral theory (ref) respectively (ref Arndt
+x2).
 

### 2019-10-11 article4_tommylars.rnw
testing R and P simultan

@@
 3  R -> CA1 0.019 0.208 0.177 1.466
+
+few items less controls
+
+      Path   LOW     t  HIGH     t
+1 DC -> CA1 0.213 2.555 0.034 0.314
+2   DC -> P 0.436 5.901 0.417 4.648
+3  P -> CA1 0.187 2.206 0.276 2.776
+> R
+       Path   LOW     t  HIGH     t
+1 DC -> CA1 0.269 2.815 0.069 0.646
+2   DC -> R 0.112 1.004 0.338 3.957
+3  R -> CA1 0.117 1.456 0.260 2.565
+>
+
+all items less controls
+
+       Path   LOW     t  HIGH     t
+1 DC -> CA1 0.355 4.786 0.133 1.348
+2   DC -> P 0.386 5.003 0.436 4.739
+3  P -> CA1 0.155 1.985 0.232 2.311
+> R
+       Path   LOW     t  HIGH     t
+1 DC -> CA1 0.417 6.879 0.144 1.484
+2   DC -> R 0.388 6.092 0.534 7.039
+3  R -> CA1 0.017 0.214 0.211 2.030
 

### 2019-10-11 article4_analysis.r

@@ -80,58 +80,29 @@ imputezw <- function(vec){
     return(vec)
 }
 
+
+
+extboot <- function(bootobj,n,nam,r){ #remembaer space between Letter and " ("P ")
+    ##this function extracts estimates and standard errors for a bootstrapped object from PLS Sem
+
+    c1 <- attr(bootobj$t,"path")
+    c2 <- bootobj$t0
+    c3 <- c(apply(bootobj$t,2,sd))
+    res <- data.frame(c1,c2,c3);colnames(res) <- c("name",paste(nam,"est",sep="_"),paste(nam,"se",sep="_"))
+    res <- res[(nrow(res)-n):nrow(res),];  rownames(res) <- NULL
+    toMatch <- c(r, "DC")
+    res <- res[(grep(paste(toMatch,collapse="|"),res$name)),]
+    res$t <- res[,2] / res[,3]
+    res <- res[,c(1,2,4)]
+    res[,2:3] <- round(res[,2:3],3)
+
+
+    return(res)
+}
+
 ## including only observations at both times
 zwadj <- subset(zw,!is.na(Q4.1_t1))
 rownames(zwadj) <- NULL
-
-## #### Princomp with only observed no imputation
-## dc1 <-  zwadj[,c("Q6.1_t1","Q6.2_t1","Q6.3_t1","Q6.4_t1","Q6.5_t1","Q6.6_t1","Q6.7_t1","Q7.1_t1","Q7.2_t1","Q7.3_t1","Q7.4_t1")]
-## dc1 <-  dc1[which(!is.na(dc1)),]
-## pdc <- fa.poly(dc1,2)
-## pdc
-
-## dc1adj <- cbind(dc11,dc12)
-## dc1adj <- round(dc1adj[which(!is.na(dc1adj[,1])),],0)
-## pdcimp <- fa.poly(dc1adj,2)
-## pdcimp
-## which(is.na(dc1adj[,1]))
-
-## ca1 <-  zwadj[,c("Q16.1_t1","Q16.2_t1","Q16.3_t1","Q16.4_t1")]
-## ca1 <-  ca1[which(!is.na(ca1)),]
-## pca1 <- fa.poly(ca1,2)
-## pca1
-
-## ca1adj <-  round(imputezw(zwadj[,c("Q16.1_t1","Q16.2_t1","Q16.3_t1","Q16.4_t1")]),0)
[…]

### 2019-10-14 article4_tommylars.rnw
still testint

--- 2019-10-07 article4_tommylars.rnw
@@
 
-Extant literature on DC struggles with a fundamental conception and prediction of the
-theory, namely if and when DC can lead to competitive advantage. This friction has been
-dubbed the "elephant in the room" (peteraf) and been tracked back to the seminal papers of
-Teece and Eisenhardt, as well as their their different theoretical antecedents of
-evolutionary economics (ref) and behavioral theory (ref) respectively (ref Arndt
-x2). Recently, distefaneo et al propopsed a theoretical integration of these varying
-conceptions of DC theory. They suggest that latent and constitutent elements of DC
-represent different constructs but are integrated in that they work differently in shaping
-strategic change.
+%% Extant literature on dynamic capabilities is battling with a fundamental conception and
+%% prediction of the theory, namely if, when and how dynamic capabilities can lead to competitive
+%% advantage.
 
-DC is often critizesd for being tautological and less focus has been placed on instances
-when dynamism can lead to poorer competitive outcomes. 
-Structural inertia, commitment \cite{schreyogg2007}. Under what conditions are changing
-capabilities counterproducttive
+Seminal contributions to the field of dynamic capabilities have argued for both direct
+\cite{Kor2005,Eriksson2014,Schilke2014a} and indirect (ref) effects of dynamic
+capabilities on competitive advantage, although increasingly the bulk of the literature
+focuses on the latter \citep{Schilke2018}. This indirect link is typically understood as
+dynamic capabilities modifying, extending or creating firm resources (helfat) (or
+lower-level operational capabilities (Winter, collis)) and thus generating competetive
+advantage (Eriksson and others). Furthermore, empirical evidence keep suggesting that both direct (ref)
+and indirect (ref) links exist. This warrant the question of \emph{when} direct and
+indirect links between dynamic capabilities and competitive advantage is most pronounced.
 
-The relationship between dynamic capabilities and competitive advantage has been one of
-great contention in the extant literature \citep{Peteraf2013,Ambrosini2009}. From this
-debate a richer understanding of how different dynamic capabilities (or functional forms
-of them) work differently to change different types of firm resources
-\citep{Helfat2015a,Teece2007,Ambrosini2009a} with implications for competitive advantage
-\citep{Peteraf2013} has emerged. Increasingly the relationship between (1) dynamic
-capabilities, (2) firm resources and routines, and competitive advantage is seen as a
-complex system with interactions between different types of each 1 and 2. Many conceptual
-contributions have excellently discussed varieties or functional forms of either dynamic
-capabilities \citep{Ambrosini2009a,Helfat2015ad,DiStefano2014} or underlying resources or
-routines \citep{Winter2003,Eisenhardt2000}. However, very few, if any, papers attempt to
-integrate varieties at multiple levels simultaneously. By asking if dynamic capabilities
-can lead to competitive advantage and how this occurs, one is far better off asking "when"
-competitive advangate is an outcome of dynamic capabiliteis and its workings.
+Moreover, firm resources or capabiltiies themselves are far from a homogenous set and
+varies among other things with respect to their uniqueness, inimatbility and value
+(barney). Important contributions have thus argued for a deeper insighi into these
+intermediaries and their mechanism calling for a "deeper insight into the variety of mechanisms that
+underlie the performance effects of capabilities.” (Schilke, 2014a: 199). 
+as well as \emph{what} different intermediaries exist.
 
-The definition of dynamic capabilities, albeit contestst, seems to be converging on
-varieties of "the ability of firms to create, modicy and extend its resource base" (ref)
-\citep{Schilke2018}. Meanwhile both dynamic capabilities as the "governing entity" and
-resources as "the governed entity" takes different forms in the literature (ref). Dynamic
-capabilities themsleves can roughly be divided into sets of simple rules governing
-undelying resources, or more complex routines developed for the same purpose
-\citep{Peteraf2013}. In other words, dynamic capabilities themselves can and cannot satisfy
-the VRIO condition. This contention is throughly covered in the literature (refs) and
-recent contribiutions have argued for interplays between simple and complex types of
-dynamic capabilities foring a more complex and initmatble dynamic system
-\citep{DiStefano2014}. Moreover, granted different forms of dynamic capabilities exist
-their impact on the "governed entity", the underlying firm resources, should also be
-varying.
+This paper investigates the boundary conditions of the VRIO condition and how dynamic
+capabilities and resources interact to create firm competitive advantage. We ask the
+following research question:
+Under which conditions are dynamic capabilities able to yield competietive advantage
+through resource orchestration and what are the different outcomes of different types of resources.
 
-To explore this we emply two radically differnet forms of dynamic capabilities / one
-geared towards transforming exitsgint resources in order to exploit them to gain
-competitive advantage (refs). The other form is geraed towards seizing new opportunities in order
-to explore new business opportunitieis (refs). We argue that competitive advantage can
-stem from each of these, but that the mechanism varies. Dynamic capabilities geared
-towards transforming for exploitation ($DC_P$) is by and of itself the result of a more
-complex set of routines configured in a way that is hard to imitate because of its path
-dependent and evolutionary nature. This legacy from evolutinoary economics is stressed as
-an important factor for creating VRIO resources (Ref peteraf). The stream of contributions
-maintaining dynamic capabilities working through the object of "changing existing
-capabilities" \citep{Teece1997,Zollo2002a,Winter2003,Zahra2006,Kale2002} also maintain
-that
-
-We argue that latent and constituted dynamic capabilites behave differently and work
-differnetly trhough differents modes (action or wahtever the term in DiStefano er).
-
-{\bf LAtent = complex process routines Teece
-Constitutent = simpler, ad hoc - Eisenhardt}
-
-We explore two different modes (natures) of dynamic capabilities and how they work
-differently (action) to create competitive advantage. Or is it the object of action as
-either resources or opportunities?
-
-By introducing different measures of different types of DC (latent and constiuted) as well
-as two different types of action (change existing or create new) we explore the workings
-of the drive train model proposed by DiStefano suggesting a fuller and more dynamic view
-on how latent and consittued DC works differently.
-
-The working of latent:
-Departing from the definintion of dynamic capabilities found in Teece (ref) and subsequent
-contributions in this tradition
-
-The working of cinstuted
-
-We identify two ditintctly different noptions of dynamic capabilities both following well
-known definitions byut weith different nature (ref distefano). We show that only the
-latent dc can directly and indirectly create CA,whereas the constituent element nature of
-DC only works through changing lower level routines.
-
-Different parts of the drive train works on different types of underlying routines
-
-Looks at competing hypotheses between Eisenhardt and teexe with respect to routinization. Finds that routininzation happens at DC level less than operational level?
-We argue that this depends on the purpose *action of the Dc and the composition of the
-focal operational capability.
-
-Reviewing the literature reveals that researchers have tended to identify dynamic capabilities post hoc, inferring their existence from successful organizational out- comes such as profitability and growth, as prior definitions would suggest (Table
-
-On the other hand we have dynamic capabilites geared toward sensing and seizing new
-opportunities as part of an effort of exploration. Such dynamic capabilities are described
-in the literature as themselves a set of more simple routines orchestrated in a manner
-such that x`
-
-Routinization at certain level, but depends on them being outward or inward looking.
-
-How can DC lead to competitive advangate. departing from the original definition this
-happens through the modification or aquisition of firm resources. But the resopurces
-themselves can and cannot be a source of competitive advantage
-
-At a minimum, in order for something to qualify as a capability, it must work in a reliable manner’ (Helfat and Peteraf, 2003: 999). Capabilities
-
-The bulk of contributions focus
-only on heterogeneity at the dynamic capabilities level, or at
-
-W
-
-work dDC offers a theory of how firms achieve
-competitive advantage over time. Yet the DC theory suffers from contradictory claims about
-competitive advantage as its outcome. On the one hand a stream of contributions argue that
-DC will lead to competitive advantage because it operates by changing operational
-capabilities in face of change and hence create strategic change (ref helfat). In this
-view these changes result in complex and path dependent processes that will be
-idiosyncratic to the firm and hard to imitate. Consequently, they can lead to competitive
-advantage.
-
-A contrary stream of literature argues that changes of operational capabilities over time
-takes the form of routines and converges towards best practice (ref EM). Such best
-practices are simpler and more observable routines that are both imitable and easy to
-copy. Such firm resources are then not idiosyncratic and can consequently not be the
-source of competitive advantage.
-
-The way DC work differnelty throug changing two sets of operational capabilities = complex
-and path dependent processes based capabilities, and simple rules/based routines.
-
-These contradictory positions have been thoroughly discussed in earlier work (see
-\cite{Peteraf2013} for a review). On the one hand DC takes the form of simple rules
-shaping underlying routines. On the other hand they take the form of complex processes.
-
-Regarding the action and the object ofthe action, simple rules are more likely to be
-involved in developing something new in response to new opportunities, while complex
-rou- tines are more concerned with changing existing resources and capabilities.
-
-In a recent "state of the art" literature review on dynamic capabilities
-\cite{Schilke2018} state that much of the attention and interest surrounding the theory is
-that it offer a route to competitive advantage which they argue is "the virtual Holy Grail
-of strategic management" (p. 393). And indeed a considerable body of the extant literature
-concerns itself with exactly this path to competitive advantage (refs from
-shcilke). Still, a discourse regarding the contingencies of the dynamic
-capabilities-competitive advantage (DC-CA) nexus (?) has panned out in the literature,
-most notably coined "the elephant in the room" \citep{Peteraf2013}: Under which conditions
-will dynamic capabilities lead to competitive advantage?
-
-\cite{Peteraf2013} argue that the seminal papers in the dynamic capabilities theory
-tradition (\cite{Teece1997} and \cite{Eisenhardt2000}) differ considerably in their view
-of to what extent the DC-CA nexus exist and under what conditions it is functional. A key
-tenant of this discourse is related to the level of routinization and the ability to
-satisfy the VRIO condition \citep{Barney1991a} of the resource-based view
-\citep{Peteraf2013}.
-
-In this paper we aim to contribute to dissecting the elephant by asking how does the DC-CA
-nexus differ between firms and what determines these differences?
-
-We do this by exploring two paths from dynamic capabilities to competitive advantage: the
-\emph{evolutionary path} and the \emph{market path}. The former is thoroughly described
-and explored in the literature (refs) and stems from the core idea of the dynamic
-capabilities theorizing. In this path dynamic capabilities work to change the operating
-routines of the firm and hence contributing to it's competitive advantage. We argue that
-this path is more suited for less dynamic environments because of its path dependent
-functioning.
-
-The \emph{market path} works not through shaping operational capabilities and routines,
-but by enabling the firm to act in factor markets for new capabilities and
-resources. Hence, it is less path dependent and can be more rapidly
-deployed. Consequently, it is more prevalent in dynamic environments.
-
-This paper contributes to the extant literature on the link between dynamic capabilities
-and competitive advantage in three ways. First, provides an empirical test to the
-drive-train model of \cite{DiStefano2014} on how dynamic capabilities can operate both
-quickly and with high frequency more directly on the strategic direction of the firm by
-acting in factor markets for important resources, and also more slowly through the
-evolutionary path of changing operational capabilities. Second, by conceptually clarifying
-the different paths to competitive advantage by linking it closely to the role of
-capability evolution and the VRIO condition. Finally, we.........
-
-CLARIFIES THE ROLE OF THE ENVIRONMENT AND MEDIATIONS HAPPENING
-
-%% How does dynamic capabilities lead to competitive advantage?
-%% Dynamic capabilities are proposed to confer a competitive advantage by adding unique value to the firm through systematic change, which enhances operational efficiency and enables increased alignment with the environment (Di Stefano et al., 2014; Peteraf et al., 2013)
-
-%% Not all organizations possess them (Collis, 1996); their path dependencies, intangibility, complexity, and organizational specificity make them hard to imitate (Gibson & Birkinshaw, 2004; Helfat & Winter, 2011); and few other means allow organizations to purposefully change on a continuous basis (Day & Wensley, 1988; Helfat et al., 2007).
-
-%% Consistent with the theoretical positions of Eisenhardt and Martin (2000), Helfat and Peteraf (2003), Zahra et al.
-(2006), and Zott (2003), among others, these researchers have argued that dynamic capabilities’ immediate purpose is to change the resource base, and that this change in the resource base, in turn, explains performance variations.
-According to this argument, resource changes serve as mediators through which dynamic capabilities affect performance.
-We
-
-%% One of the major unresolved issues in dynamic capabilities theory is to what extent and
-%% how competitive advantage is the ultimate outcome of dynamic capabilities. This very idea
-%% has
-
-%% This paper asks two questions: to what extent does a direct lnk between DC and CA exist,
-%% and what determines variations in the role of mediation between them?
-
-%% The idea that Dc impacts CA is uncontroversial (not). Little is known about how this
-%% happens. The theory holds that this happens through xreating extending and modifying the
-%% resource base. YEt, the change in firm capabilities can themselves lead to CA due to their
-%% evlutionary nature.
-
-%% Variations in the share of mediation stems from variation sin the environment. When envdyn
-%% is high firms need to act faster and hence tends to choose strategies including resource
-%% orchestration buying in factor markets cause it tkes more time to develop OR.
-
-%% In less dynamism the role of OR increases and leads to a significant proportion of CA
-%% stemming throhg the mediating effect of OR
-
-%% There is ongoing interest in (dynamic) capabilities and how they influence firm
-%% performance \citep{Fainshmidt2016a,Teece2014}. Indeed, \emph{dynamic capabilities} (DC),
-%% and its front runner, the resource-based view \citep{Barney2001,Helfat2007}, is now
-%% considered one of the major theories in strategic management
-%% \citep{Schilke2018}. Arguably, the key reason is that this theory clearly articulates how
-%% firms can alter their operating routines through dynamic capabilities. Thus, a key
-%% ingredient in this theory is that DCs can alter firms operating routines, with subsequent
-%% performance implications.
+We find thatthe dynamism surrounding hte firm represent an important boundary condition as
+suggested in parts of the literature. However, DC consinutes to generate competetive
+advnatage also in high-velocity environments, but doing increasingly so indirectly through
+resource orchestration. Furthermore, we find that non-vrio resources are more likely to
+yield competetive power in high velocity environments, and that vrio-resources tend to
+maintain their CA under any condition.
 
@@
 with the degree of environmental dynamism facing the firm.
+
+Under what cionditions are the direct path and indirect path most prevalant? Under which condi
+
+The direct
 
@@
 %% stringer under higher dynamism
+
+The link between firm resources and competitive advantage is determined by the extent to
+which resources are valuable, rare, inimitable and organized (VRIO)
+\citep{Barney1991a}. This principle is also used to evaluate how higher order capabilities
+(e.g. dynamic capabilities \citep{Winter2003,Collis1994}. This is the core principle we
+use in this article to evaluate how dynamic capabilities can and cannot create competitive
+advantage for the focal firm. Furthermore, as both higher order capabilities (e.g. dynamic
+capabilities) as well as lower-order resources and capabilities (operating routines and
+capabilities) can and cannot satisfy the VRIO condition, we find it useful to think of a
+multilevel VRIO structure in firms.
+
+\subsection{Dynamic capabilities and VRIO}
 
@@
 rules they cannot alone create competitive advantage, but could very well generate
-strategic change by facilitating acquisition of resources in factor markets. One example
-is the role of post-acquisition routines where routines to identify and deal with
-acquisition partners are a source of generating strategic change (Eisenhardt and Sull
-2001, ref). Another example is (see refs from Schilke 2018). The functioning of this
-expression of dynamic capabilities are more latent and hence mainly observable ex
-post. Hence we can see this as direct route to competitive advantage as this expression of
-dynamic capabilities work directly in the factor market in capturing resources
-needed for strategic change. We coin this direct connection as the \emph{market path}.
+strategic change by facilitating the process of resource orchestration. Resource
+orchestration is defined as "blablbalbla" (helfat). In other words, even if DC play out as
+simple rules that are not in themselves satisfying the VRIO condition, the way they work
+through creating, extending and modifying firm resources, can still yield VRIO results.
+
+On the other hand, \cite{Teece1997} and others \cite{Helfat2007} argue that dynamic
+capabiltiies will rather invariably be VRIO due to the evolutionary nature of their
+development \citep{Arndt2018,Peteraf2013}. Arguing that dynamic capabilities reflect more
+complex processes that co-evolve with responses to market changes over time and hence
+creating idiosyncratic capabilities that are unique, valuable and hard to copy
+\citep{Helfat2007,Arndt2018}. Consequently, they are likely to satisfy the VRIO condition
+and thus leading to competitive advantage.
+
+Increasingly the literature remain focused on an \emph{indirect
+  path} between dynamic capabilities and competitive advantage
+\citep{Barreto2010,Schilke2018}. The theory behind this path goes back to the core of
+dynamic capabilities where resource orchestration happens as a response to changes in the
+environment. When markets, technologies or other external factors changes, firms with high
+levels of dynamic capabilities are able to seize opportunities for changes, seize these
+opportunities and transform the resource base to fit the strategic change needed to stay
+competitive \cite{Teece2007}. This ability to adapt is by some coined \emph{evolutionary
+  fitness} defined as BLABLBALBA and stems from the ability of the firm to reconfigure
+resources in the face of change. The extant literature, however, is less clear on how the
+nature of the underlying resources matter in this indirect path. On the one hand we can
+see
+
+Following REF suggesting more reseaarch on dynamic capabilities should put forth
+competeing hypotheses we propose these first
+
+We introduce the notion of multilevel VRIO to integrate the interactions between different
+types of capabilities at different levels. This entails that dynamic capabilities (the
+high level) can consist of complex and evolutionary characteristics that are idiosyncratic
+to the firm and hence VRIO by definition along the lines of how the concept is understood
+by \cite{Teece1997}. On the other hand dynamic capabilities can also take the shape of
+simpler routines which are short lived, unstable and substitutable thus violating a key
+VRIO condition. This follows the notion of dynamic capabilities found in
+h\cite{Eisenhardt2000} arguing that they are more “more homogeneous (..) than is usually
+assumed” (EM: 1116).
+
+Moreover, these dynamic capabilities are in the extant literature argued and found to work
+directly \citep{Kor2005,Eriksson2014,Schilke2018} on competitive advantage which suggests
+that they are indeed VRIO. On the other hand, a growing body of literature (ref) as well
+a consensus on the definition of dynamic capabilities (ref), holds that they can lead to
+competitive advantage by changing underlying resources and routines. In this
+\emph{indirect path} the dynamic capabilities itself need not be VRIO as long as the
+underlying resources themselves are.
+
+\subsection{The role of dynamism}
+
+The most contentious issue in the current debate on dynamic capabilities is how their
+nature varies with the environment.
+
+If htey are indeed latent
+
+The lower level resources and routines are to be understood as conventional resources in
+line with the resources-based view
+
+WHAT IS THE ROLE OF DIRECT VS INDIRECT, HOW DOES IT RELATE TO THE ENVIRONMENT, AND WHAT
+ROLE DOES THE TYPE OF UNDERLYING RESOURCE PLAY
+
+Conventional dc literature has argued for both indirect and direct links. Indeed both
+have been found, but while the indirect link is well rooted in the theory, the direct link
+is to our knowledge less clear. The core idea of DC is that it works to modify underlying
+resources as a response to changes in the environment and hence creating strategic change
+needed to stay competitive. This resource orchestration is heavily represented in the
+literature (ref) and through this process firms are able to generate CA. In such instances
+the CA can stem from VRIO resources and/or VRIO DC. A VRIO DC would mean that the firm is able
+to shuffle and reorganize generic resources in a way that creates a new and unique
+configuration of resoures idiosyncratic and valuable to the firm. In such instances, the
+outcome whould be CA. On the other hand, the DC may not by itself be VRIO but rather a set
+of simple routines put in motion to change, but if the resources they reconfigure are
+themselves VRIO, the outcome could just as eqsily be a competetive advantage. this
+equfinaity is discussed in the literaure \cite{DiStefano2010} and makes it hard to
+distingusih between the role of DC and ordinary capabilites in generating CA.
+
+Furtemore, Considering a direct link between DC and CA, DC it self must consist of some
+VRIO characteristics to garner CA. So in owther words, when is DC working directly and
+indirectly_
+
+How are dynamic capabilities working directly on competitive advantage? The microfoundations of dynamic capabilities explicated by \cite{Teece2007} is a useful
+point of departure of this theoretical inquiry. He hold that for "analytical purposes,
+dynamic capabilities can be disaggregated into the capacity (1) to sense and shape
+opportunities and threats, (2) to seize opportunities, and (3) to maintain competitiveness
+through enhancing, combining, protecting, and, when necessary, reconfiguring the business
+enterprise’s intangible and tangible assets". Sensing and seizing is a part of what we
+would coin the "opportunity capture" of dynamic capabiliites, where as reconfiguring
+concerns itself with the "resource orchestration" needed to change assets to stay
+competetive.
+
+Hence, when considering indirect and direct paths to compettetive advantage we will have
+to be clear on two fronts: Are DC themselves VRIO and are the underlying resources and
+routines central to the resource orchestration, VRIO.
+
+       Path   LOW     t  HIGH     t
+1 DC -> CA1 0.290 2.732 0.093 0.996
+2   DC -> P 0.325 2.896 0.339 3.284
+3  P -> CA1 0.064 0.462 0.171 1.913
+>
+
+The microfoundations of dynamic capabilities—the distinct skills, processes, procedures, orga- nizational structures, decision rules, and disciplines—which undergird enterprise-level sensing, seizing, and reconfiguring capacities are difficult to develop and deploy.
+For analytical purposes, dynamic capabilities can be disaggregated into the capacity (1) to sense and shape opportunities and threats, (2) to seize opportunities, and (3) to maintain competitiveness through enhancing, combining, protecting, and, when necessary, reconfiguring the business enter- prise’s intangible and tangible assets.
+
+t its most fundamental level innovation research concerns itself with a simple
+input-output model \citep{Adams2006} where innovation output is seen as a function of
+efforts put into the innovation process. However, firms vary with respect to their ability
+to utilize input and transform it into innovation output. This transformation of input
+into output has been studied with different perspectives and conceptualizations such as
+productivity of R\&D \citep{Gwynne2015}, innovation capability \citep{Breznik2014},
+innovation factor productivity (ref) and innovation conversions rate
+\citep{Duran2015}. \newline
+
+\subsection{The idiosyncratic nature and strategic expression of IC}
+The question of why firms vary in the degrees of innovation output they get from similar
+levels of innovation input, leads on to a higher order capablility that coordinates and
+extends the first order routines and resources as input in the innovation process. By
+innovation input we mean the resources and routines put into the effort creating
+innovation which composition is dealt with in a large literature (see \cite{Becheikh2006}
+for a review). Innovation output means new products, processes, business models, and
+organizational traits as the results of a purposeful enactment of resources (Van de Ven
+1995). The mechanisms through which input is transformed to output is a reflection of firm
+idiosyncratic abilities. At the meta level this concept is related to entrepreneurial
+orientation \citep{Lumpkin1996}, entrepreneurial action \citep{Klein2016}, innovation
+capability \citep{Breznik2014}, and absorptive capacity \citep{Cohen1990a}. We go with the
+term \emph{innovation capability (IC)} defined as the "ability to continuously transform
+knowledge and ideas into new products, processes and systems for the benefit of the firm
+and its stakeholders"\cite[p. 384]{Lawson2001}. IC is characterized by some factors
+similar for all the above mentioned concepts such as the ability to \emph{sense, seize} and
+\emph{transform} opportunities into outcomes \citep{Teece2007}, and it`s idiosyncratic
+nature is argued by several earlier contributions \citep{Duran2015,Klein2016}. Or as put by
+\cite{Duran2015}: "While most researchers assume that a positive correlation exists
+between innovation input and innovation output, the “slope” of this relationship likely
+differs among organizations because of the complexity of innovation management." (ibid p
+##). Innovation management (def) is the managerial levers for creating innovation
+capabilities, i.e. their ability to orchestrate resources \citep{Sirmon2011} which is an
+important part of what \cite{Helfat2007} calls \emph{Dynamic Managerial Capabilities
+  (MDC)} defined as "the capacity of managers to purposefully create, extend, or modify
+the resource base of an organization" (ibid p 24). MDC, and hence IC, is heterogeneous
+between firms due to the evolutionary nature of developing such capabilities
+\citep{Teece2014,Eriksson2014}. Consequently, we propose the following hypothesis:\newline
+
+H1: IC is heterogeneous between firms due to differences in their sensing and seizing
+abilities \newline
+
+\cite{Teece2007,Teece2014} makes a sharp distinction between ordinary- and dynamic
+capabilities arguing, among other dimensions, that managerial emphasis in the former
+relates to cost control, whereas DC relates to entrepreneurial asset orchestration,
+i.e. "doing the things right" in novel ways. A similar line of reasoning argues that
+dynamic capabilities differs from ordinary routines and capabilities in that it goes
+beyond best practices in operational problem solving \citep{Eisenhardt2000}. Consequently,
+we would expect IC to be positively related to innovation outcomes as firms with high IC
+would generate more innovation. Moreover, as managers face changing environments, the ones
+with strong IC would emphasize innovation activities, whereas those with weaker IC would
+have to resort to other means of adapting to change, e.g. cost efficiency. In other words,
+under environmental dynamism high-IC companies will engage in sensing, seizing and
+transforming opportunities, trusting the evolutionary fitness of
+their dynamic capabilities, and preferring innovation as strategic choice. Meanwhile, low-IC
+companies will revert to operating, administering and governing the business, trusting
+their technical fitness and focus strategic choice on efficiency
+\citep{Teece2014}. \newline
+
+H2: IC is positively related to innovation activities \newline
+H3: IC is negatively related to efficiency enhancing activities \newline
+
+\subsection{The relative importance of sensing and seizing}
+
+The concept of sensing and seizing has analogous meaning in theoretical traditions tangent
+to DC. Notably entrepreneurship \citep{Hitt2011} and organizational theory
+\citep{March1991}. \cite{Hitt2011} states that "entrepreneurship involves identifying and
+exploiting opportunities" (ibid p 59) where identification is tied to the process of
+discovery \citep{Shane2000}. Based on the definitions of opportunity discovery as DEF HERE
+juxtaposed to the definition of sensing as "a scanning, creation, learning, and
+interpretive activity" \citet[p. 1322]{Teece2007} we argue that they are similar in nature
+and usable for exploring the importance of the latter in the innovation process. It also
+bears resemblance to the concept of organizational exploration as searching, risk-taking,
+discovery, experimentation, prototyping, and flexibility \citep{March1991}. Independent of
+the nature of opportunities to be sensed as being either objective
+\citep{Alvarez2007,Shane2000} or created \citep{Alvarez2007}, the process of sensing does
+require resources and capabilities for search (ref) and a clear affinity between
+opportunity and a project exist (casson and Wadeson in Mcmullen2007) suggesting s clear
+inter dependency between routines and resources, and higher order capabilities of sensing
+\citep{Teece2007} and making sense of the opportunity
+\citep{Weick1995,March1991}. Consequently, we would expect the sensing class of dynamic
+capabilities to be positively related to innovation on the one hand, and reinforcing the
+impact from innovation input simultaneously.\newline
+
+H4: Firms with strong sensing abilities will yield higher innovation output \newline
+
+H5: Sensing as dynamic capability reinforces input in the innovation process to
+generate innovation output \newline
+
+In similar ways the concepts of seizing \citep{Teece2007} and exploitation \citep{Shane2000}
+bears resemblance. However, by virtue of its nature innovation represent novel processes
+within the firm so that parts of the understanding of exploitation is
+redundant. Exploitation is defined as utilizing old certainties within the organization
+\citep{March1991} - that is existing resources and capabilities. Innovation does by its
+very nature represent a shift from existing resources and certainties (albeit often a very
+incremental one, but a shift nontheless). Hence the dichotmous nature of exploration vs
+exploitation does not always ring true for innovation processes. However, the discovery and
+exploration of new opportunities is in any case a first step of any innovation process,
+and sensing is the core class of dynamic capabiltieis in place to facilitate this
+process. When the opportunity has been discovered through sensing, the firm`s ability to
+capture value and generate innovation will rest on its ability to seize the opportunity -
+or in other words - exploit this newly arisen opportunity. As such the exploitation
+happens not on existing certainties, but of the potential future certainty arising from
+the innovation opportunitiy from the sensing. Consequently, we argue that the concept of
+seizing as rooted in a sense of grasping opportunities already sensed, is a more useful
+construct understanding firm innovation. \newline
+
+Similar to sensing, the process of seizing requires considerable efforts in enhancing
+competencies and routines (i.e. orchestrating \citep{Hitt2011}) to grasp the opportunity
+identified \citep{Shane2000}.\newline
+
+H6: Firms with strong seizing abilities will yield higher innovation output \newline
+
+H7: Seizing as dynamic capability reinforces input in the innovation process to
+generate innovation output \newline
+
+Despite being conceptually sequential (i.e. seizing follows sensing) their relative
+importance to the innovation process is less clear from the existing literature. However,
+seizing is recognizing potential from the sensed opportunities by combining novel insights
+and market evolution and dynamics. Leveraging this opportunity does, however, have
+implications for strategic choices and decisions to invest \citep{Teece2007,Helfat2015}
+and such pursuits will likely require asset specific investments
+\citep{Williamson1985}(MORE TO THE POINT REF HERE). This mechanism is fundamental as it
+ties into the incentives to develop such capabilities \emph{ex ante}
+\citep{Stieglitz2009}. When faced with a new venture opportunity firms will have to make
+timely investment decisions with potential considerable lock in effects leading to a
+Stackelberg-type investment problem \citep{Arend2009}. Comparatively, the processes of
+sensing can incur with considerable search and discovery costs (REF), but "sensing does
+not necessarily involve large commitments of resources, at least not relative to seizing"
+\citep[p. 1343]{Teece2007}.Thus, due to its asset specific requirements, the expected
+"return" from seizing should be higher than that of sensing.\newline
+
+\noindent H8: Seizing is of relatively stronger importance in transforming innovation
+input to output \newline
+
+Finally, turning to innovation output as a first step in generating value, seizing also
+plays into the process of generating business models for capturing value from innovation
+\citep{Teece2007,Helfat2015}. A business model can be understood as a "pathway by which
+technological innovation and knowhow combined with the utilization of tangible and
+intangible assets are converted into a stream of profit"
+\citep[p. 40]{Teece2017}. Consequently, seizing will play a significant role in
+transforming innovation into value for the company by re-orchestrating resources and
+capabilities \citep{Teece2010,Teece2017}. Hence, we will see seizing working in different
+parts of the input-output process. \newline
+
+\noindent H9: Seizing reinforces the process of generating value from innovation \newline
+
+%\subsection{Balancing sensing and seizing - ambidexterity?}
+%\begin{answer}
+%  Not really sure if this is important or if it just adds confusion. Perhaps suggesting
+%  writing a separate conceptual paper on the differences between exploration /exploitation
+%  vs sensing/seising at a later stage
+%\end{answer}
+
+%The classical notion of the innovator`s dilemma (ref christensen) holds that
+%firms face a trade-off between pursuing new avenues for business
+%opportunities on the one hand (novelty), and maintaining efficient organizational
+%characteristics on the other (efficiency). This trade-off is arguably leading certain
+%firms to inertia in the face of environmental change due to limited abilities to pursue
+%both. If this holds true we would expect a firm with considerable abilities for sensing, to be less
+%able to seize, and vice versa. However, a related stream of literature argues that firms
+%can do both by being \emph{ambidexterous} \citet{oreilly2004}.   \newline
+
+\section{Studying innovation capabilities in context}
+There are two important obstacles to empirically studying the working of innovation
+capabilities as dynamic capabilities at the firm level. First, dynamic capabilities are
+mainly considered valuable and operational in dynamic environments
+\citep{Teece1997a,Helfat2007}, thus finding the proper context capturing this dynamism is
+crucial. When studying the phenomena across a multitude of industries and firms with
+simultaneously, the challenge arise to identify a proper context for inquiry. We
+understand environmental dynamism to exhibit volatile and unpredictable characteristics
+such as unstable demand conditions and shifts in industry structure, and increased
+probability of supply or demand shocks \citep{Sirmon2007,Schilke2014}. In such
+environments states, situations, unfamiliar to the firm occur and challenges it`s ability
+to make sense of the market \citep{Weick1995}, i.e. matching the environment with a proper
+internal response. Moreover, firms meeting new challenges and finding existing routines
+and resource configurations to be insufficient in coping, tend to discourage truly novel
+explorative solutions \citep{schreyogg2007}. This combined "matching" and "inertia" problem
+will be remedied by dynamic capabilities making them a mediating factor for environmental
+dynamism \citep{Schilke2014}. In addressing this challenge of context we find the 2008
+global financial crisis as a useful back drop. The rapid decline in financial asset value
+coupled with soaring volatility, and subsequent falling demand in the real economy,
+constitute an interesting backdrop for our study \citep{Makkonen2014}.\newline
+
+A second challenge is the measurement and operationalization of innovation capabilities as
+dynamic capabilities \citep{Schilke2014}. A majority of studies are, however, relying on
+proxies with single items capturing the nature of dynamic capabilities
+\citep{McKelvie2009}, but several studies are increasingly building latent measures based
+on observable characteristics to develop a more nuanced understanding of the phenomenon
+\citep{Makkonen2014,Schilke2014}. We reconfigure the framework put forth by
+\cite{Helfat2015} on how observable traits at the management level is operationalized into
+sensing, seizing and transforming classes of dynamic capabilities. Following
+\cite{Breznik2014} arguing for the similar nature of dynamic- and innovation capabilities,
+we focus on the sensing and seizing aspect as most relevant for studying innovation in an
+input-output framework. Sensing and seizing are, as argued earlier in this paper, related
+to other well established constructs in the innovation and entrepreneurship literature and
+hence suitable for the innovation context, most notably the idea of resource orchestration
+\citep{Hitt2011} and exploration/exploitation \citep{March1991}.\newline
+
+\cite{Helfat2015} demonstrate that certain cognitive capabilities at the management level
+are antecedents of dynamic capabilities. Managerial \emph{perception} and \emph{attention}
+enhance the ability for sensing. Perception relates to sensing in that management "use
+cognitive frameworks they possess to “connect the dots” between changes in technology,
+demographics, markets, government policies, and other factors"
+\citep[p. 831]{Baron2006}. Attention, in turn, are related to perception, and hence to
+sensing, as it enables managers to focus on particular information to focus "on relevant
+stimuli (..)[to] facilitate environmental scanning" \citep[p. 839]{Helfat2015} necessary for
+opportunity discovery \citep{Companys2007} and, consequently, sensing.\newline
+
+Underpinning seizing are capabilities for \emph{problem solving} and
+\emph{reasoning}. These are treated as one construct by \cite{Helfat2015}. In our
+input-output model it is useful to distinguish between seizing innovation opportunities in
+the form of deciding to invest and pursue discovered potential in the sensing process
+(hence in helping generating innovation output), and the process of capturing value (i.e
+generating innovation gain) through developing business models. \cite{Helfat2015} does not
+explicitly make such a distinction presumably because their dependent variable is a
+broader "firm performance" and because the impact of problem solving and reasoning is
+working similarly in creating innovation output and innovation gain. \newline
+
+Having found a useful context and a conceptual framework for operationalizing innovation
+capabilities, we now turn to the data and methods applied in this paper.
+
+       name Mean_est     t
+3   DC -> P    0.396 6.157
+4   DC -> R    0.416 8.104
+5 DC -> CA1    0.239 4.018
+8  P -> CA1    0.172 2.724
+9  R -> CA1    0.081 1.262
+> R
+       Path   LOW     t  HIGH     t
+1 DC -> CA1 0.417 6.585 0.144 1.513
+2   DC -> R 0.388 6.078 0.534 7.525
+3  R -> CA1 0.017 0.219 0.211 2.123
+> P
+       Path   LOW     t  HIGH     t
+1 DC -> CA1 0.355 4.805 0.133 1.379
+2   DC -> P 0.386 5.294 0.436 4.663
+3  P -> CA1 0.155 2.193 0.232 2.315
+> B
+       name R_LOW_est   t.x R_HIGH_est   t.y
+1 DC -> CA1     0.355 5.407      0.044 0.400
+2   DC -> P     0.376 3.729      0.432 4.668
+3   DC -> R     0.366 5.569      0.522 7.225
+4  P -> CA1     0.158 1.989      0.220 2.357
+5  R -> CA1     0.010 0.135      0.200 2.033
+>
+
+%% creating and One example
+%% is the role of post-acquisition routines where routines to identify and deal with
+%% acquisition partners are a source of generating strategic change (Eisenhardt and Sull
+%% 2001, ref). Another example is (see refs from Schilke 2018). The functioning of this
+%% expression of dynamic capabilities are more latent and hence mainly observable ex
+%% post. Hence we can see this as direct route to competitive advantage as this expression of
+%% dynamic capabilities work directly in the factor market in capturing resources
+%% needed for strategic change. We coin this direct connection as the \emph{market path}.
 

### 2019-10-14 article4_analysis.r

@@ -113,15 +113,13 @@ dc01 <-  imputezw(zwadj[,c("Q6.2_t1","Q6.4_t1", "Q6.5_t1","Q7.1_t1","Q7.2_t1")] 
 dc02 <-  imputezw(zwadj[,c("Q6.1_t1","Q7.3_t1","Q7.4_t1")] )
 ca0 <-  imputezw(zwadj[,c("Q28","Q28a","Q28c")] )
 ca1 <-   imputezw(zwadj[,c("Q16.1_t1","Q16.2_t1","Q16.4_t1")] )
-or1 <-   imputezw(zwadj[,c("Q5.4_t1","Q5.6_t1","Q5.7_t1")])
-or0 <-   imputezw(zwadj[,c("Q21c","Q21d","Q21e")])
+or1 <-   imputezw(zwadj[,c("Q5.4_t1","Q5.6_t1","Q5.7_t1","Q5.1_t1","Q5.2_t1","Q5.3_t1","Q5.5_t1")])
+or0 <-   imputezw(zwadj[,c("Q21c","Q21d","Q21e","Q22","Q22a","Q22b","Q22c")])
 ma01 <-  imputezw(zwadj[,c( "Q8.7_t1", "Q8.8_t1", "Q8.9_t1")])
 ma02 <-  imputezw(zwadj[,c("Q24","Q24a","Q24b","Q24c","Q24d")])
 complist <- list(DC_P=dc01,DC_X=dc02,CA_t=ca0,CA=ca1,P=or1,R=ma01)
 vcontrols <- zwadj[,c("size","age","dyn","pm","lassets")]
 zwadj <- cbind(dc01,dc02,ca0,ca1,or1,or0,ma01,vcontrols)
-
-
 
 
 ######## ADJUSTING DATASET WITH DELTA
@@ -143,22 +141,21 @@ zwadj$d3 <- zwadj$Q5.7_t1 - zwadj$Q21e
 ## zwadj$d11 <- zwadj$Q7.4_t1 -zwadj$Q20e
 
 
-## zwadj$d4 <- zwadj$Q5.1_t1 - zwadj$Q22
-## zwadj$d5 <- zwadj$Q5.2_t1 - zwadj$Q22a
-## zwadj$d6 <- zwadj$Q5.3_t1 - zwadj$Q22b
-## zwadj$d7 <- zwadj$Q5.5_t1 - zwadj$Q22c
-
[…]

### 2019-10-15 article4_analysis.r
Before introducing mindset

@@ -111,22 +111,50 @@ rownames(zwadj) <- NULL
 ## Running median imputations
 dc01 <-  imputezw(zwadj[,c("Q6.2_t1","Q6.4_t1", "Q6.5_t1","Q7.1_t1","Q7.2_t1")] )
 dc02 <-  imputezw(zwadj[,c("Q6.1_t1","Q7.3_t1","Q7.4_t1")] )
+dc00 <-  imputezw(zwadj[,c("Q19", "Q20d","Q20e")] )
 ca0 <-  imputezw(zwadj[,c("Q28","Q28a","Q28c")] )
 ca1 <-   imputezw(zwadj[,c("Q16.1_t1","Q16.2_t1","Q16.4_t1")] )
 or1 <-   imputezw(zwadj[,c("Q5.4_t1","Q5.6_t1","Q5.7_t1","Q5.1_t1","Q5.2_t1","Q5.3_t1","Q5.5_t1")])
 or0 <-   imputezw(zwadj[,c("Q21c","Q21d","Q21e","Q22","Q22a","Q22b","Q22c")])
 ma01 <-  imputezw(zwadj[,c( "Q8.7_t1", "Q8.8_t1", "Q8.9_t1")])
 ma02 <-  imputezw(zwadj[,c("Q24","Q24a","Q24b","Q24c","Q24d")])
+m0 <- imputezw(zwadj[,c("Q16a","Q16b","Q17a","Q17b")])
+m1 <- imputezw(zwadj[,c("Q4.1_t1","Q4.2_t1","Q4.4_t1","Q4.5_t1")])
+#m0 <- imputezw(zwadj[,c("Q18a","Q18b","Q18d")])
+#m1 <- imputezw(zwadj[,c("Q4.7_t1","Q4.8_t1","Q4.9_t1")])
+
+
 complist <- list(DC_P=dc01,DC_X=dc02,CA_t=ca0,CA=ca1,P=or1,R=ma01)
 vcontrols <- zwadj[,c("size","age","dyn","pm","lassets")]
-zwadj <- cbind(dc01,dc02,ca0,ca1,or1,or0,ma01,vcontrols)
+zwadj <- cbind(dc01,dc02,dc00,ca0,ca1,or1,or0,ma01,m0,m1,vcontrols)
 
+#### Testing constructs
+
+
+m0 <- zwadj[,c("Q18a","Q18b","Q18d")]
[…]

### 2019-10-15 article4_analysis_v2.r
new analysis for tommy

@@ -1,0 +1,303 @@
+
+
+setwd("/Users/larshovdanmolden/Documents/git/article3")
+source("./estimation/packages.r")
+source("./estimation/article_functions.r")
+
+require("MASS")
+library(sampleSelection)
+library(mediation)
+library(reshape)
+library(huxtable)
+library(semPLS)
+###install.packages("huxtable")
+                                        #library(polycor)
+
+## This loads the data workspace where skattefunn_data.r is already loaded
+load("./data/art3base.RData")
+
+## Overall system settings
+options(digits=8)
+Sys.setlocale("LC_ALL", 'en_US.UTF-8')
+
+## Importing and cleaningemail address and the project number
+regdataraw = read.spss("./data/regdata_tommy.sav", to.data.frame=TRUE, labels=F)
+regdatazw <- regdataraw[,c("epost","prosjektnummer")] #could add ny_epost too
+regdatazw$epost <- str_trim(as.character(regdatazw$epost))
+names(regdatazw) <- c("email","pnr")
+
+## Importing Skattefunn data
+regdatasf <- sfmain[,c("Prosjektnummmer","Organisasjonsnummer")]
+names(regdatasf) <- c("pnr","orgnr") #orgnr is a unique identifier for each firm / same for pnr at project level
+datazw = read.csv("./data/skattefunn_10_clean.csv", sep=";",dec=",", header=T, na.strings="-1")
+
+md <- datazw[c("Resp","dc_t0","dc_t1")]
+md$Resp <- str_trim(as.character(md$Resp))
+colnames(md) <- c("email","dc0","dc1")
+
+## NB / regdf comes from skattefunn_data.r contains all projects, not only endreport
+matchvec <- match(md$email,regdf$email)
+regdata <- cbind(md,regdf[matchvec,])
+datazw <- cbind(datazw,regdata)
+
+## Splitting datazw in first wave and second wave
+zw0 <- data.frame(orgnr=datazw$orgnr);zw0$yr <- 2004
[…]

### 2019-10-21 article4_tommylars.rnw
after tommy meeting first draft

--- 2019-10-11 article4_tommylars.rnw
@@
 %% advantage. 
+%% This paper is about how apsobritve capacity can come about as strategic posture
+%https://arrow.dit.ie/cgi/viewcontent.cgi?article=1009&context=buschmancon
 
-Seminal contributions to the field of dynamic capabilities have argued for both direct
+% paper about the DC for MNC in india an dimpact on CA
+%https://journals.sagepub.com/doi/abs/10.1177/0971890717701781
+
+The presence of a direct path from dynamic capabilities and competetive advantage is
+somewhat puzzling. It eiter suggests ommited importrant mediating factors such as
+resources, or that dynamic capabilities can act outside "creating, extending and modifying
+the firm resources base". A growing consensus on the definition as well as the
+theoretical mechanisms underpinning dynamic capabilities suggest that dc work indirectly
+towards strategic change by changing firm resources. Hence, the presence of direct effects
+seems increasingly odd. Still, seminal contributions to the field of dynamic capabilities have argued for both direct
 \cite{Kor2005,Eriksson2014,Schilke2014a} and indirect (ref) effects of dynamic
 capabilities on competitive advantage, although increasingly the bulk of the literature
-focuses on the latter \citep{Schilke2018}. This indirect link is typically understood as
-dynamic capabilities modifying, extending or creating firm resources (helfat) (or
-lower-level operational capabilities (Winter, collis)) and thus generating competetive
-advantage (Eriksson and others). Furthermore, empirical evidence keep suggesting that both direct (ref)
-and indirect (ref) links exist. This warrant the question of \emph{when} direct and
-indirect links between dynamic capabilities and competitive advantage is most pronounced.
+focuses on the latter \citep{Schilke2018}.
 
-Moreover, firm resources or capabiltiies themselves are far from a homogenous set and
-varies among other things with respect to their uniqueness, inimatbility and value
-(barney). Important contributions have thus argued for a deeper insighi into these
-intermediaries and their mechanism calling for a "deeper insight into the variety of mechanisms that
-underlie the performance effects of capabilities.” (Schilke, 2014a: 199). 
-as well as \emph{what} different intermediaries exis .
+ Resource orchestration is defined as "blablbalbla" (helfat)
 
-%% Extant literature on dynamic capabilities is battling with a fundamental conception and
-%% prediction of the theory, namely if, when and how dynamic capabilities can lead to competitive
-%% advantage. 
-all items
+This indirect link is typically understood as dynamic capabilities modifying, extending or
+creating firm resources (helfat) (or lower-level operational capabilities (Winter,
+collis)) and thus generating competitive advantage (Eriksson and others).The direct path,
+however, is theoretically less explicitly dealt with in the extant literature although
+empirical evidence keep suggesting that both direct (ref) and indirect (ref) links exist.
 
-       Path   LOW     t  HIGH     t
-1 DC -> CA1 0.303 3.517 0.087 0.710
-2   DC -> P 0.445 6.070 0.435 3.972
-3  P -> CA1 0.273 3.174 0.308 3.164
-> R
-       Path   LOW     t  HIGH     t
-1 DC -> CA1 0.438 6.161 0.134 0.988
-2   DC -> R 0.400 5.661 0.549 8.033
-3  R -> CA1 0.015 0.186 0.195 1.555
->
+In this paper we explore to what extent a direct link between dynamic capabilities and
+competitive advantage work, and under which conditions it is most pronounced. Specifically
+the research question is:
 
-fewer items
+{\bf How is a direct link between dynamic capabilities and competitive advantage working
+  and under which conditions does it come into play or not?}
 
-      Path   LOW     t   HIGH      t
-1 DC -> CA1 0.173 1.771 -0.017 -0.172
-2   DC -> P 0.437 5.183  0.432  4.875
-3  P -> CA1 0.329 3.646  0.353  3.731
-> R
-       Path   LOW     t  HIGH     t
-1 DC -> CA1 0.292 2.891 0.049 0.438
-2   DC -> R 0.142 1.287 0.370 4.267
-3  R -> CA1 0.109 1.471 0.244 2.344
+We argue that direct link exist as a response to the multilevel notion of strategy itself
+and captures strategic change not typically associated with the resource based
+view. Furthermore, we show that the prevalence of the direct link is a function of the
+nature of underlying resources dynamic capabilities are aimed at "creating, extending and
+modifying", specifically if they are valuable and idiosyncratic to the firm or not, and
+the environment facing the firm.
 
-more items
+Our findings indicate that the direct path is less prevalent in very dynamic environments
+where the indirect path becomes far more important. Furthermore, the effect of dynamism is
+partly contingent on the nature of the firm resources suggesting a more complex
+understanding of how imitable and simple resources can play a role in generating
+competetive advantage.
 
-       Path   LOW     t  HIGH     t
-1 DC -> CA1 0.314 4.107 0.139 1.236
-2   DC -> P 0.386 5.481 0.391 3.797
-3  P -> CA1 0.291 3.596 0.292 3.011
-> R
-       Path   LOW     t  HIGH     t
-1 DC -> CA1 0.439 6.095 0.163 1.122
-2   DC -> R 0.428 5.547 0.579 7.972
-3  R -> CA1 0.019 0.208 0.177 1.466
+Our contributions are twofold. First, we explore different mediators by explicitly
+modeling a causal chain with different types of underlying resources, as well as
+under different environments. This is explicitly called for in the literature as "only
+four percent of the articles in our sample explicitly examined possible causal mechanisms,
+suggesting a significant gap in the literature" (Schilke 2018). This work sheds light on
+the contingencies and boundary conditions of the link between dynamic capabilities and the
+"holy grail of strategy" (Schilke et al), competetive advantage.
 
-Seminal contributions to the field of dynamic capabilities have argued for both direct
-\cite{Kor2005,Eriksson2014,Schilke2014a} and indirect (ref) effects of dynamic
-capabilities on competitive advantage, although increasingly the bulk of the literature
-focuses on the latter \citep{Schilke2018}. This indirect link is typically understood as
-dynamic capabilities modifying, extending or creating firm resources (helfat) (or
-lower-level operational capabilities (Winter, collis)) and thus generating competetive
-advantage (Eriksson and others). Furthermore, empirical evidence keep suggesting that both direct (ref)
-and indirect (ref) links exist. This warrant the question of \emph{when} and under which conditions direct and
-indirect links between dynamic capabilities and competitive advantage is most pronounced.
+Second, we explore a theoretical explanation for why a direct link between dynamic
+capabiliites and competetive advantage may exist. By leaning on empirical evidence
+suggesting a multitude of explanations for performance differentials between firms, we
+suggest that dyanmic capabilities can act outside the theorized path of "resource
+orchestration" through strateic efforts such as industry positioning (porter) or
+institutional leverage (Peng).
 
-Moreover, firm resources or capabiltiies themselves are far from a homogenous set and
-varies among other things with respect to their uniqueness, inimatbility and value
-(barney). Important contributions have thus argued for a deeper insighi into these
-intermediaries and their mechanism calling for a "deeper insight into the variety of mechanisms that
-underlie the performance effects of capabilities.” (Schilke, 2014a: 199). In other words,
-adding to the question of when direct and indirect links are most pronounced, we would
-also need to understand \emph{what} different forms of intermediatons work under these
-aforementioned conidtions.
+%%%%%%%%%%%%%%5
 
-Still, important empirical contributions argue for a direct link although the emerginig
-consensus of the literature argues for an indirect link. This warrants the research question:
-"Under what conditions are dynamic capabilities working directly and indirectly on firm
-competetive advangate".
+%%%%%%%%%%%%%%
 
-We argue that the reason for these differing findings stems from a two distinctly
-different factor; the /emph{environmental dynamism} facing the firm, and the /emph{nature
-  of the mediating resource being employed}.
+%% This warrant the question of \emph{when}
+%% direct and indirect links between dynamic capabilities and competitive advantage is most
+%% pronounced.
 
-TWO observetions>
-- Direct effect mediated away (disappears) in high velocity environments - Could be due to
-conception of DC as simple rules and best practices. Do they change nature? Or is it that
-they go from latent to constitutent and thus their impact becomes clearer
+%% Moreover, firm resources or capabiltiies themselves are far from a homogenous set and
+%% varies among other things with respect to their uniqueness, inimatbility and value
+%% (barney). Important contributions have thus argued for a deeper insighi into these
+%% intermediaries and their mechanism calling for a "deeper insight into the variety of mechanisms that
+%% underlie the performance effects of capabilities.” (Schilke, 2014a: 199). 
+%% as well as \emph{what} different intermediaries exist.
 
-- The mean of mediation matter in low environments.
+%% This paper investigates the boundary conditions of the VRIO condition and how dynamic
+%% capabilities and resources interact to create firm competitive advantage. We ask the
+%% following research question:
+%% Under which conditions are dynamic capabilities able to yield competietive advantage
+%% through resource orchestration and what are the different outcomes of different types of resources.
 
-What happens? VRIO?
-Routines are never VRIO
-Processes are VRIO
-VRIO concept*idea is based on normal levels of change. In dyn changes happens faster and
-the modes of routines are more important because you need more rapid change and routinesa
-re simpler models. By being changed by DC they can generate CVRIO simply because of their
-rapid deployment. Processes on the other hand are equally important and do not get less
-VRIO facing environmental dynamism. Why? Cause they are path dependent and unique to the
-firm, however should expect them to be less important if speed of change is of
-importance.
+%% We find thatthe dynamism surrounding hte firm represent an important boundary condition as
+%% suggested in parts of the literature. However, DC consinutes to generate competetive
+%% advnatage also in high-velocity environments, but doing increasingly so indirectly through
+%% resource orchestration. Furthermore, we find that non-vrio resources are more likely to
+%% yield competetive power in high velocity environments, and that vrio-resources tend to
+%% maintain their CA under any condition.
 
-.
+%% We demonstrate that two paths indeed do exist and that their relative importance varies
+%% with the degree of environmental dynamism facing the firm.
 
- and a certain consensus leans toward defining
-the concept through the idea of a mediating effect through ordinary capabilities (winter,
-helfat
+%% Under what cionditions are the direct path and indirect path most prevalant? Under which condi
 
-“Moreover, we need deeper insight into the variety of mechanisms that
-underlie the performance effects of capabilities.” (Schilke, 2014a: 199)
-
-This,
-we argue, is due to the way DC behave differently under high-velocity industries compared
-to normal times, and goes back to the original contention between the seminal papers on EM
-and TPS and their different understanding of the concept.
-
-We argue that DC comes about working differently under different circumstances. As we cant
-exactly measure and observe DC (teece) we can only observe its effects when called
-upon. They are more likely to be called upon in high velocity environments when change is
-most needed. Consecnuently Eisenhardts notion of constitutent DC becomes more pronounced
-and visible under high velocity environments where DC turns to action working as
-intended. In such conditions DC will indeed work to change underlying routines and
-capabilities to enhance competetitieve advantage. However, what we usually observe in more
-stable industries nd contexts, is DC as latent and hence more correlated with competetive
-advantage cause it is related to the potential. Actual change of routines and capabilites
-are less needed so the mediation is less pronounced and we will observe a more direct
-effect cause other factors are playing into the CA explanation such as more
-generalmanagement, resources and so on. As many of these factors normally working in
-stable environments are left out in empirical models, the general idea of DC as a proxy
-for a good firm and management becomes more prevalant and we see a direct effect as a
-consequence. Proxy for a good firm is added and shows that being a good firm is more
-important in slow enviromnetn cause much of the ability to govern ana manage abusiness is
-captured in this variable in this conducion. DC is also more prevelant cause it captures a
-similar side as a latent potential to generate CA and act more as aproxy for a good
-firm. However, in high markets the impact of DC increases as it starts to work as a
-distinct force of change changing underslying routines and capabilites. Here we also see
-that the importance of other factors of a good firm diminishes because the usual metrics
-are not important - path dependency matters less and the ability to change resources
-matters increasingly and thus only ghrouhg mediation is CA achieved.
-
-However, a difference in the type of underlying resource matter. And this also goes back
-to the difference between simple rules of action and more complex routines. VRIO is
-achieved through either direct effects from DC who is VRIO because of the path dependency
-more pronounced in normal environments. 
-evidence has pointed to a dirc
-
-Noone has looked at how dc operates differently through different OC and how these
-interact with the dynamism in the environment. Conventional wisdom holds that routines are
-not able to ca[ture VRIO whereas processes can.
-
-Extant literature on DC struggles with a fundamental conception and prediction of the
-theory, namely if and when DC can lead to competitive advantage. This friction has been
-dubbed the "elephant in the room" (peteraf) and been tracked back to the seminal papers of
-Teece and Eisenhardt, as well as their their different theoretical antecedents of
-evolutionary economics (ref) and behavioral theory (ref) respectively (ref Arndt
-x2). Recently, distefaneo et al propopsed a theoretical integration of these varying
-conceptions of DC theory. They suggest that latent and constitutent elements of DC
-represent different constructs but are integrated in that they work differently in shaping
-strategic change.
-
-Constitutent DC based on simpler rules will not create CA directly. 
-DC is often critizesd for being tautological and less focus has been placed on instances
-when dynamism can lead to poorer competitive outcomes. 
-Structural inertia, commitment \cite{schreyogg2007}. Under what conditions are changing
-capabilities counterproducttive
-
-The relationship between dynamic capabilities and competitive advantage has been one of
-great contention in the extant literature \citep{Peteraf2013,Ambrosini2009}. From this
-debate a richer understanding of how different dynamic capabilities (or functional forms
-of them) work differently to change different types of firm resources
-\citep{Helfat2015a,Teece2007,Ambrosini2009a} with implications for competitive advantage
-\citep{Peteraf2013} has emerged. Increasingly the relationship between (1) dynamic
-capabilities, (2) firm resources and routines, and competitive advantage is seen as a
-complex system with interactions between different types of each 1 and 2. Many conceptual
-contributions have excellently discussed varieties or functional forms of either dynamic
-capabilities \citep{Ambrosini2009a,Helfat2015ad,DiStefano2014} or underlying resources or
-routines \citep{Winter2003,Eisenhardt2000}. However, very few, if any, papers attempt to
-integrate varieties at multiple levels simultaneously. By asking if dynamic capabilities
-can lead to competitive advantage and how this occurs, one is far better off asking "when"
-competitive advangate is an outcome of dynamic capabiliteis and its workings.
-
-The definition of dynamic capabilities, albeit contestst, seems to be converging on
-varieties of "the ability of firms to create, modicy and extend its resource base" (ref)
-\citep{Schilke2018}. Meanwhile both dynamic capabilities as the "governing entity" and
-resources as "the governed entity" takes different forms in the literature (ref). Dynamic
-capabilities themsleves can roughly be divided into sets of simple rules governing
-undelying resources, or more complex routines developed for the same purpose
-\citep{Peteraf2013}. In other words, dynamic capabilities themselves can and cannot satisfy
-the VRIO condition. This contention is throughly covered in the literature (refs) and
-recent contribiutions have argued for interplays between simple and complex types of
-dynamic capabilities foring a more complex and initmatble dynamic system
-\citep{DiStefano2014}. Moreover, granted different forms of dynamic capabilities exist
-their impact on the "governed entity", the underlying firm resources, should also be
-varying.
-
-To explore this we emply two radically differnet forms of dynamic capabilities / one
-geared towards transforming exitsgint resources in order to exploit them to gain
-competitive advantage (refs). The other form is geraed towards seizing new opportunities in order
-to explore new business opportunitieis (refs). We argue that competitive advantage can
-stem from each of these, but that the mechanism varies. Dynamic capabilities geared
-towards transforming for exploitation ($DC_P$) is by and of itself the result of a more
-complex set of routines configured in a way that is hard to imitate because of its path
-dependent and evolutionary nature. This legacy from evolutinoary economics is stressed as
-an important factor for creating VRIO resources (Ref peteraf). The stream of contributions
-maintaining dynamic capabilities working through the object of "changing existing
-capabilities" \citep{Teece1997,Zollo2002a,Winter2003,Zahra2006,Kale2002} also maintain
-that
-
-We argue that latent and constituted dynamic capabilites behave differently and work
-differnetly trhough differents modes (action or wahtever the term in DiStefano er).
-
-{\bf LAtent = complex process routines Teece
-Constitutent = simpler, ad hoc - Eisenhardt}
-
-We explore two different modes (natures) of dynamic capabilities and how they work
-differently (action) to create competitive advantage. Or is it the object of action as
-either resources or opportunities?
-
-By introducing different measures of different types of DC (latent and constiuted) as well
-as two different types of action (change existing or create new) we explore the workings
-of the drive train model proposed by DiStefano suggesting a fuller and more dynamic view
-on how latent and consittued DC works differently.
-
-The working of latent:
-Departing from the definintion of dynamic capabilities found in Teece (ref) and subsequent
-contributions in this tradition
-
-The working of cinstuted
-
-We identify two ditintctly different noptions of dynamic capabilities both following well
-known definitions byut weith different nature (ref distefano). We show that only the
-latent dc can directly and indirectly create CA,whereas the constituent element nature of
-DC only works through changing lower level routines.
-
-Different parts of the drive train works on different types of underlying routines
-
-Looks at competing hypotheses between Eisenhardt and teexe with respect to routinization. Finds that routininzation happens at DC level less than operational level?
-We argue that this depends on the purpose *action of the Dc and the composition of the
-focal operational capability.
-
-Reviewing the literature reveals that researchers have tended to identify dynamic capabilities post hoc, inferring their existence from successful organizational out- comes such as profitability and growth, as prior definitions would suggest (Table
-
-On the other hand we have dynamic capabilites geared toward sensing and seizing new
-opportunities as part of an effort of exploration. Such dynamic capabilities are described
-in the literature as themselves a set of more simple routines orchestrated in a manner
-such that x`
-
-Routinization at certain level, but depends on them being outward or inward looking.
-
-How can DC lead to competitive advangate. departing from the original definition this
-happens through the modification or aquisition of firm resources. But the resopurces
-themselves can and cannot be a source of competitive advantage
-
-At a minimum, in order for something to qualify as a capability, it must work in a reliable manner’ (Helfat and Peteraf, 2003: 999). Capabilities
-
-The bulk of contributions focus
-only on heterogeneity at the dynamic capabilities level, or at
-
-W
-
-work dDC offers a theory of how firms achieve
-competitive advantage over time. Yet the DC theory suffers from contradictory claims about
-competitive advantage as its outcome. On the one hand a stream of contributions argue that
-DC will lead to competitive advantage because it operates by changing operational
-capabilities in face of change and hence create strategic change (ref helfat). In this
-view these changes result in complex and path dependent processes that will be
-idiosyncratic to the firm and hard to imitate. Consequently, they can lead to competitive
-advantage.
-
-A contrary stream of literature argues that changes of operational capabilities over time
-takes the form of routines and converges towards best practice (ref EM). Such best
-practices are simpler and more observable routines that are both imitable and easy to
-copy. Such firm resources are then not idiosyncratic and can consequently not be the
-source of competitive advantage.
-
-The way DC work differnelty throug changing two sets of operational capabilities = complex
-and path dependent processes based capabilities, and simple rules/based routines.
-
-These contradictory positions have been thoroughly discussed in earlier work (see
-\cite{Peteraf2013} for a review). On the one hand DC takes the form of simple rules
-shaping underlying routines. On the other hand they take the form of complex processes.
-
-Regarding the action and the object ofthe action, simple rules are more likely to be
-involved in developing something new in response to new opportunities, while complex
-rou- tines are more concerned with changing existing resources and capabilities.
-
-In a recent "state of the art" literature review on dynamic capabilities
-\cite{Schilke2018} state that much of the attention and interest surrounding the theory is
-that it offer a route to competitive advantage which they argue is "the virtual Holy Grail
-of strategic management" (p. 393). And indeed a considerable body of the extant literature
-concerns itself with exactly this path to competitive advantage (refs from
-shcilke). Still, a discourse regarding the contingencies of the dynamic
-capabilities-competitive advantage (DC-CA) nexus (?) has panned out in the literature,
-most notably coined "the elephant in the room" \citep{Peteraf2013}: Under which conditions
-will dynamic capabilities lead to competitive advantage?
-
-\cite{Peteraf2013} argue that the seminal papers in the dynamic capabilities theory
-tradition (\cite{Teece1997} and \cite{Eisenhardt2000}) differ considerably in their view
-of to what extent the DC-CA nexus exist and under what conditions it is functional. A key
-tenant of this discourse is related to the level of routinization and the ability to
-satisfy the VRIO condition \citep{Barney1991a} of the resource-based view
-\citep{Peteraf2013}.
-
-In this paper we aim to contribute to dissecting the elephant by asking how does the DC-CA
-nexus differ between firms and what determines these differences?
-
-We do this by exploring two paths from dynamic capabilities to competitive advantage: the
-\emph{evolutionary path} and the \emph{market path}. The former is thoroughly described
-and explored in the literature (refs) and stems from the core idea of the dynamic
-capabilities theorizing. In this path dynamic capabilities work to change the operating
-routines of the firm and hence contributing to it's competitive advantage. We argue that
-this path is more suited for less dynamic environments because of its path dependent
-functioning.
-
-The \emph{market path} works not through shaping operational capabilities and routines,
-but by enabling the firm to act in factor markets for new capabilities and
-resources. Hence, it is less path dependent and can be more rapidly
-deployed. Consequently, it is more prevalent in dynamic environments.
-
-This paper contributes to the extant literature on the link between dynamic capabilities
-and competitive advantage in three ways. First, provides an empirical test to the
-drive-train model of \cite{DiStefano2014} on how dynamic capabilities can operate both
-quickly and with high frequency more directly on the strategic direction of the firm by
-acting in factor markets for important resources, and also more slowly through the
-evolutionary path of changing operational capabilities. Second, by conceptually clarifying
-the different paths to competitive advantage by linking it closely to the role of
-capability evolution and the VRIO condition. Finally, we.........
-
-CLARIFIES THE ROLE OF THE ENVIRONMENT AND MEDIATIONS HAPPENING
-
-%% How does dynamic capabilities lead to competitive advantage?
-%% Dynamic capabilities are proposed to confer a competitive advantage by adding unique value to the firm through systematic change, which enhances operational efficiency and enables increased alignment with the environment (Di Stefano et al., 2014; Peteraf et al., 2013)
-
-%% Not all organizations possess them (Collis, 1996); their path dependencies, intangibility, complexity, and organizational specificity make them hard to imitate (Gibson & Birkinshaw, 2004; Helfat & Winter, 2011); and few other means allow organizations to purposefully change on a continuous basis (Day & Wensley, 1988; Helfat et al., 2007).
-
-%% Consistent with the theoretical positions of Eisenhardt and Martin (2000), Helfat and Peteraf (2003), Zahra et al.
-(2006), and Zott (2003), among others, these researchers have argued that dynamic capabilities’ immediate purpose is to change the resource base, and that this change in the resource base, in turn, explains performance variations.
-According to this argument, resource changes serve as mediators through which dynamic capabilities affect performance.
-We
-
-%% One of the major unresolved issues in dynamic capabilities theory is to what extent and
-%% how competitive advantage is the ultimate outcome of dynamic capabilities. This very idea
-%% has
-
-%% This paper asks two questions: to what extent does a direct lnk between DC and CA exist,
-%% and what determines variations in the role of mediation between them?
-
-%% The idea that Dc impacts CA is uncontroversial (not). Little is known about how this
-%% happens. The theory holds that this happens through xreating extending and modifying the
-%% resource base. YEt, the change in firm capabilities can themselves lead to CA due to their
-%% evlutionary nature.
-
-%% Variations in the share of mediation stems from variation sin the environment. When envdyn
-%% is high firms need to act faster and hence tends to choose strategies including resource
-%% orchestration buying in factor markets cause it tkes more time to develop OR.
-
-%% In less dynamism the role of OR increases and leads to a significant proportion of CA
-%% stemming throhg the mediating effect of OR
-
-%% There is ongoing interest in (dynamic) capabilities and how they influence firm
-%% performance \citep{Fainshmidt2016a,Teece2014}. Indeed, \emph{dynamic capabilities} (DC),
-%% and its front runner, the resource-based view \citep{Barney2001,Helfat2007}, is now
-%% considered one of the major theories in strategic management
-%% \citep{Schilke2018}. Arguably, the key reason is that this theory clearly articulates how
-%% firms can alter their operating routines through dynamic capabilities. Thus, a key
-%% ingredient in this theory is that DCs can alter firms operating routines, with subsequent
-%% performance implications.
-
-We demonstrate that two paths indeed do exist and that their relative importance varies
-with the degree of environmental dynamism facing the firm.
+%% The direct
 
@@
 
-%% We can use the drive train to determine hwo DC works differently under different levels of
-%% dynamism. It is not that DC does not work under stable conditions as EM claims. Is only
-%% that the effect runs stringer through the evolutionary path. Whereas the market path is
-%% stringer under higher dynamism
-This friction has been
-dubbed the "elephant in the room" (peteraf) and been tracked back to the seminal papers of
-Teece and Eisenhardt, as well as their their different theoretical antecedents of
-evolutionary economics (ref) and behavioral theory (ref) respectively (ref Arndt
-x2).
+%{\bf How is a direct link between dynamic capabiliites and competetive advantage working
+%  and under which conditions does it come into play or not?}
 
-One contentious issue surrounding the DC theory is the extent to which differing views on
-the nature of dynamic capabilities \citep{Peteraf2013} as well as their outcome. One
-strand of contributions sees DC as routines that are simple in nature and more as best
-practices to consider (EM). Thus, dynamic capabilities are more like behavioral patterns
-and less idiosyncratic to the firm and will consequently not be able to satisfy the VRIO
-condition for competitive advantage to emerge. Dynamic capabilities as such routines are
-short lived, unstable and “substitutable” (EM: 1110) thus violating a key VRIN condition,
-and they are more “more homogeneous (..) than is usually assumed” (EM: 1116). However, the
-simplicity of simple rules also makes them faster do deploy and put in motion, albeit
-potentially unstable. To the extent dynamic capabilities manifest themselves as simple
-rules they cannot alone create competitive advantage, but could very well generate
-strategic change by facilitating acquisition of resources in factor markets. One example
-is the role of post-acquisition routines where routines to identify and deal with
-acquisition partners are a source of generating strategic change (Eisenhardt and Sull
-2001, ref). Another example is (see refs from Schilke 2018). The functioning of this
-expression of dynamic capabilities are more latent and hence mainly observable ex
-post. Hence we can see this as direct route to competitive advantage as this expression of
-dynamic capabilities work directly in the factor market in capturing resources
-needed for strategic change. We coin this direct connection as the \emph{market path}.
+In the face of a growing consensus on the definition (ref) and outcome (ref) of dynamic
+capabilities as working through mediators, the presence of direct effects argued by others
+(ref) seems puzzling. However, the broader empirical literature on the antecedents of firm
+performance offers an interesting point of departure. This literature concerns itself with
+the relative importance of factors at the firm-level on the one hand, and those at the
+industry level at the other.
 
-On the other hand, a stream of contributions see dynamic capabilities as evolutionary and
-more complex routines (ref) or processes (ref) set to change underlying capabilities in
-the face of changing conditions (TPS). This notion stems from evolutionary economics
-\citep{Winter2003,Nelson1982} and the behavioral theory of the firm \citep{Cyert1963}
-holding that path dependency and complex processes for changing underlying operating
-routines are a source of competitive advantage for the firm. Along this indirect path
-change is gradual and running through changes in underlying routines. We coin this the
-\emph{evolutionary path}.
+The debate over the relative role of different levels of factors in accounting for the
+major share of the variance in firms performance has been of particular importance in the
+field of strategic management, most notably in the Strategic Management Journal
+(M. A. Fitza 2014; Hansen and Wernerfelt 1989; McGahan and Porter 1997; Rumelt
+1991). Overall, the accumulated empirical evidence show that firm factors matter far more
+for firm performance than industry factors (McGahan and Porter 2002). These stylized facts
+have been used as empirical support for the importance of idiosyncratic firm resource and
+capabilities; leading up too recent formulation of the resource and capability based
+theorizing (e.g. (Barney 1991; Teece, Pisano, and Shuen 1997)). However, the dominance of
+the firm-level explanations have been partly refuted by later scholars finding the sum of
+indirect and direct effects from industry to be of more importance than previously
+indicated by (Mcgahan etc). Moreover, the industry effect is also more time invariant
+(i.e. more stable) compared to firm level effects. Recent findings also suggest that there
+are considerable interaction effects between industry and the firm indicating that
+industry membership works directly at performance as well as indirectly through affecting
+the firm. However, little or no explanations are made for the mechanisms of this
+interaction.In other words, industry factors matter alas less than firm-level factors, and
+the indirect link from industry-level through firms are in need of further development.
 
-These paths from dynamic capabilities to competitive advantage are different expressions
-of dynamic capabilities with different mediums of intermediation. The \emph{market path}
-works in the market and his hence not typically altering lower order capabilities and
-resources in the firm directly, but rather acquiring new ones. The source of competitive
-advantage along this path stems from the interaction with the other, \emph{evolutionary
-  path} in a dynamic bundle \citep{Peteraf2013}. Such interactions create a bundle of
-capabilities and routines that are socially complex and hard to imitate
-\citep[p. 320]{DiStefano2014}. Moreover, the interactions between the two paths of dynamic
-capabilities is separable with respect to what intermediation exist. Consequently,
-separate paths exist albeit a part of a dynamic bundle.
+One way of looking at this is to consider the dynamic capabilities of the firm. Although
+an increasing consensus focuses on these dynamic capabilities as the ability to create,
+extend and modify firm resources in the face of change, there still looms an important
+stream of literature suggesting that dynamic capabilities can materialize as management
+actions (ref eisenhardt, peteraf, helfat). A management action aimed at strategic change
+will very often entail "resource orchestration" as broadly discussed in the literature
+(Helfat etc). But, strategic change are also found to come about from adapting and
+changing the positioning of the firm within its industry (ref) or simply refocusing its
+focal industry (ref). In other words, when a firm with excellent dynamic capabiliites
+senses and seizes opportunities within its domain, the implementation of strategic change
+will often both entail a considerable share of "asset orchestration" (helfat etc) as well
+as management actions directed at positioning within its industry (ref). One way to
+illustrate this is to consider Microsofts strategic change from operating system to cloud
+provider. CEO Satya Nadela and his team was able to restart the business by creating,
+extending and modifying the resources of the firm, including new skills, routiens and
+hardware, as a response to a growing demand for cloud computing (ref nadellas
+book). Meanwhile, his vision and formulated strategy also direclty put the company into a
+new industry, or at the very least reshaped the position they were already in. While
+Microsofts dynamic capabiliites worked significantly through "resource orchestration",
+the sensing and seizing of the management also ordered a direct re-positioning at the same
+time.
 
-\cite{DiStefano2014} propose an integrated framework where simple routines and more
-complex processes could contribute simultanously to the firms outcome, specifically its
-competitive advantage. In this framework, coined the "organizational drivetrain" the
-authors envision the movement of an organization as set in motion by a drivetrain system
-not unlike that of a bicycle.
+Moreover, The link between firm resources and competitive advantage is determined by the
+extent to which resources are valuable and difficult to imitate \citep{Barney1991a}. This
+principle is also used to evaluate how higher order capabilities (e.g. dynamic
+capabilities \citep{Winter2003,Collis1994,Teece2007}. Hence, for a direct link to exist
+the dynamic capabilities of the firm will have to be valuable and difficult to
+imitate. This is an area of certain contention in the literature \citep{Peteraf2013} which
+we get back to below, but an increasing majority is arguing that dynamic capabilities
+reflect more complex processes that co-evolve with responses to market changes over time
+and hence creating idiosyncratic capabilities that are unique, valuable and hard to copy
+\citep{Helfat2007,Arndt2018}. Consequently, they are likely to lead to competitive
+advantage.
 
-Building on the notion of an organizational drivetrain we argue that dynamic capabilities
-can indeed impact the organizational movement or change through two distinct but
-interconnected mechanisms (i.e. the crank set and the rear shifter). The two mechanisms
-consitutting the drivetrain is consistent with our notion of \emph{evolutionary path} and the \emph{market path}. The
-evolutionary path is instigated by more complex processes setting in motiong a chance in
-the lower order (operational) routines \cite{Collis1994,Winter2003}. In the drivetrain
-metaphor this path corresponds to change stemming from the front crank set of thich there
-are fewer gears, but with larger impact. This path is slower
-and yields a more idiosyncratic set of organizational routines which is very much in line
-with the idea put forth in the seminal founding papers \citep{Teece1997,Winter2003}.
+In most cases such direct effects between dynamic capabilities and strategic change
+resulting in competitive advantage, are combined with the indirect effects (i.e. resource
+orchestration). To test this proposition empirically is hard, but one hypothesis following
+from this is related to the role of mediators. if a direct path does not exist, the
+relationship between dynamic capabilities and competitive advantage would be fully
+mediated by the proper set of firm resources.
 
-Seeing the bike rider and her efforts to handle the levers of control (i.e. the gear
-shifter) as the dynamic capability, and consider it not only as a management effort, but
-that of the organization as a whole. The process of changing front gears are more profound
-(i.e. evolutionary) and costly, and it is for larger and slower strategic
-changes. Operating with simple routines in factor markets, however, is quicker and the
-rider does this on a more frequent basis with less effort.
+\emph{H1: The existence of a direct path from dynamic capabilities to competitive advantage
+suggest that full mediation is not present}
 
-H1: Dynamic capabilities works to create competitive advantage through two distinctly
-different paths.
+Even if the dynamic capabilities of the firm themselves are not valuable and inimitable as
+needed to create competitive advantage, the underlying resources of the firm may very well
+be. Such resources in the form of operating routines or capabilities can in turn stem from
+an inherent learning process evolutionary distinct to the firm. Operating routines can
+thus lead to competitive advantage because of their evolutionary character
+\citep{Nelson1982,Winter2003}. To the extent operating routines stems from idiosyncratic
+evolutionary process of individual firms rather than being the result of best practices,
+they can satisfy the VRIO condition and thus be a source of competitive advantage.  Hence,
+through "resource orchestration" a firm with non-valuable dynamic capabilities can achieve
+competitive advantage through the indirect path. The flip side of this is that a valuable
+dynamic capability would not be able to create competitive advantage by orchestrating
+non-valuable resources. Consequently, the mediation effects of underlying resources is
+dependent on the nature of the resource - it being valuable and inimitable or not.
 
-\subsection{The two paths of dynamic capabilities}
-The objective of strategic change is to enhance a firm’s competitive advantage
-(ref). Doing so over time makes for the evolutionary fitness of the firm
-\citep{Helfat2007}. When firms are developing capabilities for strategic change through
-creating, extending and modifying the resource base this means making decisions to develop
-operational routines. Such routines can in turn stem from an inherent learning process
-evolutionary distinct to the firm. Operating routines can thus lead to competitive
-advantage because of their evolutionary character \citep{Nelson1982,Winter2003}. To the
-extent operating routines stems from idiosyncratic evolutionary process of individual
-firms rather than being the result of investments in factor markets, they can satisfy the
-VRIO condition and thus be a source of competitive advantage. In such instances, dynamic
-capabilities work through operating routines in creating competitive advantage. This
-indirect impact on competitive advantage is very much at the core of the DC literature
-(ref). Firms with high dynamic capabilities will be able to better change operating
-routines to facilitate strategic change in response to changing conditions facing the
-firm. Dynamic capabilities then creates VRIO operating routines and hence competitive
-advantage. When this happens, firms changes their operating routines in a evolutionary
-making operating routines themselves OR itself satisfies the VRIO condition.
+\emph{H2a: When dynamic capabilities are being mediated by VRIO resources the firm can
+  achieve competitive advantage}
 
-\emph{H2: Dynamic capabilities has an indirect effect on competitive advantage through
-  changing the operating routines of the firm.}
+\emph{H2a: When dynamic capabilities are being mediated by VRIO resources the firm can not
+  achieve competitive advantage}
 
-On the other hand, resources and capabilities can to a certain extent be captured in
-factor markets through investment decisions (ref) or through alliances (ref) or M\&A
-activates (ref). By acquiring resources through investments, the operating routines of the
-firms may not be directly affected. When these acquisitions happen as a response to
-systematic resource orchestration (ref), i.e. reshaping the resource mix to obtain
-coordinated resource deployments \citep{Kor2005,Pan2006}, they would indeed have potential
-performance implications for the firm. Moreover, when this process of resource acquisition
-process of DC develops a way to acquire and mix resource for the purpose of adapting to
-change, the resources themselves would not necessarily satisfy the VRIO condition. The way
-in which this happens may be much harder to imitate due to the complexities such routines
-exhibit. Although resources themselves exhibit clear equifinality in their impact on
-competitive advantage, combined with the simple routines of the orchestration
-(i.e. dynamic capabilities), the sum would likely satisfy the VRIO condition. This is
-especially true if routines are deployed rapidly in changing market conditions. In other
-words, there are several ways in which resources can be orchestrated to generate CA,
-whereas improved OR will always mean improved competitiveness et ceteris paribus. In such
-instances DC itself can lead to CA directly.
+DEspite a growing consensus on the nature of dynamic capabilites, a serious contention is
+presen tin the literature \citep{Peteraf2013}. This stems from different notions of
+dynamic capabilities in the two "founding" papers of the theory, \cite{Eisenhardt2000} and
+\cite{Teece1997}.
 
-\emph{H3: Dynamic capabilities has a direct effect on competitive advantage through the
-  process of resource orchestration and acquisition of resources in factor markets.}
+One strand of contributions sees DC as routines that are simple in nature and more as best
+practices to consider \citep{Eisenhardt2000}. Thus, dynamic capabilities are more like
+behavioral patterns and less idiosyncratic to the firm and will consequently not be able
+to satisfy the VRIO condition for competitive advantage to emerge. Dynamic capabilities as
+such routines are short lived, unstable and “substitutable” (ibid, p 1110) thus violating
+a key VRIO condition, and they are more “more homogeneous (..) than is usually assumed”
+(ibid, 1116). However, the simplicity of simple rules also makes them faster do deploy and
+put in motion, albeit potentially unstable. To the extent dynamic capabilities manifest
+themselves as simple rules they cannot alone create competitive advantage, but could very
+well generate strategic change by facilitating the process of resource orchestration.. In
+other words, even if dynamic capabilities play out as simple rules that are not in
+themselves satisfying the VRIO condition, the way they work through creating, extending
+and modifying firm resources, can still yield competitive advantage through orchestrating
+VRIO resources.
 
-In other words, we would expect DC to have both a direct and an indirect impact on CA. The
-indirect impact stems from the \emph{evolutionary path} of complex processes, whereas the
-direct impact stems from the \emph{market path}.  Although both the direct and the
-indirect path stems from DC creating, extending and modifying the resource base (OR or
-factor market resources), the difference in the path’s stems from to what extent the
-mediating construct alone can by itself satisfy the VRIO condition. Operating routines
-can, due to their evolutionary nature, in turn shaped by DC, achieve CA
-\citep{Collis1994,Winter2003}. Factor market resources and market acquired capabilities
-and best practices can not \citep{Eisenhardt2000,Peteraf2013}, but in conjuncture with the
-routines of acting in factor markets as well as the speed of deployment, the sum of
-dynamic capabilities and factor market action would lead to competitive advantage.
+On the other hand, \cite{Teece1997} and others \cite{Helfat2007} argue that dynamic
+capabilities will rather invariably be VRIO due to the evolutionary nature of their
+development \citep{Arndt2018,Peteraf2013}. Arguing that dynamic capabilities reflect more
+complex processes that co-evolve with responses to market changes over time and hence
+creating idiosyncratic capabilities that are unique, valuable and hard to copy
+\citep{Helfat2007,Arndt2018}. Consequently, they are likely to satisfy the VRIO condition
+and thus leading to competitive advantage.
 
-However, the interlinkages between simple routines (the market path) and the coplex
-processes (the evolutionary path) would vary with the environment.
+The contention between these streams of literature is most explicit in highly dynamic
+environments (distefano, peteraf) suggesting that environmental dynamism could play into
+the presence of direct and indirect linkages between dynamic capabilities and competitive
+advantage. This is also supported in previous empirical literature \citep{Schilke2014}.
+This could suggest that dynamic capabilities exhibit different characteristics under
+various levels of environmental dynamism. This is also suggested by Eisenhardt blaboblabla
+arguing that under moderatly dynamism dynamic capabilities takes the form of best
+pracitces (e.g. aquisition targeting) and is less important than under more dynamic
+environments. However, albeit best practices, the way they are implemented in the factor
+markets are still idiosyncratic. And taken into conjunction with the routinzed process of
+changing underlying routines, VRIO will very likely emerge under more stable
+conditions. It is not that the market/direct expression of dynamic capabilities are not
+present in stable environments, rather it is less pronounced and the indirect mediated
+effect (evolutionary path) is more important. In other words, it is not neither nor, but
+degrees of importance.
 
-\subsection{Interplay under environmental dynamism}
+\emph{H3: The mediation effects of underlying resources is dependent on the environmental
+dynamism facing the firm }
 
-\cite{DiStefano2014} note that "even if specific simple rules are unstable and ephemeral,
-the system as a whole is not" and that the "real source of sustainable competitive ad- vantage for an enterprise is the difficulty of imitating and substituting for the entire dynamic bundle that the system represents" (p.sss).
+%% Increasingly the literature remain focused on an \emph{indirect
+%%   path} between dynamic capabilities and competitive advantage
+%% \citep{Barreto2010,Schilke2018}. The theory behind this path goes back to the core of
+%% dynamic capabilities where resource orchestration happens as a response to changes in the
+%% environment. When markets, technologies or other external factors changes, firms with high
+%% levels of dynamic capabilities are able to seize opportunities for changes, seize these
+%% opportunities and transform the resource base to fit the strategic change needed to stay
+%% competitive \cite{Teece2007}. This ability to adapt is by some coined \emph{evolutionary
+%%   fitness} defined as BLABLBALBA and stems from the ability of the firm to reconfigure
+%% resources in the face of change. The extant literature, however, is less clear on how the
+%% nature of the underlying resources matter in this indirect path. On the one hand we can
+%% see
 
-But the interlinkages between the parts of the system (the evolutionary- and the market
-path), are likely to vary with the environmental dynamism. Under moderatly dynamism
-dynamic capabilities takes the form of best pracitces (e.g. aquisition targeting) and is
-less important than under more dynamic environments. However, albeit best practices, the
-way they are implemented in the factor markets are still idiosyncratic. And taken into
-conjunction with the routinzed process of changing underlying routines, VRIO will very
-likely emerge under more stable conditions. It is not that the market/direct expression
-of dynamic capabilities are not present in stable environments, rather it is less pronounced and the indirect
-mediated effect (evolutionary path) is more important. In other words, it is not neither
-nor, but degrees of importance.
+%% Following REF suggesting more reseaarch on dynamic capabilities should put forth
+%% competeing hypotheses we propose these first
 
-Moreover, in high velocity environments the role of the evolutionary path tends to
-weaken as such path-dependent changes occur slower compared to the market path. From the
-market path with its simple routines we can argue that creation of "new knowledge” to
-“allow for emergent adaptation” (EM, p. 1116) is the consequence. Consequently, the market
-path is stronger and more prevalent under higher levels of environmental dynamism.
+%% We introduce the notion of multilevel VRIO to integrate the interactions between different
+%% types of capabilities at different levels. This entails that dynamic capabilities (the
+%% high level) can consist of complex and evolutionary characteristics that are idiosyncratic
+%% to the firm and hence VRIO by definition along the lines of how the concept is understood
+%% by \cite{Teece1997}. On the other hand dynamic capabilities can also take the shape of
+%% simpler routines which are short lived, unstable and substitutable thus violating a key
+%% VRIO condition. This follows the notion of dynamic capabilities found in
+%% h\cite{Eisenhardt2000} arguing that they are more “more homogeneous (..) than is usually
+%% assumed” (EM: 1116).
 
-\emph{H4: Dynamic capabilities works relatively stronger through the market path in highly
-dynamic environments.}
+%% Moreover, these dynamic capabilities are in the extant literature argued and found to work
+%% directly \citep{Kor2005,Eriksson2014,Schilke2018} on competitive advantage which suggests
+%% that they are indeed VRIO. On the other hand, a growing body of literature (ref) as well
+%% a consensus on the definition of dynamic capabilities (ref), holds that they can lead to
+%% competitive advantage by changing underlying resources and routines. In this
+%% \emph{indirect path} the dynamic capabilities itself need not be VRIO as long as the
+%% underlying resources themselves are.
+
+%% \subsection{The role of dynamism}
+
+%% The most contentious issue in the current debate on dynamic capabilities is how their
+%% nature varies with the environment.
+
+%% If htey are indeed latent
+
+%% The lower level resources and routines are to be understood as conventional resources in
+%% line with the resources-based view
+
+%% WHAT IS THE ROLE OF DIRECT VS INDIRECT, HOW DOES IT RELATE TO THE ENVIRONMENT, AND WHAT
+%% ROLE DOES THE TYPE OF UNDERLYING RESOURCE PLAY
+
+%% Conventional dc literature has argued for both indirect and direct links. Indeed both
+%% have been found, but while the indirect link is well rooted in the theory, the direct link
+%% is to our knowledge less clear. The core idea of DC is that it works to modify underlying
+%% resources as a response to changes in the environment and hence creating strategic change
+%% needed to stay competitive. This resource orchestration is heavily represented in the
+%% literature (ref) and through this process firms are able to generate CA. In such instances
+%% the CA can stem from VRIO resources and/or VRIO DC. A VRIO DC would mean that the firm is able
+%% to shuffle and reorganize generic resources in a way that creates a new and unique
+%% configuration of resoures idiosyncratic and valuable to the firm. In such instances, the
+%% outcome whould be CA. On the other hand, the DC may not by itself be VRIO but rather a set
+%% of simple routines put in motion to change, but if the resources they reconfigure are
+%% themselves VRIO, the outcome could just as eqsily be a competetive advantage. this
+%% equfinaity is discussed in the literaure \cite{DiStefano2010} and makes it hard to
+%% distingusih between the role of DC and ordinary capabilites in generating CA.
+
+%% Furtemore, Considering a direct link between DC and CA, DC it self must consist of some
+%% VRIO characteristics to garner CA. So in owther words, when is DC working directly and
+%% indirectly_
+
+%% How are dynamic capabilities working directly on competitive advantage? The microfoundations of dynamic capabilities explicated by \cite{Teece2007} is a useful
+%% point of departure of this theoretical inquiry. He hold that for "analytical purposes,
+%% dynamic capabilities can be disaggregated into the capacity (1) to sense and shape
+%% opportunities and threats, (2) to seize opportunities, and (3) to maintain competitiveness
+%% through enhancing, combining, protecting, and, when necessary, reconfiguring the business
+%% enterprise’s intangible and tangible assets". Sensing and seizing is a part of what we
+%% would coin the "opportunity capture" of dynamic capabiliites, where as reconfiguring
+%% concerns itself with the "resource orchestration" needed to change assets to stay
+%% competetive.
+
+%% Hence, when considering indirect and direct paths to compettetive advantage we will have
+%% to be clear on two fronts: Are DC themselves VRIO and are the underlying resources and
+%% routines central to the resource orchestration, VRIO.
+
+%% >
+
+%% The microfoundations of dynamic capabilities—the distinct skills, processes, procedures, orga- nizational structures, decision rules, and disciplines—which undergird enterprise-level sensing, seizing, and reconfiguring capacities are difficult to develop and deploy.
+%% For analytical purposes, dynamic capabilities can be disaggregated into the capacity (1) to sense and shape opportunities and threats, (2) to seize opportunities, and (3) to maintain competitiveness through enhancing, combining, protecting, and, when necessary, reconfiguring the business enter- prise’s intangible and tangible assets.
+
+OC som mindset / non-vrio? organizational mindset
+DC influcences IOC 
+DC influences VOC
+
+two paths / changes resources vs change mindset
+
+why so interested in operating routines resources, what about other mechanisms
+Can dc change collective cognition?
+
+ENTP - EO coen and slevin
+
+%%        name Mean_est     t
+%% 3   DC -> P    0.396 6.157
+%% 4   DC -> R    0.416 8.104
+%% 5 DC -> CA1    0.239 4.018
+%% 8  P -> CA1    0.172 2.724
+%% 9  R -> CA1    0.081 1.262
+%% > R
+%%        Path   LOW     t  HIGH     t
+%% 1 DC -> CA1 0.417 6.585 0.144 1.513
+%% 2   DC -> R 0.388 6.078 0.534 7.525
+%% 3  R -> CA1 0.017 0.219 0.211 2.123
+%% > P
+%%        Path   LOW     t  HIGH     t
+%% 1 DC -> CA1 0.355 4.805 0.133 1.379
+%% 2   DC -> P 0.386 5.294 0.436 4.663
+%% 3  P -> CA1 0.155 2.193 0.232 2.315
+%% > B
+%%        name R_LOW_est   t.x R_HIGH_est   t.y
+%% 1 DC -> CA1     0.355 5.407      0.044 0.400
+%% 2   DC -> P     0.376 3.729      0.432 4.668
+%% 3   DC -> R     0.366 5.569      0.522 7.225
+%% 4  P -> CA1     0.158 1.989      0.220 2.357
+%% 5  R -> CA1     0.010 0.135      0.200 2.033
+%% >
+
+%% %% creating and One example
+%% %% is the role of post-acquisition routines where routines to identify and deal with
+%% %% acquisition partners are a source of generating strategic change (Eisenhardt and Sull
+%% %% 2001, ref). Another example is (see refs from Schilke 2018). The functioning of this
+%% %% expression of dynamic capabilities are more latent and hence mainly observable ex
+%% %% post. Hence we can see this as direct route to competitive advantage as this expression of
+%% %% dynamic capabilities work directly in the factor market in capturing resources
+%% %% needed for strategic change. We coin this direct connection as the \emph{market path}.
+
+%% On the other hand, a stream of contributions see dynamic capabilities as evolutionary and
+%% more complex routines (ref) or processes (ref) set to change underlying capabilities in
+%% the face of changing conditions (TPS). This notion stems from evolutionary economics
+%% \citep{Winter2003,Nelson1982} and the behavioral theory of the firm \citep{Cyert1963}
+%% holding that path dependency and complex processes for changing underlying operating
+%% routines are a source of competitive advantage for the firm. Along this indirect path
+%% change is gradual and running through changes in underlying routines. We coin this the
+%% \emph{evolutionary path}.
+
+%% These paths from dynamic capabilities to competitive advantage are different expressions
+%% of dynamic capabilities with different mediums of intermediation. The \emph{market path}
+%% works in the market and his hence not typically altering lower order capabilities and
+%% resources in the firm directly, but rather acquiring new ones. The source of competitive
+%% advantage along this path stems from the interaction with the other, \emph{evolutionary
+%%   path} in a dynamic bundle \citep{Peteraf2013}. Such interactions create a bundle of
+%% capabilities and routines that are socially complex and hard to imitate
+%% \citep[p. 320]{DiStefano2014}. Moreover, the interactions between the two paths of dynamic
+%% capabilities is separable with respect to what intermediation exist. Consequently,
+%% separate paths exist albeit a part of a dynamic bundle.
+
+%% \cite{DiStefano2014} propose an integrated framework where simple routines and more
+%% complex processes could contribute simultanously to the firms outcome, specifically its
+%% competitive advantage. In this framework, coined the "organizational drivetrain" the
+%% authors envision the movement of an organization as set in motion by a drivetrain system
+%% not unlike that of a bicycle.
+
+%% Building on the notion of an organizational drivetrain we argue that dynamic capabilities
+%% can indeed impact the organizational movement or change through two distinct but
+%% interconnected mechanisms (i.e. the crank set and the rear shifter). The two mechanisms
+%% consitutting the drivetrain is consistent with our notion of \emph{evolutionary path} and the \emph{market path}. The
+%% evolutionary path is instigated by more complex processes setting in motiong a chance in
+%% the lower order (operational) routines \cite{Collis1994,Winter2003}. In the drivetrain
+%% metaphor this path corresponds to change stemming from the front crank set of thich there
+%% are fewer gears, but with larger impact. This path is slower
+%% and yields a more idiosyncratic set of organizational routines which is very much in line
+%% with the idea put forth in the seminal founding papers \citep{Teece1997,Winter2003}.
+
+%% Seeing the bike rider and her efforts to handle the levers of control (i.e. the gear
+%% shifter) as the dynamic capability, and consider it not only as a management effort, but
+%% that of the organization as a whole. The process of changing front gears are more profound
+%% (i.e. evolutionary) and costly, and it is for larger and slower strategic
+%% changes. Operating with simple routines in factor markets, however, is quicker and the
+%% rider does this on a more frequent basis with less effort.
+
+%% H1: Dynamic capabilities works to create competitive advantage through two distinctly
+%% different paths.
+
+%% \subsection{The two paths of dynamic capabilities}
+%% The objective of strategic change is to enhance a firm’s competitive advantage
+%% (ref). Doing so over time makes for the evolutionary fitness of the firm
+%% \citep{Helfat2007}. When firms are developing capabilities for strategic change through
+%% creating, extending and modifying the resource base this means making decisions to develop
+%% operational routines. Such routines can in turn stem from an inherent learning process
+%% evolutionary distinct to the firm. Operating routines can thus lead to competitive
+%% advantage because of their evolutionary character \citep{Nelson1982,Winter2003}. To the
+%% extent operating routines stems from idiosyncratic evolutionary process of individual
+%% firms rather than being the result of investments in factor markets, they can satisfy the
+%% VRIO condition and thus be a source of competitive advantage. In such instances, dynamic
+%% capabilities work through operating routines in creating competitive advantage. This
+%% indirect impact on competitive advantage is very much at the core of the DC literature
+%% (ref). Firms with high dynamic capabilities will be able to better change operating
+%% routines to facilitate strategic change in response to changing conditions facing the
+%% firm. Dynamic capabilities then creates VRIO operating routines and hence competitive
+%% advantage. When this happens, firms changes their operating routines in a evolutionary
+%% making operating routines themselves OR itself satisfies the VRIO condition.
+
+%% \emph{H2: Dynamic capabilities has an indirect effect on competitive advantage through
+%%   changing the operating routines of the firm.}
+
+%% On the other hand, resources and capabilities can to a certain extent be captured in
+%% factor markets through investment decisions (ref) or through alliances (ref) or M\&A
+%% activates (ref). By acquiring resources through investments, the operating routines of the
+%% firms may not be directly affected. When these acquisitions happen as a response to
+%% systematic resource orchestration (ref), i.e. reshaping the resource mix to obtain
+%% coordinated resource deployments \citep{Kor2005,Pan2006}, they would indeed have potential
+%% performance implications for the firm. Moreover, when this process of resource acquisition
+%% process of DC develops a way to acquire and mix resource for the purpose of adapting to
+%% change, the resources themselves would not necessarily satisfy the VRIO condition. The way
+%% in which this happens may be much harder to imitate due to the complexities such routines
+%% exhibit. Although resources themselves exhibit clear equifinality in their impact on
+%% competitive advantage, combined with the simple routines of the orchestration
+%% (i.e. dynamic capabilities), the sum would likely satisfy the VRIO condition. This is
+%% especially true if routines are deployed rapidly in changing market conditions. In other
+%% words, there are several ways in which resources can be orchestrated to generate CA,
+%% whereas improved OR will always mean improved competitiveness et ceteris paribus. In such
+%% instances DC itself can lead to CA directly.
+
+%% \emph{H3: Dynamic capabilities has a direct effect on competitive advantage through the
+%%   process of resource orchestration and acquisition of resources in factor markets.}
+
+%% In other words, we would expect DC to have both a direct and an indirect impact on CA. The
+%% indirect impact stems from the \emph{evolutionary path} of complex processes, whereas the
+%% direct impact stems from the \emph{market path}.  Although both the direct and the
+%% indirect path stems from DC creating, extending and modifying the resource base (OR or
+%% factor market resources), the difference in the path’s stems from to what extent the
+%% mediating construct alone can by itself satisfy the VRIO condition. Operating routines
+%% can, due to their evolutionary nature, in turn shaped by DC, achieve CA
+%% \citep{Collis1994,Winter2003}. Factor market resources and market acquired capabilities
+%% and best practices can not \citep{Eisenhardt2000,Peteraf2013}, but in conjuncture with the
+%% routines of acting in factor markets as well as the speed of deployment, the sum of
+%% dynamic capabilities and factor market action would lead to competitive advantage.
+
+%% However, the interlinkages between simple routines (the market path) and the coplex
+%% processes (the evolutionary path) would vary with the environment.
+
+%% \subsection{Interplay under environmental dynamism}
+
+%% \cite{DiStefano2014} note that "even if specific simple rules are unstable and ephemeral,
+%% the system as a whole is not" and that the "real source of sustainable competitive ad- vantage for an enterprise is the difficulty of imitating and substituting for the entire dynamic bundle that the system represents" (p.sss).
+
+%% But the interlinkages between the parts of the system (the evolutionary- and the market
+%% path), are likely to vary with the environmental dynamism. Under moderatly dynamism
+%% dynamic capabilities takes the form of best pracitces (e.g. aquisition targeting) and is
+%% less important than under more dynamic environments. However, albeit best practices, the
+%% way they are implemented in the factor markets are still idiosyncratic. And taken into
+%% conjunction with the routinzed process of changing underlying routines, VRIO will very
+%% likely emerge under more stable conditions. It is not that the market/direct expression
+%% of dynamic capabilities are not present in stable environments, rather it is less pronounced and the indirect
+%% mediated effect (evolutionary path) is more important. In other words, it is not neither
+%% nor, but degrees of importance.
+
+%% Moreover, in high velocity environments the role of the evolutionary path tends to
+%% weaken as such path-dependent changes occur slower compared to the market path. From the
+%% market path with its simple routines we can argue that creation of "new knowledge” to
+%% “allow for emergent adaptation” (EM, p. 1116) is the consequence. Consequently, the market
+%% path is stronger and more prevalent under higher levels of environmental dynamism.
+
+%% \emph{H4: Dynamic capabilities works relatively stronger through the market path in highly
+%% dynamic environments.}
 
@@
 financial accounts from the National Firm Registry (BRREG) for all years between 2007 and
-2014 (prior to 2007 was not accessible through our database).
+2014 (prior to 2007 was not accessible through our database).-
 
@@
 
-\section{Results}
-The focal variables of our study is presented with pairwise correlation, mean and standard
-deviation in table \ref{tab:desc}.It is worth noting that the mean value of OR and DC is
-declining over time suggesting that the average firm experience a negative development in
-core resources. The ability of the firms in our sample to generate CA is somewhat
-unchanged over the sample period. We also observe a certain correlation in the development
-in DC over time suggesting that prior period DC is a strong predictor of future
-DC. Furthermore, we see a strong correlation between DL and DC which indicates that these
-two constructs are indeed related.
-
-\begin{figure}[ht] \label{ fig7} 
-  \begin{minipage}[b]{0.5\linewidth}
-    \includegraphics[width=.99\linewidth]{full.pdf} 
-    \caption{Full model} 
-  \end{minipage} 
-  \begin{minipage}[b]{0.5\linewidth}
-    \includegraphics[width=.99\linewidth]{ma.pdf} 
-    \caption{Routine mediation} 
-  \end{minipage} 
-  \begin{minipage}[b]{0.5\linewidth}
-    \includegraphics[width=.99\linewidth]{or.pdf} 
-    \caption{Process mediation} 
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.5\linewidth}
-    \includegraphics[width=.99\linewidth]{dir.pdf} 
-    \caption{Direct model} 
-  \end{minipage} 
-\end{figure}
-
-\begin{figure}
-     \centering
-  \caption{Structural model of full estimation - PLS-SEM}
-  \input{./figure/fullmod.tex}
-\end{figure}
-
-\begin{table}
-\begin{center}
-\script size
-\begin{tabular}{lcccc}
-
-\hline \\[-2pt]
- & \multicolumn{4}{c}{{\bf Models:}} \\  \cline{2-5} \\[-3pt] 
- & \emph{Direct} & \emph{Process} & \emph{Routines} & \emph{Full}\\
- & (1) & (2) & (3) & (4)\\
-\hline
- &  &  &  & \\
-\(CA_{t-1} \rightarrow CA\) & \Sexpr{plmest[1,2]} & \Sexpr{plmest[1,3]} & \Sexpr{plmest[1,4]} & \Sexpr{plmest[1,5]}\\
- & (\Sexpr{plmt[1,2]}) & (\Sexpr{plmt[1,3]}) & (\Sexpr{plmt[1,4]}) & (\Sexpr{plmt[1,5]})\\[3pt]
- &  &  &  & \\
-\(DC_P \rightarrow CA\) & \Sexpr{plmest[2,2]} & \Sexpr{plmest[2,3]} & \Sexpr{plmest[2,4]} & \Sexpr{plmest[2,5]}\\
- & (\Sexpr{plmt[2,2]}) & (\Sexpr{plmt[2,3]}) & (\Sexpr{plmt[2,4]}) & (\Sexpr{plmt[2,5]})\\[4pt]
-\(DC_X \rightarrow CA\) & \Sexpr{plmest[3,2]} & \Sexpr{plmest[3,3]} & \Sexpr{plmest[3,4]} & \Sexpr{plmest[3,5]}\\
- & (\Sexpr{plmt[3,2]}) & (\Sexpr{plmt[3,3]}) & (\Sexpr{plmt[3,4]}) & (\Sexpr{plmt[3,5]})\\[4pt]
- &  &  &  & \\
-\(DC_P \rightarrow P\) &  & \Sexpr{plmest[4,3]} &  & \Sexpr{plmest[4,5]}\\
- &  & (\Sexpr{plmt[4,3]}) &  & (\Sexpr{plmt[4,5]})\\[4pt]
-\(DC_P \rightarrow R\) &  &  & \Sexpr{plmest[5,4]} & \Sexpr{plmest[5,5]}\\
- &  &  & (\Sexpr{plmt[5,4]}) & (\Sexpr{plmt[5,5]})\\[4pt]
-\(DC_X \rightarrow P\) &  & \Sexpr{plmest[6,3]} &  & \Sexpr{plmest[6,5]}\\
- &  & (\Sexpr{plmt[6,3]}) &  & (\Sexpr{plmt[6,5]})\\[4pt]
-\(DC_X \rightarrow R\) &  &  & \Sexpr{plmest[7,4]} & \Sexpr{plmest[7,5]}\\
- &  &  & (\Sexpr{plmt[7,4]}) & (\Sexpr{plmt[7,5]})\\[4pt]
- &  &  &  & \\
-\(P \rightarrow CA\) &  & \Sexpr{plmest[8,3]} &  & \Sexpr{plmest[8,5]}\\
- &  & (\Sexpr{plmt[8,3]}) &  & (\Sexpr{plmt[8,5]})\\[4pt]
-\(R \rightarrow CA\) &  &  & \Sexpr{plmest[9,4]} & \Sexpr{plmest[9,5]}\\
- &  &  & (\Sexpr{plmt[9,4]}) & (\Sexpr{plmt[9,5]})\\[4pt]
- &  &  &  & \\
-\hline \\[-3pt] 
-Goodness of fit & \Sexpr{gofdir} & \Sexpr{gofor} & \Sexpr{gofma} & \Sexpr{goffull}\\
-Number of observations & \Sexpr{N} & \Sexpr{N} & \Sexpr{N} & \Sexpr{N}\\
-  Firm level controls & YES & YES & YES & YES\\[3pt]
-\hline
- &  &  &  & \\
-\end{tabular}
-\end{center}
- \label{tab:reg}
-\end{table}
-
-Table \ref{tab:reg} shows a summary of the regression models proposed in the previous
-chapter. Models 1,2 and 3 are designed to test DL as \emph{antecedent} for $OR$ and
-$DC$. Consider model 1 we observe that $DL$ is influencing the level of $OR$ within the
-firm ($\beta_2 =$r) supporting H1. However, the effect disappears when we
-add $DC$ in model 2 suggesting a mediating effect. In other words we see that firms with
-initial high $DC$($\beta_3=$ \ {mod2_dc0}) and increasing $DC$ over time ($\beta_4=$
-\ {mod2_ddc}) also have better $OR$. To control for the mediating effect suggested by
-the change in coefficients for $DL$ between models 1 and 2, we performed a causal
-mediation analysis as reported in figure \ref{fig:fig3}. This analysis confirms the
-indications from models 1 and 2 showing that the direct effect from $DL$ on $OR$ is
-insignificant and small (ADE = \ {medmod1_ade}). Meanwhile, the indirect effect
-running through changes in $DC$ over time, is significant yielding a positive and
-significant indirect effect of \ {medmod1_acme}. The proportion of the effect that is
-mediated amounts to \ {medmod1_shmed}. In sum these results suggest that H1 is
-unsupported, and that the bulk of the effect is indirect running through $DC$, in line with
-the expectations in H3. Similarly, we see from model 3 that $DC$ is indeed influenced by $DL$
-above and beyond its own evolutionary trajectory. This is in line with our expectations
-and lend support to H4.
-
-To evaluate H5 proposing a feedback effect from $DC$ to $DL$, we turn to model 6 in table
-\ref{tab:reg}. Controlled for the usual firm level controls we find a positive effect
-($\xi_1=$ \ {mod6_dc0}) from $DC_{T_1}$ on $DL$ measured at $T_1$. This supports H5
-suggesting that firms with more $DC$ is more likely to generate opportunities where it
-becomes more prevalent that learning will need to take place. One interesting finding is
-also that this effect environmental dynamism decreases firms level of $DL$. This is indeed
-puzzling and we will look in to this in a post-hoc analysis.\todo{When adding interactions
-  we see that high environmental dynamism in conjunction with DC is positive for DL
-  meaning that DC will indeed work to make firms more aware of the benefits of DL when
-  environments are changing} It is also worth noting that models 1,2 and 3 have positive
-and significant $\rho$ from the Heckman selection model indicating that selection is
-leading to biased estimates. By running a Heckman correction we avoid this potential
-problem.
-
-Models 4 and 5 in table \ref{tab:reg} deals with the \emph{outcome} of DC. H6a and H6b
-both considers effects of $DC$ on the competitive advantage of the firm $CA$. $CA$ is
-influenced by the level of $DC$ of the firm indicating that dynamic capabilities are a
-source of competitive advantage in line with our expectations. Furthermore, considering
-model 5 we see that $OR$ also has a significant positive effect on $CA$ indicating that
-operating routines can also be a source of advantage for the firm. Moreover, the
-coefficient of $\Delta DC$ decline from  {mod4_ddc} to  {mod5_ddc} when we add
-$OR$. This suggests that some mediation is at work, i.e. that changes in $DC$ leads to
-changes in changes in $OR$ leading to $CA$. This indirect path is in line with the
-expectations from our hypotheses and as described in figure \ref{fig:fig2}. When formally
-testing this mediation running a causal mediation analysis (see figure \ref{fig:fig4}), we
-find added support that both a \emph{direct-} and an \emph{indirect} path exist to explain
-the relationship between $DC$ and $CA$ (ADE = \ {medmod5_ade}, ACME =
-\ {medmod5_acme}) and a total mediated share of \ {medmod5_shmed}.
-
-Table \ref{tab:hyptab} depict a summary of the hypotheses and indicate if they are
-supported or not in our analysis. We will now turn to the discussion.
-
-\section{Discussion}
-
-Moving from antecedents to outcomes we extended the \cite{Zollo2002a} model by adding
-competitive advantage to the model. We find that both operational capabilities and dynamic
-capabilities can lead to competitive advantage. The most obvious path from the mere
-definition of dynamic capabilities, runs through the evolution of operational
-capabilities. Dynamic capabilities shape operational capabilities and changes them to
-adapt, hence safeguarding that they are adapted. This is beyond the ad-hoc learning and
-adaptation taking place as repetitive actions by employees. TO BE CONTINUED
-
-\subsection{Limitations}
-
 \section{Bibliography}

### 2019-10-21 article4_tommylars.tex
after tommy meeting first draft

--- 2019-09-26 article4_tommylars.tex
@@
 
-0.343
-In a recent "state of the art" literature review on dynamic capabilities
-\cite{Schilke2018} state that much of the attention and interest surrounding the theory is
-that it offer a route to competitive advantage which they argue is "the virtual Holy Grail
-of strategic management" (p. 393). And indeed a considerable body of the extant literature
-concerns itself with exactly this path to competitive advantage (refs from
-shcilke). Still, a discourse regarding the contingencies of the dynamic
-capabilities-competitive advantage (DC-CA) nexus (?) has panned out in the literature,
-most notably coined "the elephant in the room" \citep{Peteraf2013}: Under which conditions
-will dynamic capabilities lead to competitive advantage?
+%% Extant literature on dynamic capabilities is battling with a fundamental conception and
+%% prediction of the theory, namely if, when and how dynamic capabilities can lead to competitive
+%% advantage.
 
-\cite{Peteraf2013} argue that the seminal papers in the dynamic capabilities theory
-tradition (\cite{Teece1997} and \cite{Eisenhardt2000}) differ considerably in their view
-of to what extent the DC-CA nexus exist and under what conditions it is functional. A key
-tenant of this discourse is related to the level of routinization and the ability to
-satisfy the VRIO condition \citep{Barney1991a} of the resource-based view
-\citep{Peteraf2013}.
+The presence of a direct path from dynamic capabilities and competetive advantage is
+somewhat puzzling. It eiter suggests ommited importrant mediating factors such as
+resources, or that dynamic capabilities can act outside "creating, extending and modifying
+the firm resources base". A growing consensus on the definition as well as the
+theoretical mechanisms underpinning dynamic capabilities suggest that dc work indirectly
+towards strategic change by changing firm resources. Hence, the presence of direct effects
+seems increasingly odd. Still, seminal contributions to the field of dynamic capabilities have argued for both direct
+\cite{Kor2005,Eriksson2014,Schilke2014a} and indirect (ref) effects of dynamic
+capabilities on competitive advantage, although increasingly the bulk of the literature
+focuses on the latter \citep{Schilke2018}.
 
-In this paper we aim to contribute to dissecting the elephant by asking how does the DC-CA
-nexus differ between firms and what determines these differences?
+ Resource orchestration is defined as "blablbalbla" (helfat)
 
-We do this by exploring two paths from dynamic capabilities to competitive advantage: the
-\emph{evolutionary path} and the \emph{market path}. The former is thoroughly described
-and explored in the literature (refs) and stems from the core idea of the dynamic
-capabilities theorizing. In this path dynamic capabilities work to change the operating
-routines of the firm and hence contributing to it's competitive advantage. We argue that
-this path is more suited for less dynamic environments because of its path dependent
-functioning.
+This indirect link is typically understood as dynamic capabilities modifying, extending or
+creating firm resources (helfat) (or lower-level operational capabilities (Winter,
+collis)) and thus generating competitive advantage (Eriksson and others).The direct path,
+however, is theoretically less explicitly dealt with in the extant literature although
+empirical evidence keep suggesting that both direct (ref) and indirect (ref) links exist.
 
-The \emph{market path} works not through shaping operational capabilities and routines,
-but by enabling the firm to act in factor markets for new capabilities and
-resources. Hence, it is less path dependent and can be more rapidly
-deployed. Consequently, it is more prevalent in dynamic environments.
+In this paper we explore to what extent a direct link between dynamic capabilities and
+competitive advantage work, and under which conditions it is most pronounced. Specifically
+the research question is:
 
-This paper contributes to the extant literature on the link between dynamic capabilities
-and competitive advantage in three ways. First, provides an empirical test to the
-drive-train model of \cite{DiStefano2014} on how dynamic capabilities can operate both
-quickly and with high frequency more directly on the strategic direction of the firm by
-acting in factor markets for important resources, and also more slowly through the
-evolutionary path of changing operational capabilities. Second, by conceptually clarifying
-the different paths to competitive advantage by linking it closely to the role of
-capability evolution and the VRIO condition. Finally, we.........
+{\bf How is a direct link between dynamic capabilities and competitive advantage working
+  and under which conditions does it come into play or not?}
 
-CLARIFIES THE ROLE OF THE ENVIRONMENT AND MEDIATIONS HAPPENING
+We argue that direct link exist as a response to the multilevel notion of strategy itself
+and captures strategic change not typically associated with the resource based
+view. Furthermore, we show that the prevalence of the direct link is a function of the
+nature of underlying resources dynamic capabilities are aimed at "creating, extending and
+modifying", specifically if they are valuable and idiosyncratic to the firm or not, and
+the environment facing the firm.
 
-%% How does dynamic capabilities lead to competitive advantage?
-%% Dynamic capabilities are proposed to confer a competitive advantage by adding unique value to the firm through systematic change, which enhances operational efficiency and enables increased alignment with the environment (Di Stefano et al., 2014; Peteraf et al., 2013)
+Our findings indicate that the direct path is less prevalent in very dynamic environments
+where the indirect path becomes far more important. Furthermore, the effect of dynamism is
+partly contingent on the nature of the firm resources suggesting a more complex
+understanding of how imitable and simple resources can play a role in generating
+competetive advantage.
 
-%% Not all organizations possess them (Collis, 1996); their path dependencies, intangibility, complexity, and organizational specificity make them hard to imitate (Gibson & Birkinshaw, 2004; Helfat & Winter, 2011); and few other means allow organizations to purposefully change on a continuous basis (Day & Wensley, 1988; Helfat et al., 2007).
+Our contributions are twofold. First, we explore different mediators by explicitly
+modeling a causal chain with different types of underlying resources, as well as
+under different environments. This is explicitly called for in the literature as "only
+four percent of the articles in our sample explicitly examined possible causal mechanisms,
+suggesting a significant gap in the literature" (Schilke 2018). This work sheds light on
+the contingencies and boundary conditions of the link between dynamic capabilities and the
+"holy grail of strategy" (Schilke et al), competetive advantage.
 
-%% Consistent with the theoretical positions of Eisenhardt and Martin (2000), Helfat and Peteraf (2003), Zahra et al.
-(2006), and Zott (2003), among others, these researchers have argued that dynamic capabilities’ immediate purpose is to change the resource base, and that this change in the resource base, in turn, explains performance variations.
-According to this argument, resource changes serve as mediators through which dynamic capabilities affect performance.
-We
+Second, we explore a theoretical explanation for why a direct link between dynamic
+capabiliites and competetive advantage may exist. By leaning on empirical evidence
+suggesting a multitude of explanations for performance differentials between firms, we
+suggest that dyanmic capabilities can act outside the theorized path of "resource
+orchestration" through strateic efforts such as industry positioning (porter) or
+institutional leverage (Peng).
 
-%% One of the major unresolved issues in dynamic capabilities theory is to what extent and
-%% how competitive advantage is the ultimate outcome of dynamic capabilities. This very idea
-%% has
+%%%%%%%%%%%%%%5
 
-%% This paper asks two questions: to what extent does a direct lnk between DC and CA exist,
-%% and what determines variations in the role of mediation between them?
+%%%%%%%%%%%%%%
 
-%% The idea that Dc impacts CA is uncontroversial (not). Little is known about how this
-%% happens. The theory holds that this happens through xreating extending and modifying the
-%% resource base. YEt, the change in firm capabilities can themselves lead to CA due to their
-%% evlutionary nature.
+%% This warrant the question of \emph{when}
+%% direct and indirect links between dynamic capabilities and competitive advantage is most
+%% pronounced.
 
-%% Variations in the share of mediation stems from variation sin the environment. When envdyn
-%% is high firms need to act faster and hence tends to choose strategies including resource
-%% orchestration buying in factor markets cause it tkes more time to develop OR.
+%% Moreover, firm resources or capabiltiies themselves are far from a homogenous set and
+%% varies among other things with respect to their uniqueness, inimatbility and value
+%% (barney). Important contributions have thus argued for a deeper insighi into these
+%% intermediaries and their mechanism calling for a "deeper insight into the variety of mechanisms that
+%% underlie the performance effects of capabilities.” (Schilke, 2014a: 199). 
+%% as well as \emph{what} different intermediaries exist.
 
-%% In less dynamism the role of OR increases and leads to a significant proportion of CA
-%% stemming throhg the mediating effect of OR
+%% This paper investigates the boundary conditions of the VRIO condition and how dynamic
+%% capabilities and resources interact to create firm competitive advantage. We ask the
+%% following research question:
+%% Under which conditions are dynamic capabilities able to yield competietive advantage
+%% through resource orchestration and what are the different outcomes of different types of resources.
 
-%% There is ongoing interest in (dynamic) capabilities and how they influence firm
-%% performance \citep{Fainshmidt2016a,Teece2014}. Indeed, \emph{dynamic capabilities} (DC),
-%% and its front runner, the resource-based view \citep{Barney2001,Helfat2007}, is now
-%% considered one of the major theories in strategic management
-%% \citep{Schilke2018}. Arguably, the key reason is that this theory clearly articulates how
-%% firms can alter their operating routines through dynamic capabilities. Thus, a key
-%% ingredient in this theory is that DCs can alter firms operating routines, with subsequent
-%% performance implications.
+%% We find thatthe dynamism surrounding hte firm represent an important boundary condition as
+%% suggested in parts of the literature. However, DC consinutes to generate competetive
+%% advnatage also in high-velocity environments, but doing increasingly so indirectly through
+%% resource orchestration. Furthermore, we find that non-vrio resources are more likely to
+%% yield competetive power in high velocity environments, and that vrio-resources tend to
+%% maintain their CA under any condition.
 
-We demonstrate that two paths indeed do exist and that their relative importance varies
-with the degree of environmental dynamism facing the firm.
+%% We demonstrate that two paths indeed do exist and that their relative importance varies
+%% with the degree of environmental dynamism facing the firm.
+
+%% Under what cionditions are the direct path and indirect path most prevalant? Under which condi
+
+%% The direct
 
@@
 
-%% We can use the drive train to determine hwo DC works differently under different levels of
-%% dynamism. It is not that DC does not work under stable conditions as EM claims. Is only
-%% that the effect runs stringer through the evolutionary path. Whereas the market path is
-%% stringer under higher dynamism
+%{\bf How is a direct link between dynamic capabiliites and competetive advantage working
+%  and under which conditions does it come into play or not?}
 
-One contentious issue surrounding the DC theory is the extent to which differing views on
-the nature of dynamic capabilities \citep{Peteraf2013} as well as their outcome. One
-strand of contributions sees DC as routines that are simple in nature and more as best
-practices to consider (EM). Thus, dynamic capabilities are more like behavioral patterns
-and less idiosyncratic to the firm and will consequently not be able to satisfy the VRIO
-condition for competitive advantage to emerge. Dynamic capabilities as such routines are
-short lived, unstable and “substitutable” (EM: 1110) thus violating a key VRIN condition,
-and they are more “more homogeneous (..) than is usually assumed” (EM: 1116). However, the
-simplicity of simple rules also makes them faster do deploy and put in motion, albeit
-potentially unstable. To the extent dynamic capabilities manifest themselves as simple
-rules they cannot alone create competitive advantage, but could very well generate
-strategic change by facilitating acquisition of resources in factor markets. One example
-is the role of post-acquisition routines where routines to identify and deal with
-acquisition partners are a source of generating strategic change (Eisenhardt and Sull
-2001, ref). Another example is (see refs from Schilke 2018). The functioning of this
-expression of dynamic capabilities are more latent and hence mainly observable ex
-post. Hence we can see this as direct route to competitive advantage as this expression of
-dynamic capabilities work directly in the factor market in capturing resources
-needed for strategic change. We coin this direct connection as the \emph{market path}.
+In the face of a growing consensus on the definition (ref) and outcome (ref) of dynamic
+capabilities as working through mediators, the presence of direct effects argued by others
+(ref) seems puzzling. However, the broader empirical literature on the antecedents of firm
+performance offers an interesting point of departure. This literature concerns itself with
+the relative importance of factors at the firm-level on the one hand, and those at the
+industry level at the other.
 
-On the other hand, a stream of contributions see dynamic capabilities as evolutionary and
-more complex routines (ref) or processes (ref) set to change underlying capabilities in
-the face of changing conditions (TPS). This notion stems from evolutionary economics
-\citep{Winter2003,Nelson1982} and the behavioral theory of the firm \citep{Cyert1963}
-holding that path dependency and complex processes for changing underlying operating
-routines are a source of competitive advantage for the firm. Along this indirect path
-change is gradual and running through changes in underlying routines. We coin this the
-\emph{evolutionary path}.
+The debate over the relative role of different levels of factors in accounting for the
+major share of the variance in firms performance has been of particular importance in the
+field of strategic management, most notably in the Strategic Management Journal
+(M. A. Fitza 2014; Hansen and Wernerfelt 1989; McGahan and Porter 1997; Rumelt
+1991). Overall, the accumulated empirical evidence show that firm factors matter far more
+for firm performance than industry factors (McGahan and Porter 2002). These stylized facts
+have been used as empirical support for the importance of idiosyncratic firm resource and
+capabilities; leading up too recent formulation of the resource and capability based
+theorizing (e.g. (Barney 1991; Teece, Pisano, and Shuen 1997)). However, the dominance of
+the firm-level explanations have been partly refuted by later scholars finding the sum of
+indirect and direct effects from industry to be of more importance than previously
+indicated by (Mcgahan etc). Moreover, the industry effect is also more time invariant
+(i.e. more stable) compared to firm level effects. Recent findings also suggest that there
+are considerable interaction effects between industry and the firm indicating that
+industry membership works directly at performance as well as indirectly through affecting
+the firm. However, little or no explanations are made for the mechanisms of this
+interaction.In other words, industry factors matter alas less than firm-level factors, and
+the indirect link from industry-level through firms are in need of further development.
 
-These paths from dynamic capabilities to competitive advantage are different expressions
-of dynamic capabilities with different mediums of intermediation. The \emph{market path}
-works in the market and his hence not typically altering lower order capabilities and
-resources in the firm directly, but rather acquiring new ones. The source of competitive
-advantage along this path stems from the interaction with the other, \emph{evolutionary
-  path} in a dynamic bundle \citep{Peteraf2013}. Such interactions create a bundle of
-capabilities and routines that are socially complex and hard to imitate
-\citep[p. 320]{DiStefano2014}. Moreover, the interactions between the two paths of dynamic
-capabilities is separable with respect to what intermediation exist. Consequently,
-separate paths exist albeit a part of a dynamic bundle.
+One way of looking at this is to consider the dynamic capabilities of the firm. Although
+an increasing consensus focuses on these dynamic capabilities as the ability to create,
+extend and modify firm resources in the face of change, there still looms an important
+stream of literature suggesting that dynamic capabilities can materialize as management
+actions (ref eisenhardt, peteraf, helfat). A management action aimed at strategic change
+will very often entail "resource orchestration" as broadly discussed in the literature
+(Helfat etc). But, strategic change are also found to come about from adapting and
+changing the positioning of the firm within its industry (ref) or simply refocusing its
+focal industry (ref). In other words, when a firm with excellent dynamic capabiliites
+senses and seizes opportunities within its domain, the implementation of strategic change
+will often both entail a considerable share of "asset orchestration" (helfat etc) as well
+as management actions directed at positioning within its industry (ref). One way to
+illustrate this is to consider Microsofts strategic change from operating system to cloud
+provider. CEO Satya Nadela and his team was able to restart the business by creating,
+extending and modifying the resources of the firm, including new skills, routiens and
+hardware, as a response to a growing demand for cloud computing (ref nadellas
+book). Meanwhile, his vision and formulated strategy also direclty put the company into a
+new industry, or at the very least reshaped the position they were already in. While
+Microsofts dynamic capabiliites worked significantly through "resource orchestration",
+the sensing and seizing of the management also ordered a direct re-positioning at the same
+time.
 
-\cite{DiStefano2014} propose an integrated framework where simple routines and more
-complex processes could contribute simultanously to the firms outcome, specifically its
-competitive advantage. In this framework, coined the "organizational drivetrain" the
-authors envision the movement of an organization as set in motion by a drivetrain system
-not unlike that of a bicycle.
+Moreover, The link between firm resources and competitive advantage is determined by the
+extent to which resources are valuable and difficult to imitate \citep{Barney1991a}. This
+principle is also used to evaluate how higher order capabilities (e.g. dynamic
+capabilities \citep{Winter2003,Collis1994,Teece2007}. Hence, for a direct link to exist
+the dynamic capabilities of the firm will have to be valuable and difficult to
+imitate. This is an area of certain contention in the literature \citep{Peteraf2013} which
+we get back to below, but an increasing majority is arguing that dynamic capabilities
+reflect more complex processes that co-evolve with responses to market changes over time
+and hence creating idiosyncratic capabilities that are unique, valuable and hard to copy
+\citep{Helfat2007,Arndt2018}. Consequently, they are likely to lead to competitive
+advantage.
 
-Building on the notion of an organizational drivetrain we argue that dynamic capabilities
-can indeed impact the organizational movement or change through two distinct but
-interconnected mechanisms (i.e. the crank set and the rear shifter). The two mechanisms
-consitutting the drivetrain is consistent with our notion of \emph{evolutionary path} and the \emph{market path}. The
-evolutionary path is instigated by more complex processes setting in motiong a chance in
-the lower order (operational) routines \cite{Collis1994,Winter2003}. In the drivetrain
-metaphor this path corresponds to change stemming from the front crank set of thich there
-are fewer gears, but with larger impact. This path is slower
-and yields a more idiosyncratic set of organizational routines which is very much in line
-with the idea put forth in the seminal founding papers \citep{Teece1997,Winter2003}.
+In most cases such direct effects between dynamic capabilities and strategic change
+resulting in competitive advantage, are combined with the indirect effects (i.e. resource
+orchestration). To test this proposition empirically is hard, but one hypothesis following
+from this is related to the role of mediators. if a direct path does not exist, the
+relationship between dynamic capabilities and competitive advantage would be fully
+mediated by the proper set of firm resources.
 
-Seeing the bike rider and her efforts to handle the levers of control (i.e. the gear
-shifter) as the dynamic capability, and consider it not only as a management effort, but
-that of the organization as a whole. The process of changing front gears are more profound
-(i.e. evolutionary) and costly, and it is for larger and slower strategic
-changes. Operating with simple routines in factor markets, however, is quicker and the
-rider does this on a more frequent basis with less effort.
+\emph{H1: The existence of a direct path from dynamic capabilities to competitive advantage
+suggest that full mediation is not present}
 
-H1: Dynamic capabilities works to create competitive advantage through two distinctly
-different paths.
+Even if the dynamic capabilities of the firm themselves are not valuable and inimitable as
+needed to create competitive advantage, the underlying resources of the firm may very well
+be. Such resources in the form of operating routines or capabilities can in turn stem from
+an inherent learning process evolutionary distinct to the firm. Operating routines can
+thus lead to competitive advantage because of their evolutionary character
+\citep{Nelson1982,Winter2003}. To the extent operating routines stems from idiosyncratic
+evolutionary process of individual firms rather than being the result of best practices,
+they can satisfy the VRIO condition and thus be a source of competitive advantage.  Hence,
+through "resource orchestration" a firm with non-valuable dynamic capabilities can achieve
+competitive advantage through the indirect path. The flip side of this is that a valuable
+dynamic capability would not be able to create competitive advantage by orchestrating
+non-valuable resources. Consequently, the mediation effects of underlying resources is
+dependent on the nature of the resource - it being valuable and inimitable or not.
 
-\subsection{The two paths of dynamic capabilities}
-The objective of strategic change is to enhance a firm’s competitive advantage
-(ref). Doing so over time makes for the evolutionary fitness of the firm
-\citep{Helfat2007}. When firms are developing capabilities for strategic change through
-creating, extending and modifying the resource base this means making decisions to develop
-operational routines. Such routines can in turn stem from an inherent learning process
-evolutionary distinct to the firm. Operating routines can thus lead to competitive
-advantage because of their evolutionary character \citep{Nelson1982,Winter2003}. To the
-extent operating routines stems from idiosyncratic evolutionary process of individual
-firms rather than being the result of investments in factor markets, they can satisfy the
-VRIO condition and thus be a source of competitive advantage. In such instances, dynamic
-capabilities work through operating routines in creating competitive advantage. This
-indirect impact on competitive advantage is very much at the core of the DC literature
-(ref). Firms with high dynamic capabilities will be able to better change operating
-routines to facilitate strategic change in response to changing conditions facing the
-firm. Dynamic capabilities then creates VRIO operating routines and hence competitive
-advantage. When this happens, firms changes their operating routines in a evolutionary
-making operating routines themselves OR itself satisfies the VRIO condition.
+\emph{H2a: When dynamic capabilities are being mediated by VRIO resources the firm can
+  achieve competitive advantage}
 
-\emph{H2: Dynamic capabilities has an indirect effect on competitive advantage through
-  changing the operating routines of the firm.}
+\emph{H2a: When dynamic capabilities are being mediated by VRIO resources the firm can not
+  achieve competitive advantage}
 
-On the other hand, resources and capabilities can to a certain extent be captured in
-factor markets through investment decisions (ref) or through alliances (ref) or M\&A
-activates (ref). By acquiring resources through investments, the operating routines of the
-firms may not be directly affected. When these acquisitions happen as a response to
-systematic resource orchestration (ref), i.e. reshaping the resource mix to obtain
-coordinated resource deployments \citep{Kor2005,Pan2006}, they would indeed have potential
-performance implications for the firm. Moreover, when this process of resource acquisition
-process of DC develops a way to acquire and mix resource for the purpose of adapting to
-change, the resources themselves would not necessarily satisfy the VRIO condition. The way
-in which this happens may be much harder to imitate due to the complexities such routines
-exhibit. Although resources themselves exhibit clear equifinality in their impact on
-competitive advantage, combined with the simple routines of the orchestration
-(i.e. dynamic capabilities), the sum would likely satisfy the VRIO condition. This is
-especially true if routines are deployed rapidly in changing market conditions. In other
-words, there are several ways in which resources can be orchestrated to generate CA,
-whereas improved OR will always mean improved competitiveness et ceteris paribus. In such
-instances DC itself can lead to CA directly.
+DEspite a growing consensus on the nature of dynamic capabilites, a serious contention is
+presen tin the literature \citep{Peteraf2013}. This stems from different notions of
+dynamic capabilities in the two "founding" papers of the theory, \cite{Eisenhardt2000} and
+\cite{Teece1997}.
 
-\emph{H3: Dynamic capabilities has a direct effect on competitive advantage through the
-  process of resource orchestration and acquisition of resources in factor markets.}
+One strand of contributions sees DC as routines that are simple in nature and more as best
+practices to consider \citep{Eisenhardt2000}. Thus, dynamic capabilities are more like
+behavioral patterns and less idiosyncratic to the firm and will consequently not be able
+to satisfy the VRIO condition for competitive advantage to emerge. Dynamic capabilities as
+such routines are short lived, unstable and “substitutable” (ibid, p 1110) thus violating
+a key VRIO condition, and they are more “more homogeneous (..) than is usually assumed”
+(ibid, 1116). However, the simplicity of simple rules also makes them faster do deploy and
+put in motion, albeit potentially unstable. To the extent dynamic capabilities manifest
+themselves as simple rules they cannot alone create competitive advantage, but could very
+well generate strategic change by facilitating the process of resource orchestration.. In
+other words, even if dynamic capabilities play out as simple rules that are not in
+themselves satisfying the VRIO condition, the way they work through creating, extending
+and modifying firm resources, can still yield competitive advantage through orchestrating
+VRIO resources.
 
-In other words, we would expect DC to have both a direct and an indirect impact on CA. The
-indirect impact stems from the \emph{evolutionary path} of complex processes, whereas the
-direct impact stems from the \emph{market path}.  Although both the direct and the
-indirect path stems from DC creating, extending and modifying the resource base (OR or
-factor market resources), the difference in the path’s stems from to what extent the
-mediating construct alone can by itself satisfy the VRIO condition. Operating routines
-can, due to their evolutionary nature, in turn shaped by DC, achieve CA
-\citep{Collis1994,Winter2003}. Factor market resources and market acquired capabilities
-and best practices can not \citep{Eisenhardt2000,Peteraf2013}, but in conjuncture with the
-routines of acting in factor markets as well as the speed of deployment, the sum of
-dynamic capabilities and factor market action would lead to competitive advantage.
+On the other hand, \cite{Teece1997} and others \cite{Helfat2007} argue that dynamic
+capabilities will rather invariably be VRIO due to the evolutionary nature of their
+development \citep{Arndt2018,Peteraf2013}. Arguing that dynamic capabilities reflect more
+complex processes that co-evolve with responses to market changes over time and hence
+creating idiosyncratic capabilities that are unique, valuable and hard to copy
+\citep{Helfat2007,Arndt2018}. Consequently, they are likely to satisfy the VRIO condition
+and thus leading to competitive advantage.
 
-However, the interlinkages between simple routines (the market path) and the coplex
-processes (the evolutionary path) would vary with the environment.
+The contention between these streams of literature is most explicit in highly dynamic
+environments (distefano, peteraf) suggesting that environmental dynamism could play into
+the presence of direct and indirect linkages between dynamic capabilities and competitive
+advantage. This is also supported in previous empirical literature \citep{Schilke2014}.
+This could suggest that dynamic capabilities exhibit different characteristics under
+various levels of environmental dynamism. This is also suggested by Eisenhardt blaboblabla
+arguing that under moderatly dynamism dynamic capabilities takes the form of best
+pracitces (e.g. aquisition targeting) and is less important than under more dynamic
+environments. However, albeit best practices, the way they are implemented in the factor
+markets are still idiosyncratic. And taken into conjunction with the routinzed process of
+changing underlying routines, VRIO will very likely emerge under more stable
+conditions. It is not that the market/direct expression of dynamic capabilities are not
+present in stable environments, rather it is less pronounced and the indirect mediated
+effect (evolutionary path) is more important. In other words, it is not neither nor, but
+degrees of importance.
 
-\subsection{Interplay under environmental dynamism}
+\emph{H3: The mediation effects of underlying resources is dependent on the environmental
+dynamism facing the firm }
 
-\cite{DiStefano2014} note that "even if specific simple rules are unstable and ephemeral,
-the system as a whole is not" and that the "real source of sustainable competitive ad- vantage for an enterprise is the difficulty of imitating and substituting for the entire dynamic bundle that the system represents" (p.sss).
+%% Increasingly the literature remain focused on an \emph{indirect
+%%   path} between dynamic capabilities and competitive advantage
+%% \citep{Barreto2010,Schilke2018}. The theory behind this path goes back to the core of
+%% dynamic capabilities where resource orchestration happens as a response to changes in the
+%% environment. When markets, technologies or other external factors changes, firms with high
+%% levels of dynamic capabilities are able to seize opportunities for changes, seize these
+%% opportunities and transform the resource base to fit the strategic change needed to stay
+%% competitive \cite{Teece2007}. This ability to adapt is by some coined \emph{evolutionary
+%%   fitness} defined as BLABLBALBA and stems from the ability of the firm to reconfigure
+%% resources in the face of change. The extant literature, however, is less clear on how the
+%% nature of the underlying resources matter in this indirect path. On the one hand we can
+%% see
 
-But the interlinkages between the parts of the system (the evolutionary- and the market
-path), are likely to vary with the environmental dynamism. Under moderatly dynamism
-dynamic capabilities takes the form of best pracitces (e.g. aquisition targeting) and is
-less important than under more dynamic environments. However, albeit best practices, the
-way they are implemented in the factor markets are still idiosyncratic. And taken into
-conjunction with the routinzed process of changing underlying routines, VRIO will very
-likely emerge under more stable conditions. It is not that the market/direct expression
-of dynamic capabilities are not present in stable environments, rather it is less pronounced and the indirect
-mediated effect (evolutionary path) is more important. In other words, it is not neither
-nor, but degrees of importance.
+%% Following REF suggesting more reseaarch on dynamic capabilities should put forth
+%% competeing hypotheses we propose these first
 
-Moreover, in high velocity environments the role of the evolutionary path tends to
-weaken as such path-dependent changes occur slower compared to the market path. From the
-market path with its simple routines we can argue that creation of "new knowledge” to
-“allow for emergent adaptation” (EM, p. 1116) is the consequence. Consequently, the market
-path is stronger and more prevalent under higher levels of environmental dynamism.
+%% We introduce the notion of multilevel VRIO to integrate the interactions between different
+%% types of capabilities at different levels. This entails that dynamic capabilities (the
+%% high level) can consist of complex and evolutionary characteristics that are idiosyncratic
+%% to the firm and hence VRIO by definition along the lines of how the concept is understood
+%% by \cite{Teece1997}. On the other hand dynamic capabilities can also take the shape of
+%% simpler routines which are short lived, unstable and substitutable thus violating a key
+%% VRIO condition. This follows the notion of dynamic capabilities found in
+%% h\cite{Eisenhardt2000} arguing that they are more “more homogeneous (..) than is usually
+%% assumed” (EM: 1116).
 
-\emph{H4: Dynamic capabilities works relatively stronger through the market path in highly
-dynamic environments.}
+%% Moreover, these dynamic capabilities are in the extant literature argued and found to work
+%% directly \citep{Kor2005,Eriksson2014,Schilke2018} on competitive advantage which suggests
+%% that they are indeed VRIO. On the other hand, a growing body of literature (ref) as well
+%% a consensus on the definition of dynamic capabilities (ref), holds that they can lead to
+%% competitive advantage by changing underlying resources and routines. In this
+%% \emph{indirect path} the dynamic capabilities itself need not be VRIO as long as the
+%% underlying resources themselves are.
+
+%% \subsection{The role of dynamism}
+
+%% The most contentious issue in the current debate on dynamic capabilities is how their
+%% nature varies with the environment.
+
+%% If htey are indeed latent
+
+%% The lower level resources and routines are to be understood as conventional resources in
+%% line with the resources-based view
+
+%% WHAT IS THE ROLE OF DIRECT VS INDIRECT, HOW DOES IT RELATE TO THE ENVIRONMENT, AND WHAT
+%% ROLE DOES THE TYPE OF UNDERLYING RESOURCE PLAY
+
+%% Conventional dc literature has argued for both indirect and direct links. Indeed both
+%% have been found, but while the indirect link is well rooted in the theory, the direct link
+%% is to our knowledge less clear. The core idea of DC is that it works to modify underlying
+%% resources as a response to changes in the environment and hence creating strategic change
+%% needed to stay competitive. This resource orchestration is heavily represented in the
+%% literature (ref) and through this process firms are able to generate CA. In such instances
+%% the CA can stem from VRIO resources and/or VRIO DC. A VRIO DC would mean that the firm is able
+%% to shuffle and reorganize generic resources in a way that creates a new and unique
+%% configuration of resoures idiosyncratic and valuable to the firm. In such instances, the
+%% outcome whould be CA. On the other hand, the DC may not by itself be VRIO but rather a set
+%% of simple routines put in motion to change, but if the resources they reconfigure are
+%% themselves VRIO, the outcome could just as eqsily be a competetive advantage. this
+%% equfinaity is discussed in the literaure \cite{DiStefano2010} and makes it hard to
+%% distingusih between the role of DC and ordinary capabilites in generating CA.
+
+%% Furtemore, Considering a direct link between DC and CA, DC it self must consist of some
+%% VRIO characteristics to garner CA. So in owther words, when is DC working directly and
+%% indirectly_
+
+%% How are dynamic capabilities working directly on competitive advantage? The microfoundations of dynamic capabilities explicated by \cite{Teece2007} is a useful
+%% point of departure of this theoretical inquiry. He hold that for "analytical purposes,
+%% dynamic capabilities can be disaggregated into the capacity (1) to sense and shape
+%% opportunities and threats, (2) to seize opportunities, and (3) to maintain competitiveness
+%% through enhancing, combining, protecting, and, when necessary, reconfiguring the business
+%% enterprise’s intangible and tangible assets". Sensing and seizing is a part of what we
+%% would coin the "opportunity capture" of dynamic capabiliites, where as reconfiguring
+%% concerns itself with the "resource orchestration" needed to change assets to stay
+%% competetive.
+
+%% Hence, when considering indirect and direct paths to compettetive advantage we will have
+%% to be clear on two fronts: Are DC themselves VRIO and are the underlying resources and
+%% routines central to the resource orchestration, VRIO.
+
+%% >
+
+%% The microfoundations of dynamic capabilities—the distinct skills, processes, procedures, orga- nizational structures, decision rules, and disciplines—which undergird enterprise-level sensing, seizing, and reconfiguring capacities are difficult to develop and deploy.
+%% For analytical purposes, dynamic capabilities can be disaggregated into the capacity (1) to sense and shape opportunities and threats, (2) to seize opportunities, and (3) to maintain competitiveness through enhancing, combining, protecting, and, when necessary, reconfiguring the business enter- prise’s intangible and tangible assets.
+
+%%        name Mean_est     t
+%% 3   DC -> P    0.396 6.157
+%% 4   DC -> R    0.416 8.104
+%% 5 DC -> CA1    0.239 4.018
+%% 8  P -> CA1    0.172 2.724
+%% 9  R -> CA1    0.081 1.262
+%% > R
+%%        Path   LOW     t  HIGH     t
+%% 1 DC -> CA1 0.417 6.585 0.144 1.513
+%% 2   DC -> R 0.388 6.078 0.534 7.525
+%% 3  R -> CA1 0.017 0.219 0.211 2.123
+%% > P
+%%        Path   LOW     t  HIGH     t
+%% 1 DC -> CA1 0.355 4.805 0.133 1.379
+%% 2   DC -> P 0.386 5.294 0.436 4.663
+%% 3  P -> CA1 0.155 2.193 0.232 2.315
+%% > B
+%%        name R_LOW_est   t.x R_HIGH_est   t.y
+%% 1 DC -> CA1     0.355 5.407      0.044 0.400
+%% 2   DC -> P     0.376 3.729      0.432 4.668
+%% 3   DC -> R     0.366 5.569      0.522 7.225
+%% 4  P -> CA1     0.158 1.989      0.220 2.357
+%% 5  R -> CA1     0.010 0.135      0.200 2.033
+%% >
+
+%% %% creating and One example
+%% %% is the role of post-acquisition routines where routines to identify and deal with
+%% %% acquisition partners are a source of generating strategic change (Eisenhardt and Sull
+%% %% 2001, ref). Another example is (see refs from Schilke 2018). The functioning of this
+%% %% expression of dynamic capabilities are more latent and hence mainly observable ex
+%% %% post. Hence we can see this as direct route to competitive advantage as this expression of
+%% %% dynamic capabilities work directly in the factor market in capturing resources
+%% %% needed for strategic change. We coin this direct connection as the \emph{market path}.
+
+%% On the other hand, a stream of contributions see dynamic capabilities as evolutionary and
+%% more complex routines (ref) or processes (ref) set to change underlying capabilities in
+%% the face of changing conditions (TPS). This notion stems from evolutionary economics
+%% \citep{Winter2003,Nelson1982} and the behavioral theory of the firm \citep{Cyert1963}
+%% holding that path dependency and complex processes for changing underlying operating
+%% routines are a source of competitive advantage for the firm. Along this indirect path
+%% change is gradual and running through changes in underlying routines. We coin this the
+%% \emph{evolutionary path}.
+
+%% These paths from dynamic capabilities to competitive advantage are different expressions
+%% of dynamic capabilities with different mediums of intermediation. The \emph{market path}
+%% works in the market and his hence not typically altering lower order capabilities and
+%% resources in the firm directly, but rather acquiring new ones. The source of competitive
+%% advantage along this path stems from the interaction with the other, \emph{evolutionary
+%%   path} in a dynamic bundle \citep{Peteraf2013}. Such interactions create a bundle of
+%% capabilities and routines that are socially complex and hard to imitate
+%% \citep[p. 320]{DiStefano2014}. Moreover, the interactions between the two paths of dynamic
+%% capabilities is separable with respect to what intermediation exist. Consequently,
+%% separate paths exist albeit a part of a dynamic bundle.
+
+%% \cite{DiStefano2014} propose an integrated framework where simple routines and more
+%% complex processes could contribute simultanously to the firms outcome, specifically its
+%% competitive advantage. In this framework, coined the "organizational drivetrain" the
+%% authors envision the movement of an organization as set in motion by a drivetrain system
+%% not unlike that of a bicycle.
+
+%% Building on the notion of an organizational drivetrain we argue that dynamic capabilities
+%% can indeed impact the organizational movement or change through two distinct but
+%% interconnected mechanisms (i.e. the crank set and the rear shifter). The two mechanisms
+%% consitutting the drivetrain is consistent with our notion of \emph{evolutionary path} and the \emph{market path}. The
+%% evolutionary path is instigated by more complex processes setting in motiong a chance in
+%% the lower order (operational) routines \cite{Collis1994,Winter2003}. In the drivetrain
+%% metaphor this path corresponds to change stemming from the front crank set of thich there
+%% are fewer gears, but with larger impact. This path is slower
+%% and yields a more idiosyncratic set of organizational routines which is very much in line
+%% with the idea put forth in the seminal founding papers \citep{Teece1997,Winter2003}.
+
+%% Seeing the bike rider and her efforts to handle the levers of control (i.e. the gear
+%% shifter) as the dynamic capability, and consider it not only as a management effort, but
+%% that of the organization as a whole. The process of changing front gears are more profound
+%% (i.e. evolutionary) and costly, and it is for larger and slower strategic
+%% changes. Operating with simple routines in factor markets, however, is quicker and the
+%% rider does this on a more frequent basis with less effort.
+
+%% H1: Dynamic capabilities works to create competitive advantage through two distinctly
+%% different paths.
+
+%% \subsection{The two paths of dynamic capabilities}
+%% The objective of strategic change is to enhance a firm’s competitive advantage
+%% (ref). Doing so over time makes for the evolutionary fitness of the firm
+%% \citep{Helfat2007}. When firms are developing capabilities for strategic change through
+%% creating, extending and modifying the resource base this means making decisions to develop
+%% operational routines. Such routines can in turn stem from an inherent learning process
+%% evolutionary distinct to the firm. Operating routines can thus lead to competitive
+%% advantage because of their evolutionary character \citep{Nelson1982,Winter2003}. To the
+%% extent operating routines stems from idiosyncratic evolutionary process of individual
+%% firms rather than being the result of investments in factor markets, they can satisfy the
+%% VRIO condition and thus be a source of competitive advantage. In such instances, dynamic
+%% capabilities work through operating routines in creating competitive advantage. This
+%% indirect impact on competitive advantage is very much at the core of the DC literature
+%% (ref). Firms with high dynamic capabilities will be able to better change operating
+%% routines to facilitate strategic change in response to changing conditions facing the
+%% firm. Dynamic capabilities then creates VRIO operating routines and hence competitive
+%% advantage. When this happens, firms changes their operating routines in a evolutionary
+%% making operating routines themselves OR itself satisfies the VRIO condition.
+
+%% \emph{H2: Dynamic capabilities has an indirect effect on competitive advantage through
+%%   changing the operating routines of the firm.}
+
+%% On the other hand, resources and capabilities can to a certain extent be captured in
+%% factor markets through investment decisions (ref) or through alliances (ref) or M\&A
+%% activates (ref). By acquiring resources through investments, the operating routines of the
+%% firms may not be directly affected. When these acquisitions happen as a response to
+%% systematic resource orchestration (ref), i.e. reshaping the resource mix to obtain
+%% coordinated resource deployments \citep{Kor2005,Pan2006}, they would indeed have potential
+%% performance implications for the firm. Moreover, when this process of resource acquisition
+%% process of DC develops a way to acquire and mix resource for the purpose of adapting to
+%% change, the resources themselves would not necessarily satisfy the VRIO condition. The way
+%% in which this happens may be much harder to imitate due to the complexities such routines
+%% exhibit. Although resources themselves exhibit clear equifinality in their impact on
+%% competitive advantage, combined with the simple routines of the orchestration
+%% (i.e. dynamic capabilities), the sum would likely satisfy the VRIO condition. This is
+%% especially true if routines are deployed rapidly in changing market conditions. In other
+%% words, there are several ways in which resources can be orchestrated to generate CA,
+%% whereas improved OR will always mean improved competitiveness et ceteris paribus. In such
+%% instances DC itself can lead to CA directly.
+
+%% \emph{H3: Dynamic capabilities has a direct effect on competitive advantage through the
+%%   process of resource orchestration and acquisition of resources in factor markets.}
+
+%% In other words, we would expect DC to have both a direct and an indirect impact on CA. The
+%% indirect impact stems from the \emph{evolutionary path} of complex processes, whereas the
+%% direct impact stems from the \emph{market path}.  Although both the direct and the
+%% indirect path stems from DC creating, extending and modifying the resource base (OR or
+%% factor market resources), the difference in the path’s stems from to what extent the
+%% mediating construct alone can by itself satisfy the VRIO condition. Operating routines
+%% can, due to their evolutionary nature, in turn shaped by DC, achieve CA
+%% \citep{Collis1994,Winter2003}. Factor market resources and market acquired capabilities
+%% and best practices can not \citep{Eisenhardt2000,Peteraf2013}, but in conjuncture with the
+%% routines of acting in factor markets as well as the speed of deployment, the sum of
+%% dynamic capabilities and factor market action would lead to competitive advantage.
+
+%% However, the interlinkages between simple routines (the market path) and the coplex
+%% processes (the evolutionary path) would vary with the environment.
+
+%% \subsection{Interplay under environmental dynamism}
+
+%% \cite{DiStefano2014} note that "even if specific simple rules are unstable and ephemeral,
+%% the system as a whole is not" and that the "real source of sustainable competitive ad- vantage for an enterprise is the difficulty of imitating and substituting for the entire dynamic bundle that the system represents" (p.sss).
+
+%% But the interlinkages between the parts of the system (the evolutionary- and the market
+%% path), are likely to vary with the environmental dynamism. Under moderatly dynamism
+%% dynamic capabilities takes the form of best pracitces (e.g. aquisition targeting) and is
+%% less important than under more dynamic environments. However, albeit best practices, the
+%% way they are implemented in the factor markets are still idiosyncratic. And taken into
+%% conjunction with the routinzed process of changing underlying routines, VRIO will very
+%% likely emerge under more stable conditions. It is not that the market/direct expression
+%% of dynamic capabilities are not present in stable environments, rather it is less pronounced and the indirect
+%% mediated effect (evolutionary path) is more important. In other words, it is not neither
+%% nor, but degrees of importance.
+
+%% Moreover, in high velocity environments the role of the evolutionary path tends to
+%% weaken as such path-dependent changes occur slower compared to the market path. From the
+%% market path with its simple routines we can argue that creation of "new knowledge” to
+%% “allow for emergent adaptation” (EM, p. 1116) is the consequence. Consequently, the market
+%% path is stronger and more prevalent under higher levels of environmental dynamism.
+
+%% \emph{H4: Dynamic capabilities works relatively stronger through the market path in highly
+%% dynamic environments.}
 
@@
 
-  \providecommand{\huxb}[2]{\arrayrulecolor[RGB]{#1}\global\arrayrulewidth=#2pt}
-  \providecommand{\huxvb}[2]{\color[RGB]{#1}\vrule width #2pt}
-  \providecommand{\huxtpad}[1]{\rule{0pt}{\baselineskip+#1}}
-  \providecommand{\huxbpad}[1]{\rule[-#1]{0pt}{#1}}
+\begin{kframe}
 
-\begin{table}[h]
-\centering
-\begin{threeparttable}
-\begin{tabularx}{0.9\textwidth}{p{0.18\textwidth} p{0.18\textwidth} p{0.18\textwidth} p{0.18\textwidth} p{0.18\textwidth}}
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \textbf{Factor}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft \textbf{Items}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft \textbf{Loading}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft \textbf{Alpha}\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft \textbf{CI}\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.7}}->{\huxb{0, 0, 0}{0.7}}->{\huxb{0, 0, 0}{0.7}}->{\huxb{0, 0, 0}{0.7}}->{\huxb{0, 0, 0}{0.7}}-}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright $CA$\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft CA^1\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.86\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.83\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.90\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft CA^2\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.88\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft CA^3\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.85\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}-}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright $CA_t$\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft CA_{t-1}^1\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.88\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.79\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.88\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft CA_{t-1}^2\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.80\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft CA_{t-1}^3\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.84\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}-}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright $DC_P$\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_P^1\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.71\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.82\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.88\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_P^2\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.83\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_P^3\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.70\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_P^4\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.77\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_P^5\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.82\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}-}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright $DC_X$\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_X^1\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.83\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.74\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.84\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_X^2\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.72\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft DC_X^3\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.85\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}-}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright $P$\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft P^1\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.71\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.70\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.84\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft P^2\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.82\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft P^3\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.85\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}-}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright $R$\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft R^1\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.91\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.94\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.96\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft R^2\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.94\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{}
-\arrayrulecolor{black}
-
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedright \huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft R^3\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft 0.96\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} &
-\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt}\raggedleft ~~~\huxbpad{6pt}} \tabularnewline[-0.5pt]
-
-\hhline{>{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}->{\huxb{0, 0, 0}{0.2}}-}
-\arrayrulecolor{black}
-\end{tabularx}\end{threeparttable}
-
-\end{table}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'ht' not found}}\end{kframe}
 
@@
 
-\section{Results}
-The focal variables of our study is presented with pairwise correlation, mean and standard
-deviation in table \ref{tab:desc}.It is worth noting that the mean value of OR and DC is
-declining over time suggesting that the average firm experience a negative development in
-core resources. The ability of the firms in our sample to generate CA is somewhat
-unchanged over the sample period. We also observe a certain correlation in the development
-in DC over time suggesting that prior period DC is a strong predictor of future
-DC. Furthermore, we see a strong correlation between DL and DC which indicates that these
-two constructs are indeed related.
-
-\begin{figure}[ht] \label{ fig7} 
-  \begin{minipage}[b]{0.5\linewidth}
-    \includegraphics[width=.99\linewidth]{full.pdf} 
-    \caption{Full model} 
-  \end{minipage} 
-  \begin{minipage}[b]{0.5\linewidth}
-    \includegraphics[width=.99\linewidth]{ma.pdf} 
-    \caption{Routine mediation} 
-  \end{minipage} 
-  \begin{minipage}[b]{0.5\linewidth}
-    \includegraphics[width=.99\linewidth]{or.pdf} 
-    \caption{Process mediation} 
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.5\linewidth}
-    \includegraphics[width=.99\linewidth]{dir.pdf} 
-    \caption{Direct model} 
-  \end{minipage} 
-\end{figure}
-
-\begin{figure}
-     \centering
-  \caption{Structural model of full estimation - PLS-SEM}
-  \input{./figure/fullmod.tex}
-\end{figure}
-
-\begin{table}
-\begin{center}
-\script size
-\begin{tabular}{lcccc}
-
-\hline \\[-2pt]
- & \multicolumn{4}{c}{{\bf Models:}} \\  \cline{2-5} \\[-3pt] 
- & \emph{Direct} & \emph{Process} & \emph{Routines} & \emph{Full}\\
- & (1) & (2) & (3) & (4)\\
-\hline
- &  &  &  & \\
-\(CA_{t-1} \rightarrow CA\) & 0.364 & 0.361 & 0.351 & 0.343\\
- & (7.19) & (6.49) & (6.33) & (6.27)\\[3pt]
- &  &  &  & \\
-\(DC_P \rightarrow CA\) & 0.378 & 0.342 & 0.314 & 0.299\\
- & (5.23) & (4.48) & (4.08) & (3.82)\\[4pt]
-\(DC_X \rightarrow CA\) & -0.005 & -0.045 & 0.002 & -0.066\\
- & (-0.07) & (-0.59) & (0.04) & (-0.98)\\[4pt]
- &  &  &  & \\
-\(DC_P \rightarrow P\) &  & 0.146 &  & 0.129\\
- &  & (1.93) &  & (1.7)\\[4pt]
-\(DC_P \rightarrow R\) &  &  & 0.502 & 0.496\\
- &  &  & (6.23) & (6.13)\\[4pt]
-\(DC_X \rightarrow P\) &  & 0.3 &  & 0.343\\
- &  & (3.63) &  & (4.79)\\[4pt]
-\(DC_X \rightarrow R\) &  &  & -0.099 & -0.091\\
- &  &  & (-1.28) & (-1.14)\\[4pt]
- &  &  &  & \\
-\(P \rightarrow CA\) &  & 0.182 &  & 0.185\\
- &  & (2.53) &  & (3.14)\\[4pt]
-\(R \rightarrow CA\) &  &  & 0.137 & 0.123\\
- &  &  & (2.3) & (2.15)\\[4pt]
- &  &  &  & \\
-\hline \\[-3pt] 
-Goodness of fit & 0.45 & 0.4 & 0.43 & 0.41\\
-Number of observations & 260 & 260 & 260 & 260\\
-  Firm level controls & YES & YES & YES & YES\\[3pt]
-\hline
- &  &  &  & \\
-\end{tabular}
-\end{center}
- \label{tab:reg}
-\end{table}
-
-Table \ref{tab:reg} shows a summary of the regression models proposed in the previous
-chapter. Models 1,2 and 3 are designed to test DL as \emph{antecedent} for $OR$ and
-$DC$. Consider model 1 we observe that $DL$ is influencing the level of $OR$ within the
-firm ($\beta_2 =$r) supporting H1. However, the effect disappears when we
-add $DC$ in model 2 suggesting a mediating effect. In other words we see that firms with
-initial high $DC$($\beta_3=$ \ {mod2_dc0}) and increasing $DC$ over time ($\beta_4=$
-\ {mod2_ddc}) also have better $OR$. To control for the mediating effect suggested by
-the change in coefficients for $DL$ between models 1 and 2, we performed a causal
-mediation analysis as reported in figure \ref{fig:fig3}. This analysis confirms the
-indications from models 1 and 2 showing that the direct effect from $DL$ on $OR$ is
-insignificant and small (ADE = \ {medmod1_ade}). Meanwhile, the indirect effect
-running through changes in $DC$ over time, is significant yielding a positive and
-significant indirect effect of \ {medmod1_acme}. The proportion of the effect that is
-mediated amounts to \ {medmod1_shmed}. In sum these results suggest that H1 is
-unsupported, and that the bulk of the effect is indirect running through $DC$, in line with
-the expectations in H3. Similarly, we see from model 3 that $DC$ is indeed influenced by $DL$
-above and beyond its own evolutionary trajectory. This is in line with our expectations
-and lend support to H4.
-
-To evaluate H5 proposing a feedback effect from $DC$ to $DL$, we turn to model 6 in table
-\ref{tab:reg}. Controlled for the usual firm level controls we find a positive effect
-($\xi_1=$ \ {mod6_dc0}) from $DC_{T_1}$ on $DL$ measured at $T_1$. This supports H5
-suggesting that firms with more $DC$ is more likely to generate opportunities where it
-becomes more prevalent that learning will need to take place. One interesting finding is
-also that this effect environmental dynamism decreases firms level of $DL$. This is indeed
-puzzling and we will look in to this in a post-hoc analysis.\todo{When adding interactions
-  we see that high environmental dynamism in conjunction with DC is positive for DL
-  meaning that DC will indeed work to make firms more aware of the benefits of DL when
-  environments are changing} It is also worth noting that models 1,2 and 3 have positive
-and significant $\rho$ from the Heckman selection model indicating that selection is
-leading to biased estimates. By running a Heckman correction we avoid this potential
-problem.
-
-Models 4 and 5 in table \ref{tab:reg} deals with the \emph{outcome} of DC. H6a and H6b
-both considers effects of $DC$ on the competitive advantage of the firm $CA$. $CA$ is
-influenced by the level of $DC$ of the firm indicating that dynamic capabilities are a
-source of competitive advantage in line with our expectations. Furthermore, considering
-model 5 we see that $OR$ also has a significant positive effect on $CA$ indicating that
-operating routines can also be a source of advantage for the firm. Moreover, the
-coefficient of $\Delta DC$ decline from  {mod4_ddc} to  {mod5_ddc} when we add
-$OR$. This suggests that some mediation is at work, i.e. that changes in $DC$ leads to
-changes in changes in $OR$ leading to $CA$. This indirect path is in line with the
-expectations from our hypotheses and as described in figure \ref{fig:fig2}. When formally
-testing this mediation running a causal mediation analysis (see figure \ref{fig:fig4}), we
-find added support that both a \emph{direct-} and an \emph{indirect} path exist to explain
-the relationship between $DC$ and $CA$ (ADE = \ {medmod5_ade}, ACME =
-\ {medmod5_acme}) and a total mediated share of \ {medmod5_shmed}.
-
-Table \ref{tab:hyptab} depict a summary of the hypotheses and indicate if they are
-supported or not in our analysis. We will now turn to the discussion.
-
-\section{Discussion}
-
-Moving from antecedents to outcomes we extended the \cite{Zollo2002a} model by adding
-competitive advantage to the model. We find that both operational capabilities and dynamic
-capabilities can lead to competitive advantage. The most obvious path from the mere
-definition of dynamic capabilities, runs through the evolution of operational
-capabilities. Dynamic capabilities shape operational capabilities and changes them to
-adapt, hence safeguarding that they are adapted. This is beyond the ad-hoc learning and
-adaptation taking place as repetitive actions by employees. TO BE CONTINUED
-
-\subsection{Limitations}
-
 \section{Bibliography}

### 2019-10-21 article4_analysis.r

@@ -128,22 +128,6 @@ complist <- list(DC_P=dc01,DC_X=dc02,CA_t=ca0,CA=ca1,P=or1,R=ma01)
 vcontrols <- zwadj[,c("size","age","dyn","pm","lassets")]
 zwadj <- cbind(dc01,dc02,dc00,ca0,ca1,or1,or0,ma01,m0,m1,vcontrols)
 
-#### Testing constructs
-
-
-m0 <- zwadj[,c("Q18a","Q18b","Q18d")]
-m1 <- zwadj[,c("Q4.7_t1","Q4.8_t1","Q4.9_t1")]
-
-
-
-m0c <- na.omit(m0)
-m1c <- na.omit(m1)
-
-pdc1est <- princomp(m0c)
-pdc1est$loadings
-
-pdc1est <- princomp(m1c)
-pdc1est$loadings
 
 ######## ADJUSTING DATASET WITH DELTA
 
@@ -156,113 +140,40 @@ zwadj$m2 <- zwadj$Q4.2_t1 - zwadj$Q16b
 zwadj$m3 <- zwadj$Q4.4_t1 - zwadj$Q17a
 zwadj$m4 <- zwadj$Q4.5_t1 - zwadj$Q17b
 
-## zwadj$d1 <- zwadj$Q6.1_t1 - zwadj$Q19
-## zwadj$d2 <- zwadj$Q6.2_t1 - zwadj$Q19a
-## zwadj$d3 <- zwadj$Q6.3_t1 - zwadj$Q19b
-## zwadj$d4 <- zwadj$Q6.4_t1 - zwadj$Q19c
-## zwadj$d5 <- zwadj$Q6.5_t1 - zwadj$Q19d
-## zwadj$d6 <- zwadj$Q6.6_t1 - zwadj$Q19e
-## zwadj$d7 <- zwadj$Q6.7_t1 - zwadj$Q20
-## zwadj$d8 <- zwadj$Q7.1_t1 - zwadj$Q20b
-## zwadj$d9 <- zwadj$Q7.2_t1 - zwadj$Q20c
-## zwadj$d10 <- zwadj$Q7.3_t1 - zwadj$Q20d
-## zwadj$d11 <- zwadj$Q7.4_t1 -zwadj$Q20e
-
-
- ## zwadj$d4 <- zwadj$Q5.1_t1 - zwadj$Q22
[…]

### 2019-10-21 article4_analysis_v2.r

@@ -106,27 +106,32 @@ rownames(zwadj) <- NULL
 
 
 setwd("/Users/larshovdanmolden/Documents/git/article4")
-
+alldc <- zwadj[,c("Q19a", "Q19c", "Q19d", "Q20b", "Q20c","Q19", "Q20d","Q20e","Q19b","Q20")]
 
 ## Running median imputations
 dc01 <-  imputezw(zwadj[,c("Q6.2_t1","Q6.4_t1", "Q6.5_t1","Q7.1_t1","Q7.2_t1")] )
 dc02 <-  imputezw(zwadj[,c("Q6.1_t1","Q7.3_t1","Q7.4_t1")] )
-dc00 <-  imputezw(zwadj[,c("Q19", "Q20d","Q20e")] )
+dc001 <- imputezw(zwadj[,c("Q19a", "Q19c", "Q19d", "Q20b", "Q20c")] )
+dc002 <-  imputezw(zwadj[,c("Q19", "Q20d","Q20e")] )
+dc002 <-  imputezw(zwadj[,c("Q19c", "Q20b", "Q20c")])
 ca0 <-  imputezw(zwadj[,c("Q28","Q28a","Q28c")] )
 ca1 <-   imputezw(zwadj[,c("Q16.1_t1","Q16.2_t1","Q16.4_t1")] )
 or1 <-   imputezw(zwadj[,c("Q5.4_t1","Q5.6_t1","Q5.7_t1","Q5.1_t1","Q5.2_t1","Q5.3_t1","Q5.5_t1")])
 or0 <-   imputezw(zwadj[,c("Q21c","Q21d","Q21e","Q22","Q22a","Q22b","Q22c")])
+or1 <-   imputezw(zwadj[,c("Q5.4_t1","Q5.6_t1","Q5.7_t1")])
+or0 <-   imputezw(zwadj[,c("Q21c","Q21d","Q21e")])
 ma01 <-  imputezw(zwadj[,c( "Q8.7_t1", "Q8.8_t1", "Q8.9_t1")])
 ma02 <-  imputezw(zwadj[,c("Q24","Q24a","Q24b","Q24c","Q24d")])
 m0 <- imputezw(zwadj[,c("Q16a","Q16b","Q17a","Q17b")])
 m1 <- imputezw(zwadj[,c("Q4.1_t1","Q4.2_t1","Q4.4_t1","Q4.5_t1")])
[…]

### 2019-10-21 estimation/article_functions.r

@@ -96,3 +96,35 @@ meplot <- function(model,var1,var2,ci=.95,
 
   if(rnum){return(dy.dx)}
 }
+
+
+## Imputation function
+imputezw <- function(vec){
+    meanVec <- rowMeans(vec, na.rm=TRUE) #coud be rowMeans
+    for (i in 1:nrow(vec)){
+        for (j in 1:ncol(vec)){
+            if(is.na(vec[i,j])){vec[i,j] <- meanVec[i]}
+        }
+    }
+    return(vec)
+}
+
+
+
+extboot <- function(bootobj,n,nam,r){ #remembaer space between Letter and " ("P ")
+    ##this function extracts estimates and standard errors for a bootstrapped object from PLS Sem
+
+    c1 <- attr(bootobj$t,"path")
+    c2 <- bootobj$t0
+    c3 <- c(apply(bootobj$t,2,sd))
+    res <- data.frame(c1,c2,c3);colnames(res) <- c("name",paste(nam,"est",sep="_"),paste(nam,"se",sep="_"))
+    res <- res[(nrow(res)-n):nrow(res),];  rownames(res) <- NULL
+    toMatch <- c(r, "DC")
+    res <- res[(grep(paste(toMatch,collapse="|"),res$name)),]
+    res$t <- res[,2] / res[,3]
+    res <- res[,c(1,2,4)]
+    res[,2:3] <- round(res[,2:3],3)
+
+
+    return(res)
+}

### 2019-10-25 article4_jbr.rnw
first chapter of paper 4 on non behavior

--- 2019-10-21 article4_tommylars.rnw
@@
-%https://www.gnu.org/software/emacs/manual/html_node/emacs/Fill-Commands.html
+% https://www.gnu.org/software/emacs/manual/html_node/emacs/Fill-Commands.html
 %https://academic.oup.com/journals/pages/authors/latex_files
@@
 %https://journals.sagepub.com/doi/abs/10.1177/0971890717701781
+
+Extant literature on dynamic capabilities are increasingly focusing on how firm resources
+are changed by dynamic capabilities as a response to changes in the environment
+\citep{Schilke2018,Eriksson2014}, thus placing firm resources as a mediator between
+dynamic capabilities and competetive advantage \citep{Helfat2007}. Less focus has been
+placed on the nature of these underlying firm resources (ref) and how they are capturing a
+rather heterogeneous bulk of routines, capabilities, assets and capital. Hence, there is a
+need to disentangle the black box of firm resources to provide a more nuanced
+understanding of different types of firm resources and how they interact to shape firm
+competitive advantage \cite{Schilke2018}. Indeed, this gap in the literature is explicitly
+called by \cite{Schilke2018} where they  'see an interesting opportunity for future work to add greater richness to our
+understanding of the mechanism of resource-base change, given this mechanism’s central
+role in many foundational works (..) and the diverse ways in which resource changes can
+potentially come about' (p. 419).
+
+We aim to contribute to bridging this gap by
+
+The inclusion of theoretical linkages of this sort appears to be important at this time
+not only because they are at least partially overlooked in our current understanding of
+capa- bility dynamics.
+
+we propose a model that can accommodate the diverse nature of DCs with respect to the
+objects of change that they aim to act upon and can better serve the call for a better
+understanding of micro-foundations of strategy.
+
+DCs required to adapt the more tacit and subtle aspect of human interactions (motivation,
+emotions, and identity, in partic- ular) to environmental or contextual requirements
+
+A dynamic capability is the capacity of an organization to purposefully create, extend or
+modify its resource base. The resource base of an organization includes tangible,
+intangible and human assets (or resources) as well as capabilities which the organization
+owns, controls or has access to on a preferential basis.  (Helfat
 

### 2019-10-26 article4_jbr.rnw
draft intro finished

--- 2019-10-21 article4_tommylars.rnw
@@
 
-The presence of a direct path from dynamic capabilities and competetive advantage is
-somewhat puzzling. It eiter suggests ommited importrant mediating factors such as
-resources, or that dynamic capabilities can act outside "creating, extending and modifying
-the firm resources base". A growing consensus on the definition as well as the
-theoretical mechanisms underpinning dynamic capabilities suggest that dc work indirectly
-towards strategic change by changing firm resources. Hence, the presence of direct effects
-seems increasingly odd. Still, seminal contributions to the field of dynamic capabilities have argued for both direct
-\cite{Kor2005,Eriksson2014,Schilke2014a} and indirect (ref) effects of dynamic
-capabilities on competitive advantage, although increasingly the bulk of the literature
-focuses on the latter \citep{Schilke2018}.
+Extant literature on dynamic capabilities are increasingly focusing on how firm resources
+are changed by dynamic capabilities as a response to changes in the environment
+\citep{Schilke2018,Eriksson2014}, thus placing firm resources as a mediator between
+dynamic capabilities and competetive advantage \citep{Helfat2007}. Less focus has been
+placed on the nature of these underlying firm resources (ref) and how they are capturing a
+rather heterogeneous bulk of routines, capabilities, assets and capital. Hence, there is a
+need to disentangle the black box of firm resources to provide a more nuanced
+understanding of different types of firm resources and how they interact to shape firm
+competitive advantage \cite{Schilke2018}. Indeed, this gap in the literature is explicitly
+emphasized by \cite{Schilke2018} where they 'see an interesting opportunity for future
+work to add greater richness to our understanding of the mechanism of resource-base
+change, given this mechanism’s central role in many foundational works (..) and the
+diverse ways in which resource changes can potentially come about' (p. 419).
 
- Resource orchestration is defined as "blablbalbla" (helfat)
+The conventional mechanism explored in the extant literature is related to changes in the
+firm`s resource base \citep{Eriksson2014,Schilke2018}. This mechanism is also included in
+the dominating definition of dynamic capabilities found in \citep{Helfat2007}: 'A dynamic
+capability is the capacity of an organization to purposefully create, extend or modify its
+resource base' (p. 4). And although this definition opens up for a variety of components
+included in the term 'resource base', a point we discuss later in this paper, most of the
+subsequent contributions have focused on changes in operational routines (ref),
+capabilities (ref), practices (ref) or tangible assets (ref). This focus, albeit very
+important to the development of dynamic capabilities literature, seems to leave out a
+considerable part of a firm`s 'resource base', namely those resources that are tied to how
+the employees of the firm sees their mission, internalize information and effectuates
+change. These traits of the organization is very much related to concepts of
+'organizational culture' (ref), 'employee cognition' (ref)' 'organizational genes'
+\citep{Nelson1982} and 'sense-making' \citep{Weick1995} to name but a few. However, in
+relations with dynamic capabilities one promising avenue for exploring mechanisms beyond
+the conventional ones described above, makes a clear distinction between \emph{behavioral}
+and \emph{non-behavioral} objects of change \citep{Verona2003}. These non-behavioral
+objects of change contain psychological objects such as cognitive frames, motivation and
+identity that are important for strategy formation and implementation (Gavetti etc, vince
+and gabriel ch 15 of book by verona) as they 'concerns how decisions or actions are
+shaped, subverted and transformed by emotions, and (..) determine the "way we do things
+here"' (Vince and gabriel). In this respect they work as firm resources in generating
+outcomes such as performance and competitive advantage. This notion is perhaps expressed
+most clearly by Peter Drucker`s famous quote about how 'culture eats strategy for lunch'
+(ref) insofar as . Moreover, these non-behavioral objects of change are themselves far
+from static and are found to change over time as responses to external change
+\citep{Zollo2016} thus making them a natural part of the mechanisms underpinning how
+dynamic capabilities work \citep{Schilke2018,Verona2003}. Still, far less is know about
+the non-behavioral objects of change and how they work as a mechanism in the dynamic
+capabilities theory.
 
-This indirect link is typically understood as dynamic capabilities modifying, extending or
-creating firm resources (helfat) (or lower-level operational capabilities (Winter,
-collis)) and thus generating competitive advantage (Eriksson and others).The direct path,
-however, is theoretically less explicitly dealt with in the extant literature although
-empirical evidence keep suggesting that both direct (ref) and indirect (ref) links exist.
+We aim to contribute to bridging this gap by theorize about how non-behavioral objects of
+change work as a mechanism through which dynamic capabilities influence competitive
+advantage. Specifically, we ask the following research question:
 
-In this paper we explore to what extent a direct link between dynamic capabilities and
-competitive advantage work, and under which conditions it is most pronounced. Specifically
-the research question is:
+{\bf What is the role of non-behavioral objects of change as a mechanism through which
+  dynamic capabilities can influence competitive advantage?}
 
-{\bf How is a direct link between dynamic capabilities and competitive advantage working
-  and under which conditions does it come into play or not?}
+To shed light on this important question we theorize on the role of a particular type of
+non-behavioral object of change, \emph{organizational cognition}, and how it acts as a
+mediator between dynamic capabilities and firm competitive advantage and hence has a
+pivotal place in the literature. We build on important work on the concept of
+organizational cognition (ref), non-behavioral object of change (ref) and blablabla (ref),
+and hypothesize about how organizational cognition acts as a mediator in the same way as
+conventional behavioral objects of change (such as routines and capabilities) and that
+these two are complementary to a certain degree. Moreover, we also suggest how
+organizational cognition could also influence routines and capabilites directly with
+further implications for competitive advantage.
 
-We argue that direct link exist as a response to the multilevel notion of strategy itself
-and captures strategic change not typically associated with the resource based
-view. Furthermore, we show that the prevalence of the direct link is a function of the
-nature of underlying resources dynamic capabilities are aimed at "creating, extending and
-modifying", specifically if they are valuable and idiosyncratic to the firm or not, and
-the environment facing the firm.
+This paper makes the following contributions:
 
-Our findings indicate that the direct path is less prevalent in very dynamic environments
-where the indirect path becomes far more important. Furthermore, the effect of dynamism is
-partly contingent on the nature of the firm resources suggesting a more complex
-understanding of how imitable and simple resources can play a role in generating
-competetive advantage.
-
-Our contributions are twofold. First, we explore different mediators by explicitly
-modeling a causal chain with different types of underlying resources, as well as
-under different environments. This is explicitly called for in the literature as "only
-four percent of the articles in our sample explicitly examined possible causal mechanisms,
-suggesting a significant gap in the literature" (Schilke 2018). This work sheds light on
-the contingencies and boundary conditions of the link between dynamic capabilities and the
-"holy grail of strategy" (Schilke et al), competetive advantage.
-
-Second, we explore a theoretical explanation for why a direct link between dynamic
-capabiliites and competetive advantage may exist. By leaning on empirical evidence
-suggesting a multitude of explanations for performance differentials between firms, we
-suggest that dyanmic capabilities can act outside the theorized path of "resource
-orchestration" through strateic efforts such as industry positioning (porter) or
-institutional leverage (Peng).
-
-%%%%%%%%%%%%%%5
-
-%%%%%%%%%%%%%%
-
-%% This warrant the question of \emph{when}
-%% direct and indirect links between dynamic capabilities and competitive advantage is most
-%% pronounced.
-
-%% Moreover, firm resources or capabiltiies themselves are far from a homogenous set and
-%% varies among other things with respect to their uniqueness, inimatbility and value
-%% (barney). Important contributions have thus argued for a deeper insighi into these
-%% intermediaries and their mechanism calling for a "deeper insight into the variety of mechanisms that
-%% underlie the performance effects of capabilities.” (Schilke, 2014a: 199). 
-%% as well as \emph{what} different intermediaries exist.
-
-%% This paper investigates the boundary conditions of the VRIO condition and how dynamic
-%% capabilities and resources interact to create firm competitive advantage. We ask the
-%% following research question:
-%% Under which conditions are dynamic capabilities able to yield competietive advantage
-%% through resource orchestration and what are the different outcomes of different types of resources.
-
-%% We find thatthe dynamism surrounding hte firm represent an important boundary condition as
-%% suggested in parts of the literature. However, DC consinutes to generate competetive
-%% advnatage also in high-velocity environments, but doing increasingly so indirectly through
-%% resource orchestration. Furthermore, we find that non-vrio resources are more likely to
-%% yield competetive power in high velocity environments, and that vrio-resources tend to
-%% maintain their CA under any condition.
-
-%% We demonstrate that two paths indeed do exist and that their relative importance varies
-%% with the degree of environmental dynamism facing the firm.
-
-%% Under what cionditions are the direct path and indirect path most prevalant? Under which condi
-
-%% The direct
+The rest of this paper is organized as follows:
 

### 2019-10-31 article4_jbr.rnw
developed two stage srgument expl exploit

@@
 \begin{abstract}
- We find that DC as routines to shape routines is most prevelant under moderate dynamism,
-whereas DC as routines to capture resources in factor markets are more prevelant under
-dynamic environments.
+TBD
 
@@
 the conventional ones described above, makes a clear distinction between \emph{behavioral}
-and \emph{non-behavioral} objects of change \citep{Verona2003}. These non-behavioral
+and \emph{non-behavioral} objects of change \citep{Verona2011}. These non-behavioral
 objects of change contain psychological objects such as cognitive frames, motivation and
@@
 \citep{Zollo2016} thus making them a natural part of the mechanisms underpinning how
-dynamic capabilities work \citep{Schilke2018,Verona2003}. Still, far less is know about
+dynamic capabilities work \citep{Schilke2018,Verona2011}. Still, far less is know about
 the non-behavioral objects of change and how they work as a mechanism in the dynamic
@@
 \section{Hypotheses}\label{sec:hyp}
+
+DC as resource orchestration - influencing capabilities
+DC as cognitive programmer - inluencing cognitive frames
+
+When Satya Nadella took over as CEO of Microsoft in March 2014, he took over a company in
+big trouble. The share price was just north of 30 USD and the company had just launched a
+7.2 billion USD acquisition of the failing Nokia company. The story about how Nadella
+turned Microsoft around to a valuation of 105 USD pr share and with successful mergers
+along the way is a story of excellent 'resource orchestration' as a response to exercising
+dynamic capabilites, specifically through sensing, seizing and transforming resources to
+adapt to changing market conditions \citep{Teece2007}. Nadella and his firm did a
+considerable reorientation towards the cloud and reconfigured firm capabilities to fit
+this objective - almost a school example of exercising dynamic capabilities.
+
+Moreover, and to the point of this paper, through a series of talks, interviews and his
+own book Nadella put considerable emphasis on how Microsoft managed to change their
+'mindset', that is their 'cognitive frames' (Nadella 2017): 'I focused on what would be
+our grandest endeavor, the biggest hurdle - transforming the Microsoft culture'
+(p. 89). Drawing on the concept of a 'growth mindset' \citep{Dweck2016} Nadella sees
+culture as a 'complex system of individual mindsets' and that it encompasses how 'an
+organization thinks and act' (ibid p.90).
+
+Satya Nadella is very much on the same page as recent contributions on how cognitive
+frames of an organization (i.e. its non-behavioral object of action) is a pivotal part in
+how firm resources shape outcomes such as performance and competitive advantage
+\citep{Barney1991a,Barney2001}, and how it consequently plays a role in how dynamic
+capabilities work along these lines \cite{Verona2011}. Microsoft under Nadella did
+transform the company by changing the behavioral objects of action (i.e. capabilities and
+routines), but also through changing the non-behavioral objects of action (i.e. the
+cognitive frames). In other words, the story of Microsoft`s transformation suggest that
+dynamic capabilities worked through mediating factors to influence competetive advantage,
+but that thes mediating factors exist as two distinctly different concepts working in
+tandem. Figure \ref{fig:fig1} presents a conceptual depiction of the paths running through
+these two concepts of \emph{behavioral} and \emph{cognitive} objects of action
+\citep{Zollo2016}. We use a familiar term for the conventional understanding of dynamic
+capabilities mechanism as 'resource orchestration' (ref) as a collective term to describe
+the behavioral objects of action (ref). This idea of orchestrating resources are
+particularly illuminating in that it sets an organization`s dynamic capabilities as a
+director conducting new outcomes by orchestrating the use of firm resources, and it is in
+line with a range of the most common definitions of dynamic capabilities
+\citep{Schilke2018}. The non-behavioral objects of action has no similar agreed upon
+analogy, so for the purpose of our analysis we envision this mechanism to work more as a
+cognitive process enabling the organization to tear away from their current understanding
+and ways in which things are done (Vince and Gabriel). Whereas the analogy of resource
+orchestration has its counterpart in the making of art (i.e. music, movies or theatrical
+plays), the non-behavioral objects of action are more aligned to psychology and cognitive
+therapy. The process is all about changing an organization`s thinking from the automated
+and well-known, to the more cognitively aware, what Kahneman and Tversky coins 'system two'
+thinking (ref). This change of cognitive frames will thus be more similar to a
+reprogramming effort and we henceforth refer to the process of changing the non-behavioral
+objects of action (e.g. cognitive frames, culture, etc) as 'cognitive programming'.
+
+\begin{figure}
+  \centering
+  \captionsetup{width=0.5\linewidth}
+  \input{./figure/fullmod.tex}
+  \captionof{figure}{The resource and cognitive mechanisms of dynamic capability}
+  \label{fig:fig1}
+\end{figure}
+
+RESOURCE ORCH is HITT2011 among other
+\subsection{Cognitive programming}
+Juxtaposed to the experiences from Microsoft, the case of Polaroid brings another set of
+experiences to our discussion on non-behavioral objects of action (see \citep{Tripsas2000}
+for a detailed account). Cognitive inertia on the part of the organization, not the top
+management, \todo{Check this - maybe remove the sentence on top management} played a
+pivotal part in the failing of the company`s digital imaging effort
+\citep{Verona2011}. Similar patterns are found in Kodak and Anderson Consulting (ref
+Hederson and Kaplan 2005), and Smith Corona (Danneels 2010). These examples highlight the
+absence of 'dynamic capabilities specific to the adaptation of cognitive frames, first,
+and consequently of operating processes' \citep[p. 541]{Verona2011}.
+
+Looking at dynamic capabilities through the functions of sensing, seizing and
+transformation \cite{Teece2007} makes an obvious case for resource orchestration which is also highlighted
+in the extant literature. Moreover, as discussed above, these functions are also requiring
+a certain non-behavioral object of action in order to be fully efficient. To achieve a
+competitive edge firms will have to be able to sense and seize, which require a certain
+organizational cognitive frame to be efficient. 'Dynamic capabilities are about doing the
+right things, at the right time, based on new product (and process) development, unique
+managerial orchestration processes, a strong and {\bf change-oriented organizational culture}'
+(our emphasis) \cite[p]{Teece2014}.
+
+To see how dynamic capabilities acts through cognitive objects of action (i.e. as a
+cognitive programmer) we consider two distinctly different functions of dynamic
+capabilities related to their microfoundations \citep{Teece2007}. the first function is
+related to the discovering and capturing opportunities (e.g. the ability of the
+organization to sense and seize opportunities (ibid)) which is very much related to the
+concept of exploration \citep{March1991}. Organizations with high levels of dynamic
+capabilities geared towards sensing and seizing opportunities are doing so through
+\emph{resource orchestration}, e.g. by creating, extending and modifying the resource
+base, as discussed extensively in the extant literature
+\citep{Helfat2007,DiStefano2014,Protogerou2012,Schilke2018}. However, sensing and seizing
+opportunities in the market relates to discovering market disequilibrium
+\citep{Kirzner1997} as well as upsetting existing equilibria \citep{Schumpeter1934}. The
+process of sensing and seizing 'involves understanding latent demand, the structural evolution of
+industries and markets, and likely supplier and competitor responses'
+\citep[p. 1322]{Teece2007} as well as . Individuals are the unit of analysis embedding these abilities
+and if left up to these individuals without a higher organizing framework, the firm will
+be very vulnerable because of knowledge asymmetries and incentive problems (alchian and
+demsetz 1972) and lead to sub optimal rent-appropriation on the part of the individual
+employee \citep{Blyler2003}. A similar argument applies to the function of \emph{seizing}
+where the organization is set to mobilize resources for the purpose of gaining from these
+opportunities. In order for value to be captured from opportunities, a string of
+conditions have to be met \citep{Teece2017}, but the evolution of a 'strong and
+change-oriented organizational culture' \citep[p. 331]{Teece2014} is of pivotal
+importance. Alas the sensing process requires new knowledge from a wide range of sources
+in the organization a lot of this knowledge is tacit and can lead to rent-appropriation
+from information asymmetries \citep{Blyler2003} if not sufficiently aligned with the
+cognitive frames of the organization.
+
+One consequence is a ‘program persistence bias.’ Its corollary is various forms of
+‘anti-innovation bias,’ including the ‘anti- cannibalization’ basis discussed in a later
+section. Program persistence refers to the funding of pro- grams beyond what can be
+sustained on the merits,
+
+However, in this endeavour
+simply adatping resources is a necessary but not sufficient condition for obtaining the
+needed strategic change.
+
+The functions of dynamic capabilities as highlighted above is thoroughly discussed in
+extant literature (refs), but a quick recap is useful.
+
+DC geared towards creating new or reconfiguring old (exploration vs exploitation) but true
+competetiveness over time stems from ambidexterity- link to research on cultural ambidecterity
+
+The concept of sensing and seizing has analogous meaning in theoretical traditions tangent
+to DC. Notably entrepreneurship \citep{Hitt2011} and organizational theory
+\citep{March1991}. \cite{Hitt2011} states that "entrepreneurship involves identifying and
+exploiting opportunities" (ibid p 59) where identification is tied to the process of
+discovery \citep{Shane2000}. Based on the definitions of opportunity discovery as DEF HERE
+juxtaposed to the definition of sensing as "a scanning, creation, learning, and
+interpretive activity" \citet[p. 1322]{Teece2007} we argue that they are similar in nature
+and usable for exploring the importance of the latter in the innovation process. It also
+bears resemblance to the concept of organizational exploration as searching, risk-taking,
+discovery, experimentation, prototyping, and flexibility \citep{March1991}. Independent of
+the nature of opportunities to be sensed as being either objective
+\citep{Alvarez2007,Shane2000} or created \citep{Alvarez2007}, the process of sensing does
+require resources and capabilities for search (ref) and a clear affinity between
+opportunity and a project exist (casson and Wadeson in Mcmullen2007) suggesting s clear
+inter dependency between routines and resources, and higher order capabilities of sensing
+\citep{Teece2007} and making sense of the opportunity
+\citep{Weick1995,March1991}. Consequently, we would expect the sensing class of dynamic
+capabilities to be positively related to innovation on the one hand, and reinforcing the
+impact from innovation input simultaneously.\newline
+
+To see how dynamic capabilities work to adapt cognitive frames in addition to operational
+capabilities to influence competetive advantage, it is useful to turn to their
+microfoundations \citep{Teece2007}. In this framework dynamic capabilities work through
+three expressions. First, sensing seizing. more here..
+
+Each of these dimensions relates to a function of cognitive frames within the firm beyond
+the cognitive frames of the dynamic capability itself as explored by previous
+contributions in general \citep{Teece2007} and towards management specifically
+\citep{Helfat2015,Helfat2015a}. First, sensing opportunities in the market relates to
+discovering market disequilibrium \citep{Kirzner1997} as well as upsetting existing
+equilibria \citep{Schumpeter1934}. This process is very much at the core of dynamic
+capabilities as a function of management, but its function calls for a very close
+relationship with the rest of the organization both in terms of resource orchestration and
+cognitive programming. The process of sensing 'involves understanding latent demand, the
+structural evolution of industries and markets, and likely supplier and competitor
+responses' \citep[p. 1322]{Teece2007}. Individuals are the unit of analysis embedding
+these abilities and if left up to these individuals without a higher organizing
+framework, the firm will be very vulnerable because of knowledge asymmetries and incentive
+problems (alchian and demsetz 1972) and lead to sub optimal rent-appropriation on the part
+of the individual employee \citep{Blyler2003}.
+
+A similar argument applies to the function of \emph{seizing} where the organization is set
+to mobilize resources for the purpose of gaining from these opportunities. In order for
+value to be captured from opportunities, a string of conditions have to be met
+\citep{Teece2017}, but the evolution of a 'strong and change-oriented organizational
+culture' \citep[p. 331]{Teece2014} is of pivotal importance. Alas the sensing process
+requires new knowledge from a wide range of sources in the organization a lot of this
+knowledge is tacit and can lead to rent-appropriation from information asymmetries
+\citep{Blyler2003} if not sufficiently aligned with the cognitive frames of the
+organization.
+
+Finally, the \emph{transformation} function of dynamic capabilities are related to the
+idea of continuously renewal of the resource base in order to stay competitive. This continuous
+process requires the development and maintenance of a share cognitive frame such as a
+culture, which is typically found in production processes such as LEAN and Six Sigma
+(ref).
+
+Looking at dynamic capabilities through the functions of sensing, seizing and
+transformation makes an obvious case for resource orchestration which is also highlighted
+in the extant literature. Moreover, as discussed above, these functions are also requiring
+a certain non-behavioral object of action in order to be fully efficient. To achieve a
+competitive edge firms will have to be able to sense and seize, which require a certain
+organizational cognitive frame to be efficient. 'Dynamic capabilities are about doing the
+right things, at the right time, based on new product (and process) development, unique
+managerial orchestration processes, a strong and change-oriented organizational culture'
+\cite[p]{Teece2014}.
+
+It is argued that contextual ambidexterity is grounded in the type of organizational culture (Ghoshal and Bartlett 1994; Gibson and Birkinshaw 2004; Simsek et al.
+2009) that promotes both creativity and discipline (Jelinek and Schoonhoven 1993), or both the presence of different knowledge and the integration of multiple perspectives to develop a cohesive point of view (Eisenhardt and Schoonhoven 1990).
+
+ambidextrous organizational culture wang rafiq 2014
+
+The enterprise will be vulner- able if the sensing, creative, and learning functions are left to the cognitive traits of a few individuals
+
+Three types of managerial activities can make a capability dynamic: sensing (which means
+identifying and assessing opportunities outside your company), seizing (mobilizing your
+resources to capture value from those opportunities), and transforming (continuous
+renewal).
+
+Whereas ordinary capabilities are about doing
+things right, dynamic capabilities are about doing the right things, at the right time, based on new product (and process) development, unique mana- gerial orchestration processes, a strong and change- oriented organizational culture, and a prescient assessment of the business environment and tech- nological opportunities.
+teece 2014
+
+The strength of a firm's dynamic capabilities determines the speed and degree (and
+associated cost) of aligning the firm's resources—including its business model(s)—with
+customer needs and aspirations. To achieve this, organizations must be able to
+continuously sense and seize opportunities, and to periodically transform aspects of the
+organization and culture so as to be able to proactively reposition to address yet newer
+threats and opportunities as they arise. Terse 2018
+
+Dynamic capabilities are hard for rivals to replicate because they are built on the
+idiosyncratic characteristics of entrepreneurial managers and the history-honed routines
+and culture of the organization (Teece, 2014a). In addition, there is the uncertain
+imitability of a complex system that even those directly involved may not fully understand
+(Lippman and Rumelt, 1982). Because they are a unique and valuable general-purpose
+resource, strong dynamic capabilities can serve as a firm foundation for sustainable
+competitive advantage. This is especially true the more deeply embedded the capabilities
+are in the organization, and the less they are resident only in the top management
+team. Teece 2018
+
+ Managers must articulate a vision and establish an appropriate organizational culture and an incentive system that will promote organizational identification and loyalty (Augier and Teece, 2009).
+
+Put differ- ently, selecting the right ‘architecture’ for a busi- ness requires not just understanding the choices available; it also requires assembling the evidence needed to validate conjectures and hunches about costs, customers, competitors, complementors, dis- tributors, and suppliers.
+Designing
+
+Distinct rolle
+
+H1: Cognitive frames mediates the effect of dynamic capabilities on competetive advantage
+above and beyond mediating effect of operational capabilities
+
+H2: Cognitive frames has a direct impact on operational capabilities
+
+H3: Something to do with dynamism - importance of cognitive frames increases in dynamism
+
+Minor hypotheses: On
+
+The role of cognitive frames in strategy: Schilling 2018 abstraction
+
+Proactiveness
+Coff and Blyler - who reaps the reward from rents). cognitive frames common -
+proactiveness - culture can prohibit the rent appropriation happening
+
+Cognitive programming as rent appropriation inihibitor
+
+Cognitive programming as implementation catalyst (complement to OC)
+
+Cognitive programming as alignment mechanism (link to OC)
+
+THIS IS HOW FAR I CAME
+\newpage
+
+Ethnographic study on cognitive farmes - still top management team
+http://knowledge.wharton.upenn.edu/wp-content/uploads/2013/09/13481.pdf
+
+Implications: Maybe proactiveness cog frames can help in the paradox schreyogg, and the
+elephant.
+
+We suggest that a systematic socio-cognitive approach to “competitive sensemaking” has
+been absent from theory and research on competitive strategy. We define competitive
+sensemaking as the social and cognitive processes that underlie how firms detect, define,
+and conceptualize their competitive relationships with other firms. Competitive
+sensemaking is a subset of the more general process of strategic sensemaking, which is the
+“making plausible sense” of the broad array of stimuli and circumstances that characterize
+complex market situations. Using the value-based view of value creation and capture as a
+conceptual base for our arguments, we unpack four cognitive underpinnings of competitive
+sensemaking: mental time travel, comparability, counterfactual reasoning, and stories. We
+then show how these four components were differentially involved in shaping competitive
+sensemaking in four actual market situations. In doing so, we illustrate how competitive
+sensemaking provides fundamental inputs into the value creation and value capture
+process. We conclude the paper by drawing out the implications of competitive sensemaking
+for strategy theory and research.
+
+Some strategic decisions will long be remembered for being remarkably successful, providing dramatic benefits to customers, investors, or social welfare.
+The individuals who make these decisions are often called "visionary." But what enables some people to be visionary?
+Is it a gift or skill, and can it be learned?
+In this paper I identify three main cognitive processes that underlie the creation of visionary strategy: abstraction, idealism, and long paths of analytical reasoning.
+Using a combination of examples and cognitive science, I explain how they work individually and in combination, and how they may be cultivated.
+Schiller
+
+Cognition explain organizational inertia garud and rappa
+Sharing of dominant logic pralahad and bettis (actually managmenet but maybe org as well)
+Tripsas and Gavetti 2000 focus on management cognition in digital imaging
+
+power of analogical reasoning prevailing in teh strategy makin in novel and complex worlds
+
+(Gavetti, 2012; Gavetti et al., 2005; Tripsas and Gavetti, 2000), awaiting from LB
+
+DCs are viewed as stable patterns of action that poten- tially build a string of temporary
+advantages by adding, integrating, and reconfi guring resources, which amount to sustained
+advantage once the entire pattern is taken into account (Blyler and Coff, 2003)
+
+Again, some acquiring fi rms (not many) undergo these motivational change processes (Gottschalg and Zollo, 2007) by
+
+would for the larger part argue that 
+including the 33000 people at nokia / cultural change rr
+
+Capabilities changes reinvent productivity and business processs, as well as introcuing
+new capabiltieis. 
+Cloud based capabilities and infrastructure
+
+'AS I conlcluded my talk that morning in orlando, i focused on what would be our grandest
+endeavor / the biggest hurdle, transforming the microsofg culture. p 89
+
+Defined culture as a 'complex system of individual mindsets' culture is how an
+organization thinks and acts, but indiciduals shape it. p 90
+
+%https://news.microsoft.com/2014/02/04/satya-nadella-email-to-employees-on-first-day-as-ceo/
+%https://qz.com/work/1539071/how-microsoft-ceo-satya-nadella-rebuilt-the-company-culture/
 

### 2019-10-31 article4_jbr.rnw
almost finished first draft of hyp lacking only hyp 5

@@
 
-Looking at dynamic capabilities through the functions of sensing, seizing and
-transformation \cite{Teece2007} makes an obvious case for resource orchestration which is also highlighted
-in the extant literature. Moreover, as discussed above, these functions are also requiring
-a certain non-behavioral object of action in order to be fully efficient. To achieve a
+Looking at dynamic capabilities through the functions of sensing and seizing opportunities
+\cite{Teece2007} makes an obvious case for resource orchestration which is also
+highlighted in the extant literature. This function is related to the discovering and
+capturing opportunities (e.g. the ability of the organization to sense and seize
+opportunities (ibid)) which is very much related to the concept of exploration
+\citep{March1991}Moreover, as discussed above, these functions are also requiring a
+certain non-behavioral object of action in order to be fully efficient. To achieve a
 competitive edge firms will have to be able to sense and seize, which require a certain
@@
 right things, at the right time, based on new product (and process) development, unique
-managerial orchestration processes, a strong and {\bf change-oriented organizational culture}'
-(our emphasis) \cite[p]{Teece2014}.
+managerial orchestration processes, a strong and {\bf change-oriented organizational
+  culture}' (our emphasis) \cite[p]{Teece2014}.
+
+changes resulting from execution of dynamic capabilities (e.g. sensing and seizing) may
+move existing organizational objective functions and thus render current incentive
+alignment obsolete or out of place. This leads to an objective displacement that is
+particularly prevalent in firms with high sensing and seizing capabilities because distant
+search may lead to more radical change (ref). Organizations with high levels of dynamic
+capabilities geared towards sensing and seizing opportunities are doing so through
+\emph{resource orchestration}, e.g. by creating, extending and modifying the resource
+base, as discussed extensively in the extant literature
+\citep{Helfat2007,DiStefano2014,Protogerou2012,Schilke2018}. However, sensing and seizing
+opportunities in the market relates to discovering market disequilibrium
+\citep{Kirzner1997} as well as upsetting existing equilibria \citep{Schumpeter1934}. The
+process of sensing and seizing 'involves understanding latent demand, the structural
+evolution of industries and markets, and likely supplier and competitor responses'
+\citep[p. 1322]{Teece2007} as well as 'a good deal of customer, competitor, and supplier
+information and intelligence (with a) a significant tacit component' (ibid p 1330).To make
+sure the organization respond to changes (i.e. having an efficient cognitive frame)
+stemming from executed dynamic capabilities (e.g. sensing and seizing) the firm needs to
+make sure incentives are aligned for change.
+
+Through the process of exploration, individuals in the organization may
+accumulate private and tacit information that, if unchecked, can become a source of
+knowledge asymmetries and incentive problems (alchian and demsetz 1972), and leave the
+firm vulnerable to agency problems. Accumulation of private information in the
+organization without incentive alignment of some sort can lead rent-appropriation from
+information asymmetries \citep{Blyler2003}. In such instances of potential misalignment of
+interest, a shared cognitive frame emphasizing a growth mindset can be a useful
+remedy. Furthermore, in addition to incentives alignment the more psychological element
+of change buy-in comes into play \todo{Not sure how to proceed here - should we make a
+  distinction between the incentive problem and the buy in problem? Coud they both be
+  examples of interest alignment with different faces of motivation - extrensic vs intrinsic} (ref).
+
+To see how this would work recent contribution in neuroscience is helpful. Several
+contributions have established a clear connection between having a growth mindset and
+emphasizing intrinsic motivation (Schroder et.al 2014,O`Rourke et.al 2014). Moreover,
+individuals with higher degrees of intrinsic motivation from a growth mindset exhibit a
+significant higher ability for learning and consequently for embracing new learning
+opportunities (Yeager et al 2012). In other words, individuals with a growth mindset are
+more open to change because it enhances their intrinsic motivation from learning which
+fuels their individual utility (Ng 2018). In a situation with considerable change stemming
+from execution of dynamic capabilities, an organization with a common cognitive frame
+based on a growth mindset will be able to capture more value from the change \emph{et
+  ceteris paribus}.
+
+Consequently, by instilling a growth mindset as a change in the cognitive frame of
+Microsoft, Nadella enhanced the change ability of the firm by strengthening the intrinsic
+motivation employees have to buy into the change, and meanwhile securing a certain
+interest alignment. So Nadella did not only change the resources and capabilites of the
+company due to a strategic change towards the cloud, he did also instill a growth mindset
+to utilize the motivational and non-behavioral object of action discussed above. In other
+words, dynamic capabilites can work through two distinctly different paths. The first path
+is the familiar process of changing underlying resources and operational capabilities
+(\emph{resource orchestration path}). The second is the focal path of this paper where
+dynamic capabilities changes the cognitive frames of the organization \emph{cognitive
+  programmer path}. This leads us to the following initial hypotheses:
+
+H1: Dynamic capabilities influences the quality? of operational capabilities
+
+H2: Dynamic capabilities influences the WHAT of cognitive frames
+
+The link between operational capabilities enacted through dynamic capabilites, and
+competetive advantage is well established in the literature (refs). The main notion is
+that resources and capabilites evolved through dynamic capabilites are inimatable and
+rare, and hence conducive to the conditions underpinning competetive advantage (refs
+barney). Thus our third hypothesis is well known as the first one:
+
+H3: Operational capabilites acts as a mediator between dynamic capabiliites and
+competetive advantage.
+
+Similarly, instilling a growth mindset is also leading to competetive advantge BECAUSE???
+\todo{Need to discuss this}
+
+And one more hpythoses on how COG influences resources
+
+THIS IS HOW FAR I CAME
+\newpage
+
+To make sure that these interests are aligned
+
+DC executed requires changes. These changes will require a simultanous change in cognitive
+frames of the firm for N reasons.
+
+1. Sensing and seizing activities typicaly of dynamic capabilities generate possible
+agency problems *blyler coff
+2. Information from the process is interpreted and differently at different levels in the
+corporate hierarchy (gavetti) hence aligning interpretation across the organization matter
+
+One way of overcoming this agency problems and varying interpratations of the environment,
+is to develop a common cognitive frame within which all information is interpreted and
+acted upon. Such common traits purpose and organizational identity, 
+organizatioanl values and culture \citep{Verona2011}.
 
@@
 cognitive programmer) we consider two distinctly different functions of dynamic
-capabilities related to their microfoundations \citep{Teece2007}. the first function is
+capabilities related to their microfoundations \citep{Teece2007}. The first function is
 related to the discovering and capturing opportunities (e.g. the ability of the
@@
 \citep{Kirzner1997} as well as upsetting existing equilibria \citep{Schumpeter1934}. The
-process of sensing and seizing 'involves understanding latent demand, the structural evolution of
-industries and markets, and likely supplier and competitor responses'
-\citep[p. 1322]{Teece2007} as well as . Individuals are the unit of analysis embedding these abilities
-and if left up to these individuals without a higher organizing framework, the firm will
-be very vulnerable because of knowledge asymmetries and incentive problems (alchian and
-demsetz 1972) and lead to sub optimal rent-appropriation on the part of the individual
-employee \citep{Blyler2003}. A similar argument applies to the function of \emph{seizing}
-where the organization is set to mobilize resources for the purpose of gaining from these
+process of sensing and seizing 'involves understanding latent demand, the structural
+evolution of industries and markets, and likely supplier and competitor responses'
+\citep[p. 1322]{Teece2007} as well as 'a good deal of customer, competitor, and supplier
+information and intelligence (with a) a significant tacit component' (ibid p
+1330). Consequently, in this process of exploration individuals in the organization may
+accumulate private and tacit information that, if unchecked, can become a source of
+knowledge asymmetries and incentive problems (alchian and demsetz 1972), and leave the
+firm vulnerable to agency problems. Accumulation of private information in the
+organization without incentive alignment of some sort can lead rent-appropriation from
+information asymmetries \citep{Blyler2003}. One way to  if not sufficiently aligned with the
+cognitive frames of the organization. This particular
+
+%Mindset induction effects on cognitive control: a neurobehavioral investigation.
+%Schroder HS, Moran TP, Donnellan MB, Moser JS
+%Biol Psychol. 2014 Dec; 103():27-37.
+
+%12. Yeager D.S., Dweck C.S. Mindsets that promote resilience: When students believe that personal characteristics can be developed. Educ. Psych%ol. 2012;47:302–314
+
+Proactiveness is an opportunity-seeking, forward-looking perspective characterized by the introduction of new products and ser- vices ahead of the competition and acting in anticipation of future demand.
+
+Proacteivenss can create psychological ownership (siegel 
+We build on these theoretical considerations by applying the concept of psychological ownership (Pierce et al., 2003), defined as ‘the state in which individuals feel as though the target of ownership or a piece of that target is “theirs” ’ (Pierce et al., 2003, p.
+86)
+
+Missing link between growth mindset and internal motivation
+https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5836039/
+
+Growth mindset and individual proactivity
+https://www.emerald.com/insight/content/doi/10.1108/CDI-11-2016-0194/full/html
+
+To be clear, the importance of motivation and, in particular, its strategic relevance for
+organi- zational performance and competitive advan- tage has surfaced in some recent
+contributions in the strategic management field. Managerial rent theorists (Castanias &
+Helfat, 1991, 2001), for example, submit that the availability of skills that have rent
+generation potential is a neces- sary but not sufficient condition for rent gener-
+ation. In so doing, they also point to the impor- tance of motivation for the realization
+of any such potential. Similarly, Coff (1997) discusses a number of dilemmas firms face in
+generating an advantage from human assets, and he points to the importance of governance
+mechanisms to overcome them. Finally, Makadok (2003) calls for future research into the
+genesis of competitive advantage in a way that combines competence- based issues with
+questions of governance or motivation.
+
+of the
+company’s existence and what defi nes or limits its role(s) within its social and eco-
+nomic environment (organizational identity)? What does it stand for (organizational val-
+ues)? How are things done over here (organizational culture)?
+
+include norms (leonard Barton 1992), avoidance of cognitive
+inertia (Trpisas and Gavetti 2000)
+
+organizational inertia
+Second, 
+The existence of layer upon layer of standard procedures, established capabilities, complementary assets, and/or admin- istrative routines can exacerbate decision-making biases against innovation.
+Incumbent enterprises,
+
+Individuals are the unit of analysis embedding these abilities and if left up to
+these individuals without a higher organizing framework, the firm will be very vulnerable
+because of knowledge asymmetries and incentive problems (alchian and demsetz 1972) and
+lead to sub optimal rent-appropriation on the part of the individual employee
+\citep{Blyler2003}. A similar argument applies to the function of \emph{seizing} where the
+organization is set to mobilize resources for the purpose of gaining from these
 opportunities. In order for value to be captured from opportunities, a string of
@@
 importance. Alas the sensing process requires new knowledge from a wide range of sources
-in the organization a lot of this knowledge is tacit and can lead to rent-appropriation
-from information asymmetries \citep{Blyler2003} if not sufficiently aligned with the
-cognitive frames of the organization.
+in the organization a lot of this tacit knowledge can lead to rent-appropriation
+from information asymmetries if not sufficiently aligned with the
+cognitive frames of the organization \citep{Blyler2003}. Furthermore, as cognition plays
+an important role in the sensing and seizing of opportunities \citep{Helfat2015} and the
+interpretation and understanding varies with individuals position within the
+organization, then diverging interpretations stemming from misaligned cognitive frames may
+lead to
+
+They maintain that social capital and notably individuals’ valuable internal and external social ties allow for information sharing, innovation and novel ways of thinking which in turn helps managers understand resource acquisition, integration and release
+
+Although they relate the existence of social capital
+as an antecedents to dynamic capabilities, the same argument can be applied to their
+function; to be able to capture rents for the organization and not the individual a
+certain level of social capital is needed and
+
+“firms would be unable to acquire, recombine, and release resources”
+resources” (2003: 680) without the social capital of individuals. Hence need to build
+social capital. Growth mindset - cognitive frames important to build social captail within
+the organization?
 
@@
 
+the emphasis is on the intermediary role of "asset
+orchestration" \citep{Teece2012,Sirmon2011} as related to the "the selection, con-
+figuration, alignment, and modification of tangible and intangible assets"
+\citep[p.842]{Helfat2015}. This process is very much similar to the exploration and
+exploitation of opportunities and we consider reconfiguration to come into the focus when
+these processes are seen over time and in changing contexts. Hence we are limiting this
+study to looking at the sensing and seizing class of dynamic capabilities.
+
 However, in this endeavour
@@
 competetiveness over time stems from ambidexterity- link to research on cultural ambidecterity
-
-The concept of sensing and seizing has analogous meaning in theoretical traditions tangent
-to DC. Notably entrepreneurship \citep{Hitt2011} and organizational theory
-\citep{March1991}. \cite{Hitt2011} states that "entrepreneurship involves identifying and
-exploiting opportunities" (ibid p 59) where identification is tied to the process of
-discovery \citep{Shane2000}. Based on the definitions of opportunity discovery as DEF HERE
-juxtaposed to the definition of sensing as "a scanning, creation, learning, and
-interpretive activity" \citet[p. 1322]{Teece2007} we argue that they are similar in nature
-and usable for exploring the importance of the latter in the innovation process. It also
-bears resemblance to the concept of organizational exploration as searching, risk-taking,
-discovery, experimentation, prototyping, and flexibility \citep{March1991}. Independent of
-the nature of opportunities to be sensed as being either objective
-\citep{Alvarez2007,Shane2000} or created \citep{Alvarez2007}, the process of sensing does
-require resources and capabilities for search (ref) and a clear affinity between
-opportunity and a project exist (casson and Wadeson in Mcmullen2007) suggesting s clear
-inter dependency between routines and resources, and higher order capabilities of sensing
-\citep{Teece2007} and making sense of the opportunity
-\citep{Weick1995,March1991}. Consequently, we would expect the sensing class of dynamic
-capabilities to be positively related to innovation on the one hand, and reinforcing the
-impact from innovation input simultaneously.\newline
 
@@
 Cognitive programming as alignment mechanism (link to OC)
-
-THIS IS HOW FAR I CAME
-\newpage
 

### 2019-11-01 article4_jbr.rnw
added buyin and incentinve alignment to theory

@@
 
-DC as resource orchestration - influencing capabilities
+DC as resource orchestration - influencing capabilitie
 DC as cognitive programmer - inluencing cognitive frames
@@
 opportunities (ibid)) which is very much related to the concept of exploration
-\citep{March1991}Moreover, as discussed above, these functions are also requiring a
+\citep{March1991}. Moreover, as discussed above, these functions are also requiring a
 certain non-behavioral object of action in order to be fully efficient. To achieve a
@@
 stemming from executed dynamic capabilities (e.g. sensing and seizing) the firm needs to
-make sure incentives are aligned for change.
-
-Through the process of exploration, individuals in the organization may
-accumulate private and tacit information that, if unchecked, can become a source of
+make sure incentives are aligned for change and that the organization buys into the changes.
+
+First, the \emph{incentive alignment problem} relates to how interests of the firm
+as a whole and the collection of individual are aligned \cite{Gottschalg2007} and how this
+alignment changes when the firm embarks on strategic change as triggered by execution of
+dynamic capabilities. Through the process of exploration, individuals in the organization
+may accumulate private and tacit information that, if unchecked, can become a source of
 knowledge asymmetries and incentive problems (alchian and demsetz 1972), and leave the
@@
 information asymmetries \citep{Blyler2003}. In such instances of potential misalignment of
-interest, a shared cognitive frame emphasizing a growth mindset can be a useful
-remedy. Furthermore, in addition to incentives alignment the more psychological element
-of change buy-in comes into play \todo{Not sure how to proceed here - should we make a
-  distinction between the incentive problem and the buy in problem? Coud they both be
-  examples of interest alignment with different faces of motivation - extrensic vs intrinsic} (ref).
+interest, a shared cognitive frame emphasizing a growth mindset can be a useful remedy.
+
+Second, the \emph{buy-in problem} refers to the general willingness of the organization to
+accept and value the importance of some decision or system 'without being prompted or
+required by formal governance mechanisms'\citep[p. 812]{Simsek2009}. When individuals of
+a firm buys into changes they will enhance the full organization`s ability to not only act
+upon changes (Marchand et.al 2000), but also in 'timely responsiveness' (Kohli et.al 1993,
+Simsek2009).
+
+Both the incentive alignment problem and the buy-in problem are interrelated, but still
+represents different mechanisms. They are tied to individual motivation albeit in
+different ways. The incentive alignment problem is tied to \emph{extrinsic motivation}
+(Lindenberg 2001, Brief and Aldag 1977) where the individual is motivated by rewards or
+outcome 'such as money, power, recognition and so forth'
+\citep[p. 420]{Gottschalg2007}. The buy-in problem, in turn, is related to \emph{intrinsic
+  motivation} where the individual is driven by the goal of being engaged in enjoyable
+(Lindenberg, 2001), self-determined, and competence-enhancing (Deci \& Ryan, 1985)
+behavior (hedonistic intrinsic motivation), as well as adhering to a goal of engaging in
+behavior that is compli- ant with norms and values (normative intrinsic
+motivation). \todo{some direct citations here - need rewrite}.
+
+Extrinsic motivation is often addressed through reward systems (ref) but tacit mechanisms
+such as psychological ownership \citep{Sieger2013} has been found to be very efficient in
+aligning incentives. Psychological ownership basically retains agency theory’s assumption
+of the self-interested manager, whereas the non-economic functions of ownership, such as
+efficacy, identity, and territoriality, might curtail expropriating behaviour and align
+the interests of agents and principals (cf. Pierce et al., 2003). Hence, this concept of
+psychological ownership bridges over to the intrinsic motivation of individuals. Moreover,
+intrinsic motivation in general is influenced through changing the tasks of individuals or
+at the very least accepting individuals to change ttasks themselves to fit their
+perception of their context (Hackman and Gersick), and through regimes of socialization
+and shared norms (Kerr and Jackofsky). Common for both psychological ownership and the
+intrinsic motivation enhancement in general is a feature of the employees' cognitive
+framing, which guides the mental pathways by which they decide what is, and what is not,
+important. According to Leonard- Barton (1992), these norms and values represent the
+accretion of decisions made over time in response to the interpretation of organizational
+roles. Consequently, a cognitive frame that enhances the intrinsic motivation of the
+employees are very valuable. One way of thinking of instilling an appropriate and
+efficient cognitive frame would be the concept of a growth mindset (Dweck) as also
+emphasized in the case of Microsoft.
 
 To see how this would work recent contribution in neuroscience is helpful. Several
-contributions have established a clear connection between having a growth mindset and
+contributions have established a clear connection between having a growth mindset (Dweck 200x) and
 emphasizing intrinsic motivation (Schroder et.al 2014,O`Rourke et.al 2014). Moreover,
@@
 \newpage
+
+the general capability, views, norms and rules of behavior, with regard to accessing,
+understanding and using information in a social collectivity. Zheng 2005
 

### 2019-11-13 article4_analysis_v2.r
added double medaiation test with interaction

@@ -120,16 +120,16 @@ alldc <- zwadj[,c("Q19a", "Q19c", "Q19d", "Q20b", "Q20c","Q19", "Q20d","Q20e","Q
 
 ## Running median imputations
 #dc01 <-  imputezw(zwadj[,c("Q6.4_t1", "Q6.5_t1","Q7.1_t1","Q7.2_t1")] )
-#dc02 <-  imputezw(zwadj[,c("Q6.1_t1","Q7.3_t1","Q7.4_t1")] )
+dc02 <-  imputezw(zwadj[,c("Q6.1_t1","Q7.3_t1","Q7.4_t1")] )
 #dc001 <- imputezw(zwadj[,c("Q19a", "Q19c", "Q19d", "Q20b", "Q20c")] )
-##dc002 <-  imputezw(zwadj[,c("Q19", "Q20d","Q20e")] )
-dc002 <-  imputezw(zwadj[,c("Q19d","Q19c", "Q20b", "Q20c","Q20e")])
+dc002 <-  imputezw(zwadj[,c("Q19", "Q20d","Q20e")] )
+#dc002 <-  imputezw(zwadj[,c("Q19d","Q19c", "Q20b", "Q20c","Q20e")])
 ca0 <-  imputezw(zwadj[,c("Q28","Q28a","Q28c")] )
 ca1 <-   imputezw(zwadj[,c("Q16.1_t1","Q16.2_t1","Q16.4_t1")] )
 #or1 <-   imputezw(zwadj[,c("Q5.4_t1","Q5.6_t1","Q5.7_t1","Q5.1_t1","Q5.2_t1","Q5.3_t1","Q5.5_t1")])
 #or0 <-   imputezw(zwadj[,c("Q21c","Q21d","Q21e","Q22","Q22a","Q22b","Q22c")])
 or1 <-   imputezw(zwadj[,c("Q5.4_t1","Q5.6_t1","Q5.7_t1")])
-#or0 <-   imputezw(zwadj[,c("Q21c","Q21d","Q21e")])
+or0 <-   imputezw(zwadj[,c("Q21c","Q21d","Q21e")])
 #ma01 <-  imputezw(zwadj[,c( "Q8.7_t1", "Q8.8_t1", "Q8.9_t1")])
 #ma02 <-  imputezw(zwadj[,c("Q24","Q24a","Q24b","Q24c","Q24d")])
[…]

### 2019-11-13 article4_analysis_v2.r
analysis before cleanup

@@ -82,11 +82,10 @@ imputezw <- function(vec){
     return(vec)
 }
 
-imputezw <- function(vec){
-    tempData <- mice(vec,m=10,maxit=50,meth='pmm',seed=500)
-    return(complete(tempData,1))
-}
-
+## imputezw <- function(vec){
+##     tempData <- mice(vec,m=10,maxit=50,meth='pmm',seed=500)
+##     return(complete(tempData,1))
+## }
 
 
 extboot <- function(bootobj,n,nam,r){ #remembaer space between Letter and " ("P ")
@@ -107,10 +106,10 @@ extboot <- function(bootobj,n,nam,r){ #remembaer space between Letter and " ("P 
     return(res)
 }
 
+
+
 ## including only observations at both times
-zw2 <- zw
-zw2[zw2 == 0] <- NA
-zwadj <- subset(zw2,!is.na(Q4.1_t1))
+zwadj <- subset(zw,!is.na(Q4.1_t1))
 rownames(zwadj) <- NULL
 
 
@@ -140,11 +139,12 @@ m2 <- imputezw(zwadj[,c("Q4.1_t1","Q4.2_t1","Q4.3_t1")])
 m0 <- imputezw(zwadj[,c("Q18","Q17a","Q17b")])
 #m1 <- imputezw(zwadj[,c("Q4.7_t1","Q4.8_t1","Q4.9_t1")])
 
-dcm <- (dc002+dc02)/2 ;colnames(dcm)  <-  c("dcm1","dcm2","dcm3")
+dcm <- (dc002+dc02)/2 ;colnames(dcm)  <-  c("dcm1","dcm2","dcm3") ## Average DC between two periods
 #complist <- list(DC_P=dc01,DC_X=dc02,CA_t=ca0,CA=ca1,P=or1,R=ma01)
 vcontrols <- zwadj[,c("size","age","pm","lassets","debt","assets","dyn")]
 #zwadj <- cbind(dc01,dc02,dc001,dc002,ca0,ca1,or1,or0,ma01,m0,m1,vcontrols,dyn)
 zwadj <- cbind(dc002,dc02,ca0,ca1,m1,m0,or0, or1,vcontrols,dcm)
+zwadj <- cbind(ca0,ca1,m1,m0,or0, or1,dcm)
 zwadj$de <- zwadj$debt/zwadj$assets
 
 #zwbck  <- zwadj
@@ -183,86 +183,7 @@ am1
[…]

### 2019-11-14 article4_analysis_v2.r
Added results data frames

@@ -12,7 +12,8 @@ library(huxtable)
 library(semPLS)
 library(mice)
 library(mma)
-####install.packages("semPLS")
+#install.packages("semPLSModelSelection", repos="http://R-Forge.R-project.org")
+library("semPLSModelSelection")
                                         #library(polycor)
 
 ## This loads the data workspace where skattefunn_data.r is already loaded
@@ -144,32 +145,9 @@ dcm <- (dc002+dc02)/2 ;colnames(dcm)  <-  c("dcm1","dcm2","dcm3") ## Average DC 
 vcontrols <- zwadj[,c("size","age","pm","lassets","debt","assets","dyn")]
 #zwadj <- cbind(dc01,dc02,dc001,dc002,ca0,ca1,or1,or0,ma01,m0,m1,vcontrols,dyn)
 zwadj <- cbind(dc002,dc02,ca0,ca1,m1,m0,or0, or1,vcontrols,dcm)
-zwadj <- cbind(ca0,ca1,m1,m0,or0, or1,dcm)
+#zwadj <- cbind(ca0,ca1,m1,m0,or0, or1,dcm)
 zwadj$de <- zwadj$debt/zwadj$assets
 
-#zwbck  <- zwadj
-
-
-zwadj <- zwbck
-### Making indexes for further analysis
-
-zwadj$m  <- rowMeans(m1)
-zwadj$r  <- rowMeans(or1)
-zwadj$m0  <- rowMeans(m0)
-zwadj$r0  <- rowMeans(or0)
-zwadj$ca1  <- rowMeans(ca1)
-zwadj$ca0  <- rowMeans(ca0)
-zwadj$dc0  <- rowMeans(dc002)
-zwadj$dc1  <- rowMeans(dc02)
-zwadj$dcm  <- (zwadj$dc1+zwadj$dc0)/2
-zwadj$ddc  <- zwadj$dc1-zwadj$dc0
-zwadj$dm  <- (zwadj$m-zwadj$m0)/zwadj$m0
-zwadj$dr  <- (zwadj$r-zwadj$r0)/zwadj$r0
-
-
-
-am1 <- round(psych::alpha(m1)$total[1],2)
-am1
 
 
 ## Removing missing for analysis to work
@@ -186,14 +164,12 @@ am1
 
 
 nboot <- 200
-## zwadjh <- subset(zwadj,dyn>4);nrow(zwadjh)
-## zwadjl <- subset(zwadj,dyn<=4);nrow(zwadjl)
+
 
[…]

### 2019-11-14 article4_analysis_v2.r
making funciton for wrapper and cleaning up

@@ -72,7 +72,7 @@ zw$size <- zw$Q1_t1
 zw$age <- zw$Q2_t1
 
 
-## Imputation function
+## Imputation functionxx
 imputezw <- function(vec){
     meanVec <- rowMeans(vec, na.rm=TRUE) #coud be rowMeans
     for (i in 1:nrow(vec)){
@@ -148,7 +148,7 @@ zwadj <- cbind(dc002,dc02,ca0,ca1,m1,m0,or0, or1,vcontrols,dcm)
 #zwadj <- cbind(ca0,ca1,m1,m0,or0, or1,dcm)
 zwadj$de <- zwadj$debt/zwadj$assets
 
-
+## removing pm extreme values
 
 ## Removing missing for analysis to work
 ## zwadj <- subset(zwadj,!is.na(zwadj$ca0))
@@ -182,49 +182,49 @@ CONT <- c("size","assets","pm")
 CONTm <- c("size","assets")
 #CONT <- c("pm","de","dyn","size")
 
-##### Direct only
-items <- c(DC01,CA0,CA1,CONT)
-latents <- c(rep("DC",length(DC01)),rep("CA0",length(CA0)),rep("CA1",length(CA1)),toupper(CONT))
-mm <- cbind(latents,items); colnames(mm) <- c("source","target")
-iv <- c(toupper(CONT),"CA0","DC")
-dv <- c(rep("CA1",length(CONT)),"CA1","CA1")
-sm <- cbind(iv,dv);colnames(sm) <- c("source","target")
 
-DIR <- plsm(data = zwadj, strucmod = sm, measuremod = mm)
-dir <- sempls(model = DIR, data = zwadj, wscheme = "centroid",maxit=1000)
-dir
-
-pathDiagram(dir, file = "direct", full = FALSE, edge.labels = "both", output.type = "graphics", digits = 2,graphics.fmt="pdf")
-
-dirfit <- semPLS::gof(dir)
-dirfit
-dirBoot <- bootsempls(dir, nboot = nboot, start = "ones", verbose = FALSE)
-dirout <- extboot(dirBoot,9,"",c("^M ","R "))
+CONT <- c("size","age")
+CONTm <- c("size","age")
 
 
+plswrap <-function(zwadj,CONT,CONTm){
 
+  ### MODELLING THE SEMPLS
+    ##### Direct only
[…]

### 2019-11-15 article4_jbr.rnw
Started writing up the results

--- 2019-10-31 article4_jbr.rnw
@@
 \usepackage[textsize=tiny,colorinlistoftodos]{todonotes}
-\usepackage{subfig}
+%\usepackage{subfigure}
+%\usepackage{subcaption}
+%\usepackage{caption}
+%\usepackage{tikz}
+\usepackage{caption}
 \usepackage{subcaption}
+\usepackage{filecontents}
+\usepackage{tikz-qtree}
+\usepackage{pdflscape}
+\usepackage{tikz}
+\usepackage{multirow}
+\usepackage{booktabs}
+\usepackage{color, colortbl}
 
+  \definecolor{Gray}{gray}{0.9}
+
+\captionsetup[subfigure]{labelfont=bf,textfont=normalfont,singlelinecheck=off,justification=raggedright}
 \input{preamble.tex}
@@
 
-%\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
+%\address[mymainaddress]{1600 John F Kfennedy Boulevard, Philadelphia}
 %\address[mysecondaryaddress]{360 Park Avenue South, New York}
@@
 
+<<load, results="asis", echo=FALSE >>=
+
+setwd("/Users/larshovdanmolden/Documents/git/article4")
+library(xtable)
+#load("./data/resart4.RData")
+r <- main$resmat
+rm  <- main$resmatmed
+l  <- main$loadings
+
+foolars=0.99
+
+@
 %% Extant literature on dynamic capabilities is battling with a fundamental conception and
@@
 most clearly by Peter Drucker`s famous quote about how 'culture eats strategy for lunch'
-(ref) insofar as . Moreover, these non-behavioral objects of change are themselves far
+(ref) insofar as. Moreover, these non-behavioral objects of change are themselves far
 from static and are found to change over time as responses to external change
@@
 To shed light on this important question we theorize on the role of a particular type of
-non-behavioral object of change, \emph{organizational cognition}, and how it acts as a
+non-behavioral object of change, \emph{strategic cognition}, and how it acts as a
 mediator between dynamic capabilities and firm competitive advantage and hence has a
 pivotal place in the literature. We build on important work on the concept of
-organizational cognition (ref), non-behavioral object of change (ref) and blablabla (ref),
-and hypothesize about how organizational cognition acts as a mediator in the same way as
+organizational cognition (ref), non-behavioral object of change (ref) and cognitive
+psychology (kahneman and tversky),
+and hypothesize about how strategic cognition acts as a mediator in the same way as
 conventional behavioral objects of change (such as routines and capabilities) and that
-these two are complementary to a certain degree. Moreover, we also suggest how
-organizational cognition could also influence routines and capabilites directly with
-further implications for competitive advantage.
+these two are complementary to a certain degree. Consequently, we argue, dynamic capabilities takes
+the function of a 'conductor' by orchestrating routines and capabilities, and the role of
+a 'coach' in stimulating strategic cognition. We use the case of Microsoft's transition
+into the cloud computing business as an illuminating case for demonstrating how the roles
+of 'conductor' and 'coach' coexist and act partly complimentary in generating strategic
+change and competitive advantage.
+
+SOMETHING ABOUT COMP ADV / why interesting outcome holy grail helfat schilke
 
@@
 
+\section{Definitions}
+The collective term for assets available for firms in their pursuit of their objectives
+are \emph{resources}. This term entails tangible assets such as machines, capital, and
+labor, but also intangible assets such as procedures, practices, and intellectual
+property. The process of using these resources in the pursuit of business objectives such
+as competitive advantage is a firm's \emph{capabilities} which can be a set of routines
+and skills applied. Resources and capabilities are both tied organizational behavior and
+how the organization act in their operation. Hence, they are coined \emph{behavioral
+  objects of change} \citep{Verona2011}: 'A pattern of action, a process, an operating
+routine, or any form of group activity characterized by some level of stability and
+predictability' (ibid. p.538). Such behavioral objects such as capabilities are the
+conventional understanding of how dynamic capabilities work; they 'purposefully create,
+extend and modify the resource base' (helfat). In the terminology proposed in this paper
+this process takes the shape as a 'conductor'.
+
+However, as \cite{Verona2011} points out: 'This approach misses the fundamental aspect
+that organizational capabilities specific to managing change can hardly be reduced to the
+management of behavioral change' (ibid p. 538). This opens for \emph{non-behavioral
+  objects of change} which are defined as 'behavioral antecedents, such as cognition
+(e.g. cognitive frames) and motivation' (ibid p. 539). This concept entails the 'how
+decisions or actions are shaped, subverted, and/or transformed by emotions; and it
+concerns how emotions become embedded in cultural and political practices that determine
+the "way we do things here"' (Vince and Gabriel 2011 . ch 15). One particular dimension of
+these non-behavioral objects of change particularly conducive to the context of
+generating strategic change is the \emph{strategic cognition} of the
+organization. Strategic cognition can be defined as conceptual structures in the minds of
+the individuals that encapsulate a shared understanding of the reality the
+individuals face with respect to the strategic goal of the organization \footnote{This
+  definition is based on the definition of \cite{Lakoff1987} definition of the more generic
+  'cognitive representation' and is adapted to fit the pursuit of strategic goals such as
+  competetive advantage which is the aim of this paper}. This strategic
+cognition is the result of a mental process that underlie internal
+audicences adoption of new strategic representation and identity code to move toward a
+new or existing goal \citep{Gavetti2012}. Although strategic cognition may lead to
+behavioral outcome, the nature of the concept itself is tied to cognition rather than
+actual latent action \citep{Zollo2016}. Thus, dynamic capabilities are not sufficiently
+creating strategic change through its role as 'conductor'. Additionally they need to
+exercise a role of 'coach' to adapt the strategic cognition of the organization to create
+a shared understanding of the sense and necessity of the strategic goals of the
+orientation.
+
 \section{Hypotheses}\label{sec:hyp}
 
-DC as resource orchestration - influencing capabilities
-DC as cognitive programmer - inluencing cognitive frames
+%DC as resource orchestration - influencing capabilitie
+%DC as cognitive programmer - inluencing cognitive frames
+
+%Prior research focused on managerial cognition, but gavetti shows that hierarchy matters
+%and different cognition maters
 
@@
 routines), but also through changing the non-behavioral objects of action (i.e. the
-cognitive frames). In other words, the story of Microsoft`s transformation suggest that
+strategic cognition). In other words, the story of Microsoft`s transformation suggest that
 dynamic capabilities worked through mediating factors to influence competetive advantage,
-but that thes mediating factors exist as two distinctly different concepts working in
+but that these mediating factors exist as two distinctly different concepts working in
 tandem. Figure \ref{fig:fig1} presents a conceptual depiction of the paths running through
-these two concepts of \emph{behavioral} and \emph{cognitive} objects of action
+these two concepts of \emph{capabilities} and \emph{strategic cognition} objects of action
 \citep{Zollo2016}. We use a familiar term for the conventional understanding of dynamic
-capabilities mechanism as 'resource orchestration' (ref) as a collective term to describe
-the behavioral objects of action (ref). This idea of orchestrating resources are
-particularly illuminating in that it sets an organization`s dynamic capabilities as a
-director conducting new outcomes by orchestrating the use of firm resources, and it is in
-line with a range of the most common definitions of dynamic capabilities
-\citep{Schilke2018}. The non-behavioral objects of action has no similar agreed upon
-analogy, so for the purpose of our analysis we envision this mechanism to work more as a
-cognitive process enabling the organization to tear away from their current understanding
-and ways in which things are done (Vince and Gabriel). Whereas the analogy of resource
-orchestration has its counterpart in the making of art (i.e. music, movies or theatrical
-plays), the non-behavioral objects of action are more aligned to psychology and cognitive
-therapy. The process is all about changing an organization`s thinking from the automated
-and well-known, to the more cognitively aware, what Kahneman and Tversky coins 'system two'
-thinking (ref). This change of cognitive frames will thus be more similar to a
-reprogramming effort and we henceforth refer to the process of changing the non-behavioral
-objects of action (e.g. cognitive frames, culture, etc) as 'cognitive programming'.
+capabilities mechanism as 'orchestration' (ref) as a collective term to describe the
+behavioral objects of action (ref). In this process dynamic capabilities play the role of
+a 'conductor' orchestrating capabilities of the firm, an understanding that is in line
+with a range of the most common definitions of dynamic capabilities \citep{Schilke2018}.
+
+The non-behavioral objects of action has no similar agreed upon analogy, so for the
+purpose of our analysis we envision this mechanism to work more as a cognitive process
+enabling the organization to tear away from their current understanding and ways in which
+things are done (Vince and Gabriel). Whereas the analogy of a 'conductor' suggests a
+function that composes an outcome based on the available capabilities, the notion of a
+'coach' refers to the function of enabling others to achieve their objectives. The process
+is all about changing an organization`s thinking from the automated and well-known, to the
+more cognitively aware, moving from what Kahneman and Tversky coins the automated 'system
+one' to the deliberate 'system two' thinking (ref). We will now turn to the two functions
+of dynamic capabilities in turn.
 
@@
 
-RESOURCE ORCH is HITT2011 among other
-\subsection{Cognitive programming}
+\subsection{Capabilities conductor}
+
+Satya Nadella set out to transform Microsoft by investing heavily in artificial
+intelligence and cloud computing capabilities. This entailed hiring new people, upgrading
+the skills and abilities of the current staff, and acquire infrastructure and
+hardware. Additionally, Microsoft was able to acquire and integrate a number of companies
+to support the strategic direction the company was on. Companies such as GitHub, LinkedIn
+and Citrus data became important platforms for developing new capabilities within the
+company (Nadella).
+
+This role of 'conductor' is the conventional way of understanding dynamic capabilities. It
+stems from one of the most common definitions \citep{Helfat2007} as well as the analogy of
+the process as 'resource orchestration' \citep{Sirmon2011}. It is also found in the
+empirical literature handling various functional forms of dynamic capabilities such as
+acquisition targeting \citep{Bingham2015}, alliancing \cite{Schilke2014}, new product
+development \cite{Danneels2008}, innovation capabilities \citep{Breznik2014}, marketing
+capabilities \cite{Brune2009} and alliance capabilities \cite{Kale2002,kale2007}.
+
+The bulk of prior contributions study firm capabilities and resources as the mechanism
+through which dynamic capabilities influence an outcome
+\citep{Fainshmidt2016a,Protogerou2012,Schilke2018,Eriksson2014}. Particularly, much of the
+extant literature concerns measures of accounting profitability and competitive advantage
+as the final outcome of dynamic capabilities
+\cite{shamsie2009,Schilke2014,Schilke2014a,Teece2016}. Thus, from these prior
+contributions we derive a fundamental hypotheses of the relationship between dynamic
+capabilities and competitive advantage:
+
+\emph{H1: Firm capabilities mediates the relationship between dynamic capabilities and
+  competetive advantage}
+
+However, this mechanism is solely related to behavioral objects of action while previous
+insights from the literature on organizational capabilities hold that this is only parts
+of the story \cite{Tripsas2000,Gavetti2012}. Or as highlighted by \cite{Verona2011}: Most
+'conceptualizations of DCs have in common the often implicit assumption that the object
+upon which DCs produce their effects is fundamentally of a behavioral nature: that is a
+pattern of action, a process, an operating routine, or any form of group activity
+characterized by some level of stability and predictability. This approach misses the
+fundamental aspect that organizational capabilities specific to managing change can
+hardly be reduced to the management of \emph{behavioral} change' (p. 538). Thus, they
+argue, a more holistic approach including cognition is needed \citep{Zollo2016}. This claim is also
+supported in the lessons from Microsoft's transition.
+
+% https://hbswk.hbs.edu/item/the-transformation-of-microsoft
+
+\subsection{Cognitive coach}
+
+On February 4th 2014 an email appeared in the inbox of all Microsoft employees. It was
+from Nadella who had just begun his tenure as CEO of the company. In this email he lays
+out the framework for transforming Microsoft around changing the way the company jointly
+acted. He wanted to change the culture of the company from one of inviting new ideas and
+fostering creativity. This called for changes in the \emph{cognition} of the individual
+employers as well as their capabilities and skills. Nadella made this abundantly clear in
+this email even paraphrasing Oscar Wilde in that 'we need to believe in the impossible and
+remove the improbable'. Nadella's tool for achieving this change of cognition was to
+become the notion of the growth mindset \citep{Dweck2016}. This transformation of the
+cognition of the organization to better fit the strategy he was laying out, is a proper
+example of instilling a \emph{strategic cognition} in the organization.
+
 Juxtaposed to the experiences from Microsoft, the case of Polaroid brings another set of
 experiences to our discussion on non-behavioral objects of action (see \citep{Tripsas2000}
-for a detailed account). Cognitive inertia on the part of the organization, not the top
-management, \todo{Check this - maybe remove the sentence on top management} played a
+for a detailed account). Cognitive inertia on the part of the organization played a
 pivotal part in the failing of the company`s digital imaging effort
-\citep{Verona2011}. Similar patterns are found in Kodak and Anderson Consulting (ref
-Hederson and Kaplan 2005), and Smith Corona (Danneels 2010). These examples highlight the
+\citep{Verona2011}. In other words, Polaroid did not exercise dynamic capabilities to
+change the cognition of the organization. Similar patterns are found in Kodak and Anderson Consulting (ref
+Henderson and Kaplan 2005), and Smith Corona (Danneels 2010). These examples highlight the
 absence of 'dynamic capabilities specific to the adaptation of cognitive frames, first,
-and consequently of operating processes' \citep[p. 541]{Verona2011}.
+and consequently of operating processes' \citep[p. 541]{Verona2011}. This is also
+highlighted at the core of the dynamic capabilities literature: 'Dynamic capabilities are about doing the
+right things, at the right time, based on new product (and process) development, unique
+managerial orchestration processes, a strong and {\bf change-oriented organizational
+  culture}' (our emphasis) \cite[p]{Teece2014}.
 
-Looking at dynamic capabilities through the functions of sensing, seizing and
-transformation \cite{Teece2007} makes an obvious case for resource orchestration which is also highlighted
-in the extant literature. Moreover, as discussed above, these functions are also requiring
-a certain non-behavioral object of action in order to be fully efficient. To achieve a
-competitive edge firms will have to be able to sense and seize, which require a certain
-organizational cognitive frame to be efficient. 'Dynamic capabilities are about doing the
-right things, at the right time, based on new product (and process) development, unique
-managerial orchestration processes, a strong and {\bf change-oriented organizational culture}'
-(our emphasis) \cite[p]{Teece2014}.
+When dynamic capabilities are executed it is as a response to changes in the environment
+in order to stay competitive. This processes relates to creating strategic change
+\citep{Helfat2007} and entails changing strategic direction and objectives of the
+organization. This strategic change requires, in addition to modifying, extending and
+creating firm capabilities, also some kind of alignment with the organization as a whole -
+what is often referred to as 'how we do things here' \citep{Nelson1982}, and how an
+organization thinks and act (NAdella). This alignment is possible only if the employees
+share a common cognitive frame related to the the strategic direction of the company
+enabling them to make sense of the changes ahead. This is what we have coined
+\emph{strategic cognition} and has its expression in Microsoft's development of a growth
+mindset. Strategic cognition is needed to get employees on board as well as capture the
+efficiency of non-directed change. Getting on board refers to the general willingness of
+the organization to accept and value the importance of some decision or system 'without
+being prompted or required by formal governance
+mechanisms'\citep[p. 812]{Simsek2009}. Moreover, When individuals of a firm buys into
+changes they will enhance the full organization`s ability to not only act upon changes
+(Marchand et.al 2000), but also in 'timely responsiveness' (Kohli et.al 1993,
+Simsek2009). Consequently, strategic cognition not only contributes to getting people on
+board, it also maintain a more efficient change process where the individuals take more
+responsibilities for the change itself and leverages their individual knowledge in the
+endeavor. For a firm to create real strategic change as enabled by their dynamic
+capabilities and hence stay competitive, is will need to act as a 'coach' to instill a
+strategic cognition in the organization.
 
-To see how dynamic capabilities acts through cognitive objects of action (i.e. as a
-cognitive programmer) we consider two distinctly different functions of dynamic
-capabilities related to their microfoundations \citep{Teece2007}. the first function is
-related to the discovering and capturing opportunities (e.g. the ability of the
-organization to sense and seize opportunities (ibid)) which is very much related to the
-concept of exploration \citep{March1991}. Organizations with high levels of dynamic
-capabilities geared towards sensing and seizing opportunities are doing so through
-\emph{resource orchestration}, e.g. by creating, extending and modifying the resource
-base, as discussed extensively in the extant literature
-\citep{Helfat2007,DiStefano2014,Protogerou2012,Schilke2018}. However, sensing and seizing
-opportunities in the market relates to discovering market disequilibrium
-\citep{Kirzner1997} as well as upsetting existing equilibria \citep{Schumpeter1934}. The
-process of sensing and seizing 'involves understanding latent demand, the structural evolution of
-industries and markets, and likely supplier and competitor responses'
-\citep[p. 1322]{Teece2007} as well as . Individuals are the unit of analysis embedding these abilities
-and if left up to these individuals without a higher organizing framework, the firm will
-be very vulnerable because of knowledge asymmetries and incentive problems (alchian and
-demsetz 1972) and lead to sub optimal rent-appropriation on the part of the individual
-employee \citep{Blyler2003}. A similar argument applies to the function of \emph{seizing}
-where the organization is set to mobilize resources for the purpose of gaining from these
-opportunities. In order for value to be captured from opportunities, a string of
-conditions have to be met \citep{Teece2017}, but the evolution of a 'strong and
-change-oriented organizational culture' \citep[p. 331]{Teece2014} is of pivotal
-importance. Alas the sensing process requires new knowledge from a wide range of sources
-in the organization a lot of this knowledge is tacit and can lead to rent-appropriation
-from information asymmetries \citep{Blyler2003} if not sufficiently aligned with the
-cognitive frames of the organization.
+\emph{H2: Strategic cognition mediates the relationship between dynamic capabilities and
+  competitive advantage}
 
-One consequence is a ‘program persistence bias.’ Its corollary is various forms of
-‘anti-innovation bias,’ including the ‘anti- cannibalization’ basis discussed in a later
-section. Program persistence refers to the funding of pro- grams beyond what can be
-sustained on the merits,
-
-However, in this endeavour
-simply adatping resources is a necessary but not sufficient condition for obtaining the
-needed strategic change.
-
-The functions of dynamic capabilities as highlighted above is thoroughly discussed in
-extant literature (refs), but a quick recap is useful.
-
-DC geared towards creating new or reconfiguring old (exploration vs exploitation) but true
-competetiveness over time stems from ambidexterity- link to research on cultural ambidecterity
-
-The concept of sensing and seizing has analogous meaning in theoretical traditions tangent
-to DC. Notably entrepreneurship \citep{Hitt2011} and organizational theory
-\citep{March1991}. \cite{Hitt2011} states that "entrepreneurship involves identifying and
-exploiting opportunities" (ibid p 59) where identification is tied to the process of
-discovery \citep{Shane2000}. Based on the definitions of opportunity discovery as DEF HERE
-juxtaposed to the definition of sensing as "a scanning, creation, learning, and
-interpretive activity" \citet[p. 1322]{Teece2007} we argue that they are similar in nature
-and usable for exploring the importance of the latter in the innovation process. It also
-bears resemblance to the concept of organizational exploration as searching, risk-taking,
-discovery, experimentation, prototyping, and flexibility \citep{March1991}. Independent of
-the nature of opportunities to be sensed as being either objective
-\citep{Alvarez2007,Shane2000} or created \citep{Alvarez2007}, the process of sensing does
-require resources and capabilities for search (ref) and a clear affinity between
-opportunity and a project exist (casson and Wadeson in Mcmullen2007) suggesting s clear
-inter dependency between routines and resources, and higher order capabilities of sensing
-\citep{Teece2007} and making sense of the opportunity
-\citep{Weick1995,March1991}. Consequently, we would expect the sensing class of dynamic
-capabilities to be positively related to innovation on the one hand, and reinforcing the
-impact from innovation input simultaneously.\newline
-
-To see how dynamic capabilities work to adapt cognitive frames in addition to operational
-capabilities to influence competetive advantage, it is useful to turn to their
-microfoundations \citep{Teece2007}. In this framework dynamic capabilities work through
-three expressions. First, sensing seizing. more here..
-
-Each of these dimensions relates to a function of cognitive frames within the firm beyond
-the cognitive frames of the dynamic capability itself as explored by previous
-contributions in general \citep{Teece2007} and towards management specifically
-\citep{Helfat2015,Helfat2015a}. First, sensing opportunities in the market relates to
-discovering market disequilibrium \citep{Kirzner1997} as well as upsetting existing
-equilibria \citep{Schumpeter1934}. This process is very much at the core of dynamic
-capabilities as a function of management, but its function calls for a very close
-relationship with the rest of the organization both in terms of resource orchestration and
-cognitive programming. The process of sensing 'involves understanding latent demand, the
-structural evolution of industries and markets, and likely supplier and competitor
-responses' \citep[p. 1322]{Teece2007}. Individuals are the unit of analysis embedding
-these abilities and if left up to these individuals without a higher organizing
-framework, the firm will be very vulnerable because of knowledge asymmetries and incentive
-problems (alchian and demsetz 1972) and lead to sub optimal rent-appropriation on the part
-of the individual employee \citep{Blyler2003}.
-
-A similar argument applies to the function of \emph{seizing} where the organization is set
-to mobilize resources for the purpose of gaining from these opportunities. In order for
-value to be captured from opportunities, a string of conditions have to be met
-\citep{Teece2017}, but the evolution of a 'strong and change-oriented organizational
-culture' \citep[p. 331]{Teece2014} is of pivotal importance. Alas the sensing process
-requires new knowledge from a wide range of sources in the organization a lot of this
-knowledge is tacit and can lead to rent-appropriation from information asymmetries
-\citep{Blyler2003} if not sufficiently aligned with the cognitive frames of the
-organization.
-
-Finally, the \emph{transformation} function of dynamic capabilities are related to the
-idea of continuously renewal of the resource base in order to stay competitive. This continuous
-process requires the development and maintenance of a share cognitive frame such as a
-culture, which is typically found in production processes such as LEAN and Six Sigma
-(ref).
-
-Looking at dynamic capabilities through the functions of sensing, seizing and
-transformation makes an obvious case for resource orchestration which is also highlighted
-in the extant literature. Moreover, as discussed above, these functions are also requiring
-a certain non-behavioral object of action in order to be fully efficient. To achieve a
-competitive edge firms will have to be able to sense and seize, which require a certain
-organizational cognitive frame to be efficient. 'Dynamic capabilities are about doing the
-right things, at the right time, based on new product (and process) development, unique
-managerial orchestration processes, a strong and change-oriented organizational culture'
-\cite[p]{Teece2014}.
-
-It is argued that contextual ambidexterity is grounded in the type of organizational culture (Ghoshal and Bartlett 1994; Gibson and Birkinshaw 2004; Simsek et al.
-2009) that promotes both creativity and discipline (Jelinek and Schoonhoven 1993), or both the presence of different knowledge and the integration of multiple perspectives to develop a cohesive point of view (Eisenhardt and Schoonhoven 1990).
-
-ambidextrous organizational culture wang rafiq 2014
-
-The enterprise will be vulner- able if the sensing, creative, and learning functions are left to the cognitive traits of a few individuals
-
-Three types of managerial activities can make a capability dynamic: sensing (which means
-identifying and assessing opportunities outside your company), seizing (mobilizing your
-resources to capture value from those opportunities), and transforming (continuous
-renewal).
-
-Whereas ordinary capabilities are about doing
-things right, dynamic capabilities are about doing the right things, at the right time, based on new product (and process) development, unique mana- gerial orchestration processes, a strong and change- oriented organizational culture, and a prescient assessment of the business environment and tech- nological opportunities.
-teece 2014
-
-The strength of a firm's dynamic capabilities determines the speed and degree (and
-associated cost) of aligning the firm's resources—including its business model(s)—with
-customer needs and aspirations. To achieve this, organizations must be able to
-continuously sense and seize opportunities, and to periodically transform aspects of the
-organization and culture so as to be able to proactively reposition to address yet newer
-threats and opportunities as they arise. Terse 2018
-
-Dynamic capabilities are hard for rivals to replicate because they are built on the
-idiosyncratic characteristics of entrepreneurial managers and the history-honed routines
-and culture of the organization (Teece, 2014a). In addition, there is the uncertain
-imitability of a complex system that even those directly involved may not fully understand
-(Lippman and Rumelt, 1982). Because they are a unique and valuable general-purpose
-resource, strong dynamic capabilities can serve as a firm foundation for sustainable
-competitive advantage. This is especially true the more deeply embedded the capabilities
-are in the organization, and the less they are resident only in the top management
-team. Teece 2018
-
- Managers must articulate a vision and establish an appropriate organizational culture and an incentive system that will promote organizational identification and loyalty (Augier and Teece, 2009).
-
-Put differ- ently, selecting the right ‘architecture’ for a busi- ness requires not just understanding the choices available; it also requires assembling the evidence needed to validate conjectures and hunches about costs, customers, competitors, complementors, dis- tributors, and suppliers.
-Designing
-
-Distinct rolle
-
-H1: Cognitive frames mediates the effect of dynamic capabilities on competetive advantage
-above and beyond mediating effect of operational capabilities
-
-H2: Cognitive frames has a direct impact on operational capabilities
-
-H3: Something to do with dynamism - importance of cognitive frames increases in dynamism
-
-Minor hypotheses: On
-
-The role of cognitive frames in strategy: Schilling 2018 abstraction
-
-Proactiveness
-Coff and Blyler - who reaps the reward from rents). cognitive frames common -
-proactiveness - culture can prohibit the rent appropriation happening
-
-Cognitive programming as rent appropriation inihibitor
-
-Cognitive programming as implementation catalyst (complement to OC)
-
-Cognitive programming as alignment mechanism (link to OC)
-
-THIS IS HOW FAR I CAME
-\newpage
-
-Ethnographic study on cognitive farmes - still top management team
-http://knowledge.wharton.upenn.edu/wp-content/uploads/2013/09/13481.pdf
-
-Implications: Maybe proactiveness cog frames can help in the paradox schreyogg, and the
-elephant.
-
-We suggest that a systematic socio-cognitive approach to “competitive sensemaking” has
-been absent from theory and research on competitive strategy. We define competitive
-sensemaking as the social and cognitive processes that underlie how firms detect, define,
-and conceptualize their competitive relationships with other firms. Competitive
-sensemaking is a subset of the more general process of strategic sensemaking, which is the
-“making plausible sense” of the broad array of stimuli and circumstances that characterize
-complex market situations. Using the value-based view of value creation and capture as a
-conceptual base for our arguments, we unpack four cognitive underpinnings of competitive
-sensemaking: mental time travel, comparability, counterfactual reasoning, and stories. We
-then show how these four components were differentially involved in shaping competitive
-sensemaking in four actual market situations. In doing so, we illustrate how competitive
-sensemaking provides fundamental inputs into the value creation and value capture
-process. We conclude the paper by drawing out the implications of competitive sensemaking
-for strategy theory and research.
-
-Some strategic decisions will long be remembered for being remarkably successful, providing dramatic benefits to customers, investors, or social welfare.
-The individuals who make these decisions are often called "visionary." But what enables some people to be visionary?
-Is it a gift or skill, and can it be learned?
-In this paper I identify three main cognitive processes that underlie the creation of visionary strategy: abstraction, idealism, and long paths of analytical reasoning.
-Using a combination of examples and cognitive science, I explain how they work individually and in combination, and how they may be cultivated.
-Schiller
-
-Cognition explain organizational inertia garud and rappa
-Sharing of dominant logic pralahad and bettis (actually managmenet but maybe org as well)
-Tripsas and Gavetti 2000 focus on management cognition in digital imaging
-
-power of analogical reasoning prevailing in teh strategy makin in novel and complex worlds
-
-(Gavetti, 2012; Gavetti et al., 2005; Tripsas and Gavetti, 2000), awaiting from LB
-
-DCs are viewed as stable patterns of action that poten- tially build a string of temporary
-advantages by adding, integrating, and reconfi guring resources, which amount to sustained
-advantage once the entire pattern is taken into account (Blyler and Coff, 2003)
-
-Again, some acquiring fi rms (not many) undergo these motivational change processes (Gottschalg and Zollo, 2007) by
-
-would for the larger part argue that 
-including the 33000 people at nokia / cultural change rr
-
-Capabilities changes reinvent productivity and business processs, as well as introcuing
-new capabiltieis. 
-Cloud based capabilities and infrastructure
-
-'AS I conlcluded my talk that morning in orlando, i focused on what would be our grandest
-endeavor / the biggest hurdle, transforming the microsofg culture. p 89
-
-Defined culture as a 'complex system of individual mindsets' culture is how an
-organization thinks and acts, but indiciduals shape it. p 90
-
-%https://news.microsoft.com/2014/02/04/satya-nadella-email-to-employees-on-first-day-as-ceo/
-%https://qz.com/work/1539071/how-microsoft-ceo-satya-nadella-rebuilt-the-company-culture/
-
-%{\bf How is a direct link between dynamic capabiliites and competetive advantage working
-%  and under which conditions does it come into play or not?}
-
-In the face of a growing consensus on the definition (ref) and outcome (ref) of dynamic
-capabilities as working through mediators, the presence of direct effects argued by others
-(ref) seems puzzling. However, the broader empirical literature on the antecedents of firm
-performance offers an interesting point of departure. This literature concerns itself with
-the relative importance of factors at the firm-level on the one hand, and those at the
-industry level at the other.
-
-The debate over the relative role of different levels of factors in accounting for the
-major share of the variance in firms performance has been of particular importance in the
-field of strategic management, most notably in the Strategic Management Journal
-(M. A. Fitza 2014; Hansen and Wernerfelt 1989; McGahan and Porter 1997; Rumelt
-1991). Overall, the accumulated empirical evidence show that firm factors matter far more
-for firm performance than industry factors (McGahan and Porter 2002). These stylized facts
-have been used as empirical support for the importance of idiosyncratic firm resource and
-capabilities; leading up too recent formulation of the resource and capability based
-theorizing (e.g. (Barney 1991; Teece, Pisano, and Shuen 1997)). However, the dominance of
-the firm-level explanations have been partly refuted by later scholars finding the sum of
-indirect and direct effects from industry to be of more importance than previously
-indicated by (Mcgahan etc). Moreover, the industry effect is also more time invariant
-(i.e. more stable) compared to firm level effects. Recent findings also suggest that there
-are considerable interaction effects between industry and the firm indicating that
-industry membership works directly at performance as well as indirectly through affecting
-the firm. However, little or no explanations are made for the mechanisms of this
-interaction.In other words, industry factors matter alas less than firm-level factors, and
-the indirect link from industry-level through firms are in need of further development.
-
-One way of looking at this is to consider the dynamic capabilities of the firm. Although
-an increasing consensus focuses on these dynamic capabilities as the ability to create,
-extend and modify firm resources in the face of change, there still looms an important
-stream of literature suggesting that dynamic capabilities can materialize as management
-actions (ref eisenhardt, peteraf, helfat). A management action aimed at strategic change
-will very often entail "resource orchestration" as broadly discussed in the literature
-(Helfat etc). But, strategic change are also found to come about from adapting and
-changing the positioning of the firm within its industry (ref) or simply refocusing its
-focal industry (ref). In other words, when a firm with excellent dynamic capabiliites
-senses and seizes opportunities within its domain, the implementation of strategic change
-will often both entail a considerable share of "asset orchestration" (helfat etc) as well
-as management actions directed at positioning within its industry (ref). One way to
-illustrate this is to consider Microsofts strategic change from operating system to cloud
-provider. CEO Satya Nadela and his team was able to restart the business by creating,
-extending and modifying the resources of the firm, including new skills, routiens and
-hardware, as a response to a growing demand for cloud computing (ref nadellas
-book). Meanwhile, his vision and formulated strategy also direclty put the company into a
-new industry, or at the very least reshaped the position they were already in. While
-Microsofts dynamic capabiliites worked significantly through "resource orchestration",
-the sensing and seizing of the management also ordered a direct re-positioning at the same
-time.
-
-Moreover, The link between firm resources and competitive advantage is determined by the
-extent to which resources are valuable and difficult to imitate \citep{Barney1991a}. This
-principle is also used to evaluate how higher order capabilities (e.g. dynamic
-capabilities \citep{Winter2003,Collis1994,Teece2007}. Hence, for a direct link to exist
-the dynamic capabilities of the firm will have to be valuable and difficult to
-imitate. This is an area of certain contention in the literature \citep{Peteraf2013} which
-we get back to below, but an increasing majority is arguing that dynamic capabilities
-reflect more complex processes that co-evolve with responses to market changes over time
-and hence creating idiosyncratic capabilities that are unique, valuable and hard to copy
-\citep{Helfat2007,Arndt2018}. Consequently, they are likely to lead to competitive
-advantage.
-
-In most cases such direct effects between dynamic capabilities and strategic change
-resulting in competitive advantage, are combined with the indirect effects (i.e. resource
-orchestration). To test this proposition empirically is hard, but one hypothesis following
-from this is related to the role of mediators. if a direct path does not exist, the
-relationship between dynamic capabilities and competitive advantage would be fully
-mediated by the proper set of firm resources.
-
-\emph{H1: The existence of a direct path from dynamic capabilities to competitive advantage
-suggest that full mediation is not present}
-
-Even if the dynamic capabilities of the firm themselves are not valuable and inimitable as
-needed to create competitive advantage, the underlying resources of the firm may very well
-be. Such resources in the form of operating routines or capabilities can in turn stem from
-an inherent learning process evolutionary distinct to the firm. Operating routines can
-thus lead to competitive advantage because of their evolutionary character
-\citep{Nelson1982,Winter2003}. To the extent operating routines stems from idiosyncratic
-evolutionary process of individual firms rather than being the result of best practices,
-they can satisfy the VRIO condition and thus be a source of competitive advantage.  Hence,
-through "resource orchestration" a firm with non-valuable dynamic capabilities can achieve
-competitive advantage through the indirect path. The flip side of this is that a valuable
-dynamic capability would not be able to create competitive advantage by orchestrating
-non-valuable resources. Consequently, the mediation effects of underlying resources is
-dependent on the nature of the resource - it being valuable and inimitable or not.
-
-\emph{H2a: When dynamic capabilities are being mediated by VRIO resources the firm can
-  achieve competitive advantage}
-
-\emph{H2a: When dynamic capabilities are being mediated by VRIO resources the firm can not
-  achieve competitive advantage}
-
-DEspite a growing consensus on the nature of dynamic capabilites, a serious contention is
-presen tin the literature \citep{Peteraf2013}. This stems from different notions of
-dynamic capabilities in the two "founding" papers of the theory, \cite{Eisenhardt2000} and
-\cite{Teece1997}.
-
-One strand of contributions sees DC as routines that are simple in nature and more as best
-practices to consider \citep{Eisenhardt2000}. Thus, dynamic capabilities are more like
-behavioral patterns and less idiosyncratic to the firm and will consequently not be able
-to satisfy the VRIO condition for competitive advantage to emerge. Dynamic capabilities as
-such routines are short lived, unstable and “substitutable” (ibid, p 1110) thus violating
-a key VRIO condition, and they are more “more homogeneous (..) than is usually assumed”
-(ibid, 1116). However, the simplicity of simple rules also makes them faster do deploy and
-put in motion, albeit potentially unstable. To the extent dynamic capabilities manifest
-themselves as simple rules they cannot alone create competitive advantage, but could very
-well generate strategic change by facilitating the process of resource orchestration.. In
-other words, even if dynamic capabilities play out as simple rules that are not in
-themselves satisfying the VRIO condition, the way they work through creating, extending
-and modifying firm resources, can still yield competitive advantage through orchestrating
-VRIO resources.
-
-On the other hand, \cite{Teece1997} and others \cite{Helfat2007} argue that dynamic
-capabilities will rather invariably be VRIO due to the evolutionary nature of their
-development \citep{Arndt2018,Peteraf2013}. Arguing that dynamic capabilities reflect more
-complex processes that co-evolve with responses to market changes over time and hence
-creating idiosyncratic capabilities that are unique, valuable and hard to copy
-\citep{Helfat2007,Arndt2018}. Consequently, they are likely to satisfy the VRIO condition
-and thus leading to competitive advantage.
-
-The contention between these streams of literature is most explicit in highly dynamic
-environments (distefano, peteraf) suggesting that environmental dynamism could play into
-the presence of direct and indirect linkages between dynamic capabilities and competitive
-advantage. This is also supported in previous empirical literature \citep{Schilke2014}.
-This could suggest that dynamic capabilities exhibit different characteristics under
-various levels of environmental dynamism. This is also suggested by Eisenhardt blaboblabla
-arguing that under moderatly dynamism dynamic capabilities takes the form of best
-pracitces (e.g. aquisition targeting) and is less important than under more dynamic
-environments. However, albeit best practices, the way they are implemented in the factor
-markets are still idiosyncratic. And taken into conjunction with the routinzed process of
-changing underlying routines, VRIO will very likely emerge under more stable
-conditions. It is not that the market/direct expression of dynamic capabilities are not
-present in stable environments, rather it is less pronounced and the indirect mediated
-effect (evolutionary path) is more important. In other words, it is not neither nor, but
-degrees of importance.
-
-\emph{H3: The mediation effects of underlying resources is dependent on the environmental
-dynamism facing the firm }
-
-%% Increasingly the literature remain focused on an \emph{indirect
-%%   path} between dynamic capabilities and competitive advantage
-%% \citep{Barreto2010,Schilke2018}. The theory behind this path goes back to the core of
-%% dynamic capabilities where resource orchestration happens as a response to changes in the
-%% environment. When markets, technologies or other external factors changes, firms with high
-%% levels of dynamic capabilities are able to seize opportunities for changes, seize these
-%% opportunities and transform the resource base to fit the strategic change needed to stay
-%% competitive \cite{Teece2007}. This ability to adapt is by some coined \emph{evolutionary
-%%   fitness} defined as BLABLBALBA and stems from the ability of the firm to reconfigure
-%% resources in the face of change. The extant literature, however, is less clear on how the
-%% nature of the underlying resources matter in this indirect path. On the one hand we can
-%% see
-
-%% Following REF suggesting more reseaarch on dynamic capabilities should put forth
-%% competeing hypotheses we propose these first
-
-%% We introduce the notion of multilevel VRIO to integrate the interactions between different
-%% types of capabilities at different levels. This entails that dynamic capabilities (the
-%% high level) can consist of complex and evolutionary characteristics that are idiosyncratic
-%% to the firm and hence VRIO by definition along the lines of how the concept is understood
-%% by \cite{Teece1997}. On the other hand dynamic capabilities can also take the shape of
-%% simpler routines which are short lived, unstable and substitutable thus violating a key
-%% VRIO condition. This follows the notion of dynamic capabilities found in
-%% h\cite{Eisenhardt2000} arguing that they are more “more homogeneous (..) than is usually
-%% assumed” (EM: 1116).
-
-%% Moreover, these dynamic capabilities are in the extant literature argued and found to work
-%% directly \citep{Kor2005,Eriksson2014,Schilke2018} on competitive advantage which suggests
-%% that they are indeed VRIO. On the other hand, a growing body of literature (ref) as well
-%% a consensus on the definition of dynamic capabilities (ref), holds that they can lead to
-%% competitive advantage by changing underlying resources and routines. In this
-%% \emph{indirect path} the dynamic capabilities itself need not be VRIO as long as the
-%% underlying resources themselves are.
-
-%% \subsection{The role of dynamism}
-
-%% The most contentious issue in the current debate on dynamic capabilities is how their
-%% nature varies with the environment.
-
-%% If htey are indeed latent
-
-%% The lower level resources and routines are to be understood as conventional resources in
-%% line with the resources-based view
-
-%% WHAT IS THE ROLE OF DIRECT VS INDIRECT, HOW DOES IT RELATE TO THE ENVIRONMENT, AND WHAT
-%% ROLE DOES THE TYPE OF UNDERLYING RESOURCE PLAY
-
-%% Conventional dc literature has argued for both indirect and direct links. Indeed both
-%% have been found, but while the indirect link is well rooted in the theory, the direct link
-%% is to our knowledge less clear. The core idea of DC is that it works to modify underlying
-%% resources as a response to changes in the environment and hence creating strategic change
-%% needed to stay competitive. This resource orchestration is heavily represented in the
-%% literature (ref) and through this process firms are able to generate CA. In such instances
-%% the CA can stem from VRIO resources and/or VRIO DC. A VRIO DC would mean that the firm is able
-%% to shuffle and reorganize generic resources in a way that creates a new and unique
-%% configuration of resoures idiosyncratic and valuable to the firm. In such instances, the
-%% outcome whould be CA. On the other hand, the DC may not by itself be VRIO but rather a set
-%% of simple routines put in motion to change, but if the resources they reconfigure are
-%% themselves VRIO, the outcome could just as eqsily be a competetive advantage. this
-%% equfinaity is discussed in the literaure \cite{DiStefano2010} and makes it hard to
-%% distingusih between the role of DC and ordinary capabilites in generating CA.
-
-%% Furtemore, Considering a direct link between DC and CA, DC it self must consist of some
-%% VRIO characteristics to garner CA. So in owther words, when is DC working directly and
-%% indirectly_
-
-%% How are dynamic capabilities working directly on competitive advantage? The microfoundations of dynamic capabilities explicated by \cite{Teece2007} is a useful
-%% point of departure of this theoretical inquiry. He hold that for "analytical purposes,
-%% dynamic capabilities can be disaggregated into the capacity (1) to sense and shape
-%% opportunities and threats, (2) to seize opportunities, and (3) to maintain competitiveness
-%% through enhancing, combining, protecting, and, when necessary, reconfiguring the business
-%% enterprise’s intangible and tangible assets". Sensing and seizing is a part of what we
-%% would coin the "opportunity capture" of dynamic capabiliites, where as reconfiguring
-%% concerns itself with the "resource orchestration" needed to change assets to stay
-%% competetive.
-
-%% Hence, when considering indirect and direct paths to compettetive advantage we will have
-%% to be clear on two fronts: Are DC themselves VRIO and are the underlying resources and
-%% routines central to the resource orchestration, VRIO.
-
-%% >
-
-%% The microfoundations of dynamic capabilities—the distinct skills, processes, procedures, orga- nizational structures, decision rules, and disciplines—which undergird enterprise-level sensing, seizing, and reconfiguring capacities are difficult to develop and deploy.
-%% For analytical purposes, dynamic capabilities can be disaggregated into the capacity (1) to sense and shape opportunities and threats, (2) to seize opportunities, and (3) to maintain competitiveness through enhancing, combining, protecting, and, when necessary, reconfiguring the business enter- prise’s intangible and tangible assets.
-
-OC som mindset / non-vrio? organizational mindset
-DC influcences IOC 
-DC influences VOC
-
-two paths / changes resources vs change mindset
-
-why so interested in operating routines resources, what about other mechanisms
-Can dc change collective cognition?
-
-ENTP - EO coen and slevin
-
-%%        name Mean_est     t
-%% 3   DC -> P    0.396 6.157
-%% 4   DC -> R    0.416 8.104
-%% 5 DC -> CA1    0.239 4.018
-%% 8  P -> CA1    0.172 2.724
-%% 9  R -> CA1    0.081 1.262
-%% > R
-%%        Path   LOW     t  HIGH     t
-%% 1 DC -> CA1 0.417 6.585 0.144 1.513
-%% 2   DC -> R 0.388 6.078 0.534 7.525
-%% 3  R -> CA1 0.017 0.219 0.211 2.123
-%% > P
-%%        Path   LOW     t  HIGH     t
-%% 1 DC -> CA1 0.355 4.805 0.133 1.379
-%% 2   DC -> P 0.386 5.294 0.436 4.663
-%% 3  P -> CA1 0.155 2.193 0.232 2.315
-%% > B
-%%        name R_LOW_est   t.x R_HIGH_est   t.y
-%% 1 DC -> CA1     0.355 5.407      0.044 0.400
-%% 2   DC -> P     0.376 3.729      0.432 4.668
-%% 3   DC -> R     0.366 5.569      0.522 7.225
-%% 4  P -> CA1     0.158 1.989      0.220 2.357
-%% 5  R -> CA1     0.010 0.135      0.200 2.033
-%% >
-
-%% %% creating and One example
-%% %% is the role of post-acquisition routines where routines to identify and deal with
-%% %% acquisition partners are a source of generating strategic change (Eisenhardt and Sull
-%% %% 2001, ref). Another example is (see refs from Schilke 2018). The functioning of this
-%% %% expression of dynamic capabilities are more latent and hence mainly observable ex
-%% %% post. Hence we can see this as direct route to competitive advantage as this expression of
-%% %% dynamic capabilities work directly in the factor market in capturing resources
-%% %% needed for strategic change. We coin this direct connection as the \emph{market path}.
-
-%% On the other hand, a stream of contributions see dynamic capabilities as evolutionary and
-%% more complex routines (ref) or processes (ref) set to change underlying capabilities in
-%% the face of changing conditions (TPS). This notion stems from evolutionary economics
-%% \citep{Winter2003,Nelson1982} and the behavioral theory of the firm \citep{Cyert1963}
-%% holding that path dependency and complex processes for changing underlying operating
-%% routines are a source of competitive advantage for the firm. Along this indirect path
-%% change is gradual and running through changes in underlying routines. We coin this the
-%% \emph{evolutionary path}.
-
-%% These paths from dynamic capabilities to competitive advantage are different expressions
-%% of dynamic capabilities with different mediums of intermediation. The \emph{market path}
-%% works in the market and his hence not typically altering lower order capabilities and
-%% resources in the firm directly, but rather acquiring new ones. The source of competitive
-%% advantage along this path stems from the interaction with the other, \emph{evolutionary
-%%   path} in a dynamic bundle \citep{Peteraf2013}. Such interactions create a bundle of
-%% capabilities and routines that are socially complex and hard to imitate
-%% \citep[p. 320]{DiStefano2014}. Moreover, the interactions between the two paths of dynamic
-%% capabilities is separable with respect to what intermediation exist. Consequently,
-%% separate paths exist albeit a part of a dynamic bundle.
-
-%% \cite{DiStefano2014} propose an integrated framework where simple routines and more
-%% complex processes could contribute simultanously to the firms outcome, specifically its
-%% competitive advantage. In this framework, coined the "organizational drivetrain" the
-%% authors envision the movement of an organization as set in motion by a drivetrain system
-%% not unlike that of a bicycle.
-
-%% Building on the notion of an organizational drivetrain we argue that dynamic capabilities
-%% can indeed impact the organizational movement or change through two distinct but
-%% interconnected mechanisms (i.e. the crank set and the rear shifter). The two mechanisms
-%% consitutting the drivetrain is consistent with our notion of \emph{evolutionary path} and the \emph{market path}. The
-%% evolutionary path is instigated by more complex processes setting in motiong a chance in
-%% the lower order (operational) routines \cite{Collis1994,Winter2003}. In the drivetrain
-%% metaphor this path corresponds to change stemming from the front crank set of thich there
-%% are fewer gears, but with larger impact. This path is slower
-%% and yields a more idiosyncratic set of organizational routines which is very much in line
-%% with the idea put forth in the seminal founding papers \citep{Teece1997,Winter2003}.
-
-%% Seeing the bike rider and her efforts to handle the levers of control (i.e. the gear
-%% shifter) as the dynamic capability, and consider it not only as a management effort, but
-%% that of the organization as a whole. The process of changing front gears are more profound
-%% (i.e. evolutionary) and costly, and it is for larger and slower strategic
-%% changes. Operating with simple routines in factor markets, however, is quicker and the
-%% rider does this on a more frequent basis with less effort.
-
-%% H1: Dynamic capabilities works to create competitive advantage through two distinctly
-%% different paths.
-
-%% \subsection{The two paths of dynamic capabilities}
-%% The objective of strategic change is to enhance a firm’s competitive advantage
-%% (ref). Doing so over time makes for the evolutionary fitness of the firm
-%% \citep{Helfat2007}. When firms are developing capabilities for strategic change through
-%% creating, extending and modifying the resource base this means making decisions to develop
-%% operational routines. Such routines can in turn stem from an inherent learning process
-%% evolutionary distinct to the firm. Operating routines can thus lead to competitive
-%% advantage because of their evolutionary character \citep{Nelson1982,Winter2003}. To the
-%% extent operating routines stems from idiosyncratic evolutionary process of individual
-%% firms rather than being the result of investments in factor markets, they can satisfy the
-%% VRIO condition and thus be a source of competitive advantage. In such instances, dynamic
-%% capabilities work through operating routines in creating competitive advantage. This
-%% indirect impact on competitive advantage is very much at the core of the DC literature
-%% (ref). Firms with high dynamic capabilities will be able to better change operating
-%% routines to facilitate strategic change in response to changing conditions facing the
-%% firm. Dynamic capabilities then creates VRIO operating routines and hence competitive
-%% advantage. When this happens, firms changes their operating routines in a evolutionary
-%% making operating routines themselves OR itself satisfies the VRIO condition.
-
-%% \emph{H2: Dynamic capabilities has an indirect effect on competitive advantage through
-%%   changing the operating routines of the firm.}
-
-%% On the other hand, resources and capabilities can to a certain extent be captured in
-%% factor markets through investment decisions (ref) or through alliances (ref) or M\&A
-%% activates (ref). By acquiring resources through investments, the operating routines of the
-%% firms may not be directly affected. When these acquisitions happen as a response to
-%% systematic resource orchestration (ref), i.e. reshaping the resource mix to obtain
-%% coordinated resource deployments \citep{Kor2005,Pan2006}, they would indeed have potential
-%% performance implications for the firm. Moreover, when this process of resource acquisition
-%% process of DC develops a way to acquire and mix resource for the purpose of adapting to
-%% change, the resources themselves would not necessarily satisfy the VRIO condition. The way
-%% in which this happens may be much harder to imitate due to the complexities such routines
-%% exhibit. Although resources themselves exhibit clear equifinality in their impact on
-%% competitive advantage, combined with the simple routines of the orchestration
-%% (i.e. dynamic capabilities), the sum would likely satisfy the VRIO condition. This is
-%% especially true if routines are deployed rapidly in changing market conditions. In other
-%% words, there are several ways in which resources can be orchestrated to generate CA,
-%% whereas improved OR will always mean improved competitiveness et ceteris paribus. In such
-%% instances DC itself can lead to CA directly.
-
-%% \emph{H3: Dynamic capabilities has a direct effect on competitive advantage through the
-%%   process of resource orchestration and acquisition of resources in factor markets.}
-
-%% In other words, we would expect DC to have both a direct and an indirect impact on CA. The
-%% indirect impact stems from the \emph{evolutionary path} of complex processes, whereas the
-%% direct impact stems from the \emph{market path}.  Although both the direct and the
-%% indirect path stems from DC creating, extending and modifying the resource base (OR or
-%% factor market resources), the difference in the path’s stems from to what extent the
-%% mediating construct alone can by itself satisfy the VRIO condition. Operating routines
-%% can, due to their evolutionary nature, in turn shaped by DC, achieve CA
-%% \citep{Collis1994,Winter2003}. Factor market resources and market acquired capabilities
-%% and best practices can not \citep{Eisenhardt2000,Peteraf2013}, but in conjuncture with the
-%% routines of acting in factor markets as well as the speed of deployment, the sum of
-%% dynamic capabilities and factor market action would lead to competitive advantage.
-
-%% However, the interlinkages between simple routines (the market path) and the coplex
-%% processes (the evolutionary path) would vary with the environment.
-
-%% \subsection{Interplay under environmental dynamism}
-
-%% \cite{DiStefano2014} note that "even if specific simple rules are unstable and ephemeral,
-%% the system as a whole is not" and that the "real source of sustainable competitive ad- vantage for an enterprise is the difficulty of imitating and substituting for the entire dynamic bundle that the system represents" (p.sss).
-
-%% But the interlinkages between the parts of the system (the evolutionary- and the market
-%% path), are likely to vary with the environmental dynamism. Under moderatly dynamism
-%% dynamic capabilities takes the form of best pracitces (e.g. aquisition targeting) and is
-%% less important than under more dynamic environments. However, albeit best practices, the
-%% way they are implemented in the factor markets are still idiosyncratic. And taken into
-%% conjunction with the routinzed process of changing underlying routines, VRIO will very
-%% likely emerge under more stable conditions. It is not that the market/direct expression
-%% of dynamic capabilities are not present in stable environments, rather it is less pronounced and the indirect
-%% mediated effect (evolutionary path) is more important. In other words, it is not neither
-%% nor, but degrees of importance.
-
-%% Moreover, in high velocity environments the role of the evolutionary path tends to
-%% weaken as such path-dependent changes occur slower compared to the market path. From the
-%% market path with its simple routines we can argue that creation of "new knowledge” to
-%% “allow for emergent adaptation” (EM, p. 1116) is the consequence. Consequently, the market
-%% path is stronger and more prevalent under higher levels of environmental dynamism.
-
-%% \emph{H4: Dynamic capabilities works relatively stronger through the market path in highly
-%% dynamic environments.}
-
-\begin{figure}
-  \centering
-  \captionsetup{width=0.5\linewidth}
-  \includegraphics[width=0.5\linewidth]{./figure/fig2.png}
-  \captionof{figure}{Dynamic capabilities direct and indirect paths to competitive advantage determined by the VRIO condition}
-  \label{fig:fig2}
-\end{figure}
-
-Figure \ref{fig:fig2} illustrates the two proposed paths through which DC affect
-competitive advantage. The main take away from this is that dynamic capabilities can
-affect CA through changing operational routines that by themselves can satisfy the VRIO
-condition by means of their evolutionary nature. Thus, we hypothesize that operating
-routines mediates the relationship between dynamic capabilities and competitive advantage
-the evolutionary path. Conversely, the same dynamic capabilities enable the firm to
-identify resources and capabilities in factor markets that are less idiosyncratic and
-often takes the shape of best practices that are definitely imitable and thus bot VRIO. In
-such instances, the VRIO condition is satisfied by the DC itself through its complex
-process of orchestrating and mixing resources – the market path.
+\subsection{Proactiveness as strategic cognition}
 
@@
 
-To test the relationships between dynamic capabilities and competitive advantage we need a
-proper metric of both. We also benefit vastly from studying the same firms over time.  The
-lack of h longitudinal studies to investigate dynamics over time and control for path
-dependency of organizational routines has been noted as permanent limitation for moving
-the DC literature forward empirically and theoretically \cite{Schilke2018}.
+To test the relationships between dynamic capabilities and competitive advantage, as well
+as the mediating effects on operational capabilities and strategic cognition, we need a
+proper metric of all. Particularly, it is useful to consider changes over time to capture
+the dynamic in the relationships and make for a more plausible causal argument to be put
+forth. The lack of longitudinal studies to investigate dynamics over time and control for
+path dependency of organizational routines has been noted as permanent limitation for
+moving the dynamic capabilities literature forward empirically and theoretically
+\citep{Schilke2018}.
 
 We collected survey data from R\&D active firms in Norway at two points in time
-($T_1=2005$ and $T_2=2014$). The population was all businesses registered to a scheme for
+($T_0=2005$ and $T_1=2014$). The population was all businesses registered to a scheme for
 tax deduction of R\&D costs (called SkatteFUNN). As all enterprises which are eligible for
@@
 enterprises include close to all enterprises which are involved in such activities at the
-time of our study.
+time of our study. The context of R\&D active firms is particularly relevant for studying
+dynamic capabilities because R\&D activity is a signal of responsiveness to change and
+that the firms are located in industries with a certain level of dynamism.
 
-All firms that registered R\&D activities during May to December 2005 were approached
-totaling in all 1721 firms. A web-based questionnaire was developed containing the
-measures of the key constructs of this paper. A link to the questionnaire was e-mailed to
-the firms within a month after they registered R\&D activities. The initial mailing was
-followed by two e-mail reminders. Of the firms approached, 1199 (70 \%) returned filled-in
-questionnaires. The 1199 companies that filled out the questionnaire were contacted again
-9 years later. The majority of firms were contacted in spring/summer 2014. All received a
+We contacted all the firms that were registering R\&D activities during May to December
+2005 yielding a total of 1721 firms. Using a web-based questionnaire we included items to
+measure the key constructs of this paper. Each firm received an email with a link to the
+questionnaire within a month after their registration for the R\&D tax credit. This
+initial contact was followed by two subsequent email reminders. A total of 1199 (70 \% of
+the initial sample size) answered and returned the questionnaire. In the second phase of
+the study each of these 1199 were contacted again in 2014, 9 years later, with the lion
+share of the firms contacted during the spring and summer of 2014. All received a similar
 web-based questionnaire containing the same measures of the focal constructs of this
@@
 
-All the firms in the sample was identifiable by means of the official firm
+All the firms in the sample were identifiable by means of the official firm
 identifier. This enabled us to attach financial data from the annual accounts of the firms
@@
 financial accounts from the National Firm Registry (BRREG) for all years between 2007 and
-2014 (prior to 2007 was not accessible through our database).-
+2014 (prior to 2007 was not accessible through our database). By including data from a
+second source, we aim to remedy to known short comings of similar
+contributions. See the section of control variables for short
+discussion.
+
+%% First, we
+%% remedy some of the problems possibly arising from common method bias (ref) and
+%% BLABLABLA. Capturing the same aspect of competitive advantage from several sources
+%% (i.e. both from our survey as well as through the reported profit margin from the
+%% Norwegian Firm Registry) makes the findings more reliable in terms of not relying solely
+%% on the perception of the respondents in the survey, but controlling for more objective
+%% metrics with similar characteristics. Particularly, controlling for factors such as firm
+%% profitability and balance sheet size, MORE HERE. Second, a common critique of the dynamic
+%% capabilities - competetive advantage relationship is that they both have a common
+%% confounded in simply coming from being a 'good firm'. In other words, critics argue that
+%% the reason we find strong relationships between these two are that they are the same and
+%% we are simply regressing $X$ on $X$. By including more objective measures of what
+%% constitutes a 'good firm' (e.g. profitability) we partly get at the common
+%% critique. Combined with a time lag both between $X$ (dynamic capabilities) and $Y$
+%% (competitive advantage), as well as $Y$ observed over time, we at least partly control for
+%% common factors. Moreover, we add robustness checks for endogeneity as a n extra layer of
+%% certainty (see the result section).
 
@@
 
-The focal constructs of this paper are dynamic capabilities, operational routines and
-competitive advantage. These are all operationalized using the survey data described
-above. Table 1 below describes the items used to operationalize the focal constructs and
-their internal validity in forming an additive index (Cronbach´s alpha). The results show
-that our key constructs can be represented by the items in the survey.
+The focal constructs of this paper are dynamic capabilities,
+operational capabilities, strategic cognition as measured by
+proactiveness, and competitive advantage. These are all
+operationalized using the survey data described above. Table
+\ref{tab:item} in the appendix describes the items used to
+operationalize the focal constructs and their internal validity as
+measured by Dillon-Goldstein Rho which is the preferred metric for
+this purpose \citep{Hair2019}. The results show that our key constructs
+can be represented by the items in the survey, with a minor
+caveat. The measure of strategic cognition as proactiveness loads only
+partly on one item (item 3). Statsistically, a loading of
+$\Sexpr{l[["lcog"]][3]}$ is on the weaker side of traditional 'rules
+of thumb' \citep{Hair2010}, but from a theoretical stand point the
+measure makes sense and is established in the literature (REF to EO).
 
 There are no established measurement models of dynamic capabilities
-\citep{McKelvie2009,Schilke2018}. Therefore this study builds on a mixture of qualitative
-case study methodology, literature review and statistical techniques to develop and refine
-measures of DCs. First, exploratory qualitative interviews, using a semistructured
-interview guide, were conducted with management representatives from 10 R\&D/innovative
-firms. The aim of the interviews was to get an overview of each firm's innovation and
-development processes, in particular the processes related to its dynamic capabilities and
-the management of its resources. Themes raised in the interviews were about network,
-co-operation with external R\&D-institutions, learning in the firm, adaptation and changes
-in the firm. We interviewed SMEs and larger firms, and the industries varied from
-high-tech and ICT to publishing.  Based on the interviews and an extensive literature
-review, statements identified as descriptions of dynamic capabilities and resources were
-developed and included in a questionnaire.
+\citep{McKelvie2009,Schilke2018}.Therefore this study builds on a
+mixture of qualitative case study methodology, literature review and
+statistical techniques to develop and refine measures of DCs. First,
+exploratory qualitative interviews, using a semistructured interview
+guide, were conducted with management representatives from 10
+R\&D/innovative firms. The aim of the interviews was to get an
+overview of each firm's innovation and development processes, in
+particular the processes related to its dynamic capabilities and the
+management of its resources. Themes raised in the interviews were
+about network, co-operation with external R\&D-institutions, learning
+in the firm, adaptation and changes in the firm. We interviewed SMEs
+and larger firms, and the industries varied from high-tech and ICT to
+publishing.  Based on the interviews and an extensive literature
+review, statements identified as descriptions of dynamic capabilities
+and resources were developed and included in a questionnaire.
 
@@
 
-Items measuring DC and OCs were developed as statements for which the respondents were
-asked to indicate to what extent each statement fitted a description of their business. We
-adopted one-sided seven point Likert scale where: 1 = strongly disagree and 7 = strongly
-agree. We built on prior studies where items measuring OCs have been measured relative to
-competitors \citep{McKelvie2009}.
-
-<<result1, results="asis", echo=FALSE >>=
-
-ht
-
-@
+Respondents were asked to indicate to what extent each statement fitted a description of
+their business. We adopted one-sided seven point Likert scale where: 1 = strongly disagree
+and 7 = strongly agree. We built on prior studies where items measuring OCs have been
+measured relative to competitors \citep{McKelvie2009}.
 
@@
 constructs. From the survey we add firm size, firm age, the level of dynamism facing the
-firm. Size is the reported number of employees in the firm at $T_2$, and age is the number of
-years since establishment. Dynamism is captured by asking a number of questions about the
-competitive environment facing the firm. A full list of items and their internal validity
-(0.75) is available in appendix 1111.
+firm. Size is the reported number of employees in the firm at $T_1$, and age is the number of
+years since establishment.
 
@@
 the firm´s profit and loss statements, and balance sheet. Specifically, we add the natural
-logarithm of the assets and debt of the firm to capture the leverage (debt risk) of the
-firm, as well as the capital intensity.
+logarithm of the assets to capture the capital intensity of the firm.
 
@@
 
-To test our hypotheses, we run a sequential linear regression with heteroskedastic robust
-standard errors. We test the mediation hypotheses within this framework using a causal
-mediation \citep{Baron1986,MacKinnon2008} with quasi-Bayesian confidence intervals and
-over a million simulations \citep{Imai2010}.
+Our empirical model is a mediation analysis where operational
+capabilities and proactiveness acts as mediators of the dynamic
+capabilities-competitive advantage relationship. Our data is for the
+larger part survey based with some controls gathered from registry
+data (particularly the Norwegian Company Registry). The total sample
+size of the paper is $N=262$ which makes it very suited for a latent
+variable analysis using Partial Least Squares - Structural Equation
+Modeling (PLS-SEM) \citep{Hair2010}. Particularly, PLS-SEM is useful
+when studying theoretical extensions of established theories, when the
+sample size is small, when the structural model includes many
+constructs and indicators, and when distribution issues are a concern
+\citep{Hair2019}. Indeed, the use of PLS-SEM is increasingly taking
+hold in strategic management research \citep{Hair2012}.
 
-In addition we estimate mediating models and test formally for mediation using the Baron
-\& Kenny method \citep{Baron1986,MacKinnon2008}. We estimate two mediating model to test
-if OR mediates the effect of DC on CA, and if DC mediates the effect of DL on OR,
-respectively.
+As we work with latent constructs we needed to handle missing values
+in the measurement model. Each latent variable consists of several
+observable indicator variables and the latent variable will drop an
+observation if one of the indicators are missing. Thus, to reduce the
+number of missing observations we ran a two-step validation process
+when constructing the latent variables. First, we established a
+theoretical structure based on theory and tested the constructs
+accordingly by evaluating the internal validity using Cronbachs alpha
+and composite reliability index (joreskog 1971). In this first step we
+used only observations where all indicators were complete (i.e. no
+missing). Then we imputed the mean value of the other indicators when
+one indicator had a missing value. In the second step we reran the
+model and compared the reliability measures. None of the constructs
+changed materially, but the total sample size went from $N=262$ to
+$N=240$ because some of the constructs lacked more than one item,
+rendering the imputation challenging. In these cases we dropped the
+observation. As a robustness check we reran all the models using a
+Multivariate Imputation By Chained Equations (MICE) procedure which
+makes use of the whole sample to impute missing values where more than
+one underlying item is missing. This procedure did not change the
+results materially.
+
+The complete data used in the measurement model then comprised of
+$N=240$ observations. When adding the registry data from the Norwegian
+Company Registry, the sample sized declined somewhat to $N=206$. We
+ran all the models with and without the registry data without the
+focal relationship changing materially.
+
+To test our hypotheses we then built a path-model from the latent
+variables we constructed. This resulted in four models. The results
+from the structural model is reported in figure \ref{fig:res} and
+table \ref{tab:res}. To estimate the standard errors we ran
+simulations using bootstrapping and reported the simulation number,
+standard errors and corresponding p-values. To evaluate the models we
+compared $R^2$ and $Q^2$ statistics, as well as changes in Baysian
+Information Criteria (BIC) for model comparison. All these are
+reported in table \ref{tab:res}. Finally, we tested the model for
+nonlinear effets, endogeneity and unbserved heterogeneity using
+Ramsey, Gaussian Copula approach and Information Criteria test
+respectively. These results are available in the appendix.
+
+The estimated models is based on the following specification:
+
+\begin{align}
+  CA_{i,1} & = \alpha_0 + \alpha_1 CA_{i,0} + \omega_1 \alpha_2 CAP_{i,1}
+  + \omega_2 \alpha_3 COG_{i,1} + \alpha_{4} DC_{i,0} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + \epsilon_i \\
+  CAP_{i,1} & = \beta_0 + \beta_1 CAP_{i,0} + \beta_2 DC_{i,0} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + v_i\\
+   COG_{i,1} & = \eta_0 + \eta_1 COG_{i,0} + \eta_2 DC_{i,0} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1}+ u_i
+\end{align}
+
+$CA$,$CAP$,$COG$ and $DC$ indicates the consctruct for competetive
+advantage, operational capabilities, strategic cognition
+(proactiveness) and dynamic capabilities respectively. Subscript $i$
+refers to the firm and the second subscript indicates the time $t=0$
+or $t=1$. $\mathbf{\Gamma}_m$ is an $m \times 1$ vector of coefficients
+$\gamma_1$ to $\gamma_m$ for the control variables included in the
+model captured in  $\mathbf{C}^m_{i,1}$ which is a $i \times m$ matrix
+of controls. This generic model structure corresponds to four models
+by changing the parameters $\omega_1$ and $\omega_2$ which are
+indicator variables $\omega \in [0,1]$. Our base case model is
+$\omega_1 = \omega_2 = 0$ where only the direct effects from $DC$
+including the controls is captured. Models 2 and 3 captures the
+mediation effect of $CAP$ and $COG$ respectively ($\omega_1$ or
+$\omega_2 = 1$). Our final model captures the effect of both mediators
+($\omega_1 = \omega_2 = 1$).
+
+\section{Results}
+
+\begin{table}[t]\label{tab:cor}
+  \caption{Descriptive statistics and correlation between key constructs and control
+  variables.}
+  <<corchild, child='./figure/cortab.rnw',results="asis">>=
+@
+
+\end{table}
+
+\begin{table}[t]\label{tab:res}
+  \caption{PLS-SEM results for key constructs}
+
+  \scriptsize
+  <<child-demo, child='./figure/restab.rnw'>>=
+@
+   \begin{tablenotes}
+      \tiny
+      \item Standard-errors estimated using bootstrapping with 10 000 simulations.
+      \item Firm level control variables include firm size, firm age,
+        profit margin, firm assets.
+
+    \end{tablenotes}
+  \end{table}
+
+ <<pathchild, child='./figure/medanalysisall.rnw',results="asis">>=
+@
 
@@
 \section{Appendix}
+\newpage
+
+  \begin{table}\label{tab:items}
+    \caption{Core constructs and their measurement items. Factor
+      loadings in parantheses}
+    <<itemchild, child='./figure/itemtab.rnw',results="asis">>=
+    @
+    \begin{tablenotes}
+      \tiny
+      \item Dillon-Goldstein Rho is recommended as reliability measure
+        for SEM-PLS \citep{Hair2019}.
+    \end{tablenotes}
+  \end{table}
 

### 2019-11-15 article4_analysis_v2.r

@@ -12,13 +12,15 @@ library(huxtable)
 library(semPLS)
 library(mice)
 library(mma)
+library(car)
+library(lmtest)
 #install.packages("semPLSModelSelection", repos="http://R-Forge.R-project.org")
 library("semPLSModelSelection")
                                         #library(polycor)
 
 ## This loads the data workspace where skattefunn_data.r is already loaded
 load("./data/art3base.RData")
-
+rm(list=setdiff(ls(), c("sfmain","regdf","regnskap")))
 ## Overall system settings
 options(digits=8)
 Sys.setlocale("LC_ALL", 'en_US.UTF-8')
@@ -116,13 +118,20 @@ rownames(zwadj) <- NULL
 
 
 setwd("/Users/larshovdanmolden/Documents/git/article4")
-alldc <- zwadj[,c("Q19a", "Q19c", "Q19d", "Q20b", "Q20c","Q19", "Q20d","Q20e","Q19b","Q20")]
+alldc <- zwadj[,c("Q19","Q19a", "Q19b","Q19c", "Q19d", "Q20","Q20b", "Q20c", "Q20d","Q20e")]
+alldc0 <- zwadj[,c("Q6.1_t1","Q6.2_t1","Q6.3_t1","Q6.4_t1","Q6.5_t1","Q6.7_t1","Q7.1_t1","Q7.2_t1","Q7.3_t1","Q7.4_t1")]
 
-## Running median imputations
-#dc01 <-  imputezw(zwadj[,c("Q6.4_t1", "Q6.5_t1","Q7.1_t1","Q7.2_t1")] )
-dc02 <-  imputezw(zwadj[,c("Q6.1_t1","Q7.3_t1","Q7.4_t1")] )
-#dc001 <- imputezw(zwadj[,c("Q19a", "Q19c", "Q19d", "Q20b", "Q20c")] )
-dc002 <-  imputezw(zwadj[,c("Q19", "Q20d","Q20e")] )
+alldc <- zwadj[,c("Q19","Q19c", "Q19d", "Q20b", "Q20c", "Q20d","Q20e")]
+alldc0 <- zwadj[,c("Q6.1_t1","Q6.4_t1","Q6.5_t1","Q7.1_t1","Q7.2_t1","Q7.3_t1","Q7.4_t1")]
+## Running median imputation
+
+## Running median imputation
[…]

### 2019-11-15 article4_jbr.rnw
WOrking on post hoc analysis

@@
 
-<<load, results="asis", echo=FALSE >>=
-
+<<loading, results="asis", echo=FALSE >>=
 setwd("/Users/larshovdanmolden/Documents/git/article4")
 library(xtable)
-#load("./data/resart4.RData")
+load("./data/resart4.RData")
 r <- main$resmat
@@
 l  <- main$loadings
+l <- main$loadings
+#foolars=0.99
+@
 
-foolars=0.99
-
-@
 %% Extant literature on dynamic capabilities is battling with a fundamental conception and
@@
 %https://journals.sagepub.com/doi/abs/10.1177/0971890717701781
-
+BLA
 Extant literature on dynamic capabilities are increasingly focusing on how firm resources
@@
 cognition is the result of a mental process that underlie internal
-audicences adoption of new strategic representation and identity code to move toward a
+audiences adoption of new strategic representation and identity code to move toward a
 new or existing goal \citep{Gavetti2012}. Although strategic cognition may lead to
@@
 
-The focal constructs of this paper are dynamic capabilities,
-operational capabilities, strategic cognition as measured by
-proactiveness, and competitive advantage. These are all
-operationalized using the survey data described above. Table
-\ref{tab:item} in the appendix describes the items used to
-operationalize the focal constructs and their internal validity as
-measured by Dillon-Goldstein Rho which is the preferred metric for
-this purpose \citep{Hair2019}. The results show that our key constructs
-can be represented by the items in the survey, with a minor
-caveat. The measure of strategic cognition as proactiveness loads only
-partly on one item (item 3). Statsistically, a loading of
-$\Sexpr{l[["lcog"]][3]}$ is on the weaker side of traditional 'rules
-of thumb' \citep{Hair2010}, but from a theoretical stand point the
-measure makes sense and is established in the literature (REF to EO).
+The focal constructs of this paper are dynamic capabilities, operational capabilities,
+strategic cognition as measured by proactiveness, and competitive advantage. These are all
+operationalized using the survey data described above. Table \ref{tab:item} in the
+appendix describes the items used to operationalize the focal constructs and their
+internal validity as measured by Dillon-Goldstein Rho which is the preferred metric for
+this purpose \citep{Hair2019}. The results show that our key constructs can be represented
+by the items in the survey, with a minor caveat. The measure of strategic cognition as
+proactiveness loads only partly on one item (item 3). Statsistically, a loading of
+$\Sexpr{l[["lcog"]][3]}$ is on the weaker side of traditional 'rules of thumb'
+\citep{Hair2010}, but from a theoretical stand point the measure makes sense and is
+established in the literature (REF to EO).
 
 There are no established measurement models of dynamic capabilities
-\citep{McKelvie2009,Schilke2018}.Therefore this study builds on a
-mixture of qualitative case study methodology, literature review and
-statistical techniques to develop and refine measures of DCs. First,
-exploratory qualitative interviews, using a semistructured interview
-guide, were conducted with management representatives from 10
-R\&D/innovative firms. The aim of the interviews was to get an
-overview of each firm's innovation and development processes, in
-particular the processes related to its dynamic capabilities and the
-management of its resources. Themes raised in the interviews were
-about network, co-operation with external R\&D-institutions, learning
-in the firm, adaptation and changes in the firm. We interviewed SMEs
-and larger firms, and the industries varied from high-tech and ICT to
-publishing.  Based on the interviews and an extensive literature
-review, statements identified as descriptions of dynamic capabilities
-and resources were developed and included in a questionnaire.
+\citep{McKelvie2009,Schilke2018}.Therefore this study builds on a mixture of qualitative
+case study methodology, literature review and statistical techniques to develop and refine
+measures of DCs. First, exploratory qualitative interviews, using a semi-structured
+interview guide, were conducted with management representatives from 10 R\&D/innovative
+firms. The aim of the interviews was to get an overview of each firm's innovation and
+development processes, in particular the processes related to its dynamic capabilities and
+the management of its resources. Themes raised in the interviews were about network,
+co-operation with external R\&D-institutions, learning in the firm, adaptation and changes
+in the firm. We interviewed SMEs and larger firms, and the industries varied from
+high-tech and ICT to publishing.  Based on the interviews and an extensive literature
+review, statements identified as descriptions of dynamic capabilities and resources were
+developed and included in a questionnaire.
 
@@
 their business. We adopted one-sided seven point Likert scale where: 1 = strongly disagree
-and 7 = strongly agree. We built on prior studies where items measuring OCs have been
-measured relative to competitors \citep{McKelvie2009}.
+and 7 = strongly agree. We built on prior studies where items measuring operating
+capabilities have been measured relative to competitors \citep{McKelvie2009}.
+
+The nine year lag between our points of measurement has its distinct advantages with
+respect to capturing long term trajectory of the firms. For example, the operating
+capabilities at time $t=1$ is very likely a function of operating capabilities at time
+$t=0$ as well as other factors such as dynamic capabilities. Indeed, extant literature
+argues for this path dependency of resources and routines
+\citep{Helfat2007,Winter2003}. These capabilities are said to be serial-correlated and
+path dependent. However, as dynamic capabilities and operating capabilities are distinctly
+different concepts, this kind of path dependency is also not equally clear in this
+regard. We could have firms with very high levels of dynamic capabilities at $t=0$ and
+equally a poorer level at time $t=1$. Because of the long time lag a lot of factors could
+have influenced this decline, and indeed a rather high number of over firms exhibit this
+characteristic of declining dynamic capabilities over time. As we regard dynamic
+capabilities as 'the first derivative' \citep{Winter2003} (i.e. the rate of change of the
+operating capabilites) a large initial value (at time $t=0$) could over estimate the
+expected change of the underlying capability at time $t=1$. Moreover, based on the scale
+applied (Likert from 1 through 7) a high initial value leaves nowhere to move but
+downwards. This is not to say that those firms are likely to develop poorer operating
+routines. Nor is to say that those with low dynamic capabilities at time $t=0$ are
+rendered useless in developing capabilities going forward towards $t=1$. Rather it
+suggests that a long time span may include unnecessary noise in the model. Thus, we
+estimated an average of the dynamic capabilities of the firm between time $t=0$ and $t=1$
+as a proxy for a more representative measure of the rate of change. Hence, our construct
+of $DC_0$ is actually a measure between times $t=0$ and $t=1$. As a robustness check we
+repeated the full analysis using 2005 measure as our $DC_0$. This did not severely alter
+the conclusions we draw in this paper, but had some minor effects on the significance of
+the path between $DC_0$ and $COG_1$. The full alternative analysis is included in the
+appendix.
 
@@
 
+All the constructs and the control variables are presented with descriptive statistics and
+pairwise correlations. The main estimation was tested for multicolinearity using the
+variance inflation test (VIF) with no severe multicolinearity detected. This is also
+suggested by the correlation matrix.
+
+\begin{table}[t]
+  \caption{Descriptive statistics and correlation between key constructs and control
+  variables.}
+\label{tab:cor}
+  <<corchild, child='./figure/cortab.rnw',results="asis">>=
+@
+
+\end{table}
+
 \subsection{Estimation and empirical model}
 
-Our empirical model is a mediation analysis where operational
-capabilities and proactiveness acts as mediators of the dynamic
-capabilities-competitive advantage relationship. Our data is for the
-larger part survey based with some controls gathered from registry
-data (particularly the Norwegian Company Registry). The total sample
-size of the paper is $N=262$ which makes it very suited for a latent
-variable analysis using Partial Least Squares - Structural Equation
-Modeling (PLS-SEM) \citep{Hair2010}. Particularly, PLS-SEM is useful
-when studying theoretical extensions of established theories, when the
-sample size is small, when the structural model includes many
-constructs and indicators, and when distribution issues are a concern
-\citep{Hair2019}. Indeed, the use of PLS-SEM is increasingly taking
-hold in strategic management research \citep{Hair2012}.
+Our empirical model is a mediation analysis where operational capabilities and
+proactiveness acts as mediators of the dynamic capabilities-competitive advantage
+relationship. Our data is for the larger part survey based with some controls gathered
+from registry data (particularly the Norwegian Company Registry). The total sample size of
+the paper is $N=262$ which makes it very suited for a latent variable analysis using
+Partial Least Squares - Structural Equation Modeling (PLS-SEM)
+\citep{Hair2010}. Particularly, PLS-SEM is useful when studying theoretical extensions of
+established theories, when the sample size is small, when the structural model includes
+many constructs and indicators, and when distribution issues are a concern
+\citep{Hair2019}. Indeed, the use of PLS-SEM is increasingly taking hold in strategic
+management research \citep{Hair2012}.
 
-As we work with latent constructs we needed to handle missing values
-in the measurement model. Each latent variable consists of several
-observable indicator variables and the latent variable will drop an
-observation if one of the indicators are missing. Thus, to reduce the
-number of missing observations we ran a two-step validation process
-when constructing the latent variables. First, we established a
-theoretical structure based on theory and tested the constructs
-accordingly by evaluating the internal validity using Cronbachs alpha
-and composite reliability index (joreskog 1971). In this first step we
-used only observations where all indicators were complete (i.e. no
-missing). Then we imputed the mean value of the other indicators when
-one indicator had a missing value. In the second step we reran the
-model and compared the reliability measures. None of the constructs
-changed materially, but the total sample size went from $N=262$ to
-$N=240$ because some of the constructs lacked more than one item,
-rendering the imputation challenging. In these cases we dropped the
-observation. As a robustness check we reran all the models using a
-Multivariate Imputation By Chained Equations (MICE) procedure which
-makes use of the whole sample to impute missing values where more than
-one underlying item is missing. This procedure did not change the
-results materially.
+As we work with latent constructs we needed to handle missing values in the measurement
+model. Each latent variable consists of several observable indicator variables and the
+latent variable will drop an observation if one of the indicators are missing. Thus, to
+reduce the number of missing observations we ran a two-step validation process when
+constructing the latent variables. First, we established a theoretical structure based on
+theory and tested the constructs accordingly by evaluating the internal validity using
+Cronbachs alpha and composite reliability index (joreskog 1971). In this first step we
+used only observations where all indicators were complete (i.e. no missing). Then we
+imputed the mean value of the other indicators when one indicator had a missing value. In
+the second step we reran the model and compared the reliability measures. None of the
+constructs changed materially, but the total sample size went from $N=262$ to $N=240$
+because some of the constructs lacked more than one item, rendering the imputation
+challenging. In these cases we dropped the observation. As a robustness check we reran all
+the models using a Multivariate Imputation By Chained Equations (MICE) procedure which
+makes use of the whole sample to impute missing values where more than one underlying item
+is missing. This procedure did not change the results materially.
 
-The complete data used in the measurement model then comprised of
-$N=240$ observations. When adding the registry data from the Norwegian
-Company Registry, the sample sized declined somewhat to $N=206$. We
-ran all the models with and without the registry data without the
-focal relationship changing materially.
+The complete data used in the measurement model then comprised of $N=240$
+observations. When adding the registry data from the Norwegian Company Registry, the
+sample sized declined somewhat to $N=206$. We ran all the models with and without the
+registry data without the focal relationship changing materially.
 
-To test our hypotheses we then built a path-model from the latent
-variables we constructed. This resulted in four models. The results
-from the structural model is reported in figure \ref{fig:res} and
-table \ref{tab:res}. To estimate the standard errors we ran
-simulations using bootstrapping and reported the simulation number,
-standard errors and corresponding p-values. To evaluate the models we
-compared $R^2$ and $Q^2$ statistics, as well as changes in Baysian
-Information Criteria (BIC) for model comparison. All these are
-reported in table \ref{tab:res}. Finally, we tested the model for
-nonlinear effets, endogeneity and unbserved heterogeneity using
-Ramsey, Gaussian Copula approach and Information Criteria test
-respectively. These results are available in the appendix.
+To test our hypotheses we then built a path-model from the latent variables we
+constructed. This resulted in four models. The results from the structural model is
+reported in figure \ref{fig:res} and table \ref{tab:res}. To estimate the standard errors
+we ran simulations using bootstrapping and reported the simulation number, standard errors
+and corresponding p-values. To evaluate the models we compared $R^2$ and $Q^2$ statistics,
+as well as changes in Baysian Information Criteria (BIC) for model comparison. All these
+are reported in table \ref{tab:res}. Finally, we tested the model for nonlinear effects,
+endogeneity and unbserved heterogeneity using Regression Equation Specification Error Test
+(RESET) , Gaussian Copula approach and Information Criteria test respectively. These
+results are available in the appendix.
 
@@
 
-$CA$,$CAP$,$COG$ and $DC$ indicates the consctruct for competetive
-advantage, operational capabilities, strategic cognition
-(proactiveness) and dynamic capabilities respectively. Subscript $i$
-refers to the firm and the second subscript indicates the time $t=0$
-or $t=1$. $\mathbf{\Gamma}_m$ is an $m \times 1$ vector of coefficients
-$\gamma_1$ to $\gamma_m$ for the control variables included in the
-model captured in  $\mathbf{C}^m_{i,1}$ which is a $i \times m$ matrix
-of controls. This generic model structure corresponds to four models
-by changing the parameters $\omega_1$ and $\omega_2$ which are
-indicator variables $\omega \in [0,1]$. Our base case model is
-$\omega_1 = \omega_2 = 0$ where only the direct effects from $DC$
-including the controls is captured. Models 2 and 3 captures the
-mediation effect of $CAP$ and $COG$ respectively ($\omega_1$ or
-$\omega_2 = 1$). Our final model captures the effect of both mediators
+$CA$,$CAP$,$COG$ and $DC$ indicates the consctruct for competetive advantage, operational
+capabilities, strategic cognition (proactiveness) and dynamic capabilities
+respectively. Subscript $i$ refers to the firm and the second subscript indicates the time
+$t=0$ or $t=1$. $\mathbf{\Gamma}_m$ is an $m \times 1$ vector of coefficients $\gamma_1$
+to $\gamma_m$ for the control variables included in the model captured in
+$\mathbf{C}^m_{i,1}$ which is a $i \times m$ matrix of controls. This generic model
+structure corresponds to four models by changing the parameters $\omega_1$ and $\omega_2$
+which are indicator variables $\omega \in [0,1]$. Our base case model is
+$\omega_1 = \omega_2 = 0$ where only the direct effects from $DC$ including the controls
+is captured. Models 2 and 3 captures the mediation effect of $CAP$ and $COG$ respectively
+($\omega_1$ or $\omega_2 = 1$). Our final model captures the effect of both mediators
 ($\omega_1 = \omega_2 = 1$).
@@
 \section{Results}
+The main results of our analysis are depicted both in the graphical path diagrams (figure
+\ref{fig:res}) and the regression table in table \ref{tab:res}. The empirical models are
+presented from left to right starting with the direct model. The main effect from $DC_0$
+to $CA_1$, controlled for $CA_0$, firm size, age, profit margin and assets, is positive
+and significant at the onset. Increasingly, by adding mediating variables as suggested by
+the theory, this effect diminishes to an extent suggesting that partial or full mediation
+is taking place. The effect decreases from BLA to BLA and turns insignificant. The
+mediating variables $CAP_1$ and $COG_1$ are both positive and significantly related to
+$CA_1$. This suggests that the effect between dynamic capabilities and competitive
+advantage is mediated by these two factors separately, as well as together. These findings
+both support H1 and H2. Moreover, the model becomes increasingly better both in terms if
+explanatory power ($R^2$), predictive power ($Q^2$) and the Bayesian Information Criteria
+(BIC).
 
-\begin{table}[t]\label{tab:cor}
-  \caption{Descriptive statistics and correlation between key constructs and control
-  variables.}
-  <<corchild, child='./figure/cortab.rnw',results="asis">>=
-@
-
-\end{table}
-
-\begin{table}[t]\label{tab:res}
+\begin{table}[t]
   \caption{PLS-SEM results for key constructs}
-
+\label{tab:res}
   \scriptsize
@@
         profit margin, firm assets.
-
     \end{tablenotes}
@@
 
+One striking finding, however, is that the improvement in the model between
+model 3 and 4 is neglectable, whereas it represents a considerable improvement between 2 and 3. This
+suggests that strategic cognition represents a stronger mediator than operational
+capabilities. However, the difference is too small to render further analysis all but
+conjecture on our part. Thus, we wanted found it necessary to explore the joint mediation
+between $CAP_1$ and $COG_1$.
+
+\subsection{Post-hoc analysis: joint mediation}
+
+From standard production theory we know that the isoquants
+between two factors of input rarely are angled (Leontief isoquants) suggesting that the
+factors are total complements to eachother. Rather there are trade offs between these
+factors suggesting a non-linear relationship. One way to investigate this is by means of
+joint mediation where (USE MODERATED MEDIATION RATHER). 
  <<pathchild, child='./figure/medanalysisall.rnw',results="asis">>=

### 2019-11-15 article4_analysis_v2.r

@@ -118,8 +118,8 @@ rownames(zwadj) <- NULL
 
 
 setwd("/Users/larshovdanmolden/Documents/git/article4")
-alldc <- zwadj[,c("Q19","Q19a", "Q19b","Q19c", "Q19d", "Q20","Q20b", "Q20c", "Q20d","Q20e")]
-alldc0 <- zwadj[,c("Q6.1_t1","Q6.2_t1","Q6.3_t1","Q6.4_t1","Q6.5_t1","Q6.7_t1","Q7.1_t1","Q7.2_t1","Q7.3_t1","Q7.4_t1")]
+#alldc <- zwadj[,c("Q19","Q19a", "Q19b","Q19c", "Q19d", "Q20","Q20b", "Q20c", "Q20d","Q20e")]
+#alldc0 <- zwadj[,c("Q6.1_t1","Q6.2_t1","Q6.3_t1","Q6.4_t1","Q6.5_t1","Q6.7_t1","Q7.1_t1","Q7.2_t1","Q7.3_t1","Q7.4_t1")]
 
 alldc <- zwadj[,c("Q19","Q19c", "Q19d", "Q20b", "Q20c", "Q20d","Q20e")]
 alldc0 <- zwadj[,c("Q6.1_t1","Q6.4_t1","Q6.5_t1","Q7.1_t1","Q7.2_t1","Q7.3_t1","Q7.4_t1")]
@@ -128,7 +128,7 @@ alldc0 <- zwadj[,c("Q6.1_t1","Q6.4_t1","Q6.5_t1","Q7.1_t1","Q7.2_t1","Q7.3_t1","
 ## Running median imputation
 dc02 <-  imputezw(zwadj[,c("Q6.4_t1", "Q6.5_t1","Q7.1_t1","Q7.2_t1")] )
 #dc02 <-  imputezw(zwadj[,c("Q6.1_t1","Q7.3_t1","Q7.4_t1")] )
-dc002 <- imputezw(zwadj[,c("Q19c", "Q19d", "Q20b", "Q20c")] )
+#dc002 <- imputezw(zwadj[,c("Q19c", "Q19d", "Q20b", "Q20c")] )
 dc02 <-  imputezw(alldc)
 dc002 <-  imputezw(alldc0)
 #dc002 <-  imputezw(zwadj[,c("Q19", "Q20d","Q20e")] )
[…]

### 2019-11-17 article4_jbr.rnw
Writing up conclusion

@@
 library(xtable)
+library(semPLS)
 load("./data/resart4.RData")
@@
 l  <- main$loadings
-l <- main$loadings
+ic <- data.frame(i[,c(1,4)]);colnames(ic) <- c("b","t")
+ic$rn  <- 1:nrow(ic)
+bb <- main$models$both
+bm <- main$models$mmed
+br <- main$models$rmed
 #foolars=0.99
@@
 %https://journals.sagepub.com/doi/abs/10.1177/0971890717701781
-BLA
+
 Extant literature on dynamic capabilities are increasingly focusing on how firm resources
@@
 %and different cognition maters
+
+What doe sit mean to execute DC (sense etc) and see opportunities and change underlying...
 
@@
 as well as changes in Baysian Information Criteria (BIC) for model comparison. All these
-are reported in table \ref{tab:res}. Finally, we tested the model for nonlinear effects,
-endogeneity and unbserved heterogeneity using Regression Equation Specification Error Test
-(RESET) , Gaussian Copula approach and Information Criteria test respectively. These
-results are available in the appendix.
+are reported in table \ref{tab:res}.
 
-The estimated models is based on the following specification:
+%% Finally, we tested the model for nonlinear effects,
+%% endogeneity and unbserved heterogeneity using Regression Equation Specification Error Test
+%% (RESET), Gaussian Copula approach and Information Criteria test respectively. These
+%% results are available in the appendix.
+
+The estimated models are based on the following specification:
 
@@
 
+A final model includes an interaction term between $CAP_t$ and $COG_t$ to capture any
+complementarity or substitution-effects these two may exhibit:
+
+\begin{align}
+  CA_{i,1} & = \alpha_0 + \alpha_1 CA_{i,0} + \omega_1 \alpha_2 CAP_{i,1}
+  + \omega_2 \alpha_3 COG_{i,1} + \alpha_{4} DC_{i,0} + \alpha_5 CAP_{i,1} \times  COG_{i,1} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + \epsilon_i 
+\end{align}
+
 \section{Results}
 The main results of our analysis are depicted both in the graphical path diagrams (figure
-\ref{fig:res}) and the regression table in table \ref{tab:res}. The empirical models are
-presented from left to right starting with the direct model. The main effect from $DC_0$
-to $CA_1$, controlled for $CA_0$, firm size, age, profit margin and assets, is positive
-and significant at the onset. Increasingly, by adding mediating variables as suggested by
-the theory, this effect diminishes to an extent suggesting that partial or full mediation
-is taking place. The effect decreases from BLA to BLA and turns insignificant. The
+\ref{fig:res}) and the regression table in table \ref{tab:res}. The use of PLS-SEM has
+increased substantially in the realm of marketing \citep{hult2018} and strategic management
+\citep{Hair2012} and is the topic of special issues in leading journals (e.g. Journal of
+Business Research call for papers in 2020). In this tradition we aim to present thorough
+analysis of our models and largely follows the recommendations made in recent
+contributions \citep{Hair2019}.
+
+The empirical models are presented from left to right starting with the direct model. The
+main effect from $DC_0$ to $CA_1$, controlled for $CA_0$, firm size, age, profit margin
+and assets, is positive and significant at the onset. Increasingly, by adding mediating
+variables as suggested by the theory, this effect diminishes to an extent suggesting that
+partial or full mediation is taking place. The effect decreases from 0.25 to 0.08 and
+turns insignificant when adding the two mediators. This suggests a full mediation. The
 mediating variables $CAP_1$ and $COG_1$ are both positive and significantly related to
@@
 both support H1 and H2. Moreover, the model becomes increasingly better both in terms if
-explanatory power ($R^2$), predictive power ($Q^2$) and the Bayesian Information Criteria
-(BIC).
+explanatory power ($R^2$) and predictive power ($Q^2$).
+
+When adding the interaction term  $CAP_1 \times COG_1$ we get a significant effect. this
+is compatible with the idea of behavioral ($CAP_t$) and non-behavioral ($COG_t$) objects
+of change being complementary. This lends support to H3.
+
+Our results indicate that between 37\%  and 48\% of the variation in $CA_1$ can be explained by our model,
+whereas 19\% and 18\% of the variation in our mediators $CAP_1$ and $COG_t$ respectively
+is explained.
 
@@
 
-One striking finding, however, is that the improvement in the model between
-model 3 and 4 is neglectable, whereas it represents a considerable improvement between 2 and 3. This
-suggests that strategic cognition represents a stronger mediator than operational
-capabilities. However, the difference is too small to render further analysis all but
-conjecture on our part. Thus, we wanted found it necessary to explore the joint mediation
-between $CAP_1$ and $COG_1$.
+\subsection{Robustness and assumption validation}
+The results are subject to some robustness checks not directly reported in the paper,
+albeit a summary is available in the appendix. First, controlling for functional form
+using a Ramsay RESET test we find support for a linear relationship between our
+constructs. Second, we ran the a Variance Inflation Test (VIF) to control for
+multicolinearity. None of the VIF values exceeded the suggested level indicating
+multicolinearity problems. Third, we ran two separate models where we (1) included other
+measures of $DC$ (using the original measure of $DC_0$), and (2) added fewer control
+variables to which increased the sample size (from $N=205$ to $N=240$). Appendix 2
+presents the results from all these robustness checks and assumption validations.
 
-\subsection{Post-hoc analysis: joint mediation}
+%% Second, running a Bayesian Copula approach, we assess the problem of
+%% endogeneity in the model stemming from causes such as omitted variable bias or
+%% simultaneity. The approach explicitly models the correlation between the proposed
+%% endogenous variable ant the error term by means of a copula. When including a copula in
+%% the estimation as a correction for endogeneity we can compare changes in the estimated
+%% coefficients in terms of how they change. We tested this approach on all our three main
+%% independent variables ($CAP_1$, $COG_1$ and $DC_0$) and found no support for endogeneity
+%% problems in our model. However, $CAP_1$ did not fully satisfy the non-normality assumption
+%% of this approach as tested using a Kolmogorov-Smirnoff test, so we cannot fully conclude
+%% that endogenous effects may be at play in the model. However, the normality test did not
+%% establish normality, so we believe the Bayesian Copula approach was rather efficient for
+%% our purpose. Consequently, we do not believe that we have endogeneity problems in our
+%% model.
+%% introduced the Gaussian copula approach, which controls for endogeneity by directly
+%% modeling the correlation between the endogenous variable and the error term by means of a
+%% copula Model estimation in PLS-SEM draws on a three-stage approach that belongs to the
+%% family of (alternating) least squares algorithms (Mateos-Aparicio 2011). Stage 1 of the
+%% PLS-SEM algorithm iteratively determines indicator weights, composite scores, and path
+%% coefficients. The algorithm converges when the indicator weights change only marginally
+%% from one iteration to the next. Stages 2 and 3 use the final composite scores from Stage 1
+%% as input for a series of ordinary least squares regressions. These regressions produce the
+%% final indicator loadings, indicator weights, and path coefficients, as well as related
+%% elements, such as the indirect and total effects, and R2 values (e.g., Sarstedt et
+%% al. 2017a). With Simply put, the copula connects the marginal distributions of two or more
+%% variables that follow any distribution (e.g., normal, non-normal). Park and Gupta (2012)
+%% add a copula term to the model that represents the correlation between the endogenous
+%% variable and the error term. By including this term, the effect of the endogenous
+%% regressor can be estimated consistently
 
-From standard production theory we know that the isoquants
-between two factors of input rarely are angled (Leontief isoquants) suggesting that the
-factors are total complements to eachother. Rather there are trade offs between these
-factors suggesting a non-linear relationship. One way to investigate this is by means of
-joint mediation where (USE MODERATED MEDIATION RATHER). 
  <<pathchild, child='./figure/medanalysisall.rnw',results="asis">>=
 @
+
+\section{Discussion}
+The aim of this paper is to theorize about how non-behavioral objects of change work as a
+mechanism through which dynamic capabilities influence competitive advantage. Our results
+indicate that both behavioral (\emph{operating capabilities}) and non-behavioral
+(\emph{strategic cognition}) mediates the effect from dynamic capabilities on competitive
+advantage. The first mechanism, dubbed 'conducting' in reference to the well established
+terminology of 'resource orchestration' \citep{Sirmon2011,Helfat2007}, shows a robust and
+strong function as a mediator in line with our first hypothesis. When firms exhibit strong
+dynamic capabilities they are able to adapt their operating capabilites to stay
+competitive. We hypothesized that this relationship would be positive and significant. Our
+results indicated exactly this relationship and thus lending support to hour hypothesis.
+In our example context of Microsoft Nadella did several investments in capabilities and
+resources as a response to Microsofts dynamic capabilities execution. For example, he
+acquired important capabilities from M\&A efforts, and upgraded the competencies regarding
+cloud business and big data (Nadella). This should not be surprising given the vast
+literature on indirect effects of dynamic capabilities \citep{Eriksson2014} supported by
+empirical and theoretical research
+\citep{Fainshmidt2016a,Protogerou2012,Karimi2015}. However, it adds to this ongoing effort
+of investigating mechanisms through which dynamic capabilities work which is called for in
+the literature \citep{Schilke2018}.
+
+In this vein, our second hypothesis, and the main contribution of this paper, is much more
+novel in its characteristics. Building on the important work of \cite{Verona2011} in what
+they call adding a 'human side to dynamic capabilities' we suggest that non-behavioral
+objects of action exists in parallel with behavioral ones. This view holds that cognition
+makes a difference in creating strategic change and should thus be a part of a more
+'holistic' approach to dynamic capabilities theory (ibid). The notion of cognition in
+general plays an important role in determining 'the way we do things' (Vince and Gabriel
+2011, ch 15). The idea of 'strategic cognition' seems to be a way of safeguarding that
+organization members buy into the needed strategic change identified by execution of
+dynamic capabilities. Indeed, this is also what we find in our results. Our
+operationalization of 'strategic cognition' as \emph{proactiveness} makes for a proper
+mediator in the focal relationship between dynamic capabilities and competitive
+advantage. This is the path we have dubbed 'coaching' where dynamic capabilities rather
+than orchestrating resources enables the organization to fully grasp and adapt to the proposed
+strategic change. In our Microsoft example this was exactly where Nadella put the most
+emphasis. By instilling a growth mindset Microsoft became a more proactive company, but
+the triggering mechanism was the execution of dynamic capabilities through sensing and
+seizing the opportunities they saw.
+
+Our empirical results support the idea that \emph{operating capabilities}) and
+\emph{strategic cognition} being distinctly different mechanisms through which dynamic
+capabilities influence competitive advantage.
+
+Specifically, we ask the following research question:
+
+{\bf What is the role of non-behavioral objects of change as a mechanism through which
+  dynamic capabilities can influence competitive advantage?}
+
+To shed light on this important question we theorize on the role of a particular type of
+non-behavioral object of change, \emph{strategic cognition}, and how it acts as a
+mediator between dynamic capabilities and firm competitive advantage and hence has a
+pivotal place in the literature. We build on important work on the concept of
+organizational cognition (ref), non-behavioral object of change (ref) and cognitive
+psychology (kahneman and tversky),
+and hypothesize about how strategic cognition acts as a mediator in the same way as
+conventional behavioral objects of change (such as routines and capabilities) and that
+these two are complementary to a certain degree. Consequently, we argue, dynamic capabilities takes
+the function of a 'conductor' by orchestrating routines and capabilities, and the role of
+a 'coach' in stimulating strategic cognition. We use the case of Microsoft's transition
+into the cloud computing business as an illuminating case for demonstrating how the roles
+of 'conductor' and 'coach' coexist and act partly complimentary in generating strategic
+change and competitive advantage.
 

### 2019-11-17 article4_analysis_v2.r

@@ -85,10 +85,10 @@ imputezw <- function(vec){
     return(vec)
 }
 
-## imputezw <- function(vec){
-##     tempData <- mice(vec,m=10,maxit=50,meth='pmm',seed=500)
-##     return(complete(tempData,1))
-## }
+imputezw <- function(vec){
+   tempData <- mice(vec,m=10,maxit=50,meth='pmm',seed=500)
+   return(complete(tempData,1))
+}
 
 
 extboot <- function(bootobj,n,nam,r){ #remembaer space between Letter and " ("P ")
@@ -126,7 +126,7 @@ alldc0 <- zwadj[,c("Q6.1_t1","Q6.4_t1","Q6.5_t1","Q7.1_t1","Q7.2_t1","Q7.3_t1","
 ## Running median imputation
 
 ## Running median imputation
-dc02 <-  imputezw(zwadj[,c("Q6.4_t1", "Q6.5_t1","Q7.1_t1","Q7.2_t1")] )
+#dc02 <-  imputezw(zwadj[,c("Q6.4_t1", "Q6.5_t1","Q7.1_t1","Q7.2_t1")] )
 #dc02 <-  imputezw(zwadj[,c("Q6.1_t1","Q7.3_t1","Q7.4_t1")] )
 #dc002 <- imputezw(zwadj[,c("Q19c", "Q19d", "Q20b", "Q20c")] )
 dc02 <-  imputezw(alldc)
@@ -135,10 +135,13 @@ dc002 <-  imputezw(alldc0)
 #dc002 <-  imputezw(zwadj[,c("Q19d","Q19c", "Q20b", "Q20c","Q20e")])
 ca0 <-  imputezw(zwadj[,c("Q28","Q28a","Q28c")] )
 ca1 <-   imputezw(zwadj[,c("Q16.1_t1","Q16.2_t1","Q16.4_t1")] )
-#or1 <-   imputezw(zwadj[,c("Q5.4_t1","Q5.6_t1","Q5.7_t1","Q5.1_t1","Q5.2_t1","Q5.3_t1","Q5.5_t1")])
-#or0 <-   imputezw(zwadj[,c("Q21c","Q21d","Q21e","Q22","Q22a","Q22b","Q22c")])
-or1 <-   imputezw(zwadj[,c("Q5.4_t1","Q5.6_t1","Q5.7_t1")])
-or0 <-   imputezw(zwadj[,c("Q21c","Q21d","Q21e")])
[…]

### 2019-11-17 article4_analysis_v2.r
minor adjustments

@@ -569,6 +569,24 @@ nboot=200
 main<-plswrap(zwadj, c("size","age"), c())
 mainf <-plswrap(zwadj2,c("size","lassets","pm","age"), c("size","lassets","age","pm"))
 
+interaction<-matrix(c(
+  0.26932034207859623, 0.26923690255247545, 0.04814863208543181, 5.59352011497921, 3.669225634439499E-8, 
+  0.33103128717881747, 0.3323640758665314, 0.045724630251763085, 7.2396711653245855, 1.7621459846850485E-12, 
+  0.3512170134073069, 0.35453979904198096, 0.0641087026729594, 5.478460782446121, 6.810904551457497E-8, 
+  0.18625055537645321, 0.19955110191159914, 0.06718384748338509, 2.7722519973646036, 0.005774687355312835, 
+  0.22513185914079997, 0.22544489295104994, 0.06147333291610961, 3.6622686368417523, 2.7664183068054626E-4, 
+  0.06116102318365884, 0.06014449246886341, 0.05440671102134564, 1.1241448349940368, 0.26149095523686583, 
+  0.20629260491579082, 0.21313255834073758, 0.06496708651484248, 3.1753402527703147, 0.001588948586402239, 
+  0.32932110930791636, 0.33228844472191554, 0.06206401583333989, 5.306152121903298, 1.6858410845088656E-7, 
+  0.09274062017926049, 0.09086154127388878, 0.045578858837511976, 2.034728875285789, 0.04240522287255999, 
+  0.017322516024085983, 0.015280519583150617, 0.0480473964505637, 0.36052975402963283, 0.7186032612185613, 
+  0.17666995752931067, 0.17584583914912322, 0.051281148379350314, 3.4451248287655627, 6.18817371048408E-4
+), byrow=TRUE, nrow=11, ncol=5)
+rownames(interaction)<-c("CA0 -> CA1","CAP -> CA1","CAP0 -> CAP","COG0 -> COG_","COG_ -> CA1","DC_ -> CA1","DC_ -> CAP","DC_ -> COG_","Moderating Effect 1 -> CA1","age -> CA1","size -> CA1")
+colnames(interaction)<-c("Original Sample (O)","Sample Mean (M)","Standard Deviation (STDEV)","T Statistics (|O/STDEV|)","P Values")
+interaction
+interaction<-round(interaction,3)
+i<-interaction
[…]

### 2019-11-18 article4_jbr.rnw
Paper 4 ready for submission to Tommy

@@
 
+%\usetikzlibrary{arrows.meta}
+
 %%%% TURN OFF PAGE NUMBER FOR INCLUSION IN THESIS
@@
 \begin{frontmatter}
+%Lock, Stock and Two Smoking Barrels lock stock and two mediating factors
+%The Lord of the Rings: The Two Towers
+%Bravo Two Zero (1999)
+%A tale of two mechanisms
+%Eating strategy for breakfast?
+%Push, skill and two mediating factors
 
-\title{Dynamic capabilities and competitive advantage}
+\title{A Tale of Two Mechanisms: How mediators act and interact in dynamic capabilities
+  theory\\ Lock, Stock and Two Convoking Mechanisms: Towards a holistic theory of dynamic
+  capabilitie }
 %\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
@@
 \begin{abstract}
-TBD
+This paper investigates strategic cognition as mediating factor in the dynamic
+capabilities-competitive advantage relationship. By including strategic cognition into the
+analysis in addition to the conventional mediator (operating capabilities) we argue that a
+more holistic approach to understanding the workings of dynamic capabilities emerges. We
+introduce two expressions of how dynamic capabilities work, namely as a conductor (the
+conventional mechanism) and as a coach (the cognitive mechanism). Using repeated
+cross-sectional data from Norwegian technology firms our results indicate support for our
+holistic model. This has implications for understanding how dynamic capabilites work, as
+well as practical implications for how strategic change is implemented in firms.
 
@@
 \begin{keyword}
-\texttt{Dynamic Capabilities, Deliberate Learning, Dynamics }
+\texttt{Dynamic Capabilities, strategic cognition, operating capabilities, mechanisms,
+  competitive advantage }
 \end{keyword}
@@
 library(semPLS)
-load("./data/resart4.RData")
+#load("./data/resart4.RData")
 r <- main$resmat
@@
 are changed by dynamic capabilities as a response to changes in the environment
-\citep{Schilke2018,Eriksson2014}, thus placing firm resources as a mediator between
-dynamic capabilities and competetive advantage \citep{Helfat2007}. Less focus has been
-placed on the nature of these underlying firm resources (ref) and how they are capturing a
-rather heterogeneous bulk of routines, capabilities, assets and capital. Hence, there is a
-need to disentangle the black box of firm resources to provide a more nuanced
-understanding of different types of firm resources and how they interact to shape firm
-competitive advantage \cite{Schilke2018}. Indeed, this gap in the literature is explicitly
-emphasized by \cite{Schilke2018} where they 'see an interesting opportunity for future
-work to add greater richness to our understanding of the mechanism of resource-base
-change, given this mechanism’s central role in many foundational works (..) and the
-diverse ways in which resource changes can potentially come about' (p. 419).
+\citep{Schilke2018,Eriksson2014}, thus placing firm capabilities as a mediator between
+dynamic capabilities and competetive advantage \citep{Helfat2007}. This notion of
+'orchestration' of firm resources, assets and capabilities has indeed been emphasized in
+the extant literature \citep{Sirmon2011,Helfat2015}. Less emphasis has been placed on how
+other mechanisms can be work in shaping firm competitive advantage. Indeed, this gap in
+the literature is explicitly emphasized by \cite{Schilke2018} where they 'see an
+interesting opportunity for future work to add greater richness to our understanding of
+the mechanism of resource-base change, given this mechanism’s central role in many
+foundational works (..) and the diverse ways in which resource changes can potentially
+come about' (p. 419).
 
@@
 capability is the capacity of an organization to purposefully create, extend or modify its
-resource base' (p. 4). And although this definition opens up for a variety of components
-included in the term 'resource base', a point we discuss later in this paper, most of the
-subsequent contributions have focused on changes in operational routines (ref),
-capabilities (ref), practices (ref) or tangible assets (ref). This focus, albeit very
-important to the development of dynamic capabilities literature, seems to leave out a
-considerable part of a firm`s 'resource base', namely those resources that are tied to how
-the employees of the firm sees their mission, internalize information and effectuates
-change. These traits of the organization is very much related to concepts of
-'organizational culture' (ref), 'employee cognition' (ref)' 'organizational genes'
-\citep{Nelson1982} and 'sense-making' \citep{Weick1995} to name but a few. However, in
-relations with dynamic capabilities one promising avenue for exploring mechanisms beyond
-the conventional ones described above, makes a clear distinction between \emph{behavioral}
-and \emph{non-behavioral} objects of change \citep{Verona2011}. These non-behavioral
-objects of change contain psychological objects such as cognitive frames, motivation and
-identity that are important for strategy formation and implementation (Gavetti etc, vince
-and gabriel ch 15 of book by verona) as they 'concerns how decisions or actions are
-shaped, subverted and transformed by emotions, and (..) determine the "way we do things
-here"' (Vince and gabriel). In this respect they work as firm resources in generating
-outcomes such as performance and competitive advantage. This notion is perhaps expressed
-most clearly by Peter Drucker`s famous quote about how 'culture eats strategy for lunch'
-(ref) insofar as. Moreover, these non-behavioral objects of change are themselves far
-from static and are found to change over time as responses to external change
-\citep{Zollo2016} thus making them a natural part of the mechanisms underpinning how
-dynamic capabilities work \citep{Schilke2018,Verona2011}. Still, far less is know about
-the non-behavioral objects of change and how they work as a mechanism in the dynamic
-capabilities theory.
+resource base' (p. 4). This definition opens up for a variety of components
+included in the term 'resource base', a point we discuss later in this paper. We coin this
+expression of dynamic capabilities as the {\bf conductor} envisioning a conductor
+orchestrating firm capabilities.
+
+This notion of a {\bf conductor} albeit very important to the development of dynamic
+capabilities literature, seems to leave out a considerable part of a firm`s 'resource
+base', namely those resources that are tied to how the employees of the firm sees their
+mission, internalize information and effectuates change. These traits of the organization
+is very much related to concepts of 'mindset' \citep{Dweck2016}, 'employee cognition'
+\citep{Lakoff1987,Gavetti2012} 'organizational genes' \citep{Nelson1982} and
+'sense-making' \citep{Weick1995} to name but a few. However, in relations with dynamic
+capabilities, one promising avenue for exploring mechanisms, beyond the conventional ones
+described above, makes a clear distinction between \emph{behavioral} and
+\emph{non-behavioral} objects of change \citep{Verona2011}. These non-behavioral objects
+of change contain psychological objects such as cognitive frames, motivation and identity
+that are important for strategy formation and implementation \citep{Vince2011,Gavetti2012}
+as they 'concerns how decisions or actions are shaped, subverted and transformed by
+emotions, and (..) determine the "way we do things here"' \citep[p. 338]{Vince2011}. In
+this respect they work as firm resources in generating outcomes such as performance and
+competitive advantage. This notion is popularly perhaps expressed most clearly by Peter
+Drucker`s famous quote about how 'culture eats strategy for lunch'. \footnote{The debate
+  on whether Drucker actually uttered these words are still in the open, but it was
+  attributed to him by Mark Fields in 2006} Moreover, these non-behavioral objects of
+change are themselves far from static and are found to change over time as responses to
+external change \citep{Zollo2016} thus making them a natural part of the mechanisms
+underpinning how dynamic capabilities work \citep{Schilke2018,Verona2011}.  Still, far less
+is know about the non-behavioral objects of change and how they work as a mechanism in the
+dynamic capabilities theory.We coin {\bf coach} to capture the enabling role dynamic
+capabilities plays through \emph{strategic cognition} as
+juxtaposed to the more directional role played as {\bf conductor} of \emph{operational capabilities}.
 
@@
 To shed light on this important question we theorize on the role of a particular type of
-non-behavioral object of change, \emph{strategic cognition}, and how it acts as a
-mediator between dynamic capabilities and firm competitive advantage and hence has a
-pivotal place in the literature. We build on important work on the concept of
-organizational cognition (ref), non-behavioral object of change (ref) and cognitive
-psychology (kahneman and tversky),
-and hypothesize about how strategic cognition acts as a mediator in the same way as
-conventional behavioral objects of change (such as routines and capabilities) and that
-these two are complementary to a certain degree. Consequently, we argue, dynamic capabilities takes
-the function of a 'conductor' by orchestrating routines and capabilities, and the role of
-a 'coach' in stimulating strategic cognition. We use the case of Microsoft's transition
-into the cloud computing business as an illuminating case for demonstrating how the roles
-of 'conductor' and 'coach' coexist and act partly complimentary in generating strategic
-change and competitive advantage.
+non-behavioral object of change, \emph{strategic cognition}, and how it acts as a mediator
+between dynamic capabilities and firm competitive advantage and hence has a pivotal place
+in the literature. We build on important work on the concept of organizational cognition
+\citep{Lakoff1987} , non-behavioral object of change \citep{Verona2011} and cognitive
+psychology \cite{Tversky1983,Kahneman2011} and hypothesize about how strategic cognition
+acts as a mediator in the same way as conventional behavioral objects of change (such as
+routines and capabilities) and that these two are complementary to a certain
+degree. Consequently, we argue, dynamic capabilities takes the function of a {\bf conductor}
+by orchestrating routines and capabilities, and the role of a {\bf coach} in stimulating
+strategic cognition. We use the case of Microsoft's transition into the cloud computing
+business as an illuminating case for demonstrating how the roles of {\bf conductor} and
+{\bf coach} coexist and act partly complimentary in generating strategic change and
+competitive advantage.
 
-SOMETHING ABOUT COMP ADV / why interesting outcome holy grail helfat schilke
+Centering this paper around the dynamic capabilities-competitive advantage nexus stems
+from the origins and promises of the dynamic capabilities theory. Competitive advantage is
+considered the 'holy grail' of strategic management \citep{Schilke2018} and is indeed the
+focal point of important antecedent theories of dynamic capabilities
+\citep{Arndt2018}. Consequently, contributions to push the theory forward should enable a
+better understanding of \emph{how} dynamic capabilities work to influence firms'
+competitive advantage. In this spirit, our paper makes the following contributions to
+extant dynamic capabilities theory. First, we provide clarification on the theoretical
+role of non-behavioral objects of change as well as a possible empirical
+operationalization through the concept of \emph{proactiveness}. Second, we conceptualize
+two different expressions of dynamic capabilities (i.e. {\bf conductor} and {\bf coach})
+and theorize on how they work in the dynamic capabilities-competitive advantage nexus. We
+also extend this reasoning to include how they relate to each other. Finally, we develop and
+test an empirical model suited for analyzing mediating constructs on the dynamic
+capabilities-competitive advantage nexus. The time-lag of our data in conjunction with
+advances in empirical estimations of multiple simultaneous mediators makes for an
+interesting model to push our understanding of important mechanisms in the
+theory.
 
-This paper makes the following contributions:
-
-The rest of this paper is organized as follows:
+The rest of this paper is organized as follows: First, we present a brief discussion on
+the key definitions applied in this paper. We then move on to develop hypothesis of the
+focal relationships. Third, we present the data and empirical models used to test our
+hypothesis. A discussion follows the results from our model, before we conclude by
+offering some limitations to our study as well as future directions for study.
 
@@
 turned Microsoft around to a valuation of 105 USD pr share and with successful mergers
-along the way is a story of excellent 'resource orchestration' as a response to exercising
+along the way is a story of excellent 'capabilities orchestration' as a response to exercising
 dynamic capabilites, specifically through sensing, seizing and transforming resources to
@@
 own book Nadella put considerable emphasis on how Microsoft managed to change their
-'mindset', that is their 'cognitive frames' (Nadella 2017): 'I focused on what would be
+'mindset', that is their 'cognitive frames' \citep{Nadella2017}: 'I focused on what would be
 our grandest endeavor, the biggest hurdle - transforming the Microsoft culture'
@@
 \citep{Zollo2016}. We use a familiar term for the conventional understanding of dynamic
-capabilities mechanism as 'orchestration' (ref) as a collective term to describe the
-behavioral objects of action (ref). In this process dynamic capabilities play the role of
-a 'conductor' orchestrating capabilities of the firm, an understanding that is in line
+capabilities mechanism as 'orchestration' as a collective term to describe the
+behavioral objects of action \citep{Verona2011}(ref). In this process dynamic capabilities play the role of
+a {\bf conductor} orchestrating capabilities of the firm, an understanding that is in line
 with a range of the most common definitions of dynamic capabilities \citep{Schilke2018}.
@@
 enabling the organization to tear away from their current understanding and ways in which
-things are done (Vince and Gabriel). Whereas the analogy of a 'conductor' suggests a
+things are done \citep{Vince2011}. Whereas the analogy of a {\bf conductor} suggests a
 function that composes an outcome based on the available capabilities, the notion of a
-'coach' refers to the function of enabling others to achieve their objectives. The process
+{\bf conductor} refers to the function of enabling others to achieve their objectives. The process
 is all about changing an organization`s thinking from the automated and well-known, to the
 more cognitively aware, moving from what Kahneman and Tversky coins the automated 'system
-one' to the deliberate 'system two' thinking (ref). We will now turn to the two functions
+one' to the deliberate 'system two' thinking \citep{Kahneman2011}. We will now turn to the two functions
 of dynamic capabilities in turn.
@@
 and Citrus data became important platforms for developing new capabilities within the
-company (Nadella).
+company \cite{Nadella2017}.
 
-This role of 'conductor' is the conventional way of understanding dynamic capabilities. It
+This role of {\bf conductor} is the conventional way of understanding dynamic capabilities. It
 stems from one of the most common definitions \citep{Helfat2007} as well as the analogy of
@@
 for a detailed account). Cognitive inertia on the part of the organization played a
-pivotal part in the failing of the company`s digital imaging effort
-\citep{Verona2011}. In other words, Polaroid did not exercise dynamic capabilities to
-change the cognition of the organization. Similar patterns are found in Kodak and Anderson Consulting (ref
-Henderson and Kaplan 2005), and Smith Corona (Danneels 2010). These examples highlight the
+pivotal part in the failing of the company`s digital imaging effort \citep{Verona2011}. In
+other words, Polaroid did not exercise dynamic capabilities to change the cognition of the
+organization. Similar patterns are found in Kodak and Anderson Consulting
+\citep{Kaplan2005}, and Smith Corona \citep{Danneels2010}. These examples highlight the
 absence of 'dynamic capabilities specific to the adaptation of cognitive frames, first,
 and consequently of operating processes' \citep[p. 541]{Verona2011}. This is also
-highlighted at the core of the dynamic capabilities literature: 'Dynamic capabilities are about doing the
-right things, at the right time, based on new product (and process) development, unique
-managerial orchestration processes, a strong and {\bf change-oriented organizational
-  culture}' (our emphasis) \cite[p]{Teece2014}.
+highlighted at the core of the dynamic capabilities literature: 'Dynamic capabilities are
+about doing the right things, at the right time, based on new product (and process)
+development, unique managerial orchestration processes, a strong and {\bf change-oriented
+  organizational culture}' (our emphasis) \cite[p]{Teece2014}.
 
@@
 what is often referred to as 'how we do things here' \citep{Nelson1982}, and how an
-organization thinks and act (NAdella). This alignment is possible only if the employees
-share a common cognitive frame related to the the strategic direction of the company
-enabling them to make sense of the changes ahead. This is what we have coined
+organization thinks and act \citep{Nadella2017}. This alignment is possible only if the
+employees share a common cognitive frame related to the the strategic direction of the
+company enabling them to make sense of the changes ahead. This is what we have coined
 \emph{strategic cognition} and has its expression in Microsoft's development of a growth
@@
 changes they will enhance the full organization`s ability to not only act upon changes
-(Marchand et.al 2000), but also in 'timely responsiveness' (Kohli et.al 1993,
-Simsek2009). Consequently, strategic cognition not only contributes to getting people on
-board, it also maintain a more efficient change process where the individuals take more
-responsibilities for the change itself and leverages their individual knowledge in the
-endeavor. For a firm to create real strategic change as enabled by their dynamic
-capabilities and hence stay competitive, is will need to act as a 'coach' to instill a
-strategic cognition in the organization.
+\citep{Marchand2004}, but also in 'timely responsiveness' \citep{Kohli1993}. Consequently,
+strategic cognition not only contributes to getting people on board, it also maintain a
+more efficient change process where the individuals take more responsibilities for the
+change itself and leverages their individual knowledge in the endeavor. For a firm to
+create real strategic change as enabled by their dynamic capabilities and hence stay
+competitive, is will need to act as a {\bf coach} to instill a strategic cognition in the
+organization.
 
@@
   competitive advantage}
+
+\subsection{Coaching conductor}
+
+Although Satya Nadella and Microsoft put strong emphasis on the cognitive side of
+strategic change (the role as {\bf coach}), acquisition and development of capabilities
+were also very much on their mind (the role as {\bf conductor}). It was not about letting
+'culture eat strategy for breakfast', but rather serving culture and strategy as
+complementary side-dishes. Nadella emphasized 'getting the right team in place', 'build
+new and surprising partnerships', 'be ready to catch next wave of innovation and platform
+shift' as things Microsoft needed to get right. These meant investing in new people as
+well as upgrading the capabilities of the existing staff \cite{Nadella2017}. Meanwhile, he
+also stressed that they needed to 'drive cultural change from top to bottom' and 'reframe
+our opportunity for a mobile- and cloud-first world'. (ibid p 95-96). In Microsoft, it
+clearly seems, it was exactly by being both a {\bf coach} and a {\bf conductor} at the
+same time that results would come. In other words, the giant software company strongly
+emphasized that the two mechanisms were complementary.
+
+When dynamic capabilities are executed in a firm being able to both adapt the capabilities
+and the cognitive frames simultaneously makes sense. A solid strategic cognition in tandem
+with relevant and strong capabilities would reinforce each other. This has also been
+supported in previous research where firm success has been shown to relate to the
+interconnection between resources and capabilities, and culture and attitude
+\citep{Verona2003}, and high levels of social capital \citep{Blyler2003}. Moreover, the
+lack of one (e.g. strategic cognition) can lead to unfavorable outcomes even though
+capabilites and resources are aligned for the needed strategic change
+\citep{Tripsas2000}. This leads us to our final hypothesis:
+
+\emph{H3: Strategic cognition and operating capabilities are complementary and thus
+  mutually reinforcing their individual effect on competitive advantage}
 
@@
 web-based questionnaire containing the same measures of the focal constructs of this
-paper. 283 of the firms returned filled-in questionnaire.
+paper. 262 of the firms returned filled-in questionnaire.
 
@@
 
-The focal constructs of this paper are dynamic capabilities, operational capabilities,
+The focal constructs of this paper are dynamic capabilities, operating capabilities,
 strategic cognition as measured by proactiveness, and competitive advantage. These are all
-operationalized using the survey data described above. Table \ref{tab:item} in the
-appendix describes the items used to operationalize the focal constructs and their
-internal validity as measured by Dillon-Goldstein Rho which is the preferred metric for
-this purpose \citep{Hair2019}. The results show that our key constructs can be represented
-by the items in the survey, with a minor caveat. The measure of strategic cognition as
-proactiveness loads only partly on one item (item 3). Statsistically, a loading of
-$\Sexpr{l[["lcog"]][3]}$ is on the weaker side of traditional 'rules of thumb'
-\citep{Hair2010}, but from a theoretical stand point the measure makes sense and is
-established in the literature (REF to EO).
+operationalized using the survey data described above.  To capture \emph{operating
+  capabilites} we look at the definition of these by \citep{Winter2003} as those
+capabilities that enables the firm to 'make a living' in the short term, i.e. contributing
+to the technical fitness of the firm \citep{Helfat2007}. Thus we chose to survey a firm's
+ability to handle core functions of daily operations such as operational routines,
+operational management, customer service and marketing. To capture strategic cognition we
+apply the definition derived above. Of course such a concept can have many
+actual expressions, but in the context of studyin competititve advantage the
+organization's attitude towards competition seems like a plausible starting point. In
+other word a shared cognitive frame of an overall competitive orientation is useful. Thus,
+we adopt the idea of measuring a strategic posture of the firm \citep{Covin1989} and
+particularly the notion of \emph{proactiveness} \citep{covin1991,Wales2016}.
+
+Table \ref{tab:item} in the appendix describes the items used to operationalize the focal
+constructs and their internal validity as measured by Dillon-Goldstein Rho which is the
+preferred metric for this purpose \citep{Hair2019}. The results show that our key
+constructs can be represented by the items in the survey, with a minor caveat. The measure
+of strategic cognition as proactiveness loads only partly on one item (item
+3). Statsistically, a loading of $\Sexpr{l[["lcog"]][3]}$ is on the weaker side of
+traditional 'rules of thumb' \citep{Hair2010}, but from a theoretical stand point the
+measure makes sense and is established in the literature \cite{covin2012}.
 
@@
 underlying resource components are very challenging to research in a systematic and
-econometric fashion \citep{McKelvie2009}, we follow the argument in the
-literature that more empirical work is necessary to test and refine the dynamic
-capabilities concept and how it is related to the evolutionary economic theory
-\citep{Arend2009,McKelvie2009} \todo{Rosenblom, 2000; Verona and Ravasi, 2003;}.  It
+econometric fashion \citep{McKelvie2009}, we follow the argument in the literature that
+more empirical work is necessary to test and refine the dynamic capabilities concept and
+how it is related to the evolutionary economic theory \citep{Arend2009,McKelvie2009}.  It
 is in this spirit that the research reported in this paper has been undertaken.
+% \todo{Rosenblom, 2000; Verona and Ravasi, 2003;}
 
@@
 the conclusions we draw in this paper, but had some minor effects on the significance of
-the path between $DC_0$ and $COG_1$. The full alternative analysis is included in the
-appendix.
+the path between $DC_0$ and $COG_1$.
 
@@
 We add a set of control variables expected to explain parts of the variation in our focal
-constructs. From the survey we add firm size, firm age, the level of dynamism facing the
-firm. Size is the reported number of employees in the firm at $T_1$, and age is the number of
-years since establishment.
+constructs. From the survey we add firm size and firm age. Size is the reported number of
+employees in the firm at $T_1$, and age is the number of years since establishment.
 
 To partly remedy the problem of common method bias, we add controls of financial data from
-the firm´s profit and loss statements, and balance sheet. Specifically, we add the natural
-logarithm of the assets to capture the capital intensity of the firm.
+the firm´s profit and loss statements, and balance sheet as robustness
+checks. Specifically, we add the natural logarithm of the assets to capture the capital
+intensity of the firm.
 
@@
 capabilities. Simply put both firm performance and dynamic capabilities can be due to some
-unobserved factor of the firm simply being a “good firm”. In such cases we would simply
+unobserved factor of the firm simply being a 'good firm'. In such cases we would simply
 regress one on the other and get positive results without the exact mechanism being
@@
 theory and tested the constructs accordingly by evaluating the internal validity using
-Cronbachs alpha and composite reliability index (joreskog 1971). In this first step we
-used only observations where all indicators were complete (i.e. no missing). Then we
-imputed the mean value of the other indicators when one indicator had a missing value. In
-the second step we reran the model and compared the reliability measures. None of the
-constructs changed materially, but the total sample size went from $N=262$ to $N=240$
-because some of the constructs lacked more than one item, rendering the imputation
-challenging. In these cases we dropped the observation. As a robustness check we reran all
-the models using a Multivariate Imputation By Chained Equations (MICE) procedure which
-makes use of the whole sample to impute missing values where more than one underlying item
-is missing. This procedure did not change the results materially.
+Dillon-Goldstein Rho. In this first step we used only observations where all indicators
+were complete (i.e. no missing). Then we imputed the mean value of the other indicators
+when one indicator had a missing value. In the second step we reran the model and compared
+the reliability measures. None of the constructs changed materially, but the total sample
+size went from $N=262$ to $N=240$ because some of the constructs lacked more than one
+item, rendering the imputation challenging. In these cases we dropped the observation. As
+a robustness check we reran all the models using a Multivariate Imputation By Chained
+Equations (MICE) procedure which makes use of the whole sample to impute missing values
+where more than one underlying item is missing. This procedure did not change the results
+materially.
 
@@
 we ran simulations using bootstrapping and reported the simulation number, standard errors
-and corresponding p-values. To evaluate the models we compared $R^2$ and $Q^2$ statistics,
-as well as changes in Baysian Information Criteria (BIC) for model comparison. All these
-are reported in table \ref{tab:res}.
+and corresponding p-values. To evaluate the models we compared $R^2$ and $Q^2$ statistics
+for model comparison. All these are reported in table \ref{tab:res}.
 
@@
   + \omega_2 \alpha_3 COG_{i,1} + \alpha_{4} DC_{i,0} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + \epsilon_i \\
-  CAP_{i,1} & = \beta_0 + \beta_1 CAP_{i,0} + \beta_2 DC_{i,0} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + v_i\\
-   COG_{i,1} & = \eta_0 + \eta_1 COG_{i,0} + \eta_2 DC_{i,0} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1}+ u_i
+  CAP_{i,1} & = \beta_0 + \beta_1 CAP_{i,0} + \beta_2 DC_{i,0} + v_i\\
+   COG_{i,1} & = \eta_0 + \eta_1 COG_{i,0} + \eta_2 DC_{i,0} +  u_i
 \end{align}
@@
 \begin{align}
-  CA_{i,1} & = \alpha_0 + \alpha_1 CA_{i,0} + \omega_1 \alpha_2 CAP_{i,1}
-  + \omega_2 \alpha_3 COG_{i,1} + \alpha_{4} DC_{i,0} + \alpha_5 CAP_{i,1} \times  COG_{i,1} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + \epsilon_i 
+  CA_{i,1}  = & \alpha_0 + \alpha_1 CA_{i,0} + \omega_1 \alpha_2 CAP_{i,1}
+  + \omega_2 \alpha_3 COG_{i,1} + \alpha_{4} DC_{i,0} +  \\ \nonumber
+  &\alpha_5 CAP_{i,1} \times  COG_{i,1} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + \epsilon_i
 \end{align}
@@
 multicolinearity problems. Third, we ran two separate models where we (1) included other
-measures of $DC$ (using the original measure of $DC_0$), and (2) added fewer control
-variables to which increased the sample size (from $N=205$ to $N=240$). Appendix 2
-presents the results from all these robustness checks and assumption validations.
+measures of $DC$ (using the original measure of $DC_0$), and (2) added more control
+variables to which decreased the sample size (from $N=238$ to $N=205$).
+
+%%Appendix 2
+%%presents the results from all these robustness checks and assumption validations.
 
@@
 acquired important capabilities from M\&A efforts, and upgraded the competencies regarding
-cloud business and big data (Nadella). This should not be surprising given the vast
+cloud business and big data \citep{Nadella2017}. This should not be surprising given the vast
 literature on indirect effects of dynamic capabilities \citep{Eriksson2014} supported by
@@
 'holistic' approach to dynamic capabilities theory (ibid). The notion of cognition in
-general plays an important role in determining 'the way we do things' (Vince and Gabriel
-2011, ch 15). The idea of 'strategic cognition' seems to be a way of safeguarding that
-organization members buy into the needed strategic change identified by execution of
+general plays an important role in determining 'the way we do things'
+\citep{Vince2011}. The idea of 'strategic cognition' seems to be a way of safeguarding
+that organization members buy into the needed strategic change identified by execution of
 dynamic capabilities. Indeed, this is also what we find in our results. Our
@@
 advantage. This is the path we have dubbed 'coaching' where dynamic capabilities rather
-than orchestrating resources enables the organization to fully grasp and adapt to the proposed
-strategic change. In our Microsoft example this was exactly where Nadella put the most
-emphasis. By instilling a growth mindset Microsoft became a more proactive company, but
-the triggering mechanism was the execution of dynamic capabilities through sensing and
+than orchestrating resources enables the organization to fully grasp and adapt to the
+proposed strategic change. In our Microsoft example this was exactly where Nadella put the
+most emphasis. By instilling a growth mindset Microsoft became a more proactive company,
+but the triggering mechanism was the execution of dynamic capabilities through sensing and
 seizing the opportunities they saw.
@@
 \emph{strategic cognition} being distinctly different mechanisms through which dynamic
-capabilities influence competitive advantage.
+capabilities influence competitive advantage. This suggests that dynamic capabilities have
+two roles working in tandem, both being a 'conductor' of capabilities, and a 'coach' of
+cognition at the same time. Moreover, these two types of objects of change, as thoroughly
+discussed by \cite{Verona2011}, are not independent. They work in tandem in that you are
+not able create strategic change without adapting your capabilities for the change,
+meanwhile exercising the right interpretation, understanding and attitude towards
+change. This is also one of the key lessons from the Microsoft case. Our empirical results
+do indeed support this. \emph{Operating capabilities}) and \emph{strategic cognition} are
+complementary to each other in influencing competitive advantage meaning that businesses
+will not succeed properly without being conscious of both.
 
-Specifically, we ask the following research question:
+\section{Concluding remarks}
 
-{\bf What is the role of non-behavioral objects of change as a mechanism through which
-  dynamic capabilities can influence competitive advantage?}
+We started this inquire with the aim to shed light on non-behavioral objects of change as
+an alternative mechanism between dynamic capabilities and competitive advantage. Inspired
+by the novelty of insights into the 'human side of dynamic capabilities'
+\citep{Verona2011,Zollo2016}, the forceful transformation of Microsoft (Nadella), and the
+call to investigate new mechanisms (mediators) in dynamic capabilities
+\citep{Schilke2018}, we set out to analyze the role of these non-behavioral objects of
+change. Indeed, both research and practical interest in dynamic capabilities largely stems
+from the promise of delivering competitive advantage - the 'holy grail' of strategic
+management \citep{Helfat2007,Schilke2018,Peteraf2013}. Thus, really understanding the
+mechanisms \emph{through} which dynamic capabilities can influence competitive advantage,
+is of crucial importance.
 
-To shed light on this important question we theorize on the role of a particular type of
-non-behavioral object of change, \emph{strategic cognition}, and how it acts as a
-mediator between dynamic capabilities and firm competitive advantage and hence has a
-pivotal place in the literature. We build on important work on the concept of
-organizational cognition (ref), non-behavioral object of change (ref) and cognitive
-psychology (kahneman and tversky),
-and hypothesize about how strategic cognition acts as a mediator in the same way as
-conventional behavioral objects of change (such as routines and capabilities) and that
-these two are complementary to a certain degree. Consequently, we argue, dynamic capabilities takes
-the function of a 'conductor' by orchestrating routines and capabilities, and the role of
-a 'coach' in stimulating strategic cognition. We use the case of Microsoft's transition
-into the cloud computing business as an illuminating case for demonstrating how the roles
-of 'conductor' and 'coach' coexist and act partly complimentary in generating strategic
-change and competitive advantage.
+Using recent contributions on the role of cognition in strategy
+\citep{Gavetti2012,Zollo2016,Verona2011} we hypothesized about the role strategic
+cognition, defined as 'conceptual structures in the minds of the individuals that
+encapsulate a shared understanding of the reality the individuals face with respect to
+the strategic goal of the organization'.
+
+Using a survey of $262$ Norwegian technology firms we constructed latent variables
+capturing the focal constructs of dynamic capabilities theory. Using PLS-SEM analysis we
+were able to analyze the relationships between these constructs, specifically the role of
+\emph{operating capabilities} and \emph{strategic cognition} as measured by capabilities
+for daily tasks, and proactiveness respectively. We found that these two are separate
+constructs both acting as mediators between dynamic capabilities and competitive
+advantage. Moreover, an interaction analysis also suggest that they are indeed
+complementary to each other.
+
+We have aimed at using this holistic approach to dynamic capabilities theory to explain
+firm competitive advantage - the 'holy grail' of strategic management \citep{Schilke2018}.
+Specifically we have tried to push the theory forward in understanding of \emph{how}
+dynamic capabilities work to influence firms' competitive advantage. Our contributions
+have been threefold. First, we clarified the theoretical role of non-behavioral objects of
+change and suggested a possible empirical operationalization through the concept of
+\emph{proactiveness}. Second, we suggested and demonstrated two different expressions of
+dynamic capabilities (i.e. {\bf conductor} and {\bf coach}) as well as their workings in
+the dynamic capabilities-competitive advantage nexus. We also extend this reasoning to
+include how they relate to each other. Third, we utilized time-lagged data in conjunction
+with advances in empirical estimations of multiple simultaneous mediators. In doing these
+three we believe we have helped to push our understanding of important mechanisms in the
+dynamic capabilities theory.
+
+This paper has several limitations however. First, it has been hard to capture the full
+extent of the focal constructs empirically. We have had to settle for few items to capture
+the full magnitude of the mechanisms. Future research should focus on establishing more
+comprehensive operationalization of key constructs in order to better test the
+theory. Second, we have leaned a lot on one case study to motivate our work. Although
+Microsoft is an interesting and important case, future research should include more case
+studies with more in-depth analysis to really get under the proposed mechanisms. Third,
+our sample size is on the smaller size. Granted, PLS-SEM is able to capture rather
+consistent estimates on small samples, larger samples would enable researchers to extend
+the analysis further. More industries and countries should also be included in the
+analysis, and more observations over time would be helpful in analyzing more causal claims
+in the theory.
+
+These limitations aside, we believe that this paper has helped to push the theory in a
+more 'holistic' direction as suggested by \cite{Verona2011} and hence answering the call
+for investigating more mechanisms in the dynamic capabilities theory \citep{Schilke2018}.
 

### 2019-11-18 article4_notes.tex
Paper 4 ready for submission to Tommy

@@
+%Mindset induction effects on cognitive control: a neurobehavioral investigation.
+%Schroder HS, Moran TP, Donnellan MB, Moser JS
+%Biol Psychol. 2014 Dec; 103():27-37.
+
+%12. Yeager D.S., Dweck C.S. Mindsets that promote resilience: When students believe that personal characteristics can be developed. Educ. Psych%ol. 2012;47:302–314
+
+Proactiveness is an opportunity-seeking, forward-looking perspective characterized by the introduction of new products and ser- vices ahead of the competition and acting in anticipation of future demand.
+
+Proacteivenss can create psychological ownership (siegel 
+We build on these theoretical considerations by applying the concept of psychological ownership (Pierce et al., 2003), defined as ‘the state in which individuals feel as though the target of ownership or a piece of that target is “theirs” ’ (Pierce et al., 2003, p.
+86)
+
+Missing link between growth mindset and internal motivation
+https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5836039/
+
+Growth mindset and individual proactivity
+https://www.emerald.com/insight/content/doi/10.1108/CDI-11-2016-0194/full/html
+
+To be clear, the importance of motivation and, in particular, its strategic relevance for
+organi- zational performance and competitive advan- tage has surfaced in some recent
+contributions in the strategic management field. Managerial rent theorists (Castanias &
+Helfat, 1991, 2001), for example, submit that the availability of skills that have rent
+generation potential is a neces- sary but not sufficient condition for rent gener-
+ation. In so doing, they also point to the impor- tance of motivation for the realization
+of any such potential. Similarly, Coff (1997) discusses a number of dilemmas firms face in
+generating an advantage from human assets, and he points to the importance of governance
+mechanisms to overcome them. Finally, Makadok (2003) calls for future research into the
+genesis of competitive advantage in a way that combines competence- based issues with
+questions of governance or motivation.
+
+of the
+company’s existence and what defi nes or limits its role(s) within its social and eco-
+nomic environment (organizational identity)? What does it stand for (organizational val-
+ues)? How are things done over here (organizational culture)?
+
+include norms (leonard Barton 1992), avoidance of cognitive
+inertia (Trpisas and Gavetti 2000)
+
+organizational inertia
+Second, 
+The existence of layer upon layer of standard procedures, established capabilities, complementary assets, and/or admin- istrative routines can exacerbate decision-making biases against innovation.
+Incumbent enterprises,
+
+Individuals are the unit of analysis embedding these abilities and if left up to
+these individuals without a higher organizing framework, the firm will be very vulnerable
+because of knowledge asymmetries and incentive problems (alchian and demsetz 1972) and
+lead to sub optimal rent-appropriation on the part of the individual employee
+\citep{Blyler2003}. A similar argument applies to the function of \emph{seizing} where the
+organization is set to mobilize resources for the purpose of gaining from these
+opportunities. In order for value to be captured from opportunities, a string of
+conditions have to be met \citep{Teece2017}, but the evolution of a 'strong and
+change-oriented organizational culture' \citep[p. 331]{Teece2014} is of pivotal
+importance. Alas the sensing process requires new knowledge from a wide range of sources
+in the organization a lot of this tacit knowledge can lead to rent-appropriation
+from information asymmetries if not sufficiently aligned with the
+cognitive frames of the organization \citep{Blyler2003}. Furthermore, as cognition plays
+an important role in the sensing and seizing of opportunities \citep{Helfat2015} and the
+interpretation and understanding varies with individuals position within the
+organization, then diverging interpretations stemming from misaligned cognitive frames may
+lead to
+
+They maintain that social capital and notably individuals’ valuable internal and external social ties allow for information sharing, innovation and novel ways of thinking which in turn helps managers understand resource acquisition, integration and release
+
+Although they relate the existence of social capital
+as an antecedents to dynamic capabilities, the same argument can be applied to their
+function; to be able to capture rents for the organization and not the individual a
+certain level of social capital is needed and
+
+“firms would be unable to acquire, recombine, and release resources”
+resources” (2003: 680) without the social capital of individuals. Hence need to build
+social capital. Growth mindset - cognitive frames important to build social captail within
+the organization?
+
+One consequence is a ‘program persistence bias.’ Its corollary is various forms of
+‘anti-innovation bias,’ including the ‘anti- cannibalization’ basis discussed in a later
+section. Program persistence refers to the funding of pro- grams beyond what can be
+sustained on the merits,
+
+the emphasis is on the intermediary role of "asset
+orchestration" \citep{Teece2012,Sirmon2011} as related to the "the selection, con-
+figuration, alignment, and modification of tangible and intangible assets"
+\citep[p.842]{Helfat2015}. This process is very much similar to the exploration and
+exploitation of opportunities and we consider reconfiguration to come into the focus when
+these processes are seen over time and in changing contexts. Hence we are limiting this
+study to looking at the sensing and seizing class of dynamic capabilities.
+
+However, in this endeavour
+simply adatping resources is a necessary but not sufficient condition for obtaining the
+needed strategic change.
+
+The functions of dynamic capabilities as highlighted above is thoroughly discussed in
+extant literature (refs), but a quick recap is useful.
+
+DC geared towards creating new or reconfiguring old (exploration vs exploitation) but true
+competetiveness over time stems from ambidexterity- link to research on cultural ambidecterity
+
+To see how dynamic capabilities work to adapt cognitive frames in addition to operational
+capabilities to influence competetive advantage, it is useful to turn to their
+microfoundations \citep{Teece2007}. In this framework dynamic capabilities work through
+three expressions. First, sensing seizing. more here..
+
+Each of these dimensions relates to a function of cognitive frames within the firm beyond
+the cognitive frames of the dynamic capability itself as explored by previous
+contributions in general \citep{Teece2007} and towards management specifically
+\citep{Helfat2015,Helfat2015a}. First, sensing opportunities in the market relates to
+discovering market disequilibrium \citep{Kirzner1997} as well as upsetting existing
+equilibria \citep{Schumpeter1934}. This process is very much at the core of dynamic
+capabilities as a function of management, but its function calls for a very close
+relationship with the rest of the organization both in terms of resource orchestration and
+cognitive programming. The process of sensing 'involves understanding latent demand, the
+structural evolution of industries and markets, and likely supplier and competitor
+responses' \citep[p. 1322]{Teece2007}. Individuals are the unit of analysis embedding
+these abilities and if left up to these individuals without a higher organizing
+framework, the firm will be very vulnerable because of knowledge asymmetries and incentive
+problems (alchian and demsetz 1972) and lead to sub optimal rent-appropriation on the part
+of the individual employee \citep{Blyler2003}.
+
+A similar argument applies to the function of \emph{seizing} where the organization is set
+to mobilize resources for the purpose of gaining from these opportunities. In order for
+value to be captured from opportunities, a string of conditions have to be met
+\citep{Teece2017}, but the evolution of a 'strong and change-oriented organizational
+culture' \citep[p. 331]{Teece2014} is of pivotal importance. Alas the sensing process
+requires new knowledge from a wide range of sources in the organization a lot of this
+knowledge is tacit and can lead to rent-appropriation from information asymmetries
+\citep{Blyler2003} if not sufficiently aligned with the cognitive frames of the
+organization.
+
+Finally, the \emph{transformation} function of dynamic capabilities are related to the
+idea of continuously renewal of the resource base in order to stay competitive. This continuous
+process requires the development and maintenance of a share cognitive frame such as a
+culture, which is typically found in production processes such as LEAN and Six Sigma
+(ref).
+
+Looking at dynamic capabilities through the functions of sensing, seizing and
+transformation makes an obvious case for resource orchestration which is also highlighted
+in the extant literature. Moreover, as discussed above, these functions are also requiring
+a certain non-behavioral object of action in order to be fully efficient. To achieve a
+competitive edge firms will have to be able to sense and seize, which require a certain
+organizational cognitive frame to be efficient. 'Dynamic capabilities are about doing the
+right things, at the right time, based on new product (and process) development, unique
+managerial orchestration processes, a strong and change-oriented organizational culture'
+\cite[p]{Teece2014}.
+
+It is argued that contextual ambidexterity is grounded in the type of organizational culture (Ghoshal and Bartlett 1994; Gibson and Birkinshaw 2004; Simsek et al.
+2009) that promotes both creativity and discipline (Jelinek and Schoonhoven 1993), or both the presence of different knowledge and the integration of multiple perspectives to develop a cohesive point of view (Eisenhardt and Schoonhoven 1990).
+
+ambidextrous organizational culture wang rafiq 2014
+
+The enterprise will be vulner- able if the sensing, creative, and learning functions are left to the cognitive traits of a few individuals
+
+Three types of managerial activities can make a capability dynamic: sensing (which means
+identifying and assessing opportunities outside your company), seizing (mobilizing your
+resources to capture value from those opportunities), and transforming (continuous
+renewal).
+
+Whereas ordinary capabilities are about doing
+things right, dynamic capabilities are about doing the right things, at the right time, based on new product (and process) development, unique mana- gerial orchestration processes, a strong and change- oriented organizational culture, and a prescient assessment of the business environment and tech- nological opportunities.
+teece 2014
+
+The strength of a firm's dynamic capabilities determines the speed and degree (and
+associated cost) of aligning the firm's resources—including its business model(s)—with
+customer needs and aspirations. To achieve this, organizations must be able to
+continuously sense and seize opportunities, and to periodically transform aspects of the
+organization and culture so as to be able to proactively reposition to address yet newer
+threats and opportunities as they arise. Terse 2018
+
+Dynamic capabilities are hard for rivals to replicate because they are built on the
+idiosyncratic characteristics of entrepreneurial managers and the history-honed routines
+and culture of the organization (Teece, 2014a). In addition, there is the uncertain
+imitability of a complex system that even those directly involved may not fully understand
+(Lippman and Rumelt, 1982). Because they are a unique and valuable general-purpose
+resource, strong dynamic capabilities can serve as a firm foundation for sustainable
+competitive advantage. This is especially true the more deeply embedded the capabilities
+are in the organization, and the less they are resident only in the top management
+team. Teece 2018
+
+ Managers must articulate a vision and establish an appropriate organizational culture and an incentive system that will promote organizational identification and loyalty (Augier and Teece, 2009).
+
+Put differ- ently, selecting the right ‘architecture’ for a busi- ness requires not just understanding the choices available; it also requires assembling the evidence needed to validate conjectures and hunches about costs, customers, competitors, complementors, dis- tributors, and suppliers.
+Designing
+
+Distinct rolle
+
+H1: Cognitive frames mediates the effect of dynamic capabilities on competetive advantage
+above and beyond mediating effect of operational capabilities
+
+H2: Cognitive frames has a direct impact on operational capabilities
+
+H3: Something to do with dynamism - importance of cognitive frames increases in dynamism
+
+Minor hypotheses: On
+
+The role of cognitive frames in strategy: Schilling 2018 abstraction
+
+Proactiveness
+Coff and Blyler - who reaps the reward from rents). cognitive frames common -
+proactiveness - culture can prohibit the rent appropriation happening
+
+Cognitive programming as rent appropriation inihibitor
+
+Cognitive programming as implementation catalyst (complement to OC)
+
+Cognitive programming as alignment mechanism (link to OC)
+
+Ethnographic study on cognitive farmes - still top management team
+http://knowledge.wharton.upenn.edu/wp-content/uploads/2013/09/13481.pdf
+
+Implications: Maybe proactiveness cog frames can help in the paradox schreyogg, and the
+elephant.
+
+We suggest that a systematic socio-cognitive approach to “competitive sensemaking” has
+been absent from theory and research on competitive strategy. We define competitive
+sensemaking as the social and cognitive processes that underlie how firms detect, define,
+and conceptualize their competitive relationships with other firms. Competitive
+sensemaking is a subset of the more general process of strategic sensemaking, which is the
+“making plausible sense” of the broad array of stimuli and circumstances that characterize
+complex market situations. Using the value-based view of value creation and capture as a
+conceptual base for our arguments, we unpack four cognitive underpinnings of competitive
+sensemaking: mental time travel, comparability, counterfactual reasoning, and stories. We
+then show how these four components were differentially involved in shaping competitive
+sensemaking in four actual market situations. In doing so, we illustrate how competitive
+sensemaking provides fundamental inputs into the value creation and value capture
+process. We conclude the paper by drawing out the implications of competitive sensemaking
+for strategy theory and research.
+
+Some strategic decisions will long be remembered for being remarkably successful, providing dramatic benefits to customers, investors, or social welfare.
+The individuals who make these decisions are often called "visionary." But what enables some people to be visionary?
+Is it a gift or skill, and can it be learned?
+In this paper I identify three main cognitive processes that underlie the creation of visionary strategy: abstraction, idealism, and long paths of analytical reasoning.
+Using a combination of examples and cognitive science, I explain how they work individually and in combination, and how they may be cultivated.
+Schiller
+
+Cognition explain organizational inertia garud and rappa
+Sharing of dominant logic pralahad and bettis (actually managmenet but maybe org as well)
+Tripsas and Gavetti 2000 focus on management cognition in digital imaging
+
+power of analogical reasoning prevailing in teh strategy makin in novel and complex worlds
+
+(Gavetti, 2012; Gavetti et al., 2005; Tripsas and Gavetti, 2000), awaiting from LB
+
+DCs are viewed as stable patterns of action that poten- tially build a string of temporary
+advantages by adding, integrating, and reconfi guring resources, which amount to sustained
+advantage once the entire pattern is taken into account (Blyler and Coff, 2003)
+
+Again, some acquiring fi rms (not many) undergo these motivational change processes (Gottschalg and Zollo, 2007) by
+
+would for the larger part argue that 
+including the 33000 people at nokia / cultural change rr
+
+Capabilities changes reinvent productivity and business processs, as well as introcuing
+new capabiltieis. 
+Cloud based capabilities and infrastructure
+
+'AS I conlcluded my talk that morning in orlando, i focused on what would be our grandest
+endeavor / the biggest hurdle, transforming the microsofg culture. p 89
+
+Defined culture as a 'complex system of individual mindsets' culture is how an
+organization thinks and acts, but indiciduals shape it. p 90
+
+%https://news.microsoft.com/2014/02/04/satya-nadella-email-to-employees-on-first-day-as-ceo/
+%https://qz.com/work/1539071/how-microsoft-ceo-satya-nadella-rebuilt-the-company-culture/
+
+%{\bf How is a direct link between dynamic capabiliites and competetive advantage working
+%  and under which conditions does it come into play or not?}
+
+In the face of a growing consensus on the definition (ref) and outcome (ref) of dynamic
+capabilities as working through mediators, the presence of direct effects argued by others
+(ref) seems puzzling. However, the broader empirical literature on the antecedents of firm
+performance offers an interesting point of departure. This literature concerns itself with
+the relative importance of factors at the firm-level on the one hand, and those at the
+industry level at the other.
+
+The debate over the relative role of different levels of factors in accounting for the
+major share of the variance in firms performance has been of particular importance in the
+field of strategic management, most notably in the Strategic Management Journal
+(M. A. Fitza 2014; Hansen and Wernerfelt 1989; McGahan and Porter 1997; Rumelt
+1991). Overall, the accumulated empirical evidence show that firm factors matter far more
+for firm performance than industry factors (McGahan and Porter 2002). These stylized facts
+have been used as empirical support for the importance of idiosyncratic firm resource and
+capabilities; leading up too recent formulation of the resource and capability based
+theorizing (e.g. (Barney 1991; Teece, Pisano, and Shuen 1997)). However, the dominance of
+the firm-level explanations have been partly refuted by later scholars finding the sum of
+indirect and direct effects from industry to be of more importance than previously
+indicated by (Mcgahan etc). Moreover, the industry effect is also more time invariant
+(i.e. more stable) compared to firm level effects. Recent findings also suggest that there
+are considerable interaction effects between industry and the firm indicating that
+industry membership works directly at performance as well as indirectly through affecting
+the firm. However, little or no explanations are made for the mechanisms of this
+interaction.In other words, industry factors matter alas less than firm-level factors, and
+the indirect link from industry-level through firms are in need of further development.
+
+One way of looking at this is to consider the dynamic capabilities of the firm. Although
+an increasing consensus focuses on these dynamic capabilities as the ability to create,
+extend and modify firm resources in the face of change, there still looms an important
+stream of literature suggesting that dynamic capabilities can materialize as management
+actions (ref eisenhardt, peteraf, helfat). A management action aimed at strategic change
+will very often entail "resource orchestration" as broadly discussed in the literature
+(Helfat etc). But, strategic change are also found to come about from adapting and
+changing the positioning of the firm within its industry (ref) or simply refocusing its
+focal industry (ref). In other words, when a firm with excellent dynamic capabiliites
+senses and seizes opportunities within its domain, the implementation of strategic change
+will often both entail a considerable share of "asset orchestration" (helfat etc) as well
+as management actions directed at positioning within its industry (ref). One way to
+illustrate this is to consider Microsofts strategic change from operating system to cloud
+provider. CEO Satya Nadela and his team was able to restart the business by creating,
+extending and modifying the resources of the firm, including new skills, routiens and
+hardware, as a response to a growing demand for cloud computing (ref nadellas
+book). Meanwhile, his vision and formulated strategy also direclty put the company into a
+new industry, or at the very least reshaped the position they were already in. While
+Microsofts dynamic capabiliites worked significantly through "resource orchestration",
+the sensing and seizing of the management also ordered a direct re-positioning at the same
+time.
+
+Moreover, The link between firm resources and competitive advantage is determined by the
+extent to which resources are valuable and difficult to imitate \citep{Barney1991a}. This
+principle is also used to evaluate how higher order capabilities (e.g. dynamic
+capabilities \citep{Winter2003,Collis1994,Teece2007}. Hence, for a direct link to exist
+the dynamic capabilities of the firm will have to be valuable and difficult to
+imitate. This is an area of certain contention in the literature \citep{Peteraf2013} which
+we get back to below, but an increasing majority is arguing that dynamic capabilities
+reflect more complex processes that co-evolve with responses to market changes over time
+and hence creating idiosyncratic capabilities that are unique, valuable and hard to copy
+\citep{Helfat2007,Arndt2018}. Consequently, they are likely to lead to competitive
+advantage.
+
+In most cases such direct effects between dynamic capabilities and strategic change
+resulting in competitive advantage, are combined with the indirect effects (i.e. resource
+orchestration). To test this proposition empirically is hard, but one hypothesis following
+from this is related to the role of mediators. if a direct path does not exist, the
+relationship between dynamic capabilities and competitive advantage would be fully
+mediated by the proper set of firm resources.
+
+\emph{H1: The existence of a direct path from dynamic capabilities to competitive advantage
+suggest that full mediation is not present}
+
+Even if the dynamic capabilities of the firm themselves are not valuable and inimitable as
+needed to create competitive advantage, the underlying resources of the firm may very well
+be. Such resources in the form of operating routines or capabilities can in turn stem from
+an inherent learning process evolutionary distinct to the firm. Operating routines can
+thus lead to competitive advantage because of their evolutionary character
+\citep{Nelson1982,Winter2003}. To the extent operating routines stems from idiosyncratic
+evolutionary process of individual firms rather than being the result of best practices,
+they can satisfy the VRIO condition and thus be a source of competitive advantage.  Hence,
+through "resource orchestration" a firm with non-valuable dynamic capabilities can achieve
+competitive advantage through the indirect path. The flip side of this is that a valuable
+dynamic capability would not be able to create competitive advantage by orchestrating
+non-valuable resources. Consequently, the mediation effects of underlying resources is
+dependent on the nature of the resource - it being valuable and inimitable or not.
+
+\emph{H2a: When dynamic capabilities are being mediated by VRIO resources the firm can
+  achieve competitive advantage}
+
+\emph{H2a: When dynamic capabilities are being mediated by VRIO resources the firm can not
+  achieve competitive advantage}
+
+DEspite a growing consensus on the nature of dynamic capabilites, a serious contention is
+presen tin the literature \citep{Peteraf2013}. This stems from different notions of
+dynamic capabilities in the two "founding" papers of the theory, \cite{Eisenhardt2000} and
+\cite{Teece1997}.
+
+One strand of contributions sees DC as routines that are simple in nature and more as best
+practices to consider \citep{Eisenhardt2000}. Thus, dynamic capabilities are more like
+behavioral patterns and less idiosyncratic to the firm and will consequently not be able
+to satisfy the VRIO condition for competitive advantage to emerge. Dynamic capabilities as
+such routines are short lived, unstable and “substitutable” (ibid, p 1110) thus violating
+a key VRIO condition, and they are more “more homogeneous (..) than is usually assumed”
+(ibid, 1116). However, the simplicity of simple rules also makes them faster do deploy and
+put in motion, albeit potentially unstable. To the extent dynamic capabilities manifest
+themselves as simple rules they cannot alone create competitive advantage, but could very
+well generate strategic change by facilitating the process of resource orchestration.. In
+other words, even if dynamic capabilities play out as simple rules that are not in
+themselves satisfying the VRIO condition, the way they work through creating, extending
+and modifying firm resources, can still yield competitive advantage through orchestrating
+VRIO resources.
+
+On the other hand, \cite{Teece1997} and others \cite{Helfat2007} argue that dynamic
+capabilities will rather invariably be VRIO due to the evolutionary nature of their
+development \citep{Arndt2018,Peteraf2013}. Arguing that dynamic capabilities reflect more
+complex processes that co-evolve with responses to market changes over time and hence
+creating idiosyncratic capabilities that are unique, valuable and hard to copy
+\citep{Helfat2007,Arndt2018}. Consequently, they are likely to satisfy the VRIO condition
+and thus leading to competitive advantage.
+
+The contention between these streams of literature is most explicit in highly dynamic
+environments (distefano, peteraf) suggesting that environmental dynamism could play into
+the presence of direct and indirect linkages between dynamic capabilities and competitive
+advantage. This is also supported in previous empirical literature \citep{Schilke2014}.
+This could suggest that dynamic capabilities exhibit different characteristics under
+various levels of environmental dynamism. This is also suggested by Eisenhardt blaboblabla
+arguing that under moderatly dynamism dynamic capabilities takes the form of best
+pracitces (e.g. aquisition targeting) and is less important than under more dynamic
+environments. However, albeit best practices, the way they are implemented in the factor
+markets are still idiosyncratic. And taken into conjunction with the routinzed process of
+changing underlying routines, VRIO will very likely emerge under more stable
+conditions. It is not that the market/direct expression of dynamic capabilities are not
+present in stable environments, rather it is less pronounced and the indirect mediated
+effect (evolutionary path) is more important. In other words, it is not neither nor, but
+degrees of importance.
+
+\emph{H3: The mediation effects of underlying resources is dependent on the environmental
+dynamism facing the firm }
+
+%% Increasingly the literature remain focused on an \emph{indirect
+%%   path} between dynamic capabilities and competitive advantage
+%% \citep{Barreto2010,Schilke2018}. The theory behind this path goes back to the core of
+%% dynamic capabilities where resource orchestration happens as a response to changes in the
+%% environment. When markets, technologies or other external factors changes, firms with high
+%% levels of dynamic capabilities are able to seize opportunities for changes, seize these
+%% opportunities and transform the resource base to fit the strategic change needed to stay
+%% competitive \cite{Teece2007}. This ability to adapt is by some coined \emph{evolutionary
+%%   fitness} defined as BLABLBALBA and stems from the ability of the firm to reconfigure
+%% resources in the face of change. The extant literature, however, is less clear on how the
+%% nature of the underlying resources matter in this indirect path. On the one hand we can
+%% see
+
+%% Following REF suggesting more reseaarch on dynamic capabilities should put forth
+%% competeing hypotheses we propose these first
+
+%% We introduce the notion of multilevel VRIO to integrate the interactions between different
+%% types of capabilities at different levels. This entails that dynamic capabilities (the
+%% high level) can consist of complex and evolutionary characteristics that are idiosyncratic
+%% to the firm and hence VRIO by definition along the lines of how the concept is understood
+%% by \cite{Teece1997}. On the other hand dynamic capabilities can also take the shape of
+%% simpler routines which are short lived, unstable and substitutable thus violating a key
+%% VRIO condition. This follows the notion of dynamic capabilities found in
+%% h\cite{Eisenhardt2000} arguing that they are more “more homogeneous (..) than is usually
+%% assumed” (EM: 1116).
+
+%% Moreover, these dynamic capabilities are in the extant literature argued and found to work
+%% directly \citep{Kor2005,Eriksson2014,Schilke2018} on competitive advantage which suggests
+%% that they are indeed VRIO. On the other hand, a growing body of literature (ref) as well
+%% a consensus on the definition of dynamic capabilities (ref), holds that they can lead to
+%% competitive advantage by changing underlying resources and routines. In this
+%% \emph{indirect path} the dynamic capabilities itself need not be VRIO as long as the
+%% underlying resources themselves are.
+
+%% \subsection{The role of dynamism}
+
+%% The most contentious issue in the current debate on dynamic capabilities is how their
+%% nature varies with the environment.
+
+%% If htey are indeed latent
+
+%% The lower level resources and routines are to be understood as conventional resources in
+%% line with the resources-based view
+
+%% WHAT IS THE ROLE OF DIRECT VS INDIRECT, HOW DOES IT RELATE TO THE ENVIRONMENT, AND WHAT
+%% ROLE DOES THE TYPE OF UNDERLYING RESOURCE PLAY
+
+%% Conventional dc literature has argued for both indirect and direct links. Indeed both
+%% have been found, but while the indirect link is well rooted in the theory, the direct link
+%% is to our knowledge less clear. The core idea of DC is that it works to modify underlying
+%% resources as a response to changes in the environment and hence creating strategic change
+%% needed to stay competitive. This resource orchestration is heavily represented in the
+%% literature (ref) and through this process firms are able to generate CA. In such instances
+%% the CA can stem from VRIO resources and/or VRIO DC. A VRIO DC would mean that the firm is able
+%% to shuffle and reorganize generic resources in a way that creates a new and unique
+%% configuration of resoures idiosyncratic and valuable to the firm. In such instances, the
+%% outcome whould be CA. On the other hand, the DC may not by itself be VRIO but rather a set
+%% of simple routines put in motion to change, but if the resources they reconfigure are
+%% themselves VRIO, the outcome could just as eqsily be a competetive advantage. this
+%% equfinaity is discussed in the literaure \cite{DiStefano2010} and makes it hard to
+%% distingusih between the role of DC and ordinary capabilites in generating CA.
+
+%% Furtemore, Considering a direct link between DC and CA, DC it self must consist of some
+%% VRIO characteristics to garner CA. So in owther words, when is DC working directly and
+%% indirectly_
+
+%% How are dynamic capabilities working directly on competitive advantage? The microfoundations of dynamic capabilities explicated by \cite{Teece2007} is a useful
+%% point of departure of this theoretical inquiry. He hold that for "analytical purposes,
+%% dynamic capabilities can be disaggregated into the capacity (1) to sense and shape
+%% opportunities and threats, (2) to seize opportunities, and (3) to maintain competitiveness
+%% through enhancing, combining, protecting, and, when necessary, reconfiguring the business
+%% enterprise’s intangible and tangible assets". Sensing and seizing is a part of what we
+%% would coin the "opportunity capture" of dynamic capabiliites, where as reconfiguring
+%% concerns itself with the "resource orchestration" needed to change assets to stay
+%% competetive.
+
+%% Hence, when considering indirect and direct paths to compettetive advantage we will have
+%% to be clear on two fronts: Are DC themselves VRIO and are the underlying resources and
+%% routines central to the resource orchestration, VRIO.
+
+%% >
+
+%% The microfoundations of dynamic capabilities—the distinct skills, processes, procedures, orga- nizational structures, decision rules, and disciplines—which undergird enterprise-level sensing, seizing, and reconfiguring capacities are difficult to develop and deploy.
+%% For analytical purposes, dynamic capabilities can be disaggregated into the capacity (1) to sense and shape opportunities and threats, (2) to seize opportunities, and (3) to maintain competitiveness through enhancing, combining, protecting, and, when necessary, reconfiguring the business enter- prise’s intangible and tangible assets.
+
+OC som mindset / non-vrio? organizational mindset
+DC influcences IOC 
+DC influences VOC
+
+two paths / changes resources vs change mindset
+
+why so interested in operating routines resources, what about other mechanisms
+Can dc change collective cognition?
+
+ENTP - EO coen and slevin
+
+%%        name Mean_est     t
+%% 3   DC -> P    0.396 6.157
+%% 4   DC -> R    0.416 8.104
+%% 5 DC -> CA1    0.239 4.018
+%% 8  P -> CA1    0.172 2.724
+%% 9  R -> CA1    0.081 1.262
+%% > R
+%%        Path   LOW     t  HIGH     t
+%% 1 DC -> CA1 0.417 6.585 0.144 1.513
+%% 2   DC -> R 0.388 6.078 0.534 7.525
+%% 3  R -> CA1 0.017 0.219 0.211 2.123
+%% > P
+%%        Path   LOW     t  HIGH     t
+%% 1 DC -> CA1 0.355 4.805 0.133 1.379
+%% 2   DC -> P 0.386 5.294 0.436 4.663
+%% 3  P -> CA1 0.155 2.193 0.232 2.315
+%% > B
+%%        name R_LOW_est   t.x R_HIGH_est   t.y
+%% 1 DC -> CA1     0.355 5.407      0.044 0.400
+%% 2   DC -> P     0.376 3.729      0.432 4.668
+%% 3   DC -> R     0.366 5.569      0.522 7.225
+%% 4  P -> CA1     0.158 1.989      0.220 2.357
+%% 5  R -> CA1     0.010 0.135      0.200 2.033
+%% >
+
+%% %% creating and One example
+%% %% is the role of post-acquisition routines where routines to identify and deal with
+%% %% acquisition partners are a source of generating strategic change (Eisenhardt and Sull
+%% %% 2001, ref). Another example is (see refs from Schilke 2018). The functioning of this
+%% %% expression of dynamic capabilities are more latent and hence mainly observable ex
+%% %% post. Hence we can see this as direct route to competitive advantage as this expression of
+%% %% dynamic capabilities work directly in the factor market in capturing resources
+%% %% needed for strategic change. We coin this direct connection as the \emph{market path}.
+
+%% On the other hand, a stream of contributions see dynamic capabilities as evolutionary and
+%% more complex routines (ref) or processes (ref) set to change underlying capabilities in
+%% the face of changing conditions (TPS). This notion stems from evolutionary economics
+%% \citep{Winter2003,Nelson1982} and the behavioral theory of the firm \citep{Cyert1963}
+%% holding that path dependency and complex processes for changing underlying operating
+%% routines are a source of competitive advantage for the firm. Along this indirect path
+%% change is gradual and running through changes in underlying routines. We coin this the
+%% \emph{evolutionary path}.
+
+%% These paths from dynamic capabilities to competitive advantage are different expressions
+%% of dynamic capabilities with different mediums of intermediation. The \emph{market path}
+%% works in the market and his hence not typically altering lower order capabilities and
+%% resources in the firm directly, but rather acquiring new ones. The source of competitive
+%% advantage along this path stems from the interaction with the other, \emph{evolutionary
+%%   path} in a dynamic bundle \citep{Peteraf2013}. Such interactions create a bundle of
+%% capabilities and routines that are socially complex and hard to imitate
+%% \citep[p. 320]{DiStefano2014}. Moreover, the interactions between the two paths of dynamic
+%% capabilities is separable with respect to what intermediation exist. Consequently,
+%% separate paths exist albeit a part of a dynamic bundle.
+
+%% \cite{DiStefano2014} propose an integrated framework where simple routines and more
+%% complex processes could contribute simultanously to the firms outcome, specifically its
+%% competitive advantage. In this framework, coined the "organizational drivetrain" the
+%% authors envision the movement of an organization as set in motion by a drivetrain system
+%% not unlike that of a bicycle.
+
+%% Building on the notion of an organizational drivetrain we argue that dynamic capabilities
+%% can indeed impact the organizational movement or change through two distinct but
+%% interconnected mechanisms (i.e. the crank set and the rear shifter). The two mechanisms
+%% consitutting the drivetrain is consistent with our notion of \emph{evolutionary path} and the \emph{market path}. The
+%% evolutionary path is instigated by more complex processes setting in motiong a chance in
+%% the lower order (operational) routines \cite{Collis1994,Winter2003}. In the drivetrain
+%% metaphor this path corresponds to change stemming from the front crank set of thich there
+%% are fewer gears, but with larger impact. This path is slower
+%% and yields a more idiosyncratic set of organizational routines which is very much in line
+%% with the idea put forth in the seminal founding papers \citep{Teece1997,Winter2003}.
+
+%% Seeing the bike rider and her efforts to handle the levers of control (i.e. the gear
+%% shifter) as the dynamic capability, and consider it not only as a management effort, but
+%% that of the organization as a whole. The process of changing front gears are more profound
+%% (i.e. evolutionary) and costly, and it is for larger and slower strategic
+%% changes. Operating with simple routines in factor markets, however, is quicker and the
+%% rider does this on a more frequent basis with less effort.
+
+%% H1: Dynamic capabilities works to create competitive advantage through two distinctly
+%% different paths.
+
+%% \subsection{The two paths of dynamic capabilities}
+%% The objective of strategic change is to enhance a firm’s competitive advantage
+%% (ref). Doing so over time makes for the evolutionary fitness of the firm
+%% \citep{Helfat2007}. When firms are developing capabilities for strategic change through
+%% creating, extending and modifying the resource base this means making decisions to develop
+%% operational routines. Such routines can in turn stem from an inherent learning process
+%% evolutionary distinct to the firm. Operating routines can thus lead to competitive
+%% advantage because of their evolutionary character \citep{Nelson1982,Winter2003}. To the
+%% extent operating routines stems from idiosyncratic evolutionary process of individual
+%% firms rather than being the result of investments in factor markets, they can satisfy the
+%% VRIO condition and thus be a source of competitive advantage. In such instances, dynamic
+%% capabilities work through operating routines in creating competitive advantage. This
+%% indirect impact on competitive advantage is very much at the core of the DC literature
+%% (ref). Firms with high dynamic capabilities will be able to better change operating
+%% routines to facilitate strategic change in response to changing conditions facing the
+%% firm. Dynamic capabilities then creates VRIO operating routines and hence competitive
+%% advantage. When this happens, firms changes their operating routines in a evolutionary
+%% making operating routines themselves OR itself satisfies the VRIO condition.
+
+%% \emph{H2: Dynamic capabilities has an indirect effect on competitive advantage through
+%%   changing the operating routines of the firm.}
+
+%% On the other hand, resources and capabilities can to a certain extent be captured in
+%% factor markets through investment decisions (ref) or through alliances (ref) or M\&A
+%% activates (ref). By acquiring resources through investments, the operating routines of the
+%% firms may not be directly affected. When these acquisitions happen as a response to
+%% systematic resource orchestration (ref), i.e. reshaping the resource mix to obtain
+%% coordinated resource deployments \citep{Kor2005,Pan2006}, they would indeed have potential
+%% performance implications for the firm. Moreover, when this process of resource acquisition
+%% process of DC develops a way to acquire and mix resource for the purpose of adapting to
+%% change, the resources themselves would not necessarily satisfy the VRIO condition. The way
+%% in which this happens may be much harder to imitate due to the complexities such routines
+%% exhibit. Although resources themselves exhibit clear equifinality in their impact on
+%% competitive advantage, combined with the simple routines of the orchestration
+%% (i.e. dynamic capabilities), the sum would likely satisfy the VRIO condition. This is
+%% especially true if routines are deployed rapidly in changing market conditions. In other
+%% words, there are several ways in which resources can be orchestrated to generate CA,
+%% whereas improved OR will always mean improved competitiveness et ceteris paribus. In such
+%% instances DC itself can lead to CA directly.
+
+%% \emph{H3: Dynamic capabilities has a direct effect on competitive advantage through the
+%%   process of resource orchestration and acquisition of resources in factor markets.}
+
+%% In other words, we would expect DC to have both a direct and an indirect impact on CA. The
+%% indirect impact stems from the \emph{evolutionary path} of complex processes, whereas the
+%% direct impact stems from the \emph{market path}.  Although both the direct and the
+%% indirect path stems from DC creating, extending and modifying the resource base (OR or
+%% factor market resources), the difference in the path’s stems from to what extent the
+%% mediating construct alone can by itself satisfy the VRIO condition. Operating routines
+%% can, due to their evolutionary nature, in turn shaped by DC, achieve CA
+%% \citep{Collis1994,Winter2003}. Factor market resources and market acquired capabilities
+%% and best practices can not \citep{Eisenhardt2000,Peteraf2013}, but in conjuncture with the
+%% routines of acting in factor markets as well as the speed of deployment, the sum of
+%% dynamic capabilities and factor market action would lead to competitive advantage.
+
+%% However, the interlinkages between simple routines (the market path) and the coplex
+%% processes (the evolutionary path) would vary with the environment.
+
+%% \subsection{Interplay under environmental dynamism}
+
+%% \cite{DiStefano2014} note that "even if specific simple rules are unstable and ephemeral,
+%% the system as a whole is not" and that the "real source of sustainable competitive ad- vantage for an enterprise is the difficulty of imitating and substituting for the entire dynamic bundle that the system represents" (p.sss).
+
+%% But the interlinkages between the parts of the system (the evolutionary- and the market
+%% path), are likely to vary with the environmental dynamism. Under moderatly dynamism
+%% dynamic capabilities takes the form of best pracitces (e.g. aquisition targeting) and is
+%% less important than under more dynamic environments. However, albeit best practices, the
+%% way they are implemented in the factor markets are still idiosyncratic. And taken into
+%% conjunction with the routinzed process of changing underlying routines, VRIO will very
+%% likely emerge under more stable conditions. It is not that the market/direct expression
+%% of dynamic capabilities are not present in stable environments, rather it is less pronounced and the indirect
+%% mediated effect (evolutionary path) is more important. In other words, it is not neither
+%% nor, but degrees of importance.
+
+%% Moreover, in high velocity environments the role of the evolutionary path tends to
+%% weaken as such path-dependent changes occur slower compared to the market path. From the
+%% market path with its simple routines we can argue that creation of "new knowledge” to
+%% “allow for emergent adaptation” (EM, p. 1116) is the consequence. Consequently, the market
+%% path is stronger and more prevalent under higher levels of environmental dynamism.
+
+%% \emph{H4: Dynamic capabilities works relatively stronger through the market path in highly
+%% dynamic environments.}
+
+To see how dynamic capabilities work as 'coach' we consider two 
+Looking at dynamic capabilities through the functions of sensing and seizing opportunities
+\cite{Teece2007} makes an obvious case for resource orchestration which is also
+highlighted in the extant literature. This function is related to the discovering and
+capturing opportunities (e.g. the ability of the organization to sense and seize
+opportunities (ibid)) which is very much related to the concept of exploration
+\citep{March1991}. Moreover, as discussed above, these functions are also requiring a
+certain non-behavioral object of action in order to be fully efficient. To achieve a
+competitive edge firms will have to be able to sense and seize, which require a certain
+organizational cognitive frame to be efficient.
+
+changes resulting from execution of dynamic capabilities (e.g. sensing and seizing) may
+move existing organizational objective functions and thus render current incentive
+alignment obsolete or out of place. This leads to an objective displacement that is
+particularly prevalent in firms with high sensing and seizing capabilities because distant
+search may lead to more radical change (ref). Organizations with high levels of dynamic
+capabilities geared towards sensing and seizing opportunities are doing so through
+\emph{resource orchestration}, e.g. by creating, extending and modifying the resource
+base, as discussed extensively in the extant literature
+\citep{Helfat2007,DiStefano2014,Protogerou2012,Schilke2018}. However, sensing and seizing
+opportunities in the market relates to discovering market disequilibrium
+\citep{Kirzner1997} as well as upsetting existing equilibria \citep{Schumpeter1934}. The
+process of sensing and seizing 'involves understanding latent demand, the structural
+evolution of industries and markets, and likely supplier and competitor responses'
+\citep[p. 1322]{Teece2007} as well as 'a good deal of customer, competitor, and supplier
+information and intelligence (with a) a significant tacit component' (ibid p 1330).To make
+sure the organization respond to changes (i.e. having an efficient cognitive frame)
+stemming from executed dynamic capabilities (e.g. sensing and seizing) the firm needs to
+make sure incentives are aligned for change and that the organization buys into the changes.
+
+First, the \emph{incentive alignment problem} relates to how interests of the firm
+as a whole and the collection of individual are aligned \cite{Gottschalg2007} and how this
+alignment changes when the firm embarks on strategic change as triggered by execution of
+dynamic capabilities. Through the process of exploration, individuals in the organization
+may accumulate private and tacit information that, if unchecked, can become a source of
+knowledge asymmetries and incentive problems (alchian and demsetz 1972), and leave the
+firm vulnerable to agency problems. Accumulation of private information in the
+organization without incentive alignment of some sort can lead rent-appropriation from
+information asymmetries \citep{Blyler2003}. In such instances of potential misalignment of
+interest, a shared cognitive frame emphasizing a growth mindset can be a useful remedy.
+
+Second, the \emph{buy-in problem} refers to the general willingness of the organization to
+accept and value the importance of some decision or system 'without being prompted or
+required by formal governance mechanisms'\citep[p. 812]{Simsek2009}. When individuals of
+a firm buys into changes they will enhance the full organization`s ability to not only act
+upon changes (Marchand et.al 2000), but also in 'timely responsiveness' (Kohli et.al 1993,
+Simsek2009).
+
+Both the incentive alignment problem and the buy-in problem are interrelated, but still
+represents different mechanisms. They are tied to individual motivation albeit in
+different ways. The incentive alignment problem is tied to \emph{extrinsic motivation}
+(Lindenberg 2001, Brief and Aldag 1977) where the individual is motivated by rewards or
+outcome 'such as money, power, recognition and so forth'
+\citep[p. 420]{Gottschalg2007}. The buy-in problem, in turn, is related to \emph{intrinsic
+  motivation} where the individual is driven by the goal of being engaged in enjoyable
+(Lindenberg, 2001), self-determined, and competence-enhancing (Deci \& Ryan, 1985)
+behavior (hedonistic intrinsic motivation), as well as adhering to a goal of engaging in
+behavior that is compli- ant with norms and values (normative intrinsic
+motivation). \todo{some direct citations here - need rewrite}.
+
+Extrinsic motivation is often addressed through reward systems (ref) but tacit mechanisms
+such as psychological ownership \citep{Sieger2013} has been found to be very efficient in
+aligning incentives. Psychological ownership basically retains agency theory’s assumption
+of the self-interested manager, whereas the non-economic functions of ownership, such as
+efficacy, identity, and territoriality, might curtail expropriating behaviour and align
+the interests of agents and principals (cf. Pierce et al., 2003). Hence, this concept of
+psychological ownership bridges over to the intrinsic motivation of individuals. Moreover,
+intrinsic motivation in general is influenced through changing the tasks of individuals or
+at the very least accepting individuals to change ttasks themselves to fit their
+perception of their context (Hackman and Gersick), and through regimes of socialization
+and shared norms (Kerr and Jackofsky). Common for both psychological ownership and the
+intrinsic motivation enhancement in general is a feature of the employees' cognitive
+framing, which guides the mental pathways by which they decide what is, and what is not,
+important. According to Leonard- Barton (1992), these norms and values represent the
+accretion of decisions made over time in response to the interpretation of organizational
+roles. Consequently, a cognitive frame that enhances the intrinsic motivation of the
+employees are very valuable. One way of thinking of instilling an appropriate and
+efficient cognitive frame would be the concept of a growth mindset (Dweck) as also
+emphasized in the case of Microsoft.
+
+To see how this would work recent contribution in neuroscience is helpful. Several
+contributions have established a clear connection between having a growth mindset (Dweck 200x) and
+emphasizing intrinsic motivation (Schroder et.al 2014,O`Rourke et.al 2014). Moreover,
+individuals with higher degrees of intrinsic motivation from a growth mindset exhibit a
+significant higher ability for learning and consequently for embracing new learning
+opportunities (Yeager et al 2012). In other words, individuals with a growth mindset are
+more open to change because it enhances their intrinsic motivation from learning which
+fuels their individual utility (Ng 2018). In a situation with considerable change stemming
+from execution of dynamic capabilities, an organization with a common cognitive frame
+based on a growth mindset will be able to capture more value from the change \emph{et
+  ceteris paribus}.
+
+Consequently, by instilling a growth mindset as a change in the cognitive frame of
+Microsoft, Nadella enhanced the change ability of the firm by strengthening the intrinsic
+motivation employees have to buy into the change, and meanwhile securing a certain
+interest alignment. So Nadella did not only change the resources and capabilites of the
+company due to a strategic change towards the cloud, he did also instill a growth mindset
+to utilize the motivational and non-behavioral object of action discussed above. In other
+words, dynamic capabilites can work through two distinctly different paths. The first path
+is the familiar process of changing underlying resources and operational capabilities
+(\emph{resource orchestration path}). The second is the focal path of this paper where
+dynamic capabilities changes the cognitive frames of the organization \emph{cognitive
+  programmer path}. This leads us to the following initial hypotheses:
+
+H1: Dynamic capabilities influences the quality? of operational capabilities
+
+H2: Dynamic capabilities influences the WHAT of cognitive frames
+
+The link between operational capabilities enacted through dynamic capabilites, and
+competetive advantage is well established in the literature (refs). The main notion is
+that resources and capabilites evolved through dynamic capabilites are inimatable and
+rare, and hence conducive to the conditions underpinning competetive advantage (refs
+barney). Thus our third hypothesis is well known as the first one:
+
+H3: Operational capabilites acts as a mediator between dynamic capabiliites and
+competetive advantage.
+
+Similarly, instilling a growth mindset is also leading to competetive advantge BECAUSE???
+\todo{Need to discuss this}
+
+And one more hpythoses on how COG influences resources
+
+THIS IS HOW FAR I CAME
+
+the general capability, views, norms and rules of behavior, with regard to accessing,
+understanding and using information in a social collectivity. Zheng 2005
+
+To make sure that these interests are aligned
+
+DC executed requires changes. These changes will require a simultanous change in cognitive
+frames of the firm for N reasons.
+
+1. Sensing and seizing activities typicaly of dynamic capabilities generate possible
+agency problems *blyler coff
+2. Information from the process is interpreted and differently at different levels in the
+corporate hierarchy (gavetti) hence aligning interpretation across the organization matter
+
+One way of overcoming this agency problems and varying interpratations of the environment,
+is to develop a common cognitive frame within which all information is interpreted and
+acted upon. Such common traits purpose and organizational identity, 
+organizatioanl values and culture \citep{Verona2011}.
+
+To see how dynamic capabilities acts through cognitive objects of action (i.e. as a
+cognitive programmer) we consider two distinctly different functions of dynamic
+capabilities related to their microfoundations \citep{Teece2007}. The first function is
+related to the discovering and capturing opportunities (e.g. the ability of the
+organization to sense and seize opportunities (ibid)) which is very much related to the
+concept of exploration \citep{March1991}. Organizations with high levels of dynamic
+capabilities geared towards sensing and seizing opportunities are doing so through
+\emph{resource orchestration}, e.g. by creating, extending and modifying the resource
+base, as discussed extensively in the extant literature
+\citep{Helfat2007,DiStefano2014,Protogerou2012,Schilke2018}. However, sensing and seizing
+opportunities in the market relates to discovering market disequilibrium
+\citep{Kirzner1997} as well as upsetting existing equilibria \citep{Schumpeter1934}. The
+process of sensing and seizing 'involves understanding latent demand, the structural
+evolution of industries and markets, and likely supplier and competitor responses'
+\citep[p. 1322]{Teece2007} as well as 'a good deal of customer, competitor, and supplier
+information and intelligence (with a) a significant tacit component' (ibid p
+1330). Consequently, in this process of exploration individuals in the organization may
+accumulate private and tacit information that, if unchecked, can become a source of
+knowledge asymmetries and incentive problems (alchian and demsetz 1972), and leave the
+firm vulnerable to agency problems. Accumulation of private information in the
+organization without incentive alignment of some sort can lead rent-appropriation from
+information asymmetries \citep{Blyler2003}. One way to  if not sufficiently aligned with the
+cognitive frames of the organization. This particular
+
 The other path, the market path, is characerized by smaller routines and practices that

### 2019-11-18 figure/fullmod.tex
Paper 4 ready for submission to Tommy

@@
    \centering
-   \tikzstyle{mynode}=[circle,draw, ultra thin, draw=black, fill=white, minimum size=17mm,inner sep=0pt, align=center]
+   \tikzstyle{mynode}=[circle,draw, ultra thin, draw=black, fill=white, minimum
+   size=17mm,inner sep=0pt, align=center]
 
-   \node[mynode] (dc1){$DC_P$};
-   \node[mynode,below of=dc1, yshift=-2cm] (dc2){$DC_X$};
-   \node[mynode,right of=dc1, xshift=3cm] (or){$P$};
-   \node[mynode,right of=dc2, xshift=3cm] (ma){$R$};
-   \node[mynode,right of=ma, xshift=3cm, yshift=1.5cm] (ca){$CA$};
+   \tikzstyle{mytext}=[fill=none, minimum
+   size=17mm,inner sep=0pt, align=center]
+
+   \node[mynode] (dc1){$DC$};
+
+   \node[mynode,right of=dc1, yshift= 2cm, xshift=2.5cm] (cap){$CAP$};
+   \node[mynode,right of=dc1, yshift=-2cm,xshift=2.5cm] (cog){$COG$};
+   \node[mynode,right of=dc1, xshift=6cm] (ca){$CA$};
+   \node[mytext,above of=dc1,rotate=36, xshift=1.6cm,yshift=0cm] (ro){\bf Conductor};
+   \node[mytext,above of=dc1,rotate=-36, xshift=2.8cm,yshift=-1.5cm] (cp){\bf Coach};
+
+   \draw[-latex] (dc1.north east) -- node[text width=0.5cm,font=\footnotesize, above=2pt,align=left,
+   fill=none] {} (cap.west);
+
+    \draw[-latex] (dc1.south east) -- node[text width=0.5cm,font=\footnotesize, above=2pt,align=left,
+     fill=none] {} (cog.west);
+
+    \draw[-latex] (cap.east) -- node[text width=0.5cm,font=\footnotesize, above=2pt,align=left,
+      fill=none] {} (ca.north west);
+
+    \draw[-latex] (cog.east) -- node[text width=0.5cm,font=\footnotesize, above=2pt,align=left,
+    fill=none] {} (ca.south west);
 
         \draw[-latex] (dc1.east) -- node[text width=0.5cm,font=\footnotesize, above=2pt,align=left,
-   fill=white] {$0.129^{*}$} (or.west);
+      fill=none] {} (ca.west);
 
-   \draw[-latex] (dc2.east) -- node[text width=0.5cm,font=\footnotesize, above=2pt, align=left,
-   fill=white] {$-0.091^{}$} (ma.west);
+   %\draw[-latex] (dc2.east) -- node[text width=0.5cm,font=\footnotesize, above=2pt, align=left,
+   %fill=none] {} (cap.west);
 
-   \draw[-latex] (dc1.south east) -- node[text width=0.5cm,font=\footnotesize,  above=2pt,
-   align=left, fill=white,sloped, near end] {$0.496^{***}$} (ma.north west);
+   %\draw[-latex] (dc1.south east) -- node[text width=0.5cm,font=\footnotesize,  above=2pt,
+   %align=left, fill=white,sloped, near end] {$0.496^{***}$} (ma.north west);
 
-   \draw[-latex] (dc2.north east) -- node[text width=0.5cm,font=\footnotesize, above=2pt,align=left,
-   fill=white,sloped, near end]{$0.343^{***}$} (or.south west);
+   %\draw[-latex] (dc2.north east) -- node[text width=0.5cm,font=\footnotesize, above=2pt,align=left,
+   %fill=white,sloped, near end]{$0.343^{***}$} (or.south west);
 
-    \draw[-latex] (or.east) -- node[text width=0.5cm,font=\footnotesize, align=left,above=2pt,
-   fill=white,sloped]{$0.185^{***}$} (ca.north west);
+    %\draw[-latex] (or.east) -- node[text width=0.5cm,font=\footnotesize, align=left,above=2pt,
+   %fill=white,sloped]{$0.185^{***}$} (ca.north west);
 
-   \draw[-latex] (ma.east) -- node[text width=0.5cm,font=\footnotesize, below=2pt,
-   fill=white,sloped]{$0.123^{**}$} (ca.south west);
+   %\draw[-latex] (ma.east) -- node[text width=0.5cm,font=\footnotesize, below=2pt,
+   %fill=white,sloped]{$0.123^{**}$} (ca.south west);
 
-   \draw[-latex] (dc1.north)[bend left] to node[text width=0.5cm,font=\footnotesize, above=2pt,align=center,
-   fill=white]{$0.299^{***}$}(ca.north);
+   %\draw[-latex] (dc1.north)[bend left] to node[text width=0.5cm,font=\footnotesize, above=2pt,align=center,
 
-   \draw[-latex] (dc2.south)[bend right] to node[text width=0.5cm,font=\footnotesize,below=2pt, align=left,
-   fill=white]{$-0.066^{}$} (ca.south);
+   %fill=white]{$0.299^{***}$}(ca.north);
+
+   %\draw[-latex] (dc2.south)[bend right] to node[text width=0.5cm,font=\footnotesize,below=2pt, align=left,
+   %fill=white]{$-0.066^{}$} (ca.south);
 

### 2019-12-11 article4_jbr.rnw
Ready for submission

@@
 
-\title{A Tale of Two Mechanisms: How mediators act and interact in dynamic capabilities
-  theory\\ Lock, Stock and Two Convoking Mechanisms: Towards a holistic theory of dynamic
-  capabilitie }
+\title{One goal, two paths: How dynamic capabilities enable competitive advantage through behavioral and non-behavioral objects of change}
 %\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
@@
 \begin{abstract}
-This paper investigates strategic cognition as mediating factor in the dynamic
-capabilities-competitive advantage relationship. By including strategic cognition into the
-analysis in addition to the conventional mediator (operating capabilities) we argue that a
-more holistic approach to understanding the workings of dynamic capabilities emerges. We
-introduce two expressions of how dynamic capabilities work, namely as a conductor (the
-conventional mechanism) and as a coach (the cognitive mechanism). Using repeated
-cross-sectional data from Norwegian technology firms our results indicate support for our
-holistic model. This has implications for understanding how dynamic capabilites work, as
-well as practical implications for how strategic change is implemented in firms.
+% This paper investigates strategic cognition as mediating factor in the dynamic
+% capabilities-competitive advantage relationship. By including strategic cognition into the
+% analysis in addition to the conventional mediator (operating capabilities) we argue that a
+% more holistic approach to understanding the workings of dynamic capabilities emerges. We
+% introduce two expressions of how dynamic capabilities work, namely as a conductor (the
+% conventional mechanism) and as a coach (the cognitive mechanism). Using repeated
+% cross-sectional data from Norwegian technology firms our results indicate support for our
+% holistic model. This has implications for understanding how dynamic capabilites work, as
+% well as practical implications for how strategic change is implemented in firms.
+
+  The ultimate goal in the theory of dynamic capabilities (DCs) is competitive advantage.
+  This paper analyzes to what extent DCs influence competitive advantage through two paths
+  - one old, and one new - namely behavioral and non-behavioral objects of change.  In
+  addition to emergent theorizing and real world examples, we use the metaphor of “DC as
+  coach” and DC as conductor” to build a conceptual model and derive hypotheses.  Using
+  longitudinal survey data with a 10 year time lag we find that DCs influence competitive
+  advantage through both paths. Thus, the paper empirically validates emergent theorizing
+  proposing non-behavioral objects of change as a new path between DC and competitive
+  advantage. Moreover, the paper helps to broaden the conceptual basis for empirically
+  investigating how DCs enable competitive advantage. This has implications for
+  understanding how dynamic capabilities work, as well as practical implications for how
+  strategic change is implemented in firms.
 
@@
 %https://journals.sagepub.com/doi/abs/10.1177/0971890717701781
+The ultimate goal in the theory of dynamic capabilities ($DC$) is competitive advantage
+\citep{Schilke2014,Helfat2007,Protogerou2012,Li2014,Efrat2018a,Mikalef2017,Davcik2016a}. Extant
+theory argues that competitive advantage ($CA$) stem from resources and routines that are
+well aligned to firms’ competitive environment
+\citep{Helfat2007,Peteraf2013,Teece1997,Li2014,Jantunen201,Makkonen2014}. Dynamic
+capabilities are a source of longer-term competitive advantage in this perspective through
+its capacity to purposefully change these lower-level routines and capabilities
+\citep{Winter2003,Helfat2011,Schilke2018,Pezeshkan2016b,Lin2014a}, also referred to as
+ordinary, substantive, and zero-level routines and capabilities
+\citep{Winter2003,Danneels2008,Collis1994}. As a group, these lower level routines and
+capabilities are called 'behavioral objects of change' \citep{Verona2011,Zollo2016}, and constitutes an
+important path through which DCs can enable competitive advantage \citep{Verona2011}.
 
-Extant literature on dynamic capabilities are increasingly focusing on how firm resources
-are changed by dynamic capabilities as a response to changes in the environment
-\citep{Schilke2018,Eriksson2014}, thus placing firm capabilities as a mediator between
-dynamic capabilities and competetive advantage \citep{Helfat2007}. This notion of
-'orchestration' of firm resources, assets and capabilities has indeed been emphasized in
-the extant literature \citep{Sirmon2011,Helfat2015}. Less emphasis has been placed on how
-other mechanisms can be work in shaping firm competitive advantage. Indeed, this gap in
-the literature is explicitly emphasized by \cite{Schilke2018} where they 'see an
-interesting opportunity for future work to add greater richness to our understanding of
-the mechanism of resource-base change, given this mechanism’s central role in many
-foundational works (..) and the diverse ways in which resource changes can potentially
-come about' (p. 419).
+However, less emphasis has been placed on how other mechanisms can be work in shaping firm
+competitive advantage. Indeed, this gap in the literature is explicitly emphasized by
+\citep{Schilke2018} where they 'see an interesting opportunity for future work to add
+greater richness to our understanding of the mechanism of resource-base change, given this
+mechanisms central role in many foundational works (..) and the diverse ways in which
+resource changes can potentially come the mechanism of resource-base change, given this
+mechanisms central role in many foundational works (..) and the diverse ways in which
+resource changes can potentially come about' (p. 419).
 
-The conventional mechanism explored in the extant literature is related to changes in the
-firm`s resource base \citep{Eriksson2014,Schilke2018}. This mechanism is also included in
-the dominating definition of dynamic capabilities found in \citep{Helfat2007}: 'A dynamic
-capability is the capacity of an organization to purposefully create, extend or modify its
-resource base' (p. 4). This definition opens up for a variety of components
-included in the term 'resource base', a point we discuss later in this paper. We coin this
-expression of dynamic capabilities as the {\bf conductor} envisioning a conductor
-orchestrating firm capabilities.
+Indeed, the extant conceptualization of the $DC-CA$ link leaves out a considerable part of
+a firm‘s 'resource base' that are non-behavioral, such as resources that are tied to how
+the employees of the firm sees their mission, internalize information and effectuates
+change. These traits of the organization is very much related to concepts of 'mindset'
+\citep{Dweck2016}, ’employee cognition’ \citep{Lakoff1987,Gavetti2012} 'organizational
+genes' \citep{Nelson1982} and 'sense-making' \citep{Weick1995} to name but a few. However,
+in relations with dynamic capabilities, one promising avenue for exploring mechanisms,
+beyond the conventional behavioral objects of change is to examine the role of
+\emph{non-behavioral} objects of change in the theory of DC \citep{Verona2011}. These
+non-behavioral objects of change contain psychological objects such as cognitive frames,
+motivation and identity that are important for strategy formation and implementation
+\citep{Vince2011,Gavetti2012} as they 'concern how decisions or actions are shaped,
+subverted and transformed by emotions, and (..) determine the ”way we do things here”'
+\cite[p. 338]{Vince2011}.
 
-This notion of a {\bf conductor} albeit very important to the development of dynamic
-capabilities literature, seems to leave out a considerable part of a firm`s 'resource
-base', namely those resources that are tied to how the employees of the firm sees their
-mission, internalize information and effectuates change. These traits of the organization
-is very much related to concepts of 'mindset' \citep{Dweck2016}, 'employee cognition'
-\citep{Lakoff1987,Gavetti2012} 'organizational genes' \citep{Nelson1982} and
-'sense-making' \citep{Weick1995} to name but a few. However, in relations with dynamic
-capabilities, one promising avenue for exploring mechanisms, beyond the conventional ones
-described above, makes a clear distinction between \emph{behavioral} and
-\emph{non-behavioral} objects of change \citep{Verona2011}. These non-behavioral objects
-of change contain psychological objects such as cognitive frames, motivation and identity
-that are important for strategy formation and implementation \citep{Vince2011,Gavetti2012}
-as they 'concerns how decisions or actions are shaped, subverted and transformed by
-emotions, and (..) determine the "way we do things here"' \citep[p. 338]{Vince2011}. In
-this respect they work as firm resources in generating outcomes such as performance and
-competitive advantage. This notion is popularly perhaps expressed most clearly by Peter
-Drucker`s famous quote about how 'culture eats strategy for lunch'. \footnote{The debate
-  on whether Drucker actually uttered these words are still in the open, but it was
-  attributed to him by Mark Fields in 2006} Moreover, these non-behavioral objects of
+Moreover, these non-behavioral objects of
 change are themselves far from static and are found to change over time as responses to
@@
 is know about the non-behavioral objects of change and how they work as a mechanism in the
-dynamic capabilities theory.We coin {\bf coach} to capture the enabling role dynamic
-capabilities plays through \emph{strategic cognition} as
-juxtaposed to the more directional role played as {\bf conductor} of \emph{operational capabilities}.
+dynamic capabilities theory.
 
-We aim to contribute to bridging this gap by theorize about how non-behavioral objects of
-change work as a mechanism through which dynamic capabilities influence competitive
-advantage. Specifically, we ask the following research question:
+We aim to contribute to bridging this gap by analyzing to what extent DCs influence
+competitive advantage through two paths - one old, and one new - namely behavioral and
+non-behavioral objects of change.  Specifically, we ask the following research question:
 
@@
 
-To shed light on this important question we theorize on the role of a particular type of
-non-behavioral object of change, \emph{strategic cognition}, and how it acts as a mediator
-between dynamic capabilities and firm competitive advantage and hence has a pivotal place
-in the literature. We build on important work on the concept of organizational cognition
-\citep{Lakoff1987} , non-behavioral object of change \citep{Verona2011} and cognitive
-psychology \cite{Tversky1983,Kahneman2011} and hypothesize about how strategic cognition
-acts as a mediator in the same way as conventional behavioral objects of change (such as
-routines and capabilities) and that these two are complementary to a certain
-degree. Consequently, we argue, dynamic capabilities takes the function of a {\bf conductor}
-by orchestrating routines and capabilities, and the role of a {\bf coach} in stimulating
-strategic cognition. We use the case of Microsoft's transition into the cloud computing
-business as an illuminating case for demonstrating how the roles of {\bf conductor} and
-{\bf coach} coexist and act partly complimentary in generating strategic change and
-competitive advantage.
+To help answer this research question we build a conceptual model which illuminates the
+relationships between $DC$, behavioral and non-behavioral objects of change and $CA$. The
+model firmly integrates theorizing on organizational cognition \citep{Lakoff1987},
+non-behavioral object of change \citep{Verona2011} and cognitive psychology
+\citep{Tversky1983,Kahneman2011} into the $DC-CA$ nexus. Specifically, we focus on a
+particular type of non-behavioral object of change, strategic cognition, and how it acts
+as a mediator between dynamic capabilities and firm competitive advantage and hence has a
+pivotal place in the literature. Reflecting this, we argue that DCs have two important
+functions, namely 'DC as {\bf coach}' and 'DC as {\bf conductor}':
 
-Centering this paper around the dynamic capabilities-competitive advantage nexus stems
-from the origins and promises of the dynamic capabilities theory. Competitive advantage is
-considered the 'holy grail' of strategic management \citep{Schilke2018} and is indeed the
-focal point of important antecedent theories of dynamic capabilities
-\citep{Arndt2018}. Consequently, contributions to push the theory forward should enable a
-better understanding of \emph{how} dynamic capabilities work to influence firms'
-competitive advantage. In this spirit, our paper makes the following contributions to
-extant dynamic capabilities theory. First, we provide clarification on the theoretical
-role of non-behavioral objects of change as well as a possible empirical
-operationalization through the concept of \emph{proactiveness}. Second, we conceptualize
-two different expressions of dynamic capabilities (i.e. {\bf conductor} and {\bf coach})
-and theorize on how they work in the dynamic capabilities-competitive advantage nexus. We
-also extend this reasoning to include how they relate to each other. Finally, we develop and
-test an empirical model suited for analyzing mediating constructs on the dynamic
-capabilities-competitive advantage nexus. The time-lag of our data in conjunction with
-advances in empirical estimations of multiple simultaneous mediators makes for an
-interesting model to push our understanding of important mechanisms in the
-theory.
+Dynamic capabilities take the function of a {\bf conductor} by orchestrating routines and
+capabilities, and the role of a {\bf coach} in stimulating strategic cognition.  We discuss this
+theoretical understanding of $DC$ and use the case of Microsoft’s transition into the cloud
+computing business as an illuminating case. Importantly, this case demonstrates how the
+roles of conductor and coach coexist and in generating strategic change and competitive
+advantage.
+
+The conceptual model is used to derive a set of hypotheses which is tested against
+longitudinal survey data with a 10 year time lag. We find that $DC$ influence competitive
+advantage through both behavioral and non-behavioral objects of change. Thus, the paper
+empirically validates emergent theorizing proposing non-behavioral objects of change as a
+new path between $DC$ and competitive advantage. Moreover, the paper helps to broaden the
+conceptual basis for empirically investigating how $DC$ enable competitive advantage. This
+has implications for understanding how dynamic capabilities work, as well as practical
+implications for how strategic change is implemented in firms. Thus, the paper clarifies
+the theoretical role of non-behavioral objects of change as well as a possible
+operationalization through the concept of \emph{strategic cognition}. Moreover, we
+conceptualize two different expressions of dynamic capabilities (i.e. conductor and coach)
+and theorize on how they work in the $DC-CA$ nexus. Finally, we develop and test an empirical model
+suited for analyzing mediating constructs on the dynamic capabilities-competitive
+advantage nexus. The time-lag of our data in conjunction with advances in empirical
+estimations of multiple simultaneous mediators makes for an interesting model to push our
+understanding of important mechanisms in the theory.
 
@@
 
-\section{Definitions}
+\section{Theoretical background and hypotheses}
+
+Competitive advantage is considered the ’holy grail’ of strategic management
+\citep{Schilke2018} and is indeed the focal point of important antecedent theories of
+dynamic capabilities \citep{Arndt2018,Pezeshkan2016b}. Consequently, contributions to push
+the theory forward should enable a better understanding of how dynamic capabilities work
+to influence firms’ competitive advantage.
+
 The collective term for assets available for firms in their pursuit of their objectives
-are \emph{resources}. This term entails tangible assets such as machines, capital, and
-labor, but also intangible assets such as procedures, practices, and intellectual
-property. The process of using these resources in the pursuit of business objectives such
-as competitive advantage is a firm's \emph{capabilities} which can be a set of routines
-and skills applied. Resources and capabilities are both tied organizational behavior and
-how the organization act in their operation. Hence, they are coined \emph{behavioral
-  objects of change} \citep{Verona2011}: 'A pattern of action, a process, an operating
-routine, or any form of group activity characterized by some level of stability and
-predictability' (ibid. p.538). Such behavioral objects such as capabilities are the
-conventional understanding of how dynamic capabilities work; they 'purposefully create,
-extend and modify the resource base' (helfat). In the terminology proposed in this paper
-this process takes the shape as a 'conductor'.
+are \emph{resources} \citep{Helfat2011,Helfat2007}. This term entails tangible assets such
+as machines, capital, and labor, but also intangible assets such as procedures, practices,
+and intellectual property \citep{Pisano2017}. The process of using these resources in the
+pursuit of business objectives such as competitive advantage is a firm's
+\emph{capabilities} which can be a set of routines and skills applied
+\citep{Helfat2007,Helfat2011}. Resources and capabilities are both tied organizational
+behavior and how the organization act in their operation. Hence, they are coined
+\emph{behavioral objects of change} \citep{Verona2011}: 'A pattern of action, a process,
+an operating routine, or any form of group activity characterized by some level of
+stability and predictability' (ibid. p.538). Such behavioral objects such as capabilities
+are the conventional understanding of how dynamic capabilities work; they 'purposefully
+create, extend and modify the resource base' \cite[p. 4]{Helfat2007}. In the terminology
+proposed in this paper this process takes the shape as a {\bf conductor} envisioning a
+conductor orchestrating firm capabilities. Extant literature on dynamic capabilities are
+increasingly focusing on how firm resources are changed by dynamic capabilities as a
+response to changes in the environment \citep{Schilke2018,Eriksson2014}, thus placing firm
+capabilities as a mediator between dynamic capabilities and competetive advantage
+\citep{Helfat2007}. This notion of 'orchestration' of firm resources, assets and
+capabilities has indeed been emphasized in the extant literature
+\citep{Sirmon2011,Helfat2015}. Thus the notion of a {\bf conductor} captures a directional
+role played by $DC$ in terms of its functioning to 'orchestrate' \emph{behavioral}
+objects of changes such as \emph{operational capabilities}.
 
@@
 actual latent action \citep{Zollo2016}. Thus, dynamic capabilities are not sufficiently
-creating strategic change through its role as 'conductor'. Additionally they need to
-exercise a role of 'coach' to adapt the strategic cognition of the organization to create
+creating strategic change through its role as {\bf conductor}. Additionally they need to
+exercise a role to adapt the strategic cognition of the organization to create
 a shared understanding of the sense and necessity of the strategic goals of the
-orientation.
+orientation. We coin {\bf coach} to capture the enabling role dynamic
+capabilities plays through \emph{strategic cognition} as
+juxtaposed to the more directional role played as {\bf conductor} of \emph{operational
+  capabilities}. According to the Cambridge dictionary the noun 'coach' means 'someone
+whose job is to teach people to improve' and 'someone whose job is to train and
+organize'. Albeit often used in relation to sports it is also increasingly used for any
+process of 'learning and development intervention that uses a collaborative, reflective, goal-focused
+relationship to achieve professional outcomes' \cite[p. 253]{Jones2016}. We use the word
+as an analogous idiom for an organizational process focusing on the subject (e.g. the firm or an
+individual) to utilize own capacities as well as activating latent motivations. Thus it is
+juxtaposed to a {\bf conductor} that creates results through directions and
+orchestration.
 
-\section{Hypotheses}\label{sec:hyp}
-
-%DC as resource orchestration - influencing capabilitie
-%DC as cognitive programmer - inluencing cognitive frames
-
-%Prior research focused on managerial cognition, but gavetti shows that hierarchy matters
-%and different cognition maters
-
-What doe sit mean to execute DC (sense etc) and see opportunities and change underlying...
+\subsection{Conducting and coaching at Microsoft}\label{sec:case}
 
@@
 function that composes an outcome based on the available capabilities, the notion of a
-{\bf conductor} refers to the function of enabling others to achieve their objectives. The process
-is all about changing an organization`s thinking from the automated and well-known, to the
-more cognitively aware, moving from what Kahneman and Tversky coins the automated 'system
-one' to the deliberate 'system two' thinking \citep{Kahneman2011}. We will now turn to the two functions
-of dynamic capabilities in turn.
-
-\begin{figure}
-  \centering
-  \captionsetup{width=0.5\linewidth}
-  \input{./figure/fullmod.tex}
-  \captionof{figure}{The resource and cognitive mechanisms of dynamic capability}
-  \label{fig:fig1}
-\end{figure}
+{\bf coach} refers to the function of enabling others to achieve their objectives. The
+process is all about getting employees on board, and by changing an organization`s
+thinking from the automated and well-known, to the more cognitively aware. We will now
+turn to the two functions of dynamic capabilities in turn.
 
@@
 through which dynamic capabilities influence an outcome
-\citep{Fainshmidt2016a,Protogerou2012,Schilke2018,Eriksson2014}. Particularly, much of the
-extant literature concerns measures of accounting profitability and competitive advantage
-as the final outcome of dynamic capabilities
+\citep{Pezeshkan2016b,Fainshmidt2016a,Protogerou2012,Schilke2018}. Particularly, much of
+the extant literature concerns measures of accounting profitability and competitive
+advantage as the final outcome of dynamic capabilities
 \cite{shamsie2009,Schilke2014,Schilke2014a,Teece2016}. Thus, from these prior
@@
 
-Juxtaposed to the experiences from Microsoft, the case of Polaroid brings another set of
+vJuxtaposed to the experiences from Microsoft, the case of Polaroid brings another set of
 experiences to our discussion on non-behavioral objects of action (see \citep{Tripsas2000}
@@
 what is often referred to as 'how we do things here' \citep{Nelson1982}, and how an
-organization thinks and act \citep{Nadella2017}. This alignment is possible only if the
+organization think and act \citep{Nadella2017}. This alignment is possible only if the
 employees share a common cognitive frame related to the the strategic direction of the
@@
 changes they will enhance the full organization`s ability to not only act upon changes
-\citep{Marchand2004}, but also in 'timely responsiveness' \citep{Kohli1993}. Consequently,
-strategic cognition not only contributes to getting people on board, it also maintain a
-more efficient change process where the individuals take more responsibilities for the
-change itself and leverages their individual knowledge in the endeavor. For a firm to
-create real strategic change as enabled by their dynamic capabilities and hence stay
+\citep{Marchand2004}, but also in 'timely responsiveness' \citep{Kohli1993}.
+
+Seminal contributions in cognitive psychology describes this state of actively engaging in
+cognitive processes 'system 2 thinking' and define it as allocating 'attention to the
+effortful mental activities that demand it, including complex computations'
+\cite[p. 21]{Kahneman2011}. This is juxtaposed to the more automated 'system 1' which
+'operates automatically and quickly, with little or no effort and no sense of voluntary
+control' (ibid). The process is all about changing an organization`s thinking from the
+automated and well-known, to the more cognitively aware. The extent to which individuals
+in an organization is enabled to allocate attention to effortful mental activities related
+to understanding needs for strategic change instead of relying on automatic reasoning
+\citep{Tversky1983} or rules of thumb \citep{Kahneman1979}, can be a forceful remedy
+aganist organizational inertia \citep{Adriaenssen2016}.
+
+Consequently, strategic cognition not only contributes to getting people on board, it also
+maintain a more efficient change process where the individuals take more responsibilities
+for the change itself and leverages their individual knowledge in the endeavor. For a firm
+to create real strategic change as enabled by their dynamic capabilities and hence stay
 competitive, is will need to act as a {\bf coach} to instill a strategic cognition in the
@@
 
-\subsection{Proactiveness as strategic cognition}
+\begin{figure}
+  \centering
+  \captionsetup{width=0.5\linewidth}
+  \input{./figure/fullmod.tex}
+  \captionof{figure}{The resource and cognitive mechanisms of dynamic capability}
+  \label{fig:fig1}
+\end{figure}
 
@@
 
-We collected survey data from R\&D active firms in Norway at two points in time
-($T_0=2005$ and $T_1=2014$). The population was all businesses registered to a scheme for
+We use a unique data set where Norwegian technology firms were administered a survey at
+two points in time. ($T_0 = 2005$ and $T_2 = 2014$). The data combine the secondary data
+from an earlier survey with registery data and a follow-up survey conducted by the
+authors. The baseline survey was captured in 2005 when a web based survey was sent to 1721
+technology firms in Norway intending to capture the concept of dynamic capabilities
+\citep{Alsos2007}. Approximatly 70\% of the firms returned filled-in questionaires mouting
+to a total sample size of 1199 firms. Details of the data gathering process and the
+validation is available in \cite{Alsos2007}, but a brief explanation is waranted. The
+authors used a mixed methods approach combining an extensive literature review with
+qualitative interviews and testing in the field. Face validity of the items was further
+examined by testing the items on experts. The authors of the present paper did take part
+in this data initial collection. However, we have been given access to the raw data
+collected in 2005. The second author of this paper followed up with a similar survey in
+the spring/summer of 2014, 9 years after the first round. All the same firms received a
+web-based questionnaire containing the same measures of the key constructs in this
+paper. Following htis second round we were left with a sample size of 283 representing the
+number of firms returning a filled-in second questionnaire.
+
+The population was all businesses registered to a scheme for
 tax deduction of R\&D costs (called SkatteFUNN). As all enterprises which are eligible for
@@
 that the firms are located in industries with a certain level of dynamism.
-
-We contacted all the firms that were registering R\&D activities during May to December
-2005 yielding a total of 1721 firms. Using a web-based questionnaire we included items to
-measure the key constructs of this paper. Each firm received an email with a link to the
-questionnaire within a month after their registration for the R\&D tax credit. This
-initial contact was followed by two subsequent email reminders. A total of 1199 (70 \% of
-the initial sample size) answered and returned the questionnaire. In the second phase of
-the study each of these 1199 were contacted again in 2014, 9 years later, with the lion
-share of the firms contacted during the spring and summer of 2014. All received a similar
-web-based questionnaire containing the same measures of the focal constructs of this
-paper. 262 of the firms returned filled-in questionnaire.
 
@@
 increased substantially in the realm of marketing \citep{hult2018} and strategic management
-\citep{Hair2012} and is the topic of special issues in leading journals (e.g. Journal of
+\citep{Hair2012,Valaei2017} and is the topic of special issues in leading journals \citep{Hair2020} (e.g. Journal of
 Business Research call for papers in 2020). In this tradition we aim to present thorough
@@
 
-When adding the interaction term  $CAP_1 \times COG_1$ we get a significant effect. this
-is compatible with the idea of behavioral ($CAP_t$) and non-behavioral ($COG_t$) objects
-of change being complementary. This lends support to H3.
+When adding the interaction term $CAP_1 \times COG_1$ we get a significant effect. this is
+compatible with the idea of behavioral ($CAP_t$) and non-behavioral ($COG_t$) objects of
+change being complementary. This lends support to H3.
 
-Our results indicate that between 37\%  and 48\% of the variation in $CA_1$ can be explained by our model,
-whereas 19\% and 18\% of the variation in our mediators $CAP_1$ and $COG_t$ respectively
-is explained.
+Our results indicate that between 37\% and 48\% of the variation in $CA_1$ can be
+explained by our model, whereas 19\% and 18\% of the variation in our mediators $CAP_1$
+and $COG_t$ respectively is explained.
 
@@
 acquired important capabilities from M\&A efforts, and upgraded the competencies regarding
-cloud business and big data \citep{Nadella2017}. This should not be surprising given the vast
-literature on indirect effects of dynamic capabilities \citep{Eriksson2014} supported by
-empirical and theoretical research
-\citep{Fainshmidt2016a,Protogerou2012,Karimi2015}. However, it adds to this ongoing effort
-of investigating mechanisms through which dynamic capabilities work which is called for in
-the literature \citep{Schilke2018}.
+cloud business and big data \citep{Nadella2017}. This should not be surprising given the
+vast literature on indirect effects of dynamic capabilities
+\citep{Schilke2018,Eriksson2014} supported by empirical and theoretical research
+\citep{Pezeshkan2016b,Fainshmidt2016a,Protogerou2012,Karimi2015}. However, it adds to this
+ongoing effort of investigating mechanisms through which dynamic capabilities work which
+is called for in the literature \citep{Schilke2018}.
 
@@
 meanwhile exercising the right interpretation, understanding and attitude towards
-change. This is also one of the key lessons from the Microsoft case. Our empirical results
-do indeed support this. \emph{Operating capabilities}) and \emph{strategic cognition} are
-complementary to each other in influencing competitive advantage meaning that businesses
-will not succeed properly without being conscious of both.
+change. Our third hypothesis considers strategic cognition in tandem with relevant and
+strong capabilities and hold that they would reinforce each other. This has also been
+supported in previous research where firm success has been shown to relate to the
+interconnection between resources and capabilities, and culture and attitude
+\citep{Verona2003}, and high levels of social capital \citep{Blyler2003}. Moreover, the
+lack of one (e.g. strategic cognition) can lead to unfavorable outcomes even though
+capabilites and resources are aligned for the needed strategic change
+\citep{Tripsas2000}. This is also one of the key lessons from the Microsoft case. Our
+empirical results do indeed support this. \emph{Operating capabilities}) and
+\emph{strategic cognition} are complementary to each other in influencing competitive
+advantage meaning that businesses will not succeed properly without being conscious of
+both.
 
@@
 change and suggested a possible empirical operationalization through the concept of
-\emph{proactiveness}. Second, we suggested and demonstrated two different expressions of
-dynamic capabilities (i.e. {\bf conductor} and {\bf coach}) as well as their workings in
-the dynamic capabilities-competitive advantage nexus. We also extend this reasoning to
-include how they relate to each other. Third, we utilized time-lagged data in conjunction
+\emph{proactiveness}. This has implications for how we operationalize important mediators
+in the $DC-CA$ nexus.
+
+Second, we suggested and demonstrated two different expressions of dynamic capabilities
+(i.e. {\bf conductor} and {\bf coach}) as well as their workings in the dynamic
+capabilities-competitive advantage nexus. This insight adds to the nascent work of
+bringing cognition into broader strategic management field in general
+\citep{Gavetti2012,Gavetti2005a} and dynamic capabilities in particular
+\citep{Helfat2015,Arndt2018}. In particular, the evolutionary and resource based roots of
+$DC$ theory has to a large extent been dominating the field \citep{Arndt2018,Peteraf2013}
+leaving an important side of cognition \cite{Verona2011} and heuristics \cite{Arndt2015}
+less explored. Particularly, the call for exploring new mediators of the $DC-CA$ nexus
+\citep{Schilke2018} is particularly relevant to moving $DC$ theory forward. Our
+conceptualization is thus an important contribution to this work. Bringing the notion of
+simultanously separate and interpendent expressions of $DC$ has implications for
+strategizing and decisions to pursue capability aquisition and development. As with the
+case of Microsoft, our data shows that simultanously maintaining 'strategic cognition'
+adds to outcome of the strategic change. Thus, managers who underestimate these effects
+may very well end up delivering less value than they otherwise could.
+
+Third, we utilized time-lagged data in conjunction
 with advances in empirical estimations of multiple simultaneous mediators. In doing these
@@
 analysis, and more observations over time would be helpful in analyzing more causal claims
-in the theory.
+in the theory. Forth, we have examined two particular types of behavioral and
+non-behavioral objects of change. Thus, future research should examine other types in
+order to develop e more elaborate and holistic understanding of how behavioral and
+nonbehavioral objects of change influence competitive advantage in the theory of DC.
 

### 2019-12-11 article4_tommylars.rnw
Ready for submission

@@
 %https://journals.sagepub.com/doi/abs/10.1177/0971890717701781
+
+Extant literature on dynamic capabilities are increasingly focusing on how firm resources
+are changed by dynamic capabilities as a response to changes in the environment
+\citep{Schilke2018,Eriksson2014}, thus placing firm resources as a mediator between
+dynamic capabilities and competetive advantage \citep{Helfat2007}.
 
@@
 \emph{H2a: When dynamic capabilities are being mediated by VRIO resources the firm can
-  achieve competitive advantage}
+o  achieve competitive advantage}
 

### 2020-01-22 article4_jbr.rnw
Finalized for inclusion in dissertation

@@
 
-\section{Introduction}
+\section*{Introduction}
 
@@
 library(semPLS)
-#load("./data/resart4.RData")
+load("./data/resart4.RData")
 r <- main$resmat
@@
 
-\section{Theoretical background and hypotheses}
+\section*{Theoretical background and hypotheses}
 
@@
 
-\subsection{Conducting and coaching at Microsoft}\label{sec:case}
+\subsection*{Conducting and coaching at Microsoft}\label{sec:case}
 
@@
 
-\subsection{Capabilities conductor}
+\subsection*{Capabilities conductor}
 
@@
 
-\subsection{Cognitive coach}
+\subsection*{Cognitive coach}
 
@@
 
-\subsection{Coaching conductor}
+\subsection*{Coaching conductor}
 
@@
   \captionsetup{width=0.5\linewidth}
-  \input{./figure/fullmod.tex}
+  \input{/Users/larshovdanmolden/Documents/git/article4/figure/fullmod.tex}
   \captionof{figure}{The resource and cognitive mechanisms of dynamic capability}
@@
 
-\section{Data and methods}
+\section*{Data and methods}
 
@@
 
-\subsection{Variable construction}
+\subsection*{Variable construction}
 
@@
 
-\subsection{Control variables}
+\subsection*{Control variables}
 
@@
 \label{tab:cor}
-  <<corchild, child='./figure/cortab.rnw',results="asis">>=
+  <<corchild, child='/Users/larshovdanmolden/Documents/git/article4/figure/cortab.rnw',results="asis">>=
 @
@@
 
-\subsection{Estimation and empirical model}
+\subsection*{Estimation and empirical model}
 
@@
 
-\section{Results}
+\section*{Results}
 The main results of our analysis are depicted both in the graphical path diagrams (figure
@@
   \scriptsize
-  <<child-demo, child='./figure/restab.rnw'>>=
+  <<child-demo, child='/Users/larshovdanmolden/Documents/git/article4/figure/restab.rnw'>>=
 @
@@
 
-\subsection{Robustness and assumption validation}
+\subsection*{Robustness and assumption validation}
 The results are subject to some robustness checks not directly reported in the paper,
@@
 
- <<pathchild, child='./figure/medanalysisall.rnw',results="asis">>=
+ <<pathchild, child='/Users/larshovdanmolden/Documents/git/article4/figure/medanalysisall.rnw',results="asis">>=
 @
 
-\section{Discussion}
+\section*{Discussion}
 The aim of this paper is to theorize about how non-behavioral objects of change work as a
@@
 
-\section{Concluding remarks}
+\section*{Concluding remarks}
 
@@
 
-\section{Bibliography}
+\section*{Bibliography}
 
@@
 
-\section{Appendix}
+\section*{Appendix}
 \newpage
@@
       loadings in parantheses}
-    <<itemchild, child='./figure/itemtab.rnw',results="asis">>=
+    <<itemchild, child='/Users/larshovdanmolden/Documents/git/article4/figure/itemtab.rnw',results="asis">>=
     @

### 2020-02-25 article4_jbr_diss.rnw
submitted dissertation

--- 2020-01-22 article4_jbr.rnw
@@
 
-\begin{frontmatter}
+%\begin{frontmatter}
 %Lock, Stock and Two Smoking Barrels lock stock and two mediating factors
@@
 
-\title{One goal, two paths: How dynamic capabilities enable competitive advantage through behavioral and non-behavioral objects of change}
+%\title{One goal, two paths: How dynamic capabilities enable competitive advantage through behavioral and non-behavioral objects of change}
 %\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
@@
 
-\begin{abstract}
 % This paper investigates strategic cognition as mediating factor in the dynamic
@@
 
+{\large \bf One goal, two paths: How dynamic capabilities enable competitive advantage through behavioral and non-behavioral objects of change}\\
+\newline
+
+% \begin{abstract}
+{\bf Abstract:}\\
   The ultimate goal in the theory of dynamic capabilities (DCs) is competitive advantage.
@@
 
-\end{abstract}
+%\end{abstract}
 
@@
 
-\end{frontmatter}
+%\end{frontmatter}
 
@@
 
-\doublespacing
+%\doublespacing
 
 \section*{Introduction}
+
+%Frame flexibility: The role of cognitive and emotional framing in innovation adoption by incumbent firms rafaelli2019
 
@@
 setwd("/Users/larshovdanmolden/Documents/git/article4")
-library(xtable)
-library(semPLS)
-load("./data/resart4.RData")
+#library(xtable)
+#library(semPLS)
+#load("./data/resart4.RData")
 r <- main$resmat
@@
 \begin{align}
-  CA_{i,1} & = \alpha_0 + \alpha_1 CA_{i,0} + \omega_1 \alpha_2 CAP_{i,1}
-  + \omega_2 \alpha_3 COG_{i,1} + \alpha_{4} DC_{i,0} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + \epsilon_i \\
+  CA_{i,1}  = & \alpha_0 + \alpha_1 CA_{i,0} + \omega_1 \alpha_2 CAP_{i,1} + \\
+           & \omega_2 \alpha_3 COG_{i,1} + \alpha_{4} DC_{i,0} + \mathbf{\Gamma}_m\mathbf{C}^m_{i,1} + \epsilon_i
+\end{align}
+
+\begin{align}
   CAP_{i,1} & = \beta_0 + \beta_1 CAP_{i,0} + \beta_2 DC_{i,0} + v_i\\
@@
 \begin{tablenotes}
+
       \tiny
-      \item Standard-errors estimated using bootstrapping with 10 000 simulations.
+      \item Standard-errors estimated using bootstrapping with 10 000 simulations. \vspace{-1em}
       \item Firm level control variables include firm size, firm age,
@@
 
+\begin{figure}\label{fig:med4}
  <<pathchild, child='/Users/larshovdanmolden/Documents/git/article4/figure/medanalysisall.rnw',results="asis">>=
 @
+\caption{Mediation analysis - graphical representation}
+\end{figure}
 
@@
 
-\section*{Bibliography}
-
-\singlespacing
-\bibliography{Dissertation_clean}
+%\section*{Bibliography}
+
+%\singlespacing
+%\bibliography{Dissertation_clean}
 
 \section*{Appendix}
-\newpage
-
-  \begin{table}\label{tab:items}
+
+\begin{table}[t!]
+  \label{tab:items}
     \caption{Core constructs and their measurement items. Factor

### 2020-02-25 article4_jbr_diss.tex
submitted dissertation

--- 2020-02-25 article4_jbr_diss.rnw
@@
 
-<<loading, results="asis", echo=FALSE >>=
-setwd("/Users/larshovdanmolden/Documents/git/article4")
-#library(xtable)
-#library(semPLS)
-#load("./data/resart4.RData")
-r <- main$resmat
-rm  <- main$resmatmed
-l  <- main$loadings
-ic <- data.frame(i[,c(1,4)]);colnames(ic) <- c("b","t")
-ic$rn  <- 1:nrow(ic)
-bb <- main$models$both
-bm <- main$models$mmed
-br <- main$models$rmed
-#foolars=0.99
-@
-
 %% Extant literature on dynamic capabilities is battling with a fundamental conception and
@@
 well aligned to firms’ competitive environment
-\citep{Helfat2007,Peteraf2013,Teece1997,Li2014,Jantunen201,Makkonen2014}. Dynamic
+\citep{Helfat2007,Peteraf2013,Teece1997,Li2014,Jantunen2018,Makkonen2014}. Dynamic
 capabilities are a source of longer-term competitive advantage in this perspective through
@@
 empirical literature handling various functional forms of dynamic capabilities such as
-acquisition targeting \citep{Bingham2015}, alliancing \cite{Schilke2014}, new product
-development \cite{Danneels2008}, innovation capabilities \citep{Breznik2014}, marketing
-capabilities \cite{Brune2009} and alliance capabilities \cite{Kale2002,kale2007}.
+acquisition targeting \citep{Bingham2015}, alliancing \citep{Schilke2014}, new product
+development \citep{Danneels2008}, innovation capabilities \citep{Breznik2014}, marketing
+capabilities \citep{Brune2009} and alliance capabilities \citep{Kale2002,kale2007}.
 
@@
 of strategic cognition as proactiveness loads only partly on one item (item
-3). Statsistically, a loading of $\Sexpr{l[["lcog"]][3]}$ is on the weaker side of
+3). Statsistically, a loading of $0.53$ is on the weaker side of
 traditional 'rules of thumb' \citep{Hair2010}, but from a theoretical stand point the
@@
 \label{tab:cor}
-  <<corchild, child='/Users/larshovdanmolden/Documents/git/article4/figure/cortab.rnw',results="asis">>=
-@
+
+\singlespacing
+\tiny
+\setlength{\tabcolsep}{3pt}
+% latex table generated in R 3.6.1 by xtable 1.8-4 package
+% Tue Jan 28 12:23:38 2020
+\begingroup\scriptsize
+\begin{tabular}{lp{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}p{0.290in}}
+  \hline
+ & Mean & SD & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
+  \hline
+1) $CA_1$ & 3.89 & 1.39 & 1 &  &  &  &  &  &  &  &  &  &  \\ 
+  2) $CA_0$ & 3.88 & 1.47 & 0.38 & 1 &  &  &  &  &  &  &  &  &  \\ 
+  3) $DC_0$ & 4.66 & 0.84 & 0.3 & 0.06 & 1 &  &  &  &  &  &  &  &  \\ 
+  4) $CAP_1$ & 4.17 & 0.99 & 0.54 & 0.18 & 0.36 & 1 &  &  &  &  &  &  &  \\ 
+  5) $CAP_0$ & 4.23 & 1.17 & 0.32 & 0.41 & 0.21 & 0.36 & 1 &  &  &  &  &  &  \\ 
+  6) $COG_1$ & 4.63 & 1.15 & 0.45 & 0.06 & 0.39 & 0.46 & 0.25 & 1 &  &  &  &  &  \\ 
+  7) $COG_0$ & 4.71 & 1.26 & 0.19 & 0.27 & 0.24 & 0.15 & 0.37 & 0.34 & 1 &  &  &  &  \\ 
+  8) Size & 4.33 & 1.90 & 0.36 & 0.29 & 0.06 & 0.31 & 0.29 & 0.11 & 0.13 & 1 &  &  &  \\ 
+  9) ln(Assets) & 10.01 & 2.03 & 0.35 & 0.33 & 0.06 & 0.32 & 0.26 & 0.08 & 0.11 & 0.87 & 1 &  &  \\ 
+  11) Margin & -0.07 & 0.66 & 0.18 & 0.24 & 0 & 0.09 & 0.13 & -0.06 & -0.09 & 0.07 & 0.02 & 1 &  \\ 
+  12) Age & 25.12 & 14.24 & 0.17 & 0.18 & -0.05 & 0.19 & 0.17 & -0.02 & -0.05 & 0.52 & 0.51 & 0.04 & 1 \\ 
+   \hline
+\end{tabular}
+\endgroup
 
@@
 constructed. This resulted in four models. The results from the structural model is
-reported in figure \ref{fig:res} and table \ref{tab:res}. To estimate the standard errors
+reported in figure \ref{fig:med4} and table \ref{tab:res}. To estimate the standard errors
 we ran simulations using bootstrapping and reported the simulation number, standard errors
@@
 The estimated models are based on the following specification:
-
 \begin{align}
@@
 complementarity or substitution-effects these two may exhibit:
-
 \begin{align}
@@
 The main results of our analysis are depicted both in the graphical path diagrams (figure
-\ref{fig:res}) and the regression table in table \ref{tab:res}. The use of PLS-SEM has
+\ref{fig:med4}) and the regression table in table \ref{tab:res}. The use of PLS-SEM has
 increased substantially in the realm of marketing \citep{hult2018} and strategic management
@@
 analysis of our models and largely follows the recommendations made in recent
-contributions \citep{Hair2019}.
+xcontributions \citep{Hair2019}.
 
@@
   \scriptsize
-  <<child-demo, child='/Users/larshovdanmolden/Documents/git/article4/figure/restab.rnw'>>=
-@
+
+\begin{tabular}{l*{5}{l}}
+
+  \hline                                                                                                                                                                                \\[-0.5em]
+                           & (1)                        & (2)                           & (3)                           & (4)                        & (5)                              \\ 
+  %                        & \multicolumn{1}{c}{Direct} & \multicolumn{1}{c}{CAP model} & \multicolumn{1}{c}{COG model} & \multicolumn{1}{c}{BOTH model}                                \\
+  \hline                                                                                                                                                                                \\
+  \rowcolor{Gray}
+                           & $\mathbf{CA_t}$            & $\mathbf{CA_t}$               & $\mathbf{CA_t}$               & $\mathbf{CA_t}$            & $\mathbf{CA_t}$                  \\     
+  $DC_{t-1}$               & 0.246             & 0.134                & 0.126                & 0.083             & 0.061                  \\
+                           & (5.52)  & (2.72)     & (2.49)     & (1.6)  & (1.12)       \\ [1em]
+  $CAP_{t}$                &                            & 0.382                &                               & 0.324             & 0.331                  \\
+                           &                            & (7.65)     &                               & (6.38)  & (7.24)       \\[1em]
+  $COG_{t}$                &                            &                               & 0.301                & 0.188             & 0.225                  \\
+                           &                            &                               & (5.27)     & (3.11)  & (3.66)       \\ [1em]
+    $CAP_{t} \times COG_t$ &                            &                               &                               &                            & 0.093                  \\
+                           &                            &                               &                               &                            & (2.04)       \\ [1em]
+    \rowcolor{Gray}
+                           & $\mathbf{}$                & $\mathbf{CAP_t}$              & $\mathbf{}$                   & $\mathbf{CAP_t}$           & $\mathbf{CAP_t}$                 \\
+  $DC_{t-1}$               &                            & 0.237                &                               & 0.224             & 0.206                  \\ 
+                           &                            & (4.12)     &                               & (3.38)  & (3.17)       \\[1em]
+    \rowcolor{Gray}
+                           & $\mathbf{}$                & $\mathbf{}$                   & $\mathbf{COG_t}$              & $\mathbf{COG_t}$           & $\mathbf{COG_t}$                 \\
+  $DC_{t-1}$               &                            &                               & 0.325                & 0.331             & 0.329                  \\
+                           &                            &                               & (5.23)    & (5.29) & (5.31)       \\  \\[-0.5em]
+  \hline                                                                                                                                                                                \\[-0.5em]
+  CA controls              & YES                        & YES                           & YES                           & YES                        & YES                              \\
+  CAP controls             &                            & YES                           &                               & YES                        & YES                              \\
+  COG controls             &                            &                               & YES                           & YES                        & YES                              \\
+  $R^2$                    & 0.3   & 0.44      & 0.37      & 0.47   & 0.48                             \\
+  $Q^2$                    & 0.2   & 0.31      & 0.25      & 0.32   & 0.31                             \\
+ % GOF                      & round(r[13,2],2)   & round(r[13,3],2)      & round(r[13,4],2)      & round(r[13,5],2)   &                                  \\
+ % BIC                      & round(r[14,2],1)   & round(r[14,3],1)      & round(r[14,4],1)      & round(r[14,5],1)   & round((r[14,5]*0.996),1) \\
+  N                        & 240   & 232      & 240      & 232   & 232                              \\
+  \hline
+ % \multicolumn{4}{l}{\tiny Standardized coefficients. T-values in parantheses}                                                                                                         \\
+\end{tabular}
 \begin{tablenotes}
@@
 
-\begin{figure}\label{fig:med4}
- <<pathchild, child='/Users/larshovdanmolden/Documents/git/article4/figure/medanalysisall.rnw',results="asis">>=
-@
+\begin{figure}
+
+\usetikzlibrary{arrows.meta}
+% \begin{minipage}{.48\textwidth}
+\begin{tabular}{cc}
+  % \subcaption{DIRECT model}
+
+ %\end{minipage}
+ %\begin{minipage}{.48\textwidth}
+   % \subcaption{CAP model}
+  \begin{tikzpicture}
+
+    \tikzstyle{mynode}=[circle,draw,thin, draw=black, fill=white, minimum
+    size=12mm,inner sep=0pt, align=center]
+
+    \tikzstyle{mynode2}=[circle,draw, ultra thin, draw=gray,text=gray, fill=white, minimum
+    size=12mm,inner sep=0pt, align=center]
+
+    \tikzstyle{gof}=[draw, ultra thin, draw=none, minimum size=18mm,inner sep=0pt, align=center]
+
+    \node[mynode] (m){$CAP_t$};
+    \node[mynode,below left=of m,yshift=0.5cm,xshift=-0.5cm](a) {$DC_{t-1}$};
+    \node[mynode,below right=of m,yshift=0.5cm,xshift=0.5cm](b) {$CA_{t}$};
+    \node[mynode2,below of=m,yshift=-1.5cm](c) {$COG_{t}$};
+    \node[gof,below of=c,yshift=-0cm](gof) {$R^2= 0.44$, $Q^2= 0.31$};
+
+    \draw[-latex, line width=0.3mm] (a.east) -- node[text width=0.8cm,font=\scriptsize, align=center,
+    fill=white] {$0.134^{*}$} (b.west);
+
+    \draw[-latex, line width=0.3mm] (a.north) -- node[text width=0.8cm,font=\footnotesize, align=center, fill=white] {$0.237^{*}$} (m.west);
+    \draw[ -latex, line width=0.3mm] (m.east) -- node[text
+    width=0.8cm,font=\footnotesize,align=center, fill=white] {$0.382^{*}$} (b.north);
+
+    \draw[gray,-latex] (a.south) -- node[text width=1.3cm,font=\scriptsize, align=left, fill=none] {} (c.west);
+    \draw[gray, -latex,line ] (c.east) -- node[text
+    width=1.3cm,font=\scriptsize,align=right, fill=none] {} (b.south);
+
+   \end{tikzpicture}
+ %\end{minipage}
+ %\begin{minipage}{.48\textwidth}
+ %  \subcaption{COG model}
+    &
+  \begin{tikzpicture}
+
+    \tikzstyle{mynode}=[circle,draw, thin, draw=black, fill=white, minimum
+    size=12mm,inner sep=0pt, align=center]
+
+    \tikzstyle{mynode2}=[circle,draw, ultra thin, draw=gray,text=gray, fill=white, minimum
+    size=12mm,inner sep=0pt, align=center]
+
+    \tikzstyle{gof}=[draw, ultra thin, draw=none, minimum size=18mm,inner sep=0pt, align=center]
+
+    \node[mynode2] (m){$CAP_t$};
+    \node[mynode,below left=of m,yshift=0.5cm,xshift=-0.5cm](a) {$DC_{t-1}$};
+    \node[mynode,below right=of m,yshift=0.5cm,xshift=0.5cm](b) {$CA_{t}$};
+    \node[mynode,below of=m,yshift=-1.5cm](c) {$COG_{t}$};
+    \node[gof,below of=c,yshift=-0cm](gof) {$R^2= 0.37$, $Q^2= 0.25$};
+
+    \draw[-latex, line width=0.3mm] (a.east) -- node[text width=0.8cm,font=\scriptsize, align=center,
+    fill=white] {$0.126^{*}$} (b.west);
+
+    \draw[gray,-latex] (a.north) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=none] {} (m.west);
+    \draw[gray, -latex,line ] (m.east) -- node[text
+    width=0.8cm,font=\scriptsize,align=right, fill=none] {} (b.north);
+
+    \draw[-latex, line width=0.3mm] (a.south) -- node[text width=0.8cm,font=\scriptsize, align=center, fill=white] {$0.325^{*}$} (c.west);
+    \draw[-latex, line width=0.3mm] (c.east) -- node[text
+    width=0.8 cm,font=\scriptsize,align=center, fill=white] {$0.301^{*}$} (b.south);
+
+   \end{tikzpicture}
+ %\end{minipage}
+ %\begin{minipage}{.48\textwidth}
+ %  \subcaption{FULL model}
+  \\
+  \begin{tikzpicture}
+
+    \tikzstyle{mynode}=[circle,draw, thin, draw=black, fill=white, minimum
+    size=12mm,inner sep=0pt, align=center]
+
+    \tikzstyle{mynode2}=[circle,draw, ultra thin, draw=gray,text=gray, fill=white, minimum
+    size=12mm,inner sep=0pt, align=center]
+
+    \tikzstyle{gof}=[draw, ultra thin, draw=none, minimum size=18mm,inner sep=0pt, align=center]
+
+    \node[mynode] (m){$CAP_t$};
+    \node[mynode,below left=of m,yshift=0.5cm,xshift=-0.5cm](a) {$DC_{t-1}$};
+    \node[mynode,below right=of m,yshift=0.5cm,xshift=0.5cm](b) {$CA_{t}$};
+    \node[mynode,below of=m,yshift=-1.5cm](c) {$COG_{t}$};
+    \node[gof,below of=c,yshift=-0cm](gof) {$R^2= 0.47$, $Q^2= 0.32$};
+
+    \draw[-latex,line width=0.3mm] (a.east) -- node[text width=0.8cm,font=\scriptsize, align=center,
+    fill=white] {$0.083$} (b.west);
+
+    \draw[-latex,line width=0.3mm] (a.north) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=white] {$0.224^{*}$} (m.west);
+    \draw[ -latex,line width=0.3mm ] (m.east) -- node[text
+    width=0.8cm,font=\scriptsize,align=right, fill=white] {$0.324^{*}$} (b.north);
+
+    \draw[-latex,line width=0.3mm] (a.south) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=white] {$0.331^{*}$} (c.west);
+    \draw[-latex,line width=0.3mm ] (c.east) -- node[text
+    width=0.8cm,font=\scriptsize,align=right, fill=white] {$0.188^{*}$} (b.south);
+
+   \end{tikzpicture}
+    &
+    \begin{tikzpicture}
+
+    \tikzstyle{mynode}=[circle,draw, thin, draw=black, fill=white, minimum
+    size=12mm,inner sep=0pt, align=center]
+
+    \tikzstyle{mynode2}=[circle,draw, ultra thin, draw=gray,text=gray, fill=white, minimum
+    size=12mm,inner sep=0pt, align=center]
+
+    \tikzstyle{gof}=[draw, ultra thin, draw=none, minimum size=18mm,inner sep=0pt, align=center]
+
+    \node[mynode] (m){$CAP_t$};
+    \node[mynode,below left=of m,yshift=0.5cm,xshift=-0.5cm](a) {$DC_{t-1}$};
+    \node[mynode,below right=of m,yshift=0.5cm,xshift=0.5cm](b) {$CA_{t}$};
+    \coordinate (CAf) at ([xshift=-1.25cm]b.west);
+    \node[mynode,below of=m,yshift=-1.5cm](c) {$COG_{t}$};
+    \node[gof,below of=c,yshift=-0cm](gof) {$R^2= 0.48$, $Q^2= 0.31$};
+
+    \draw[-latex,line width=0.3mm] (a.south east) -- node[above,text width=0.8cm,font=\scriptsize, align=left,
+    fill=white] {$0.061$} (b.south west);
+
+    \draw[-latex,line width=0.3mm] (a.north) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=white] {$0.206^{*}$} (m.west);
+    \draw[ -latex,line width=0.3mm ] (m.east) -- node[text
+    width=0.8cm,font=\scriptsize,align=right, fill=white] {$0.331^{*}$} (b.north);
+
+    \draw[-latex,line width=0.3mm] (a.south) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=white] {$0.329^{*}$} (c.west);
+    \draw[-latex,line width=0.3mm ] (c.east) -- node[text
+    width=0.8cm,font=\scriptsize,align=right, fill=white] {$0.225^{*}$} (b.south);
+
+     \draw[line width=0.3mm] (m.south east) to[bend left=20] node[text width=0.8cm,font=\scriptsize, align=center,
+    fill=none] {} (c.north east);
+
+    \draw[{Circle[black]}-latex,line width=0.3mm] (CAf.east) -- node[above, text width=0.2cm,font=\scriptsize, align=center,
+    fill=white] {$0.093^{*}$} (b.west);
+
+   \end{tikzpicture}
+% \end{minipage}
+\end{tabular}
 \caption{Mediation analysis - graphical representation}
+\label{fig:med4}
 \end{figure}
@@
 $DC$ theory has to a large extent been dominating the field \citep{Arndt2018,Peteraf2013}
-leaving an important side of cognition \cite{Verona2011} and heuristics \cite{Arndt2015}
+leaving an important side of cognition \citep{Verona2011} and heuristics \citep{Arndt2015}
 less explored. Particularly, the call for exploring new mediators of the $DC-CA$ nexus
@@
 
+\newpage
 \section*{Appendix}
 
-\begin{table}[t!]
+\begin{table}[h]
   \label{tab:items}
@@
       loadings in parantheses}
-    <<itemchild, child='/Users/larshovdanmolden/Documents/git/article4/figure/itemtab.rnw',results="asis">>=
-    @
+
+\scriptsize
+\singlespacing
+\setlist[itemize]{leftmargin=*}
+
+\begin{tabular}{p{2cm} c p{9cm}}
+
+\textbf{Construct}     & \textbf{Rho}               & \textbf{Items}\\ \toprule%
+  \textbf{Dynamic} \\ \textbf{Capabilities} &\textbf{$0.89$} &\vspace{-5mm} 
+                                                             \begin{itemize} 
+                                                               \setlength\itemsep{-0.2em} 
+                                                             \item Management receive frequent information about the employee's newly gained experiences ($0.69$)
+                                                             \item Knowledge and experiences are shared a cross teams in the firm ($0.77$)
+                                                             \item Knowledge and experiences are shared a cross teams in the firm ($0.76$)
+                                                             \item Positive and negative experiences are shared between employees ($0.82$)
+                                                             \item The employees are involved in discussions where the way of doing business is questioned ($0.79$)
+                                                             \item The employees are encouraged to engage in critical discussions on how the company is conducting its business ($0.62$)
+                                                             \item We conduct evaluations of "what has worked and what has not worked" in regards to larger projects etc ($0.61$)
+                                                             \end{itemize} \\ \midrule%
+ \textbf{Operating}                                                                            \\ \textbf{Capabilities} & \textbf{$0.84$}} & \vspace{-5mm} 
+                                                               \begin{itemize} \setlength\itemsep{-0.2em} 
+                                                               \item The firm has better marketing competence than the competitors ($0.78$)
+                                                               \item Compared to our competitors our firm is particularly skilled in customer service ($0.71$)
+                                                               \itemCompared to our competitors our firm is particularly skilled in management and operations  ($0.86$)
+                                                               \end{itemize} \\  \midrule%
+
+   \textbf{Strategic} \\ \textbf{Cognition} & \textbf{$0.82$} & \vspace{-5mm} 
+                                                               \begin{itemize} \setlength\itemsep{-0.2em} 
+                                                               \item Compared to our competitiors our firm typically refrain from action until competitors move, and then answer ($0.89$)
+                                                               \item Compared to our competitors we are often first movers in introducing new products, services, administrative routines, production methods etc ($0.87$)
+                                                               \item We relate to our competitors by adopting a "go get them" attitude. We are gonna win this ($0.53$)
+                                                               \end{itemize} \\  \midrule%
+
+   \textbf{Competitive} \\ \textbf{Advantage} & \textbf{$0.89$} & \vspace{-5mm} 
+                                                               \begin{itemize} \setlength\itemsep{-0.2em} 
+                                                               \item The firm has better financial results than our competitors ($0.85$)
+                                                               \item The firm has a stronger revenue growth than our competitors ($0.87$)
+                                                               \item The firm has a larger market share than our competitors ($0.87$)
+                                                               \end{itemize} \\  \bottomrule%
+
+\end{tabular}
     \begin{tablenotes}

### 2020-02-25 figure/cortab.rnw
submitted dissertation

\singlespacing
\tiny
\setlength{\tabcolsep}{3pt}
<<corcalc, results="asis", echo=FALSE>>=

cormat <- mainf$cormat
rownames(cormat) <- c("1) $CA_1$",
                     "2) $CA_0$",
                     "3) $DC_0$",
                     "4) $CAP_1$",
                     "5) $CAP_0$",
                     "6) $COG_1$",
                     "7) $COG_0$",
                     "8) Size",
                     "9) ln(Assets)",
                     "11) Margin",
                     "12) Age")

names(cormat) <- c("Mean","SD",paste(seq(1:(length(cormat)-2)),sep=","))

print(xtable(cormat ,size="\\small",caption="Correlation matrix \\label{tab:cor}", align = c("l", rep("p{0.290in}",(dim(cormat)[2]))),table.placement="h", size = "\\small", tabular.environment="longtable"), size="scriptsize", label='tab:cor', caption.placement="top", floating=FALSE,latex.environments=NULL,sanitize.text.function=function(x){x})
@

### 2020-02-25 figure/itemtab.rnw
submitted dissertation

\scriptsize
\singlespacing
\setlist[itemize]{leftmargin=*}

\begin{tabular}{p{2cm} c p{9cm}}

\textbf{Construct}     & \textbf{Rho}               & \textbf{Items}\\ \toprule%
  \textbf{Dynamic} \\ \textbf{Capabilities} &\textbf{$\Sexpr{dgr["DC"]}$} &\vspace{-5mm} 
                                                             \begin{itemize} 
                                                               \setlength\itemsep{-0.2em} 
                                                             \item Management and employees of the firm are strongly encouraged to front new visions, objectives and ideas ($\Sexpr{l[["ldcm"]][1]}$)
                                                             \item We systematically identify which resources we can utilize (economic, competencies, political and organizational ($\Sexpr{l[["ldcm"]][2]}$)
                                                             \item We systematically search for new business concepts through observing what happens in our environment ($\Sexpr{l[["ldcm"]][3]}$)
                                                             \item Systematic transfer of resources for development of new business areas is common in our firm ($\Sexpr{l[["ldcm"]][4]}$)
                                                             \item We have developed routines that enable us to recombine existing resources in novel ways ($\Sexpr{l[["ldcm"]][5]}$)
                                                             \item The firm is continously searching for partners to develop our resource base (economic, competencies, political, organizational) ($\Sexpr{l[["ldcm"]][6]}$)
                                                             \item The firm employees is given space to utilize new opportunities without existing daily activities sufferingc ($\Sexpr{l[["ldcm"]][7]}$)
                                                             \end{itemize} \\ \midrule%
 \textbf{Operating}                                                                            \\ \textbf{Capabilities} & \textbf{$\Sexpr{dgr["R"]}$}} & \vspace{-5mm} 
                                                               \begin{itemize} \setlength\itemsep{-0.2em} 
                                                               \item The firm has better marketing competence than the competitors ($\Sexpr{l[["lcap"]][1]}$)
                                                               \item Compared to our competitors our firm is particularly skilled in customer service ($\Sexpr{l[["lcap"]][2]}$)
                                                               \itemCompared to our competitors our firm is particularly skilled in management and operations  ($\Sexpr{l[["lcap"]][3]}$)
                                                               \end{itemize} \\  \midrule%

   \textbf{Strategic} \\ \textbf{Cognition} & \textbf{$\Sexpr{dgr["M"]}$} & \vspace{-5mm} 
                                                               \begin{itemize} \setlength\itemsep{-0.2em} 
                                                               \item Compared to our competitiors our firm typically refrain from action until competitors move, and then answer ($\Sexpr{l[["lcog"]][1]}$)
                                                               \item Compared to our competitors we are often first movers in introducing new products, services, administrative routines, production methods etc ($\Sexpr{l[["lcog"]][2]}$)
                                                               \item We relate to our competitors by adopting a "go get them" attitude. We are gonna win this ($\Sexpr{l[["lcog"]][3]}$)
                                                               \end{itemize} \\  \midrule%

   \textbf{Competitive} \\ \textbf{Advantage} & \textbf{$\Sexpr{dgr["CA1"]}$} & \vspace{-5mm} 
                                                               \begin{itemize} \setlength\itemsep{-0.2em} 
                                                               \item The firm has better financial results than our competitors ($\Sexpr{l[["lca"]][1]}$)
                                                               \item The firm has a stronger revenue growth than our competitors ($\Sexpr{l[["lca"]][2]}$)
                                                               \item The firm has a larger market share than our competitors ($\Sexpr{l[["lca"]][3]}$)
                                                               \end{itemize} \\  \bottomrule%

\end{tabular}

### 2020-02-25 figure/medanalysisall.rnw
submitted dissertation

\usetikzlibrary{arrows.meta}
% \begin{minipage}{.48\textwidth}
\begin{tabular}{cc}
  % \subcaption{DIRECT model}

 %\end{minipage}
 %\begin{minipage}{.48\textwidth}
   % \subcaption{CAP model}
  \begin{tikzpicture}

    \tikzstyle{mynode}=[circle,draw,thin, draw=black, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{mynode2}=[circle,draw, ultra thin, draw=gray,text=gray, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{gof}=[draw, ultra thin, draw=none, minimum size=18mm,inner sep=0pt, align=center]

    \node[mynode] (m){$CAP_t$};
    \node[mynode,below left=of m,yshift=0.5cm,xshift=-0.5cm](a) {$DC_{t-1}$};
    \node[mynode,below right=of m,yshift=0.5cm,xshift=0.5cm](b) {$CA_{t}$};
    \node[mynode2,below of=m,yshift=-1.5cm](c) {$COG_{t}$};
    \node[gof,below of=c,yshift=-0cm](gof) {$R^2= \Sexpr{r[11,3]}$, $Q^2= \Sexpr{r[12,3]}$};

    \draw[-latex, line width=0.3mm] (a.east) -- node[text width=0.8cm,font=\scriptsize, align=center,
    fill=white] {$\Sexpr{r[1,3]}^{*}$} (b.west);

    \draw[-latex, line width=0.3mm] (a.north) -- node[text width=0.8cm,font=\footnotesize, align=center, fill=white] {$\Sexpr{r[7,3]}^{*}$} (m.west);
    \draw[ -latex, line width=0.3mm] (m.east) -- node[text
    width=0.8cm,font=\footnotesize,align=center, fill=white] {$\Sexpr{r[3,3]}^{*}$} (b.north);

    \draw[gray,-latex] (a.south) -- node[text width=1.3cm,font=\scriptsize, align=left, fill=none] {} (c.west);
    \draw[gray, -latex,line ] (c.east) -- node[text
    width=1.3cm,font=\scriptsize,align=right, fill=none] {} (b.south);

   \end{tikzpicture}
 %\end{minipage}
 %\begin{minipage}{.48\textwidth}
 %  \subcaption{COG model}
    &
  \begin{tikzpicture}

    \tikzstyle{mynode}=[circle,draw, thin, draw=black, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{mynode2}=[circle,draw, ultra thin, draw=gray,text=gray, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{gof}=[draw, ultra thin, draw=none, minimum size=18mm,inner sep=0pt, align=center]

    \node[mynode2] (m){$CAP_t$};
    \node[mynode,below left=of m,yshift=0.5cm,xshift=-0.5cm](a) {$DC_{t-1}$};
    \node[mynode,below right=of m,yshift=0.5cm,xshift=0.5cm](b) {$CA_{t}$};
    \node[mynode,below of=m,yshift=-1.5cm](c) {$COG_{t}$};
    \node[gof,below of=c,yshift=-0cm](gof) {$R^2= \Sexpr{r[11,4]}$, $Q^2= \Sexpr{r[12,4]}$};

    \draw[-latex, line width=0.3mm] (a.east) -- node[text width=0.8cm,font=\scriptsize, align=center,
    fill=white] {$\Sexpr{r[1,4]}^{*}$} (b.west);

    \draw[gray,-latex] (a.north) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=none] {} (m.west);
    \draw[gray, -latex,line ] (m.east) -- node[text
    width=0.8cm,font=\scriptsize,align=right, fill=none] {} (b.north);

    \draw[-latex, line width=0.3mm] (a.south) -- node[text width=0.8cm,font=\scriptsize, align=center, fill=white] {$\Sexpr{r[9,4]}^{*}$} (c.west);
    \draw[-latex, line width=0.3mm] (c.east) -- node[text
    width=0.8 cm,font=\scriptsize,align=center, fill=white] {$\Sexpr{r[5,4]}^{*}$} (b.south);

   \end{tikzpicture}
 %\end{minipage}
 %\begin{minipage}{.48\textwidth}
 %  \subcaption{FULL model}
  \\
  \begin{tikzpicture}

    \tikzstyle{mynode}=[circle,draw, thin, draw=black, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{mynode2}=[circle,draw, ultra thin, draw=gray,text=gray, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{gof}=[draw, ultra thin, draw=none, minimum size=18mm,inner sep=0pt, align=center]

    \node[mynode] (m){$CAP_t$};
    \node[mynode,below left=of m,yshift=0.5cm,xshift=-0.5cm](a) {$DC_{t-1}$};
    \node[mynode,below right=of m,yshift=0.5cm,xshift=0.5cm](b) {$CA_{t}$};
    \node[mynode,below of=m,yshift=-1.5cm](c) {$COG_{t}$};
    \node[gof,below of=c,yshift=-0cm](gof) {$R^2= \Sexpr{r[11,5]}$, $Q^2= \Sexpr{r[12,5]}$};

    \draw[-latex,line width=0.3mm] (a.east) -- node[text width=0.8cm,font=\scriptsize, align=center,
    fill=white] {$\Sexpr{r[1,5]}$} (b.west);

    \draw[-latex,line width=0.3mm] (a.north) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=white] {$\Sexpr{r[7,5]}^{*}$} (m.west);
    \draw[ -latex,line width=0.3mm ] (m.east) -- node[text
    width=0.8cm,font=\scriptsize,align=right, fill=white] {$\Sexpr{r[3,5]}^{*}$} (b.north);

    \draw[-latex,line width=0.3mm] (a.south) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=white] {$\Sexpr{r[9,5]}^{*}$} (c.west);
    \draw[-latex,line width=0.3mm ] (c.east) -- node[text
    width=0.8cm,font=\scriptsize,align=right, fill=white] {$\Sexpr{r[5,5]}^{*}$} (b.south);

   \end{tikzpicture}
    &
    \begin{tikzpicture}

    \tikzstyle{mynode}=[circle,draw, thin, draw=black, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{mynode2}=[circle,draw, ultra thin, draw=gray,text=gray, fill=white, minimum
    size=12mm,inner sep=0pt, align=center]

    \tikzstyle{gof}=[draw, ultra thin, draw=none, minimum size=18mm,inner sep=0pt, align=center]

    \node[mynode] (m){$CAP_t$};
    \node[mynode,below left=of m,yshift=0.5cm,xshift=-0.5cm](a) {$DC_{t-1}$};
    \node[mynode,below right=of m,yshift=0.5cm,xshift=0.5cm](b) {$CA_{t}$};
    \coordinate (CAf) at ([xshift=-1.25cm]b.west);
    \node[mynode,below of=m,yshift=-1.5cm](c) {$COG_{t}$};
    \node[gof,below of=c,yshift=-0cm](gof) {$R^2= 0.48$, $Q^2= 0.31$};

    \draw[-latex,line width=0.3mm] (a.south east) -- node[above,text width=0.8cm,font=\scriptsize, align=left,
    fill=white] {$\Sexpr{ic[6,1]}$} (b.south west);

    \draw[-latex,line width=0.3mm] (a.north) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=white] {$\Sexpr{ic[7,1]}^{*}$} (m.west);
    \draw[ -latex,line width=0.3mm ] (m.east) -- node[text
    width=0.8cm,font=\scriptsize,align=right, fill=white] {$\Sexpr{ic[2,1]}^{*}$} (b.north);

    \draw[-latex,line width=0.3mm] (a.south) -- node[text width=0.8cm,font=\scriptsize, align=left, fill=white] {$\Sexpr{ic[8,1]}^{*}$} (c.west);
    \draw[-latex,line width=0.3mm ] (c.east) -- node[text
    width=0.8cm,font=\scriptsize,align=right, fill=white] {$\Sexpr{ic[5,1]}^{*}$} (b.south);

     \draw[line width=0.3mm] (m.south east) to[bend left=20] node[text width=0.8cm,font=\scriptsize, align=center,
    fill=none] {} (c.north east);

    \draw[{Circle[black]}-latex,line width=0.3mm] (CAf.east) -- node[above, text width=0.2cm,font=\scriptsize, align=center,
    fill=white] {$\Sexpr{ic[9,1]}^{*}$} (b.west);

   \end{tikzpicture}
% \end{minipage}
\end{tabular}

### 2020-02-25 notes.tex
submitted dissertation

Extant literature on dynamic capabilities are increasingly focusing on how firm resources
are changed by dynamic capabilities as a response to changes in the environment
\citep{Schilke2018,Eriksson2014}, thus placing firm capabilities as a mediator between
dynamic capabilities and competetive advantage \citep{Helfat2007}. This notion of
'orchestration' of firm resources, assets and capabilities has indeed been emphasized in
the extant literature \citep{Sirmon2011,Helfat2015}.

The conventional mechanism explored in the extant literature is related to changes in the
firm`s resource base \citep{Eriksson2014,Schilke2018}. This mechanism is also included in
the dominating definition of dynamic capabilities found in \citep{Helfat2007}: 'A dynamic
capability is the capacity of an organization to purposefully create, extend or modify its
resource base' (p. 4). This definition opens up for a variety of components
included in the term 'resource base', a point we discuss later in this paper. We coin this
expression of dynamic capabilities as the {\bf conductor} envisioning a conductor
orchestrating firm capabilities.

This notion of a {\bf conductor} albeit very important to the development of dynamic
capabilities literature, seems to leave out a considerable part of a firm`s 'resource
base', namely those resources that are tied to how the employees of the firm sees their
mission, internalize information and effectuates change. These traits of the organization
is very much related to concepts of 'mindset' \citep{Dweck2016}, 'employee cognition'
\citep{Lakoff1987,Gavetti2012} 'organizational genes' \citep{Nelson1982} and
'sense-making' \citep{Weick1995} to name but a few. However, in relations with dynamic
capabilities, one promising avenue for exploring mechanisms, beyond the conventional ones
described above, makes a clear distinction between \emph{behavioral} and
\emph{non-behavioral} objects of change \citep{Verona2011}. These non-behavioral objects
of change contain psychological objects such as cognitive frames, motivation and identity
that are important for strategy formation and implementation \citep{Vince2011,Gavetti2012}
as they 'concerns how decisions or actions are shaped, subverted and transformed by
emotions, and (..) determine the "way we do things here"' \citep[p. 338]{Vince2011}. In
this respect they work as firm resources in generating outcomes such as performance and
competitive advantage. This notion is popularly perhaps expressed most clearly by Peter
Drucker`s famous quote about how 'culture eats strategy for lunch'. \footnote{The debate
  on whether Drucker actually uttered these words are still in the open, but it was
  attributed to him by Mark Fields in 2006} Moreover, these non-behavioral objects of
change are themselves far from static and are found to change over time as responses to
external change \citep{Zollo2016} thus making them a natural part of the mechanisms
underpinning how dynamic capabilities work \citep{Schilke2018,Verona2011}.  Still, far less
is know about the non-behavioral objects of change and how they work as a mechanism in the
dynamic capabilities theory.We coin {\bf coach} to capture the enabling role dynamic
capabilities plays through \emph{strategic cognition} as
juxtaposed to the more directional role played as {\bf conductor} of \emph{operational capabilities}.
